### 2016-08-12 paper/paper.tex
Empty paper

% vim: set spell spelllang=en tw=100 :

\documentclass[letterpaper]{article}
\usepackage[pass]{geometry}

\usepackage{ijcai16}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{tikz}

\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds}

\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}

\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
\newcommand{\citep}[1]{\cite{#1}}

% cref style
\crefname{figure}{Figure}{Figures}
\Crefname{figure}{Figure}{Figures}

% http://tex.stackexchange.com/questions/22100/the-bar-and-overline-commands
\newcommand{\shortoverline}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}

\title{Between Subgraph Isomorphism and Maximum Common Subgraph}

\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
    Research Council [grant number EP/K503058/1]} \\
University of Glasgow, Glasgow, Scotland \\
ruth.hoffmann@glasgow.ac.uk \and c.mccreesh.1@research.gla.ac.uk}

\pdfinfo{
    /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
    /Author (Ruth Hoffmann and Ciaran McCreesh)
}

\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}

\section*{Acknowledgements}

We're not going to thank anyone, no, no.

\bibliographystyle{named}
\bibliography{paper}

\end{document}

### 2016-08-12 paper/paper.tex
Write a few words

@@
 \usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{cleveref}
@@
 \newcommand{\citep}[1]{\cite{#1}}
+
+\theoremstyle{definition}
+\newtheorem{proposition}{Proposition}
 
@@
 \begin{abstract}
+    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
+    ``as much of the pattern as possible'' inside the target graph. In general, this is maximum
+    common subgraph problem, which is much more computationally challenging in practice than
+    subgraph isomorphism. We present and evaluate a new constraint-style algorithm which lies
+    between these two approaches, for cases when nearly all of the pattern is present.
 \end{abstract}
@@
 \section{Introduction}
+
+The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
+\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
+edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
+mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
+many vertices of the pattern into the target as possible. In the induced case, this is known as the
+maximum common induced subgraph problem (we discuss the non-induced case below). However, although
+recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
+vertices, the state of the art for the maximum common subgraph problem becomes computationally
+infeasible at only 35 vertices when working with unlabelled graphs \citep{CP2016MCSPaper}. This is
+largely because strong inference, based upon the degrees of vertices
+\citep{DBLP:journals/ai/Solnon10} and the distances between them
+\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
+but not maximum common subgraph, and so the state space in the former is much more restricted. In
+this work we discuss an intermediate problem, where we must map all but $k$ vertices of the pattern
+graph into the target. We then present and evaluate an algorithm which, when $k$ is small (say,
+between 1 and 3) is much more scaleable than general maximum common subgraph algorithms.
+
+\section{Some Maths}
+
+A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping from
+$\operatorname{V}(P)$ to $\operatorname{V}(T)$ which maps adjacent vertices to adjacent vertices. An
+induced subgraph isomorphism additionally maps non-adjacent vertices to non-adjacent vertices.
+
+A common induced subgraph of graphs $G$ and $H$ is a graph $P$, together with two induced subgraph
+isomorphisms to $G$ and $H$; a maximum common induced subgraph is a common induced subgraph with as
+many vertices as possible.
+
+A maximum common partial (i.e.\ non-induced) subgraph would allow us to select every vertex in the
+pattern, and none of the edges. The objective is therefore changed to maximise the number of edges,
+rather than vertices. However, this is not what we are looking for: usually maximum common subgraph
+problems are symmetric in their inputs, but we are allowing extra edges only in the target, not in
+the pattern.
+
+We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
+but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P[-k] \rightarrowtail
+T$ and $P[-k] \hookrightarrow T$ respectively.
+
+A non-induced subgraph-except-$k$ isomorphism from $P$ to $T$ is equivalent to a subgraph
+isomorphism between $P$ and $T$ with $k$ extra universally-adjacent vertices. (However, we can do a
+bit better algorithmically.) For induced subgraph-except-$k$ isomorphisms, such an approach cannot
+work.
+
+The following propositions hold for both non-induced and induced subgraph-except-$k$ isomorphisms.
+
+\begin{proposition}
+    If $p \mapsto t$ then $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
+\end{proposition}
+
+\section{An Algorithm}
+
+\section{Empirical Evaluation}
+
+\section{Conclusion}
 

### 2016-08-12 code/sequential.cc
Some code

@@ -1,0 +1,365 @@
+/* vim: set sw=4 sts=4 et foldmethod=syntax : */
+
+#include "sequential.hh"
+
+#include <algorithm>
+#include <functional>
+#include <list>
+#include <map>
+#include <tuple>
+#include <utility>
+#include <vector>
+
+#include <iostream>
+
+#include <boost/dynamic_bitset.hpp>
+
+using std::find_if;
+using std::get;
+using std::greater;
+using std::list;
+using std::make_pair;
+using std::map;
+using std::pair;
+using std::to_string;
+using std::tuple;
+using std::unique;
+using std::vector;
+
+using std::cerr;
+using std::endl;
+
+using bitset = boost::dynamic_bitset<>;
+
+namespace
+{
+    struct Domain
+    {
+        unsigned v;
+        bool fixed;
+        bitset values;
+    };
+
+    using Domains = vector<Domain>;
+
+    struct Assignments
+    {
+        vector<tuple<unsigned, unsigned, bool> > trail;
+
+        auto push_branch(unsigned a, unsigned b) -> void
+        {
+            trail.emplace_back(a, b, true);
+        }
+
+        auto push_implication(unsigned a, unsigned b) -> void
+        {
+            if (trail.end() == find_if(trail.begin(), trail.end(), [&] (const auto & x) {
+                        return get<0>(x) == a && get<1>(x) == b;
+                        }))
+                trail.emplace_back(a, b, false);
+        }
+
+        auto pop() -> void
+        {
+            while ((! trail.empty()) && (! get<2>(trail.back())))
+                trail.pop_back();
+
+            if (! trail.empty())
+                trail.pop_back();
+        }
+
+        auto store_to(map<int, int> & m) -> void
+        {
+            for (auto & t : trail) {
+                m.emplace(get<0>(t), get<1>(t));
+            }
+        }
+    };
+
+    struct SIP
+    {
+        const Params & params;
+
+        Result result;
+
+        list<pair<vector<bitset>, vector<bitset> > > adjacency_constraints;
+        vector<unsigned> pattern_degrees, target_degrees;
+
+        Domains initial_domains;
+
+        SIP(const Params & k, const Graph & pattern, const Graph & target) :
+            params(k),
+            pattern_degrees(pattern.size()),
+            target_degrees(target.size()),
+            initial_domains(pattern.size())
+        {
+            // build up distance 1 adjacency bitsets
[…]

### 2016-08-12 code/solve_subgraph_isomorphism.cc

@@ -1,0 +1,235 @@
+/* vim: set sw=4 sts=4 et foldmethod=syntax : */
+
+#include "lad.hh"
+#include "dimacs.hh"
+#include "sequential.hh"
+
+#include <boost/program_options.hpp>
+
+#include <iostream>
+#include <exception>
+#include <cstdlib>
+#include <chrono>
+#include <thread>
+#include <mutex>
+#include <condition_variable>
+
+namespace po = boost::program_options;
+
+using std::chrono::steady_clock;
+using std::chrono::duration_cast;
+using std::chrono::milliseconds;
+
+/* Helper: return a function that runs the specified algorithm, dealing
+ * with timing information and timeouts. */
+template <typename Result_, typename Params_, typename Data_>
+auto run_this_wrapped(const std::function<Result_ (const Data_ &, const Params_ &)> & func)
+    -> std::function<Result_ (const Data_ &, Params_ &, bool &, int)>
+{
+    return [func] (const Data_ & data, Params_ & params, bool & aborted, int timeout) -> Result_ {
+        /* For a timeout, we use a thread and a timed CV. We also wake the
+         * CV up if we're done, so the timeout thread can terminate. */
+        std::thread timeout_thread;
+        std::mutex timeout_mutex;
+        std::condition_variable timeout_cv;
+        std::atomic<bool> abort;
+        abort.store(false);
+        params.abort = &abort;
+        if (0 != timeout) {
+            timeout_thread = std::thread([&] {
+                    auto abort_time = std::chrono::steady_clock::now() + std::chrono::seconds(timeout);
+                    {
+                        /* Sleep until either we've reached the time limit,
+                         * or we've finished all the work. */
+                        std::unique_lock<std::mutex> guard(timeout_mutex);
+                        while (! abort.load()) {
+                            if (std::cv_status::timeout == timeout_cv.wait_until(guard, abort_time)) {
+                                /* We've woken up, and it's due to a timeout. */
+                                aborted = true;
+                                break;
+                            }
+                        }
+                    }
+                    abort.store(true);
+                    });
+        }
+
+        /* Start the clock */
+        params.start_time = std::chrono::steady_clock::now();
+        auto result = func(data, params);
+
+        /* Clean up the timeout thread */
+        if (timeout_thread.joinable()) {
+            {
+                std::unique_lock<std::mutex> guard(timeout_mutex);
+                abort.store(true);
+                timeout_cv.notify_all();
+            }
[…]

### 2016-08-12 code/sequential.cc
Add --except, which only works for 1, and not with d2graphs

@@ -45,6 +45,7 @@ namespace
     struct Assignments
     {
         vector<tuple<unsigned, unsigned, bool> > trail;
+        unsigned wildcard;
 
         auto push_branch(unsigned a, unsigned b) -> void
         {
@@ -71,7 +72,10 @@ namespace
         auto store_to(map<int, int> & m) -> void
         {
             for (auto & t : trail) {
-                m.emplace(get<0>(t), get<1>(t));
+                if (get<1>(t) == wildcard)
+                    m.emplace(get<0>(t), -1);
+                else
+                    m.emplace(get<0>(t), get<1>(t));
             }
         }
     };
@@ -79,6 +83,7 @@ namespace
     struct SIP
     {
         const Params & params;
+        unsigned domain_size;
 
         Result result;
 
@@ -87,11 +92,15 @@ namespace
 
         Domains initial_domains;
 
+        unsigned wildcard;
+
         SIP(const Params & k, const Graph & pattern, const Graph & target) :
             params(k),
+            domain_size(params.except >= 1 ? target.size() + 1 : target.size()),
             pattern_degrees(pattern.size()),
-            target_degrees(target.size()),
-            initial_domains(pattern.size())
+            target_degrees(domain_size),
+            initial_domains(pattern.size()),
+            wildcard(target.size())
         {
             // build up distance 1 adjacency bitsets
             add_adjacency_constraints(pattern, target);
@@ -101,6 +110,9 @@ namespace
 
             for (unsigned t = 0 ; t < target.size() ; ++t)
                 target_degrees[t] = target.degree(t);
+
+            if (params.except >= 1)
+                target_degrees.at(target.size()) = 0;
 
             vector<vector<vector<unsigned> > > p_nds(adjacency_constraints.size());
             vector<vector<vector<unsigned> > > t_nds(adjacency_constraints.size());
@@ -132,21 +144,33 @@ namespace
             // build up initial domains
             for (unsigned p = 0 ; p < pattern.size() ; ++p) {
                 initial_domains[p].v = p;
-                initial_domains[p].values = bitset(target.size());
+                initial_domains[p].values = bitset(domain_size);
                 initial_domains[p].fixed = false;
 
+                // decide initial domain values
                 for (unsigned t = 0 ; t < target.size() ; ++t) {
                     bool ok = true;
                     for (auto & c : adjacency_constraints) {
-                        if (! (c.first[p][p] == c.second[t][t] && c.first[p].count() <= c.second[t].count())) {
+                        // check loops
[…]

### 2016-08-12 code/solve_subgraph_isomorphism.cc

@@ -93,6 +93,7 @@ auto main(int argc, char * argv[]) -> int
             ("timeout",            po::value<int>(),  "Abort after this many seconds")
             ("format",             po::value<std::string>(), "Specify graph file format (lad or dimacs)")
             ("d2graphs",                              "Use d2 graphs")
+            ("except",             po::value<int>(),  "Allow this many pattern vertices to be excluded")
             ;
 
         po::options_description all_options{ "All options" };
@@ -151,6 +152,8 @@ auto main(int argc, char * argv[]) -> int
         Params params;
 
         params.d2graphs = options_vars.count("d2graphs");
+        if (options_vars.count("except"))
+            params.except = options_vars["except"].as<int>();
 
         auto read_function = read_lad;
 
@@ -210,10 +213,12 @@ auto main(int argc, char * argv[]) -> int
             for (unsigned i = 0 ; i < graphs.first.size() ; ++i) {
                 for (unsigned j = 0 ; j < graphs.first.size() ; ++j) {
                     if (graphs.first.adjacent(i, j)) {
-                        if (! graphs.second.adjacent(result.isomorphism.find(i)->second, result.isomorphism.find(j)->second)) {
-                            std::cerr << "Oops! not an isomorphism: " << i << " -- " << j << " but "
-                               << result.isomorphism.find(i)->second << " -/- " << result.isomorphism.find(j)->second << std::endl;
-                            return EXIT_FAILURE;
+                        if (result.isomorphism.find(i)->second != -1 && result.isomorphism.find(j)->second != -1) {
+                            if (! graphs.second.adjacent(result.isomorphism.find(i)->second, result.isomorphism.find(j)->second)) {
+                                std::cerr << "Oops! not an isomorphism: " << i << " -- " << j << " but "
+                                   << result.isomorphism.find(i)->second << " -/- " << result.isomorphism.find(j)->second << std::endl;
+                                return EXIT_FAILURE;
+                            }
                         }
                     }
                 }

### 2016-08-12 code/sequential.cc
Support --except >= 2, still no d2graphs

@@ -45,7 +45,6 @@ namespace
     struct Assignments
     {
         vector<tuple<unsigned, unsigned, bool> > trail;
-        unsigned wildcard;
 
         auto push_branch(unsigned a, unsigned b) -> void
         {
@@ -69,10 +68,10 @@ namespace
                 trail.pop_back();
         }
 
-        auto store_to(map<int, int> & m) -> void
+        auto store_to(map<int, int> & m, unsigned wildcard_start) -> void
         {
             for (auto & t : trail) {
-                if (get<1>(t) == wildcard)
+                if (get<1>(t) >= wildcard_start)
                     m.emplace(get<0>(t), -1);
                 else
                     m.emplace(get<0>(t), get<1>(t));
@@ -92,15 +91,15 @@ namespace
 
         Domains initial_domains;
 
-        unsigned wildcard;
+        unsigned wildcard_start;
 
         SIP(const Params & k, const Graph & pattern, const Graph & target) :
             params(k),
-            domain_size(params.except >= 1 ? target.size() + 1 : target.size()),
+            domain_size(target.size() + params.except),
             pattern_degrees(pattern.size()),
             target_degrees(domain_size),
             initial_domains(pattern.size()),
-            wildcard(target.size())
+            wildcard_start(target.size())
         {
             // build up distance 1 adjacency bitsets
             add_adjacency_constraints(pattern, target);
@@ -183,7 +182,8 @@ namespace
 
                 // wildcard in domain?
                 if (params.except >= 1)
-                    initial_domains[p].values.set(wildcard);
+                    for (unsigned v = wildcard_start ; v != domain_size ; ++v)
+                        initial_domains[p].values.set(v);
             }
         }
 
@@ -301,7 +301,7 @@ namespace
                     d.values.reset(unit_domain_value);
 
                     // adjacency
-                    if (unit_domain_value != wildcard)
+                    if (unit_domain_value < wildcard_start)
                         for (auto & c : adjacency_constraints)
                             if (c.first[unit_domain_v].test(d.v))
                                 d.values &= c.second[unit_domain_value];
@@ -329,7 +329,7 @@ namespace
             auto branch_domain = select_branch_domain(domains);
 
             if (domains.end() == branch_domain) {
-                assignments.store_to(result.isomorphism);
+                assignments.store_to(result.isomorphism, wildcard_start);
                 return true;
             }
 
@@ -343,7 +343,15 @@ namespace
[…]

### 2016-08-13 paper/paper.tex
Proposition some more

@@
 
-The following propositions hold for both non-induced and induced subgraph-except-$k$ isomorphisms.
+\begin{proposition}
+    For both non-induced and induced subgraph-except-$k$ isomorphisms, if $p \mapsto t$ then
+    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
+\end{proposition}
 
 \begin{proposition}
-    If $p \mapsto t$ then $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
+    More powerfully, if $p \mapsto t$ then $\operatorname{nds}(p)[k, k+1, \ldots] \preceq
+    \operatorname{nds}(t)$.
+\end{proposition}
+
+As well as reasoning about degrees, we can also reason about paths.
+
+\begin{proposition}
+    If $p \mapsto t$ and $q \mapsto u$ then $\operatorname{paths}(p, q, 2) \le
+    \operatorname{paths}(t, u, 2) + k$.
+\end{proposition}
+
+This leads to the following:
+
+\begin{proposition}
+    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$, and edges
+    between vertices $p$ and $q$ if there are at least $n$ simple paths of length exactly $\ell$
+    between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism $i : P[-k] \rightarrowtail
+    T$ induces a new subgraph-except-$k$ isomorphism $i^{n, 2} : P^{n, 2}[-k]
+    \rightarrowtail T^{n - k, 2}$.
 \end{proposition}

### 2016-08-13 paper/paper.tex
Fixing notation.

@@
 We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
-but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P[-k] \rightarrowtail
-T$ and $P[-k] \hookrightarrow T$ respectively.
+but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P[k] \rightarrowtail
+T$ and $P[k] \hookrightarrow T$ respectively.
 
@@
     between vertices $p$ and $q$ if there are at least $n$ simple paths of length exactly $\ell$
-    between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism $i : P[-k] \rightarrowtail
-    T$ induces a new subgraph-except-$k$ isomorphism $i^{n, 2} : P^{n, 2}[-k]
+    between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism $i : P[k] \rightarrowtail
+    T$ induces a new subgraph-except-$k$ isomorphism $i^{n, 2} : P^{n, 2}[k]
     \rightarrowtail T^{n - k, 2}$.

### 2016-08-13 code/sequential.cc
Wildcard has high degree

@@ -111,7 +111,7 @@ namespace
                 target_degrees[t] = target.degree(t);
 
             if (params.except >= 1)
-                target_degrees.at(target.size()) = 0;
+                target_degrees.at(target.size()) = target.size() + 1;
 
             vector<vector<vector<unsigned> > > p_nds(adjacency_constraints.size());
             vector<vector<vector<unsigned> > > t_nds(adjacency_constraints.size());

### 2016-08-13 code/sequential.cc
Don't make pattern bitsets larger

@@ -191,8 +191,8 @@ namespace
         {
             auto & d1 = *adjacency_constraints.insert(
                     adjacency_constraints.end(), make_pair(vector<bitset>(), vector<bitset>()));
-            build_d1_adjacency(pattern, d1.first);
-            build_d1_adjacency(target, d1.second);
+            build_d1_adjacency(pattern, false, d1.first);
+            build_d1_adjacency(target, true, d1.second);
 
             if (params.d2graphs) {
                 auto & d21 = *adjacency_constraints.insert(
@@ -202,16 +202,16 @@ namespace
                 auto & d23 = *adjacency_constraints.insert(
                         adjacency_constraints.end(), make_pair(vector<bitset>(), vector<bitset>()));
 
-                build_d2_adjacency(pattern, d21.first, d22.first, d23.first);
-                build_d2_adjacency(target, d21.second, d22.second, d23.second);
+                build_d2_adjacency(pattern, false, d21.first, d22.first, d23.first);
+                build_d2_adjacency(target, true, d21.second, d22.second, d23.second);
             }
         }
 
-        auto build_d1_adjacency(const Graph & graph, vector<bitset> & adj) const -> void
+        auto build_d1_adjacency(const Graph & graph, bool is_target, vector<bitset> & adj) const -> void
         {
             adj.resize(graph.size());
             for (unsigned t = 0 ; t < graph.size() ; ++t) {
-                adj[t] = bitset(domain_size, 0);
+                adj[t] = bitset(is_target ? domain_size : graph.size(), 0);
                 for (unsigned u = 0 ; u < graph.size() ; ++u)
                     if (t != u && graph.adjacent(t, u))
                         adj[t].set(u);
@@ -219,6 +219,7 @@ namespace
         }
 
         auto build_d2_adjacency(const Graph & graph,
+                bool is_target,
                 vector<bitset> & adj1,
                 vector<bitset> & adj2,
                 vector<bitset> & adj3) const -> void
@@ -227,9 +228,9 @@ namespace
             adj2.resize(graph.size());
             adj3.resize(graph.size());
             for (unsigned t = 0 ; t < graph.size() ; ++t) {
-                adj1[t] = bitset(domain_size, 0);
-                adj2[t] = bitset(domain_size, 0);
-                adj3[t] = bitset(domain_size, 0);
+                adj1[t] = bitset(is_target ? domain_size : graph.size(), 0);
[…]

### 2016-08-13 paper/paper.tex
More experimental notation.

--- 2016-08-12 paper/paper.tex
@@
 \newcommand{\shortoverline}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
+
+%to do comments
+\usepackage{color}
+\newcommand{\todo}[1]{{\color{red} {[}{#1}{]}}}
 
@@
 \section{Some Maths}
-
-A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping from
-$\operatorname{V}(P)$ to $\operatorname{V}(T)$ which maps adjacent vertices to adjacent vertices. An
-induced subgraph isomorphism additionally maps non-adjacent vertices to non-adjacent vertices.
+A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping
+$i: P \rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
+isomorphism $i: P \hookrightarrow T$, additionally maps non-adjacent vertices to non-adjacent
+ vertices.
 
@@
 We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
-but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P[-k] \rightarrowtail
-T$ and $P[-k] \hookrightarrow T$ respectively.
+but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written
+$i_{k}: P \rightarrowtail T$ and $i_{k}: P \hookrightarrow T$ respectively.
 
@@
 
-The following propositions hold for both non-induced and induced subgraph-except-$k$ isomorphisms.
+\todo{Define $\preceq$, deg, nds, paths}
 
 \begin{proposition}
-    If $p \mapsto t$ then $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
+    Let $p$ be a vertex of $P$ and $t$ a vertex in $T$. For both non-induced and induced
+    subgraph-except-$k$ isomorphisms, if $i_{k}(p) = t$ then
+    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
+\end{proposition}
+
+\begin{proposition}
+    More powerfully, if $i_{k}(p) = t$ then $\operatorname{nds}(p)[k, k+1, \ldots] \preceq
+    \operatorname{nds}(t)$.
+\end{proposition}
+
+As well as reasoning about degrees, we can also reason about paths.
+
+\begin{proposition}
+    If $i_{k}(p) = t$ and $i_{k}(q) = u$ then $\operatorname{paths}(p, q, 2) \le
+    \operatorname{paths}(t, u, 2) + k$.
+\end{proposition}
+
+This leads to the following:
+
+\begin{proposition}
+    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$, and
+    and $p,q\in\operatorname{V}(G)$, with $p$ and $q$ adjacent if there are at least $n$
+    simple paths of length exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$
+    isomorphism $i_{k}: P \rightarrowtail T$ induces a new subgraph-except-$k$ isomorphism
+    $i^{n, 2}_{k} : P^{n, 2}\rightarrowtail T^{n - k, 2}$.
 \end{proposition}

### 2016-08-13 paper/paper.tex
Notation and prop4 fixes.

@@
 \usepackage{tikz}
+\usepackage{mathtools}
 
@@
 A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping
-$i: P \rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
-isomorphism $i: P \hookrightarrow T$, additionally maps non-adjacent vertices to non-adjacent
+$P \rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
+isomorphism $P \hookrightarrow T$, additionally maps non-adjacent vertices to non-adjacent
  vertices.
@@
 but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written
-$i_{k}: P \rightarrowtail T$ and $i_{k}: P \hookrightarrow T$ respectively.
+$P \prescript{}{k}{\rightarrowtail} T$ and $P \prescript{}{k}{\hookrightarrow} T$ respectively.
 
@@
     Let $p$ be a vertex of $P$ and $t$ a vertex in $T$. For both non-induced and induced
-    subgraph-except-$k$ isomorphisms, if $i_{k}(p) = t$ then
+    subgraph-except-$k$ isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
     $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
@@
 \begin{proposition}
-    More powerfully, if $i_{k}(p) = t$ then $\operatorname{nds}(p)[k, k+1, \ldots] \preceq
-    \operatorname{nds}(t)$.
+    More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
+    $\operatorname{nds}(p)[k+1, k+2, \ldots] \preceq \operatorname{nds}(t)$.
 \end{proposition}
@@
 \begin{proposition}
-    If $i_{k}(p) = t$ and $i_{k}(q) = u$ then $\operatorname{paths}(p, q, 2) \le
-    \operatorname{paths}(t, u, 2) + k$.
+    If $p \prescript{}{k}{\mapsto} t$ and $q \prescript{}{k}{\mapsto} u$ then
+     $\operatorname{paths}(p, q, 2) \le \operatorname{paths}(t, u, 2) + k$.
 \end{proposition}
@@
 \begin{proposition}
-    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$, and
-    and $p,q\in\operatorname{V}(G)$, with $p$ and $q$ adjacent if there are at least $n$
-    simple paths of length exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$
-    isomorphism $i_{k}: P \rightarrowtail T$ induces a new subgraph-except-$k$ isomorphism
-    $i^{n, 2}_{k} : P^{n, 2}\rightarrowtail T^{n - k, 2}$.
+    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$. Let $p$ and $q$ be adjacent vertices of $G^{n, \ell}$, if there are at least $n$ simple paths of length
+    exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism
+    $P \prescript{}{k}{\rightarrowtail} T$ induces a new subgraph-except-$k$ isomorphism
+    $P{n, 2}\prescript{}{k}{\rightarrowtail} T^{n - k, 2}$.
 \end{proposition}

### 2016-08-13 paper/paper.tex
prop4 fixed.

@@
 \begin{proposition}
-    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$. Let $p$ and $q$ be adjacent vertices of $G^{n, \ell}$, if there are at least $n$ simple paths of length
-    exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism
+    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$. The
+    vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent, if there are at least $n$ simple paths of
+    length exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism
     $P \prescript{}{k}{\rightarrowtail} T$ induces a new subgraph-except-$k$ isomorphism
-    $P{n, 2}\prescript{}{k}{\rightarrowtail} T^{n - k, 2}$.
+    $P^{n, 2}\prescript{}{k}{\rightarrowtail} T^{n - k, 2}$.
 \end{proposition}

### 2016-08-13 paper/paper.tex
Start thinking about experiments
Remember to revert this commit later

@@
 \author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
-    Research Council [grant number EP/K503058/1]} \\
+Research Council [grant number EP/K503058/1]} \and Craig Reilly \\
 University of Glasgow, Glasgow, Scotland \\
-ruth.hoffmann@glasgow.ac.uk \and c.mccreesh.1@research.gla.ac.uk}
+ruth.hoffmann@glasgow.ac.uk \and \{c.mccreesh.1,c.reilly.2\}@research.gla.ac.uk}
 
@@
     /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
-    /Author (Ruth Hoffmann and Ciaran McCreesh)
+    /Author (Ruth Hoffmann and Ciaran McCreesh and Craig Reilly)
 }
@@
 
+\subsection{Induced}
+
+Comparison with the clique and CP models.
+
+\subsection{Non-Induced}
+
+Just results.
+
+\subsection{Parallel Search}
+
+\subsection{Filtering and Propagation}
+
+\subsubsection{Initial Domain Sizes}
+
+Remember loops can make this overly optimistic if we just take the products!
+
+\subsubsection{Is Path Filtering Useful?}
+
 \section{Conclusion}

### 2016-08-13 code/sequential.cc
Induced option

@@ -306,6 +306,8 @@ namespace
                         for (auto & c : adjacency_constraints)
                             if (c.first[unit_domain_v].test(d.v))
                                 d.values &= c.second[unit_domain_value];
+                            else if (params.induced)
+                                d.values &= ~c.second[unit_domain_value];
 
                     if (d.values.none())
                         return false;

### 2016-08-13 code/solve_subgraph_isomorphism.cc

@@ -94,6 +94,7 @@ auto main(int argc, char * argv[]) -> int
             ("format",             po::value<std::string>(), "Specify graph file format (lad or dimacs)")
             ("d2graphs",                              "Use d2 graphs")
             ("except",             po::value<int>(),  "Allow this many pattern vertices to be excluded")
+            ("induced",                               "Induced")
             ;
 
         po::options_description all_options{ "All options" };
@@ -152,6 +153,7 @@ auto main(int argc, char * argv[]) -> int
         Params params;
 
         params.d2graphs = options_vars.count("d2graphs");
+        params.induced = options_vars.count("induced");
         if (options_vars.count("except"))
             params.except = options_vars["except"].as<int>();
 

### 2016-08-13 paper/paper.tex
Proof of Prop1

@@
 \begin{proposition}
-    Let $p$ be a vertex of $P$ and $t$ a vertex in $T$. For both non-induced and induced
+    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
     subgraph-except-$k$ isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
@@
 \end{proposition}
+\begin{proof}
+Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$.
+Then by the definition of subgraph isomorphisms, $\operatorname{deg}(p) \le \operatorname{deg}(t)$.
+Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$.
+Then
+\[
+\operatorname{deg}_{P}(p)-k \le \operatorname{deg}_{P'}(p) \le \operatorname{deg}_{P}(p) \le \operatorname{deg}(t).
+\]
+\end{proof}
 

### 2016-08-13 code/solve_subgraph_isomorphism.cc
Induced verifier

@@ -223,6 +223,15 @@ auto main(int argc, char * argv[]) -> int
                             }
                         }
                     }
+                    else if (params.induced && ! graphs.first.adjacent(i, j)) {
+                        if (result.isomorphism.find(i)->second != -1 && result.isomorphism.find(j)->second != -1) {
+                            if (graphs.second.adjacent(result.isomorphism.find(i)->second, result.isomorphism.find(j)->second)) {
+                                std::cerr << "Oops! not an induced isomorphism: " << i << " -/- " << j << " but "
+                                   << result.isomorphism.find(i)->second << " -- " << result.isomorphism.find(j)->second << std::endl;
+                                return EXIT_FAILURE;
+                            }
+                        }
+                    }
                 }
             }
         }

### 2016-08-13 code/sequential.cc
Some of these things must not be like the others

@@ -312,6 +312,49 @@ namespace
                     if (d.values.none())
                         return false;
                 }
+
+                if (! cheap_all_different(domains))
+                    return false;
+            }
+
+            return true;
+        }
+
+        auto cheap_all_different(Domains & domains) -> bool
+        {
+            // pick domains smallest first, with tiebreaking
+            vector<int> domains_order;
+            domains_order.resize(domains.size());
+            iota(domains_order.begin(), domains_order.begin() + domains.size(), 0);
+
+            sort(domains_order.begin(), domains_order.begin() + domains.size(),
+                    [&] (int a, int b) {
+                        return (domains.at(a).values.count() < domains.at(b).values.count()) || (domains.at(a).values.count() == domains.at(b).values.count() && a < b);
+                        });
+
+            // counting all-different
+            bitset domains_so_far = bitset(domain_size, 0), hall = bitset(domain_size, 0);
+            unsigned neighbours_so_far = 0;
+
+            for (int i = 0, i_end = domains.size() ; i != i_end ; ++i) {
+                auto & d = domains.at(domains_order.at(i));
+
+                d.values &= ~hall;
+
+                if (d.values.none())
+                    return false;
+
+                domains_so_far |= d.values;
+                ++neighbours_so_far;
+
+                unsigned domains_so_far_popcount = domains_so_far.count();
+                if (domains_so_far_popcount < neighbours_so_far)
+                    return false;
+                else if (domains_so_far_popcount == neighbours_so_far) {
+                    neighbours_so_far = 0;
+                    hall |= domains_so_far;
+                    domains_so_far.reset();
+                }
             }
 
             return true;

### 2016-08-13 paper/paper.tex
Added preamble file, fixed naming.

@@
 \documentclass[letterpaper]{article}
-\usepackage[pass]{geometry}
 
-\usepackage{ijcai16}
-\usepackage{times}
-\usepackage{complexity}
-\usepackage{microtype}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{cleveref}
-\usepackage{tikz}
-\usepackage{mathtools}
-
-\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds}
-
-\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
-\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
-\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
-\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
-\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
-
-\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
-\newcommand{\citep}[1]{\cite{#1}}
-
-\theoremstyle{definition}
-\newtheorem{proposition}{Proposition}
-
-% cref style
-\crefname{figure}{Figure}{Figures}
-\Crefname{figure}{Figure}{Figures}
-
-% http://tex.stackexchange.com/questions/22100/the-bar-and-overline-commands
-\newcommand{\shortoverline}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
-
-%to do comments
-\usepackage{color}
-\newcommand{\todo}[1]{{\color{red} {[}{#1}{]}}}
+\include{preamble}
 
@@
 
-We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
+We define a $k$-less-subgraph isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
 but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written
-$P \prescript{}{k}{\rightarrowtail} T$ and $P \prescript{}{k}{\hookrightarrow} T$ respectively.
+$P \lessnonind{k} T$ and $P \lessind{k} T$ respectively.
 
-A non-induced subgraph-except-$k$ isomorphism from $P$ to $T$ is equivalent to a subgraph
+A non-induced $k$-less-subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph
 isomorphism between $P$ and $T$ with $k$ extra universally-adjacent vertices. (However, we can do a
-bit better algorithmically.) For induced subgraph-except-$k$ isomorphisms, such an approach cannot
+bit better algorithmically.) For induced $k$-less-subgraph isomorphisms, such an approach cannot
 work.
+
+Let $S$ and $T$ be two sequences. We define $S \preceq T$
 
@@
     Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
-    subgraph-except-$k$ isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
-    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
+    $k$-less-subgraph isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
+    $\deg(p) \le \deg(t) + k$.
 \end{proposition}
@@
 Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$.
-Then by the definition of subgraph isomorphisms, $\operatorname{deg}(p) \le \operatorname{deg}(t)$.
+Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$.
 Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$.
@@
 \[
-\operatorname{deg}_{P}(p)-k \le \operatorname{deg}_{P'}(p) \le \operatorname{deg}_{P}(p) \le \operatorname{deg}(t).
+\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t).
 \]
@@
     More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
-    $\operatorname{nds}(p)[k+1, k+2, \ldots] \preceq \operatorname{nds}(t)$.
+    $\nds(p)[k+1, k+2, \ldots] \preceq \nds(t)$.
 \end{proposition}
+
+\begin{proof}
+Let
+
+\end{proof}
 
@@
     vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent, if there are at least $n$ simple paths of
-    length exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism
-    $P \prescript{}{k}{\rightarrowtail} T$ induces a new subgraph-except-$k$ isomorphism
-    $P^{n, 2}\prescript{}{k}{\rightarrowtail} T^{n - k, 2}$.
+    length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less-subgraph isomorphism
+    $P \lessnonind{k} T$ induces a new $k$-less-subgraph isomorphism
+    $P^{n, 2}\lessnonind{k} T^{n - k, 2}$.
 \end{proposition}

### 2016-08-13 code/sequential.cc
Value ordering heuristic on all wildcard values

@@ -111,7 +111,8 @@ namespace
                 target_degrees[t] = target.degree(t);
 
             if (params.except >= 1)
-                target_degrees.at(target.size()) = target.size() + 1;
+                for (unsigned v = 0 ; v < params.except ; ++v)
+                    target_degrees.at(wildcard_start + v) = target.size() + 1;
 
             vector<vector<vector<unsigned> > > p_nds(adjacency_constraints.size());
             vector<vector<vector<unsigned> > > t_nds(adjacency_constraints.size());

### 2016-08-13 code/sequential.cc
Change the value ordering heuristic, because reasons

@@ -112,7 +112,7 @@ namespace
 
             if (params.except >= 1)
                 for (unsigned v = 0 ; v < params.except ; ++v)
-                    target_degrees.at(wildcard_start + v) = target.size() + 1;
+                    target_degrees.at(wildcard_start + v) = 0;
 
             vector<vector<vector<unsigned> > > p_nds(adjacency_constraints.size());
             vector<vector<vector<unsigned> > > t_nds(adjacency_constraints.size());

### 2016-08-14 code/sequential.cc
Stats on initial domain sizes

@@ -6,6 +6,7 @@
 #include <functional>
 #include <list>
 #include <map>
+#include <numeric>
 #include <tuple>
 #include <utility>
 #include <vector>
@@ -142,18 +143,24 @@ namespace
             }
 
             // build up initial domains
+            vector<pair<unsigned, unsigned> > initial_domain_sizes;
             for (unsigned p = 0 ; p < pattern.size() ; ++p) {
                 initial_domains[p].v = p;
                 initial_domains[p].values = bitset(domain_size);
                 initial_domains[p].fixed = false;
 
+                initial_domain_sizes.emplace_back(0, 0);
+
                 // decide initial domain values
                 for (unsigned t = 0 ; t < target.size() ; ++t) {
-                    bool ok = true;
+                    bool ok = true, count_towards_domain_stats = true;
+
                     for (auto & c : adjacency_constraints) {
                         // check loops
-                        if (c.first[p][p] != c.second[t][t])
+                        if (c.first[p][p] != c.second[t][t]) {
                             ok = false;
+                            count_towards_domain_stats = false;
+                        }
 
                         // check degree
                         if (ok && 0 == params.except && ! (c.first[p].count() <= c.second[t].count()))
@@ -177,14 +184,23 @@ namespace
                         }
                     }
 
-                    if (ok)
+                    if (ok) {
+                        ++initial_domain_sizes.back().first;
                         initial_domains[p].values.set(t);
+                    }
+
+                    if (count_towards_domain_stats)
+                        ++initial_domain_sizes.back().second;
                 }
 
                 // wildcard in domain?
                 if (params.except >= 1)
                     for (unsigned v = wildcard_start ; v != domain_size ; ++v)
                         initial_domains[p].values.set(v);
+
+                // record stats
+                for (auto & d : initial_domain_sizes)
+                    result.stats.emplace("d" + to_string(p), to_string(d.first) + "/" + to_string(d.second));
             }
         }
 

### 2016-08-14 code/sequential.cc
Get loops right

@@ -157,7 +157,11 @@ namespace
 
                     for (auto & c : adjacency_constraints) {
                         // check loops
-                        if (c.first[p][p] != c.second[t][t]) {
+                        if (c.first[p][p] && ! c.second[t][t]) {
+                            ok = false;
+                            count_towards_domain_stats = false;
+                        }
+                        else if (params.induced && ! c.first[p][p] && c.second[t][t]) {
                             ok = false;
                             count_towards_domain_stats = false;
                         }
@@ -230,7 +234,7 @@ namespace
             for (unsigned t = 0 ; t < graph.size() ; ++t) {
                 adj[t] = bitset(is_target ? domain_size : graph.size(), 0);
                 for (unsigned u = 0 ; u < graph.size() ; ++u)
-                    if (t != u && graph.adjacent(t, u))
+                    if (graph.adjacent(t, u))
                         adj[t].set(u);
             }
         }

### 2016-08-14 code/sequential.cc
Do early unit propagation, record domain sizes

@@ -143,13 +143,10 @@ namespace
             }
 
             // build up initial domains
-            vector<pair<unsigned, unsigned> > initial_domain_sizes;
             for (unsigned p = 0 ; p < pattern.size() ; ++p) {
                 initial_domains[p].v = p;
                 initial_domains[p].values = bitset(domain_size);
                 initial_domains[p].fixed = false;
-
-                initial_domain_sizes.emplace_back(0, 0);
 
                 // decide initial domain values
                 for (unsigned t = 0 ; t < target.size() ; ++t) {
@@ -188,23 +185,14 @@ namespace
                         }
                     }
 
-                    if (ok) {
-                        ++initial_domain_sizes.back().first;
+                    if (ok)
                         initial_domains[p].values.set(t);
-                    }
-
-                    if (count_towards_domain_stats)
-                        ++initial_domain_sizes.back().second;
                 }
 
                 // wildcard in domain?
                 if (params.except >= 1)
                     for (unsigned v = wildcard_start ; v != domain_size ; ++v)
                         initial_domains[p].values.set(v);
-
-                // record stats
-                for (auto & d : initial_domain_sizes)
-                    result.stats.emplace("d" + to_string(p), to_string(d.first) + "/" + to_string(d.second));
             }
         }
 
@@ -306,8 +294,13 @@ namespace
             while (! domains.empty()) {
                 auto unit_domain_iter = select_unit_domain(domains);
 
-                if (unit_domain_iter == domains.end())
-                    break;
+                if (unit_domain_iter == domains.end()) {
+                    if (! cheap_all_different(domains))
+                        return false;
+                    unit_domain_iter = select_unit_domain(domains);
+                    if (unit_domain_iter == domains.end())
+                        break;
+                }
 
                 auto unit_domain_v = unit_domain_iter->v;
                 auto unit_domain_value = unit_domain_iter->values.find_first();
@@ -333,9 +326,6 @@ namespace
                     if (d.values.none())
                         return false;
                 }
-
-                if (! cheap_all_different(domains))
-                    return false;
             }
 
             return true;
@@ -390,9 +380,6 @@ namespace
 
             ++result.nodes;
 
-            if (! unit_propagate(domains, assignments))
-                return false;
-
             auto branch_domain = select_branch_domain(domains);
 
             if (domains.end() == branch_domain) {
@@ -437,8 +424,9 @@ namespace
                         new_domains.emplace_back(Domain{ unsigned(d.v), false, d.values });
                 }
 
[…]

### 2016-08-14 code/sequential.cc
Degree and NDS filtering optional

@@ -118,27 +118,29 @@ namespace
             vector<vector<vector<unsigned> > > p_nds(adjacency_constraints.size());
             vector<vector<vector<unsigned> > > t_nds(adjacency_constraints.size());
 
-            for (unsigned p = 0 ; p < pattern.size() ; ++p) {
-                unsigned cn = 0;
-                for (auto & c : adjacency_constraints) {
-                    p_nds[cn].resize(pattern.size());
-                    for (unsigned q = 0 ; q < pattern.size() ; ++q)
-                        if (c.first[p][q])
-                            p_nds[cn][p].push_back(c.first[q].count());
-                    sort(p_nds[cn][p].begin(), p_nds[cn][p].end(), greater<unsigned>());
-                    ++cn;
+            if (params.nds) {
+                for (unsigned p = 0 ; p < pattern.size() ; ++p) {
+                    unsigned cn = 0;
+                    for (auto & c : adjacency_constraints) {
+                        p_nds[cn].resize(pattern.size());
+                        for (unsigned q = 0 ; q < pattern.size() ; ++q)
+                            if (c.first[p][q])
+                                p_nds[cn][p].push_back(c.first[q].count());
+                        sort(p_nds[cn][p].begin(), p_nds[cn][p].end(), greater<unsigned>());
+                        ++cn;
+                    }
                 }
-            }
 
-            for (unsigned t = 0 ; t < target.size() ; ++t) {
-                unsigned cn = 0;
-                for (auto & c : adjacency_constraints) {
-                    t_nds[cn].resize(target.size());
-                    for (unsigned q = 0 ; q < target.size() ; ++q)
-                        if (c.second[t][q])
-                            t_nds[cn][t].push_back(c.second[q].count());
-                    sort(t_nds[cn][t].begin(), t_nds[cn][t].end(), greater<unsigned>());
-                    ++cn;
+                for (unsigned t = 0 ; t < target.size() ; ++t) {
+                    unsigned cn = 0;
+                    for (auto & c : adjacency_constraints) {
+                        t_nds[cn].resize(target.size());
+                        for (unsigned q = 0 ; q < target.size() ; ++q)
+                            if (c.second[t][q])
+                                t_nds[cn][t].push_back(c.second[q].count());
+                        sort(t_nds[cn][t].begin(), t_nds[cn][t].end(), greater<unsigned>());
+                        ++cn;
+                    }
                 }
             }
 
@@ -164,11 +166,11 @@ namespace
                         }
 
                         // check degree
[…]

### 2016-08-14 code/solve_subgraph_isomorphism.cc

@@ -109,6 +109,8 @@ auto main(int argc, char * argv[]) -> int
             ("timeout",            po::value<int>(),  "Abort after this many seconds")
             ("format",             po::value<std::string>(), "Specify graph file format (lad or dimacs)")
             ("d2graphs",                              "Use d2 graphs")
+            ("degree",                                "Use degree filtering")
+            ("nds",                                   "Use NDS filtering")
             ("except",             po::value<int>(),  "Allow this many pattern vertices to be excluded")
             ("induced",                               "Induced")
             ;
@@ -170,6 +172,8 @@ auto main(int argc, char * argv[]) -> int
 
         params.d2graphs = options_vars.count("d2graphs");
         params.induced = options_vars.count("induced");
+        params.degree = options_vars.count("degree");
+        params.nds = options_vars.count("nds");
         if (options_vars.count("except"))
             params.except = options_vars["except"].as<int>();
 

### 2016-08-14 code/sequential.cc
Unused

@@ -152,18 +152,14 @@ namespace
 
                 // decide initial domain values
                 for (unsigned t = 0 ; t < target.size() ; ++t) {
-                    bool ok = true, count_towards_domain_stats = true;
+                    bool ok = true;
 
                     for (auto & c : adjacency_constraints) {
                         // check loops
-                        if (c.first[p][p] && ! c.second[t][t]) {
+                        if (c.first[p][p] && ! c.second[t][t])
                             ok = false;
-                            count_towards_domain_stats = false;
-                        }
-                        else if (params.induced && ! c.first[p][p] && c.second[t][t]) {
+                        else if (params.induced && ! c.first[p][p] && c.second[t][t])
                             ok = false;
-                            count_towards_domain_stats = false;
-                        }
 
                         // check degree
                         if (ok && params.degree && 0 == params.except && ! (c.first[p].count() <= c.second[t].count()))

### 2016-08-14 code/sequential.cc
Unit propagate on modified domains

@@ -424,7 +424,7 @@ namespace
                         new_domains.emplace_back(Domain{ unsigned(d.v), false, d.values });
                 }
 
-                if (unit_propagate(domains, assignments))
+                if (unit_propagate(new_domains, assignments))
                     if (solve(new_domains, assignments))
                         return true;
 

### 2016-08-15 code/sequential.cc
Exclude wildcards from domain stat counts

@@ -437,8 +437,12 @@ namespace
 
         auto record_domain_sizes_in_stats(const Domains & domains)
         {
+            auto wildcards = bitset(domain_size);
+            for (unsigned v = wildcard_start ; v != domain_size ; ++v)
+                wildcards.set(v);
+
             for (auto & d : domains)
-                result.stats.emplace("IDS" + to_string(d.v), to_string(d.values.count()));
+                result.stats.emplace("IDS" + to_string(d.v), to_string((d.values & ~wildcards).count()));
         }
 
         auto run()

### 2016-08-15 code/sequential.cc
Early abortions

@@ -400,6 +400,9 @@ namespace
             bool already_did_a_wildcard = false;
 
             for (auto & branch_value : branch_values) {
+                if (*params.abort)
+                    return false;
+
                 if (already_did_a_wildcard && branch_value >= wildcard_start)
                     continue;
 

### 2016-08-15 paper/paper.tex
Another experiment we need
Move things around

@@
 
-\section{Some Maths}
+\subsection{Definitions and Notations}
+
 A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping
@@
 
+\subsection{Models and Algorithms}
+
+\section{Domain Filtering}
+
 A non-induced $k$-less-subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph
@@
 
-\todo{Define $\preceq$, deg, nds, paths}
+\todo{Define $\preceq$, deg, nds}
 
@@
 
+\section{Filtering During Search}
+
 As well as reasoning about degrees, we can also reason about paths.
+
+\todo{Define paths}
 
@@
 
-\section{An Algorithm}
+\section{A New Algorithm}
 
@@
 
-Comparison with the clique and CP models.
+Comparison with the clique and CP models, as well as ``drop k vertices and try each in turn''.
 
@@
 
-Just results.
+Just results and ``drop k vertices and try each in turn''.
 
 \subsection{Parallel Search}
-
-\subsection{Filtering and Propagation}
-
-\subsubsection{Initial Domain Sizes}
-
-Remember loops can make this overly optimistic if we just take the products!
-
-\subsubsection{Is Path Filtering Useful?}
 

### 2016-08-15 paper/paper.tex
Maybe fix propositions
Experimental setup
Reword intro a bit

@@
 largely because strong inference, based upon the degrees of vertices
-\citep{DBLP:journals/ai/Solnon10} and the distances between them
+\citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
 \citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
@@
 this work we discuss an intermediate problem, where we must map all but $k$ vertices of the pattern
-graph into the target. We then present and evaluate an algorithm which, when $k$ is small (say,
-between 1 and 3) is much more scaleable than general maximum common subgraph algorithms.
+graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then weakened
+forms of degree and path based filterings are still effective in pruning the search space and
+providing additional constraints respectively. We then show that combining these techniques does
+lead to a practical algorithm which can scale to work with the families of graphs commonly used to
+benchmark subgraph isomorphism algorithms.
 
@@
 
+\subsection{Experimental Setup}
+
 \section{Domain Filtering}
@@
     $k$-less-subgraph isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
-    $\deg(p) \le \deg(t) + k$.
+    $\deg(p) - k \le \deg(t)$.
 \end{proposition}
@@
     More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
-    $\nds(p)[k+1, k+2, \ldots] \preceq \nds(t)$.
+    $(\nds(p)[k+1] - k, \nds(p)[k+2] - k, \ldots) \preceq \nds(t)$.
 \end{proposition}

### 2016-08-15 code/sequential.cc
Induced via complement graph

@@ -105,6 +105,9 @@ namespace
             // build up distance 1 adjacency bitsets
             add_adjacency_constraints(pattern, target);
 
+            if (params.induced)
+                add_complement_constraints(pattern, target);
+
             for (unsigned p = 0 ; p < pattern.size() ; ++p)
                 pattern_degrees[p] = pattern.degree(p);
 
@@ -158,8 +161,6 @@ namespace
                         // check loops
                         if (c.first[p][p] && ! c.second[t][t])
                             ok = false;
-                        else if (params.induced && ! c.first[p][p] && c.second[t][t])
-                            ok = false;
 
                         // check degree
                         if (ok && params.degree && 0 == params.except && ! (c.first[p].count() <= c.second[t].count()))
@@ -200,8 +201,8 @@ namespace
         {
             auto & d1 = *adjacency_constraints.insert(
                     adjacency_constraints.end(), make_pair(vector<bitset>(), vector<bitset>()));
-            build_d1_adjacency(pattern, false, d1.first);
-            build_d1_adjacency(target, true, d1.second);
+            build_d1_adjacency(pattern, false, d1.first, false);
+            build_d1_adjacency(target, true, d1.second, false);
 
             if (params.d2graphs) {
                 auto & d21 = *adjacency_constraints.insert(
@@ -216,13 +217,21 @@ namespace
             }
         }
 
-        auto build_d1_adjacency(const Graph & graph, bool is_target, vector<bitset> & adj) const -> void
+        auto add_complement_constraints(const Graph & pattern, const Graph & target) -> void
+        {
+            auto & d1 = *adjacency_constraints.insert(
+                    adjacency_constraints.end(), make_pair(vector<bitset>(), vector<bitset>()));
+            build_d1_adjacency(pattern, false, d1.first, true);
+            build_d1_adjacency(target, true, d1.second, true);
+        }
+
+        auto build_d1_adjacency(const Graph & graph, bool is_target, vector<bitset> & adj, bool complement) const -> void
         {
             adj.resize(graph.size());
             for (unsigned t = 0 ; t < graph.size() ; ++t) {
                 adj[t] = bitset(is_target ? domain_size : graph.size(), 0);
                 for (unsigned u = 0 ; u < graph.size() ; ++u)
-                    if (graph.adjacent(t, u))
+                    if (graph.adjacent(t, u) != complement)
                         adj[t].set(u);
             }
         }
@@ -320,8 +329,6 @@ namespace
                         for (auto & c : adjacency_constraints)
[…]

### 2016-08-15 paper/paper.tex
A pretty graph
More experiments to do

@@
 
-\include{preamble}
+\usepackage[pass]{geometry}
+
+\usepackage{ijcai16}
+\usepackage{times}
+\usepackage{complexity}
+\usepackage{microtype}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{cleveref}
+\usepackage{tikz}
+\usepackage{mathtools}
+\usepackage{graphicx}
+
+\usepackage{showframe}
+
+\makeatletter\@ifpackageloaded{showframe}{
+    % show lines down the middle columns too
+    % http://tex.stackexchange.com/questions/16199/test-if-a-package-or-package-option-is-loaded
+\newlength\Fcolumnseprule\setlength\Fcolumnseprule{0.4pt}\def\@outputdblcol{%
+  \if@firstcolumn\global \@firstcolumnfalse \global \setbox\@leftcolumn \box\@outputbox
+  \else
+    \global \@firstcolumntrue
+    \setbox\@outputbox \vbox{\hb@xt@\textwidth{\hb@xt@\columnwidth{\box\@leftcolumn \hss}%
+    \vrule \@width\Fcolumnseprule\hfil{\normalcolor\vrule \@width\columnseprule}
+    \hfil\vrule \@width\Fcolumnseprule\hb@xt@\columnwidth {\box\@outputbox \hss}}}\@combinedblfloats\@outputpage
+    \begingroup\@dblfloatplacement\@startdblcolumn\@whilesw\if@fcolmade \fi{\@outputpage\@startdblcolumn}\endgroup
+  \fi
+}}{}
+\makeatother
+
+\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds}
+
+\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
+\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
+\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
+\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
+\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
+
+\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
+\newcommand{\citep}[1]{\cite{#1}}
+
+\theoremstyle{definition}
+\newtheorem{proposition}{Proposition}
+
+% cref style
+\crefname{figure}{Figure}{Figures}
+\Crefname{figure}{Figure}{Figures}
+
+% http://tex.stackexchange.com/questions/22100/the-bar-and-overline-commands
+\newcommand{\shortoverline}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
+
+% Maths operators
+\newcommand{\nds}{\operatorname{nds}}
+\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
+\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
+
+% to do comments
+\usepackage{color}
+\newcommand{\todo}[1]{{\color{red} {[}{#1}{]}}}
 
@@
 
-\section{Domain Filtering}
+\section{Domain Filtering using Degrees}
 
@@
 
-\section{Filtering During Search}
+In \cref{figure:ids} we show that this is useful in practice.
+
+\begin{figure}
+    \includegraphics*{gen-graph-ids.pdf}
+    \caption{We get domain filtering. Woohoo.}\label{figure:ids}
+\end{figure}
+
+\section{Filtering During Search Using Paths}
 
@@
 
+To allow for fast propagation, we create supplemental graphs for paths of length 2, looking at
+counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).
+We then investigate whether this leads to new constraints being generated. By an assignment, we mean
+considering mapping a pattern vertex $p$ to a target vertex $t$ (and not $\bot$) which does not
+violate any loop constraints. An assignment pair is two assignments with distinct $p$ and distinct
+$t$, which we say is permitted if it does not violate any adjacency constraint. We define the
+permitted assignment pair ratio to be the proportion of assignment pairs which are permitted.
+Finally, we scatter plot the permitted assignment pair ratio with and without supplemental
+graphs\footnote{Because of the large sizes of the domains, we randomly sample one million pairs
+rather than considering every pair. In some cases, we have nearly a thousand domains, each with nearly
+ten thousand values---a complete quadratic calculation involving even a trivial arithmetic operation
+on this would take many hours.}. For $k = 0$, we see many points above the $x-y$ diagonal, which
+shows that for many instances, we are able to create a substantial number of new constraints at the
+top of search; on the other hand, there are also points on the diagonal, which shows that sometimes
+this technique provides no benefit. (Occasionally, points fall below the $x-y$ diagonal. This is
+because the use of neighbourhood degree sequence reasoning on supplemental graphs can also lead to
+increased domain filtering, which could in turn eliminate a higher proportion of forbidden than
+permitted assignment pairs.) For $k = 1$ and $k = 2$, the proportion of points above the diagonal
+diminishes, but we are still able to create new constraints for many instances. By the time $k = 3$,
+most of the benefit is disappearing---although sometimes we are still able to make a difference, and
+bear in mind that sometimes adding just one new constrained pair can vastly reduce the search space.
+
+A closer inspection of the raw data shows that for $k = 3$, nearly all of the instances showing a
+strong improvement are from the ``LV'' family of graphs.
+
+\begin{figure*}
+    \includegraphics*{gen-graph-constraints.pdf}\\[0.1cm]
+    \includegraphics*{gen-graph-constraints-induced.pdf}
+    \caption{We get new constraints. More woohoo.}\label{figure:constraints}
+\end{figure*}
+
 \section{A New Algorithm}
@@
 \section{Empirical Evaluation}
+
+\begin{figure}
+    \includegraphics*{gen-graph-runtimes.pdf}
+    \caption{Look how amazing our stuff is.}\label{figure:runtimes}
+\end{figure}
 
@@
 
+What proportion of instances are actually satisfiable as $k$ increases?
+
 \subsection{Non-Induced}
@@
 Just results and ``drop k vertices and try each in turn''.
+
+What proportion of instances are actually satisfiable as $k$ increases?
 

### 2016-08-18 code/sequential.cc
Make building d2 stuff a bit faster

@@ -212,8 +212,8 @@ namespace
                 auto & d23 = *adjacency_constraints.insert(
                         adjacency_constraints.end(), make_pair(vector<bitset>(), vector<bitset>()));
 
-                build_d2_adjacency(pattern, false, d21.first, d22.first, d23.first);
-                build_d2_adjacency(target, true, d21.second, d22.second, d23.second);
+                build_d2_adjacency(pattern, d1.first, false, d21.first, d22.first, d23.first);
+                build_d2_adjacency(target, d1.second, true, d21.second, d22.second, d23.second);
             }
         }
 
@@ -236,7 +236,9 @@ namespace
             }
         }
 
-        auto build_d2_adjacency(const Graph & graph,
+        auto build_d2_adjacency(
+                const Graph & graph,
+                const vector<bitset> & d1_adj,
                 bool is_target,
                 vector<bitset> & adj1,
                 vector<bitset> & adj2,
@@ -249,10 +251,10 @@ namespace
                 adj1[t] = bitset(is_target ? domain_size : graph.size(), 0);
                 adj2[t] = bitset(is_target ? domain_size : graph.size(), 0);
                 adj3[t] = bitset(is_target ? domain_size : graph.size(), 0);
-                for (unsigned u = 0 ; u < graph.size() ; ++u)
-                    if (t != u && graph.adjacent(t, u))
-                        for (unsigned v = 0 ; v < graph.size() ; ++v)
-                            if (u != v && t != v && graph.adjacent(u, v)) {
+                for (auto u = d1_adj[t].find_first() ; u != bitset::npos ; u = d1_adj[t].find_next(u))
+                    if (t != u)
+                        for (auto v = d1_adj[u].find_first() ; v != bitset::npos ; v = d1_adj[u].find_next(v))
+                            if (u != v && t != v) {
                                 if (adj2[t].test(v))
                                     adj3[t].set(v);
                                 else if (adj1[t].test(v))

### 2016-08-18 code/sequential.cc
Refactor a bit to make excepts easier

@@ -247,6 +247,9 @@ namespace
             adj1.resize(graph.size());
             adj2.resize(graph.size());
             adj3.resize(graph.size());
+
+            vector<vector<unsigned> > counts(graph.size(), vector<unsigned>(graph.size(), 0));
+
             for (unsigned t = 0 ; t < graph.size() ; ++t) {
                 adj1[t] = bitset(is_target ? domain_size : graph.size(), 0);
                 adj2[t] = bitset(is_target ? domain_size : graph.size(), 0);
@@ -254,15 +257,19 @@ namespace
                 for (auto u = d1_adj[t].find_first() ; u != bitset::npos ; u = d1_adj[t].find_next(u))
                     if (t != u)
                         for (auto v = d1_adj[u].find_first() ; v != bitset::npos ; v = d1_adj[u].find_next(v))
-                            if (u != v && t != v) {
-                                if (adj2[t].test(v))
-                                    adj3[t].set(v);
-                                else if (adj1[t].test(v))
-                                    adj2[t].set(v);
-                                else
-                                    adj1[t].set(v);
-                            }
+                            if (u != v && t != v)
+                                ++counts[t][v];
             }
+
+            for (unsigned t = 0 ; t < graph.size() ; ++t)
+                for (unsigned u = 0 ; u < graph.size() ; ++u) {
+                    if (counts[t][u] >= 3)
+                        adj3[t].set(u);
+                    if (counts[t][u] >= 2)
+                        adj2[t].set(u);
+                    if (counts[t][u] >= 1)
+                        adj1[t].set(u);
+                }
         }
 
         auto select_branch_domain(Domains & domains) -> Domains::iterator

### 2016-08-18 code/sequential.cc
Expensive stats

@@ -195,6 +195,23 @@ namespace
                     for (unsigned v = wildcard_start ; v != domain_size ; ++v)
                         initial_domains[p].values.set(v);
             }
+
+            if (params.expensive_stats) {
+                unsigned long long pairs_seen = 0, pairs_disallowed = 0;
+                for (auto & d : initial_domains)
+                    for (auto & e : initial_domains)
+                        if (d.v != e.v)
+                            for (auto v = d.values.find_first() ; v != bitset::npos && v < wildcard_start ; v = d.values.find_next(v))
+                                for (auto w = e.values.find_first() ; w != bitset::npos && w < wildcard_start ; w = e.values.find_next(w)) {
+                                    ++pairs_seen;
+                                    for (auto & c : adjacency_constraints)
+                                        if (c.first[d.v].test(e.v) && ! c.second[v].test(w))
+                                            ++pairs_disallowed;
+                                }
+
+                result.stats.emplace("PS", to_string(pairs_seen));
+                result.stats.emplace("PD", to_string(pairs_disallowed));
+            }
         }
 
         auto add_adjacency_constraints(const Graph & pattern, const Graph & target) -> void
@@ -263,11 +280,11 @@ namespace
 
             for (unsigned t = 0 ; t < graph.size() ; ++t)
                 for (unsigned u = 0 ; u < graph.size() ; ++u) {
-                    if (counts[t][u] >= 3)
+                    if (counts[t][u] >= 3 + (is_target ? 0 : params.except))
                         adj3[t].set(u);
-                    if (counts[t][u] >= 2)
+                    if (counts[t][u] >= 2 + (is_target ? 0 : params.except))
                         adj2[t].set(u);
-                    if (counts[t][u] >= 1)
+                    if (counts[t][u] >= 1 + (is_target ? 0 : params.except))
                         adj1[t].set(u);
                 }
         }
@@ -471,10 +488,11 @@ namespace
             // eliminate isolated vertices?
 
             if (unit_propagate(initial_domains, assignments)) {
-                record_domain_sizes_in_stats(initial_domains);
+                if (params.expensive_stats)
+                    record_domain_sizes_in_stats(initial_domains);
                 solve(initial_domains, assignments);
             }
-            else
+            else if (params.expensive_stats)
                 record_domain_sizes_in_stats(initial_domains);
         }
     };

### 2016-08-18 code/sequential.cc
Injective

@@ -203,10 +203,12 @@ namespace
                         if (d.v != e.v)
                             for (auto v = d.values.find_first() ; v != bitset::npos && v < wildcard_start ; v = d.values.find_next(v))
                                 for (auto w = e.values.find_first() ; w != bitset::npos && w < wildcard_start ; w = e.values.find_next(w)) {
-                                    ++pairs_seen;
-                                    for (auto & c : adjacency_constraints)
-                                        if (c.first[d.v].test(e.v) && ! c.second[v].test(w))
-                                            ++pairs_disallowed;
+                                    if (v != w) {
+                                        ++pairs_seen;
+                                        for (auto & c : adjacency_constraints)
+                                            if (c.first[d.v].test(e.v) && ! c.second[v].test(w))
+                                                ++pairs_disallowed;
+                                    }
                                 }
 
                 result.stats.emplace("PS", to_string(pairs_seen));

### 2016-08-18 code/sequential.cc
Silly me

@@ -205,9 +205,13 @@ namespace
                                 for (auto w = e.values.find_first() ; w != bitset::npos && w < wildcard_start ; w = e.values.find_next(w)) {
                                     if (v != w) {
                                         ++pairs_seen;
+                                        bool disallowed = false;
                                         for (auto & c : adjacency_constraints)
                                             if (c.first[d.v].test(e.v) && ! c.second[v].test(w))
-                                                ++pairs_disallowed;
+                                                disallowed = true;
+
+                                        if (disallowed)
+                                            ++pairs_disallowed;
                                     }
                                 }
 

### 2016-08-19 code/sequential.cc
Just sample for stats

@@ -7,6 +7,7 @@
 #include <list>
 #include <map>
 #include <numeric>
+#include <random>
 #include <tuple>
 #include <utility>
 #include <vector>
@@ -21,9 +22,11 @@ using std::greater;
 using std::list;
 using std::make_pair;
 using std::map;
+using std::mt19937;
 using std::pair;
 using std::to_string;
 using std::tuple;
+using std::uniform_int_distribution;
 using std::unique;
 using std::vector;
 
@@ -197,23 +200,32 @@ namespace
             }
 
             if (params.expensive_stats) {
-                unsigned long long pairs_seen = 0, pairs_disallowed = 0;
-                for (auto & d : initial_domains)
-                    for (auto & e : initial_domains)
-                        if (d.v != e.v)
-                            for (auto v = d.values.find_first() ; v != bitset::npos && v < wildcard_start ; v = d.values.find_next(v))
-                                for (auto w = e.values.find_first() ; w != bitset::npos && w < wildcard_start ; w = e.values.find_next(w)) {
-                                    if (v != w) {
-                                        ++pairs_seen;
-                                        bool disallowed = false;
-                                        for (auto & c : adjacency_constraints)
-                                            if (c.first[d.v].test(e.v) && ! c.second[v].test(w))
-                                                disallowed = true;
+                vector<pair<Domain *, unsigned> > assignments;
 
-                                        if (disallowed)
-                                            ++pairs_disallowed;
-                                    }
-                                }
+                for (auto & d : initial_domains)
+                    for (auto v = d.values.find_first() ; v != bitset::npos && v < wildcard_start ; v = d.values.find_next(v))
+                        assignments.emplace_back(&d, v);
+
+                unsigned long long pairs_seen = 0, pairs_disallowed = 0;
+                if (assignments.size() >= 2) {
+                    uniform_int_distribution<decltype(assignments)::size_type> all_dist(0, assignments.size() - 1), all_but_first_dist(1, assignments.size() - 1);
+                    mt19937 rand(666);
+                    for (unsigned n = 0 ; n < 1000000 ; ++n) {
+                        swap(assignments[0], assignments[all_dist(rand)]);
+                        swap(assignments[1], assignments[all_but_first_dist(rand)]);
+                        auto & a = assignments[0], & b = assignments[1];
+                        if (a.first->v != b.first->v && a.second != b.second) {
+                            ++pairs_seen;
+                            bool disallowed = false;
+                            for (auto & c : adjacency_constraints)
[…]

### 2016-08-19 paper/paper.tex
Moved preamble into paper.
Longererer titles
Incomprehensible explanation

@@
 \usepackage{graphicx}
-
-\usepackage{showframe}
-
-\makeatletter\@ifpackageloaded{showframe}{
-    % show lines down the middle columns too
-    % http://tex.stackexchange.com/questions/16199/test-if-a-package-or-package-option-is-loaded
-\newlength\Fcolumnseprule\setlength\Fcolumnseprule{0.4pt}\def\@outputdblcol{%
-  \if@firstcolumn\global \@firstcolumnfalse \global \setbox\@leftcolumn \box\@outputbox
-  \else
-    \global \@firstcolumntrue
-    \setbox\@outputbox \vbox{\hb@xt@\textwidth{\hb@xt@\columnwidth{\box\@leftcolumn \hss}%
-    \vrule \@width\Fcolumnseprule\hfil{\normalcolor\vrule \@width\columnseprule}
-    \hfil\vrule \@width\Fcolumnseprule\hb@xt@\columnwidth {\box\@outputbox \hss}}}\@combinedblfloats\@outputpage
-    \begingroup\@dblfloatplacement\@startdblcolumn\@whilesw\if@fcolmade \fi{\@outputpage\@startdblcolumn}\endgroup
-  \fi
-}}{}
-\makeatother
 
@@
 
-A closer inspection of the raw data shows that for $k = 3$, nearly all of the instances showing a
-strong improvement are from the ``LV'' family of graphs.
-
-\begin{figure*}
-    \includegraphics*{gen-graph-constraints.pdf}\\[0.1cm]
-    \includegraphics*{gen-graph-constraints-induced.pdf}
-    \caption{We get new constraints. More woohoo.}\label{figure:constraints}
-\end{figure*}
-
 \section{A New Algorithm}
@@
 \section{Empirical Evaluation}
-
-\begin{figure}
-    \includegraphics*{gen-graph-runtimes.pdf}
-    \caption{Look how amazing our stuff is.}\label{figure:runtimes}
-\end{figure}
 
@@
 
-What proportion of instances are actually satisfiable as $k$ increases?
-
 \subsection{Non-Induced}
@@
 Just results and ``drop k vertices and try each in turn''.
-
-What proportion of instances are actually satisfiable as $k$ increases?
 

### 2016-08-21 code/sequential.cc
Iterative solver

@@ -3,6 +3,7 @@
 #include "sequential.hh"
 
 #include <algorithm>
+#include <chrono>
 #include <functional>
 #include <list>
 #include <map>
@@ -29,6 +30,10 @@ using std::tuple;
 using std::uniform_int_distribution;
 using std::unique;
 using std::vector;
+
+using std::chrono::duration_cast;
+using std::chrono::milliseconds;
+using std::chrono::steady_clock;
 
 using std::cerr;
 using std::endl;
@@ -523,5 +528,35 @@ auto sequential_subgraph_isomorphism(const pair<Graph, Graph> & graphs, const Pa
     sip.run();
 
     return sip.result;
+}
+
+auto sequential_ix_subgraph_isomorphism(const pair<Graph, Graph> & graphs, const Params & params) -> Result
+{
+    auto modified_params = params;
+    Result modified_result;
+
+    while (! *modified_params.abort) {
+        auto start_time = steady_clock::now();
+
+        SIP sip(modified_params, graphs.first, graphs.second);
+
+        sip.run();
+
+        auto pass_time = duration_cast<milliseconds>(steady_clock::now() - start_time);
+        modified_result.times.push_back(pass_time);
+
+        modified_result.nodes += sip.result.nodes;
+        if (! sip.result.isomorphism.empty()) {
+            modified_result.isomorphism = sip.result.isomorphism;
+            return modified_result;
+        }
+        else
+            modified_result.stats.emplace("FAIL" + to_string(modified_params.except), to_string(pass_time.count()));
+
+        if (++modified_params.except >= graphs.first.size())
+            break;
+    }
+
+    return modified_result;
 }
 

### 2016-08-21 code/solve_subgraph_isomorphism.cc

@@ -99,7 +99,8 @@ auto run_this(Result_ func(const Data_ &, const Params_ &)) -> std::function<Res
 auto main(int argc, char * argv[]) -> int
 {
     auto subgraph_isomorphism_algorithms = {
-        std::make_pair( std::string{ "sequential" },         sequential_subgraph_isomorphism )
+        std::make_pair( std::string{ "sequential" },         sequential_subgraph_isomorphism ),
+        std::make_pair( std::string{ "sequentialix" },       sequential_ix_subgraph_isomorphism )
     };
 
     try {

### 2016-08-22 code/sequential.cc
Hacky fixing, for now

@@ -101,6 +101,7 @@ namespace
         Domains initial_domains;
 
         unsigned wildcard_start;
+        bitset all_wildcards;
 
         SIP(const Params & k, const Graph & pattern, const Graph & target) :
             params(k),
@@ -110,6 +111,10 @@ namespace
             initial_domains(pattern.size()),
             wildcard_start(target.size())
         {
+            all_wildcards = bitset(domain_size);
+            for (unsigned v = wildcard_start ; v != domain_size ; ++v)
+                all_wildcards.set(v);
+
             // build up distance 1 adjacency bitsets
             add_adjacency_constraints(pattern, target);
 
@@ -132,26 +137,28 @@ namespace
             if (params.nds) {
                 for (unsigned p = 0 ; p < pattern.size() ; ++p) {
                     unsigned cn = 0;
-                    for (auto & c : adjacency_constraints) {
+                    auto & c = *adjacency_constraints.begin();
+                    // for (auto & c : adjacency_constraints) {
                         p_nds[cn].resize(pattern.size());
                         for (unsigned q = 0 ; q < pattern.size() ; ++q)
                             if (c.first[p][q])
                                 p_nds[cn][p].push_back(c.first[q].count());
                         sort(p_nds[cn][p].begin(), p_nds[cn][p].end(), greater<unsigned>());
                         ++cn;
-                    }
+                    // }
                 }
 
                 for (unsigned t = 0 ; t < target.size() ; ++t) {
                     unsigned cn = 0;
-                    for (auto & c : adjacency_constraints) {
+                    auto & c = *adjacency_constraints.begin();
+                    //for (auto & c : adjacency_constraints) {
                         t_nds[cn].resize(target.size());
                         for (unsigned q = 0 ; q < target.size() ; ++q)
                             if (c.second[t][q])
                                 t_nds[cn][t].push_back(c.second[q].count());
                         sort(t_nds[cn][t].begin(), t_nds[cn][t].end(), greater<unsigned>());
                         ++cn;
-                    }
+                    //}
                 }
             }
 
@@ -184,7 +191,7 @@ namespace
 
                     // neighbourhood degree sequences
                     if (params.nds) {
-                        for (unsigned cn = 0 ; cn < adjacency_constraints.size() && ok ; ++cn) {
+                        for (unsigned cn = 0 ; cn < 1 && ok ; ++cn) {
                             for (unsigned i = params.except ; i < p_nds[cn][p].size() ; ++i) {
[…]

### 2016-08-22 code/sequential.cc
Fix NDS

@@ -137,28 +137,26 @@ namespace
             if (params.nds) {
                 for (unsigned p = 0 ; p < pattern.size() ; ++p) {
                     unsigned cn = 0;
-                    auto & c = *adjacency_constraints.begin();
-                    // for (auto & c : adjacency_constraints) {
+                    for (auto & c : adjacency_constraints) {
                         p_nds[cn].resize(pattern.size());
                         for (unsigned q = 0 ; q < pattern.size() ; ++q)
                             if (c.first[p][q])
                                 p_nds[cn][p].push_back(c.first[q].count());
                         sort(p_nds[cn][p].begin(), p_nds[cn][p].end(), greater<unsigned>());
                         ++cn;
-                    // }
+                    }
                 }
 
                 for (unsigned t = 0 ; t < target.size() ; ++t) {
                     unsigned cn = 0;
-                    auto & c = *adjacency_constraints.begin();
-                    //for (auto & c : adjacency_constraints) {
+                    for (auto & c : adjacency_constraints) {
                         t_nds[cn].resize(target.size());
                         for (unsigned q = 0 ; q < target.size() ; ++q)
                             if (c.second[t][q])
                                 t_nds[cn][t].push_back(c.second[q].count());
                         sort(t_nds[cn][t].begin(), t_nds[cn][t].end(), greater<unsigned>());
                         ++cn;
-                    //}
+                    }
                 }
             }
 
@@ -193,7 +191,7 @@ namespace
                     if (params.nds) {
                         for (unsigned cn = 0 ; cn < 1 && ok ; ++cn) {
                             for (unsigned i = params.except ; i < p_nds[cn][p].size() ; ++i) {
-                                if (t_nds[cn][t][i - params.except] < p_nds[cn][p][i]) {
+                                if (t_nds[cn][t][i - params.except] + params.except < p_nds[cn][p][i]) {
                                     ok = false;
                                     break;
                                 }

### 2016-08-25 code/sequential.cc
More filtering options

@@ -115,11 +115,8 @@ namespace
             for (unsigned v = wildcard_start ; v != domain_size ; ++v)
                 all_wildcards.set(v);
 
-            // build up distance 1 adjacency bitsets
+            // build up adjacency bitsets
             add_adjacency_constraints(pattern, target);
-
-            if (params.induced)
-                add_complement_constraints(pattern, target);
 
             for (unsigned p = 0 ; p < pattern.size() ; ++p)
                 pattern_degrees[p] = pattern.degree(p);
@@ -131,10 +128,39 @@ namespace
                 for (unsigned v = 0 ; v < params.except ; ++v)
                     target_degrees.at(wildcard_start + v) = 0;
 
-            vector<vector<vector<unsigned> > > p_nds(adjacency_constraints.size());
-            vector<vector<vector<unsigned> > > t_nds(adjacency_constraints.size());
+            vector<vector<vector<unsigned> > > p_nds(params.cnds ? adjacency_constraints.size() * adjacency_constraints.size() : adjacency_constraints.size());
+            vector<vector<vector<unsigned> > > t_nds(params.cnds ? adjacency_constraints.size() * adjacency_constraints.size() : adjacency_constraints.size());
 
-            if (params.nds) {
+            if (params.cnds) {
+                for (unsigned p = 0 ; p < pattern.size() ; ++p) {
+                    unsigned cn = 0;
+                    for (auto & c : adjacency_constraints) {
+                        for (auto & d : adjacency_constraints) {
+                            p_nds[cn].resize(pattern.size());
+                            for (unsigned q = 0 ; q < pattern.size() ; ++q)
+                                if (c.first[p][q])
+                                    p_nds[cn][p].push_back(d.first[q].count());
+                            sort(p_nds[cn][p].begin(), p_nds[cn][p].end(), greater<unsigned>());
+                            ++cn;
+                        }
+                    }
+                }
+
+                for (unsigned t = 0 ; t < target.size() ; ++t) {
+                    unsigned cn = 0;
+                    for (auto & c : adjacency_constraints) {
+                        for (auto & d : adjacency_constraints) {
+                            t_nds[cn].resize(target.size());
+                            for (unsigned q = 0 ; q < target.size() ; ++q)
+                                if (c.second[t][q])
+                                    t_nds[cn][t].push_back(d.second[q].count());
[…]

### 2016-08-25 code/solve_subgraph_isomorphism.cc

@@ -110,8 +110,10 @@ auto main(int argc, char * argv[]) -> int
             ("timeout",            po::value<int>(),  "Abort after this many seconds")
             ("format",             po::value<std::string>(), "Specify graph file format (lad or dimacs)")
             ("d2graphs",                              "Use d2 graphs")
+            ("d2cgraphs",                             "Use d2 complement graphs")
             ("degree",                                "Use degree filtering")
             ("nds",                                   "Use NDS filtering")
+            ("cnds",                                  "Use Combined NDS filtering")
             ("except",             po::value<int>(),  "Allow this many pattern vertices to be excluded")
             ("induced",                               "Induced")
             ("expensive-stats",                       "Calculate expensive stats")
@@ -173,9 +175,11 @@ auto main(int argc, char * argv[]) -> int
         Params params;
 
         params.d2graphs = options_vars.count("d2graphs");
+        params.d2cgraphs = options_vars.count("d2cgraphs");
         params.induced = options_vars.count("induced");
         params.degree = options_vars.count("degree");
         params.nds = options_vars.count("nds");
+        params.cnds = options_vars.count("cnds");
         params.expensive_stats = options_vars.count("expensive-stats");
         if (options_vars.count("except"))
             params.except = options_vars["except"].as<int>();

### 2016-08-25 code/sequential.cc
Fastererer for small domains

@@ -5,6 +5,7 @@
 #include <algorithm>
 #include <chrono>
 #include <functional>
+#include <limits>
 #include <list>
 #include <map>
 #include <numeric>
@@ -24,6 +25,7 @@ using std::list;
 using std::make_pair;
 using std::map;
 using std::mt19937;
+using std::numeric_limits;
 using std::pair;
 using std::to_string;
 using std::tuple;
@@ -38,70 +40,249 @@ using std::chrono::steady_clock;
 using std::cerr;
 using std::endl;
 
-using bitset = boost::dynamic_bitset<>;
-
 namespace
 {
-    struct Domain
+    /// We'll use an array of unsigned long longs to represent our bits.
+    using BitWord = unsigned long long;
+
+    /// Number of bits per word.
+    static const constexpr int bits_per_word = sizeof(BitWord) * 8;
+
+    /**
+     * A bitset with a fixed maximum size. This only provides the operations
+     * we actually use in the bitset algorithms: it's more readable this way
+     * than doing all the bit voodoo inline.
+     *
+     * Indices start at 0.
+     */
+    template <unsigned words_>
+    class FixedBitSet
     {
-        unsigned v;
-        bool fixed;
-        bitset values;
-    };
+        private:
+            using Bits = std::array<BitWord, words_>;
 
-    using Domains = vector<Domain>;
+            Bits _bits = {{ }};
 
-    struct Assignments
-    {
-        vector<tuple<unsigned, unsigned, bool> > trail;
+        public:
+            FixedBitSet() = default;
 
-        auto push_branch(unsigned a, unsigned b) -> void
-        {
-            trail.emplace_back(a, b, true);
-        }
-
-        auto push_implication(unsigned a, unsigned b) -> void
-        {
-            if (trail.end() == find_if(trail.begin(), trail.end(), [&] (const auto & x) {
-                        return get<0>(x) == a && get<1>(x) == b;
-                        }))
-                trail.emplace_back(a, b, false);
-        }
-
-        auto pop() -> void
-        {
-            while ((! trail.empty()) && (! get<2>(trail.back())))
-                trail.pop_back();
-
-            if (! trail.empty())
-                trail.pop_back();
-        }
-
-        auto store_to(map<int, int> & m, unsigned wildcard_start) -> void
-        {
-            for (auto & t : trail) {
-                if (get<1>(t) >= wildcard_start)
-                    m.emplace(get<0>(t), -1);
-                else
[…]

### 2016-08-25 code/sequential.cc
A bit fasterererer code

@@ -621,21 +621,24 @@ namespace
         auto cheap_all_different(Domains & domains) -> bool
         {
             // pick domains smallest first, with tiebreaking
-            vector<int> domains_order;
+            vector<pair<int, int> > domains_order;
             domains_order.resize(domains.size());
-            iota(domains_order.begin(), domains_order.begin() + domains.size(), 0);
+            for (unsigned d = 0 ; d < domains.size() ; ++d) {
+                domains_order[d].first = d;
+                domains_order[d].second = domains[d].values.count();
+            }
 
             sort(domains_order.begin(), domains_order.begin() + domains.size(),
-                    [&] (int a, int b) {
-                        return (domains.at(a).values.count() < domains.at(b).values.count()) || (domains.at(a).values.count() == domains.at(b).values.count() && a < b);
-                        });
+                    [&] (const pair<int, int> & a, const pair<int, int> & b) {
+                        return a.second < b.second || (a.second == b.second && a.first < b.first);
+                    });
 
             // counting all-different
             Bitset_ domains_so_far = Bitset_(domain_size), hall = Bitset_(domain_size);
             unsigned neighbours_so_far = 0;
 
             for (int i = 0, i_end = domains.size() ; i != i_end ; ++i) {
-                auto & d = domains.at(domains_order.at(i));
+                auto & d = domains.at(domains_order.at(i).first);
 
                 d.values &= ~hall;
 

### 2016-08-25 code/sequential.cc
high-wildcards option

@@ -307,7 +307,7 @@ namespace
 
             if (params.except >= 1)
                 for (unsigned v = 0 ; v < params.except ; ++v)
-                    target_degrees.at(wildcard_start + v) = 0;
+                    target_degrees.at(wildcard_start + v) = params.high_wildcards ? target.size() + 1 : 0;
 
             vector<vector<vector<unsigned> > > p_nds(params.cnds ? adjacency_constraints.size() * adjacency_constraints.size() : adjacency_constraints.size());
             vector<vector<vector<unsigned> > > t_nds(params.cnds ? adjacency_constraints.size() * adjacency_constraints.size() : adjacency_constraints.size());

### 2016-08-25 code/solve_subgraph_isomorphism.cc

@@ -115,6 +115,7 @@ auto main(int argc, char * argv[]) -> int
             ("nds",                                   "Use NDS filtering")
             ("cnds",                                  "Use Combined NDS filtering")
             ("except",             po::value<int>(),  "Allow this many pattern vertices to be excluded")
+            ("high-wildcards",                        "Treat wildcard vertices as having high degree")
             ("induced",                               "Induced")
             ("expensive-stats",                       "Calculate expensive stats")
             ;
@@ -181,6 +182,7 @@ auto main(int argc, char * argv[]) -> int
         params.nds = options_vars.count("nds");
         params.cnds = options_vars.count("cnds");
         params.expensive_stats = options_vars.count("expensive-stats");
+        params.high_wildcards = options_vars.count("high-wildcards");
         if (options_vars.count("except"))
             params.except = options_vars["except"].as<int>();
 

### 2016-08-26 paper/paper.tex
Showframe hackery, for now
New experiments, and use gpgnode results
General format tinkering
Some runtimes
Histogrammification
Plotting
Words words words

--- 2016-08-15 paper/paper.tex
@@
 lead to a practical algorithm which can scale to work with the families of graphs commonly used to
-benchmark subgraph isomorphism algorithms.
+benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in a substantial
+portion of ; in many more cases, we can at least obtain an upper bound.
 
@@
 
-A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping
-$P \rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
-isomorphism $P \hookrightarrow T$, additionally maps non-adjacent vertices to non-adjacent
- vertices.
+A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping $P
+\rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
+isomorphism $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
+We define a $k$-less-subgraph isomorphism from $P$ to $T$ to be a subgraph isomorphism from all but
+$k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
+\lessind{k} T$ respectively.
 
@@
 isomorphisms to $G$ and $H$; a maximum common induced subgraph is a common induced subgraph with as
-many vertices as possible.
+many vertices as possible. An induced $k$-less subgraph isomorphism $P \lessind{k} T$ is equivalent
+to a common induced subgraph of $P$ and $T$ with $|\operatorname{V}(P)| - k$ vertices.
 
-A maximum common partial (i.e.\ non-induced) subgraph would allow us to select every vertex in the
-pattern, and none of the edges. The objective is therefore changed to maximise the number of edges,
-rather than vertices. However, this is not what we are looking for: usually maximum common subgraph
-problems are symmetric in their inputs, but we are allowing extra edges only in the target, not in
-the pattern.
+If defined similarly, a maximum common non-induced subgraph would allow us to select every vertex in
+the smaller of the two graphs, and none of the edges. It is therefore traditional to change the
+objective to maximise the number of edges selected, rather than vertices, when a non-induced common
+subgraph is sought---this problem is usually called the maximum common \emph{partial} subgraph
+problem instead. However, this is not what we will be discussing in this paper: maximum common
+subgraph problems are symmetric in their inputs, but when discussing the non-induced case we are
+allowing extra edges only in the target graph, not in the pattern.
 
-We define a $k$-less-subgraph isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
-but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written
-$P \lessnonind{k} T$ and $P \lessind{k} T$ respectively.
+?? Draw an example.
 
-\subsection{Models and Algorithms}
+\subsection{Constraint Models and Algorithms}
 
@@
 
-Comparison with the clique and CP models, as well as ``drop k vertices and try each in turn''.
+What proportion of instances are actually satisfiable as $k$ increases?
+
+\begin{figure}
+    \includegraphics*{gen-graph-which-k-by-family.pdf}
+    \caption{There are satisfiable instances for small values of $k$. Yay.}\label{figure:which-k}
+\end{figure}
+
+\subsection{Non-Induced}
 
@@
 
-\subsection{Non-Induced}
+\subsection{Solving from the Top Down}
 
-Just results and ``drop k vertices and try each in turn''.
-
-What proportion of instances are actually satisfiable as $k$ increases?
-
-\subsection{Parallel Search}
+\begin{figure}
+    \includegraphics*{gen-graph-versus-cp.pdf}
+    \caption{A righteous spanking.}\label{figure:versus-cp}
+\end{figure}
 

### 2016-08-30 paper/paper.tex
Minor cosmetic changes.

@@
 \newcommand{\nds}{\operatorname{nds}}
+\newcommand{\paths}{\operatorname{paths}}
 \newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
 \newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
+\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
 
@@
     Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
-    $k$-less-subgraph isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
+    $k$-less-subgraph isomorphisms, if $p \lessmap t$ then
     $\deg(p) - k \le \deg(t)$.
@@
 \begin{proposition}
-    More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
+    More powerfully, if $p \lessmap t$ then
     $(\nds(p)[k+1] - k, \nds(p)[k+2] - k, \ldots) \preceq \nds(t)$.
@@
 
-\todo{Define paths}
+A \emph{path} between two vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$.
+We define $\paths(p,q,n)$ to be the number of paths of length $n$ between the vertices $p$ and $q$.
+%\todo{Define paths}
 
 \begin{proposition}
-    If $p \prescript{}{k}{\mapsto} t$ and $q \prescript{}{k}{\mapsto} u$ then
-     $\operatorname{paths}(p, q, 2) \le \operatorname{paths}(t, u, 2) + k$.
+    Let $p,q \in V(P)$ and $t,u\in V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
+     $\paths(p, q, 2) \le \paths(t, u, 2) + k$.
 \end{proposition}

### 2016-08-30 paper/paper.tex
Needing to restart machine, tmp paper update.

@@
 \begin{proposition}
+    \label{prop:deg}
     Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
@@
 \end{proof}
+\begin{figure}
+    \begin{center}
+        \begin{tikzpicture}{every node/.style={circle, inner sep=1mm}}
+            \node[fill=black] (p)  {};
+            \node[fill=red] (n1) [above left of = p] {};
+            \node[fill=blue] (n2) [above of = p] {};
+            \node[fill=blue] (n3) [above right of = p] {};
+            \node[fill=green] (q) [above of = n2] {};
+            %\path[]
+        \end{tikzpicture}
+        \caption{Graph that Craig wanted}
+        \label{fig:nds}
+    \end{center}
+\end{figure}
 
@@
     Let $p,q \in V(P)$ and $t,u\in V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
-     $\paths(p, q, 2) \le \paths(t, u, 2) + k$.
+     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
 \end{proposition}
+\begin{proof}
+Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
+\begin{align*}
+P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
+ = & \{((p,x),(x,q)) : x\in N(p) \text{ and } x\in N(q) \} \\
+ = & \{((p,x),(x,q)) : x\in N(p)\cap N(q) \} .
+\end{align*}
+So $\paths(p,q,2) = | N(p)\cap N(q)| \leq deg(p)$.
+
+If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
+\[
+|N(p)\cap N(q)| - k \leq deg(p) - k \leq deg(t).
+\]
+As $|N(p)\cap N(q)|\leq deg(p) \leq |N(t)\cap N(u)|\leq deg(t)$, we have
+\[
+|N(p)\cap N(q)| - k \leq deg(p) - k\leq |N(t)\cap N(u)|\leq deg(t)
+\]
+which is
+\[
+\paths(p, q, 2) - k \leq \paths(t, u, 2).
+\]
+\end{proof}
 

### 2016-08-30 paper/paper.tex
Added a graph Craig wanted.

@@
     \begin{center}
-        \begin{tikzpicture}{every node/.style={circle, inner sep=1mm}}
+        \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
             \node[fill=black] (p) {};
-            \node[fill=red] (n1) [above left of = p] {};
-            \node[fill=blue] (n2) [above of = p] {};
-            \node[fill=blue] (n3) [above right of = p] {};
-            \node[fill=green] (q) [above of = n2] {};
-            %\path[]
+            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
+            \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
+            \node[fill=uofgpumpkin] (n1) [left of = n2] {};
+            \node[fill=uofglawn] (n3) [right of = n2] {};
+            \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
+            \path (p) edge (n1) edge (n2) edge (n3)
+                (n1) edge (q)
+                (n2) edge (n3) edge (q)
+                (n3) edge (q);
         \end{tikzpicture}

### 2016-08-30 paper/paper.tex
Prop 2, Cor 1, Defns, Proofs

@@
 
-Let $S$ and $T$ be two sequences. We define $S \preceq T$
-
-\todo{Define $\preceq$, deg, nds}
+Let $p$ be a vertex in a graph $P$, the \emph{degree} of $p$, $\deg(p)$, is the number of vertices
+to which it is adjacent
 
@@
 
+A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $N(p) = \{ q \in V_p | p
+\text{ and } q \text{ are adjacent }\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
+degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
+neighbours.
+
+Let $S = ( s_1 , \ldots , s_n )$ and $T = ( t_1 , \ldots , t_m)$ be two sequences.  We say that $S
+\preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
+t_j$.  (When considering a $k$-less-subgraph isomorphism) we say that $S \prescript{}{k}{\preceq}
+T$ if $n - k \leq m$ and $\forall s_i \in S \setminus S_k$, where $S_k$ is a subsequence of $S$
+containing up to $k$ members of $S$, there exists a distinct $t_j \in T$ with $s_i - k \leq t_j$.
+
 \begin{proposition}
-    More powerfully, if $p \lessmap t$ then
-    $(\nds(p)[k+1] - k, \nds(p)[k+2] - k, \ldots) \preceq \nds(t)$.
+If $p \prescript{}{k}{\mapsto} t$, then $\nds(p) \prescript{}{k}{\preceq} \nds(t)$.
 \end{proposition}
@@
 \begin{proof}
-Let
+Let $p \prescript{}{k}{\mapsto} t$.  Then $\deg(p) - k \leq \deg(q)$, by Proposition 1, which
+implies that $|\nds(p)| -k \leq |\nds(t)|$.
 
+Also, $p \prescript{}{k}{\mapsto} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
+is some subset of $P$ with $|P_k| \leq k$, $q \prescript{}{k}{\mapsto} u$, where $u \in N(t)$ and
+each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by Proposition 1.  Hence $\nds(p)
+\prescript{}{k}{\preceq} \nds(t)$.
 \end{proof}
+
+Figure\ref{fig:nds} illustrates the three cases possible when filtering by neighbourhood degree
+sequence.  Removing the top node causes each entry in $\nds(p)$ to be reduced; removing the 
+left-middle node removes an entry from $\nds(p)$; and removing either of the connected nodes in the
+middle layer causes both the size of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.
+
+\begin{corollary}
+You can just ignore the first K things in $\nds(p)$, assuming it's ordered.
+\end{corollary}
+
+\begin{proof}
+Do we need this?
+\end{proof}
+
 \begin{figure}

### 2016-08-30 paper/paper.tex
Prop 2, Cor 1, Defns, Proofs, Cor env
Notational fixes.

@@
 \newtheorem{proposition}{Proposition}
+\newtheorem{corollary}{Corollary}
 
@@
 \newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
-
+\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
+\newcommand{\V}{\operatorname{V}}
 % to do comments
@@
 many vertices as possible. An induced $k$-less subgraph isomorphism $P \lessind{k} T$ is equivalent
-to a common induced subgraph of $P$ and $T$ with $|\operatorname{V}(P)| - k$ vertices.
+to a common induced subgraph of $P$ and $T$ with $|\V(P)| - k$ vertices.
 
@@
 allowing extra edges only in the target graph, not in the pattern.
-
-?? Draw an example.
-
+\todo{is this example graph still needed??}
 \subsection{Constraint Models and Algorithms}
@@
     Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
-    $k$-less-subgraph isomorphisms, if $p \lessmap t$ then
+    $k$-less-subgraph isomorphisms, if $p \lessmap{k} t$ then
     $\deg(p) - k \le \deg(t)$.
@@
 
-A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $N(p) = \{ q \in V_p | p
-\text{ and } q \text{ are adjacent }\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
+A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $N(p) = \{ q \in \V(P) :
+ p \text{ and } q \text{ are adjacent }\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
 degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
@@
 \preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
-t_j$.  (When considering a $k$-less-subgraph isomorphism) we say that $S \prescript{}{k}{\preceq}
+t_j$.  (When considering a $k$-less-subgraph isomorphism) we say that $S \lesspreceq{k}
 T$ if $n - k \leq m$ and $\forall s_i \in S \setminus S_k$, where $S_k$ is a subsequence of $S$
@@
 \begin{proposition}
-If $p \prescript{}{k}{\mapsto} t$, then $\nds(p) \prescript{}{k}{\preceq} \nds(t)$.
+If $p \lessmap{k} t$, then $\nds(p) \lesspreceq{k} \nds(t)$.
 \end{proposition}
@@
 \begin{proof}
-Let $p \prescript{}{k}{\mapsto} t$.  Then $\deg(p) - k \leq \deg(q)$, by Proposition 1, which
+Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by Proposition 1, which
 implies that $|\nds(p)| -k \leq |\nds(t)|$.
 
-Also, $p \prescript{}{k}{\mapsto} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
-is some subset of $P$ with $|P_k| \leq k$, $q \prescript{}{k}{\mapsto} u$, where $u \in N(t)$ and
+Also, $p \lessmap{k} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
+is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
 each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by Proposition 1.  Hence $\nds(p)
-\prescript{}{k}{\preceq} \nds(t)$.
+\lesspreceq{k} \nds(t)$.
 \end{proof}
@@
 \begin{proposition}
-    Let $p,q \in V(P)$ and $t,u\in V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
+    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
      $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
@@
 \begin{proposition}
-    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$. The
+    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$. The
     vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent, if there are at least $n$ simple paths of

### 2016-09-01 paper/paper.tex
notation changes.

@@
 % Maths operators
-\newcommand{\nds}{\operatorname{nds}}
 \newcommand{\paths}{\operatorname{paths}}
@@
 \newcommand{\V}{\operatorname{V}}
+\newcommand{\N}{\operatorname{N}}
+\newcommand{\nds}{\operatorname{S}}
 % to do comments
@@
 
-A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $N(p) = \{ q \in \V(P) :
+A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $\N(p) = \{ q \in \V(P) :
  p \text{ and } q \text{ are adjacent }\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
@@
 
-Also, $p \lessmap{k} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
-is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
+Also, $p \lessmap{k} t$ implies that for each $q \in \N(p)\setminus P_k$, where $P_k$
+is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in \N(t)$ and
 each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by Proposition 1.  Hence $\nds(p)
@@
 P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
- = & \{((p,x),(x,q)) : x\in N(p) \text{ and } x\in N(q) \} \\
- = & \{((p,x),(x,q)) : x\in N(p)\cap N(q) \} .
+ = & \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \} \\
+ = & \{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} .
 \end{align*}
-So $\paths(p,q,2) = | N(p)\cap N(q)| \leq deg(p)$.
+So $\paths(p,q,2) = | \N(p)\cap \N(q)| \leq deg(p)$.
 
@@
 \[
-|N(p)\cap N(q)| - k \leq deg(p) - k \leq deg(t).
+|\N(p)\cap \N(q)| - k \leq deg(p) - k \leq deg(t).
 \]
-As $|N(p)\cap N(q)|\leq deg(p) \leq |N(t)\cap N(u)|\leq deg(t)$, we have
+As $|\N(p)\cap \N(q)|\leq deg(p) \leq |\N(t)\cap \N(u)|\leq deg(t)$, we have
 \[
-|N(p)\cap N(q)| - k \leq deg(p) - k\leq |N(t)\cap N(u)|\leq deg(t)
+|\N(p)\cap \N(q)| - k \leq deg(p) - k\leq |\N(t)\cap \N(u)|\leq deg(t)
 \]
@@
     $P \lessnonind{k} T$ induces a new $k$-less-subgraph isomorphism
-    $P^{n, 2}\lessnonind{k} T^{n - k, 2}$.
+    $P^{n+k, 2}\lessnonind{k} T^{n, 2}$.
 \end{proposition}

### 2016-09-01 paper/paper.tex
complement graphs section, nds corollary + sketch proof

--- 2016-08-30 paper/paper.tex
@@
 allowing extra edges only in the target graph, not in the pattern.
-\todo{is this example graph still needed??}
+
+\todo{is this example graph still needed?? yes, Patrick likes pictures}
+
 \subsection{Constraint Models and Algorithms}
@@
 \subsection{Experimental Setup}
+
+\section{Relationship between non-induced and induced subgraph isomorphism}
+
+The \emph{complement} of a graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.
+
+\begin{proposition}\label{prop:comp}
+Let $i$ be an assignment of $T$ vertices to $P$ vertices.
+Then $i$ satisfies the definition of $P \hookrightarrow T$ if and only if both $i$ satisfies the definition of $P \rightarrowtail T$ and $\bar{P} \rightarrowtail \bar{T}$.
+\end{proposition}
+
+\begin{proof}
+Follows directly from the definition of an induced subgraph isomorphism and the definition of the complement of a graph.  Could flesh this out if we need to fill up space and look cleverer??
+\end{proof}
+
+\begin{corollary}
+Let $i$ be an assignment of $T$ vertices to $P$ vertices.
+Then $i$ satisfies the definition of $P \lessind{k} T$ if and only if both $i$ satisfies the definition of $P \lessnonind{k} T$ and $\bar{P} \lessnonind{k} \bar{T}$.
+\end{corollary}
+
+Should we just give the corollary as the proof??
+
+In our algorithm we make use of \cref{prop:comp} by seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\bar{P} \rightarrowtail \bar{T}$ when searching for an induced subgraph isomorphism.
+Further, \cref{prop:comp} tells us that every induced subgraph isomorphism is equivalent to simultaneous non-induced subgraph isomorphisms both $P$ and $T$ as well as their complements.
 
@@
 \preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
-t_j$.  (When considering a $k$-less-subgraph isomorphism) we say that $S \lesspreceq{k}
+t_j$.  When considering a $k$-less-subgraph isomorphism we say that $S \lesspreceq{k}
 T$ if $n - k \leq m$ and $\forall s_i \in S \setminus S_k$, where $S_k$ is a subsequence of $S$
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:nds}
 If $p \lessmap{k} t$, then $\nds(p) \lesspreceq{k} \nds(t)$.
@@
 \begin{proof}
-Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by Proposition 1, which
+Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
 implies that $|\nds(p)| -k \leq |\nds(t)|$.
@@
 is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
-each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by Proposition 1.  Hence $\nds(p)
+each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
 \lesspreceq{k} \nds(t)$.
@@
 \begin{corollary}
-You can just ignore the first K things in $\nds(p)$, assuming it's ordered.
+Since both $\nds(p)$ and $\nds(t)$ are non-ascending, wlog we can replace $S \setminus S_k$ from the definition of $S \lesspreceq{k}
+T$ with $S[k, n]$.
 \end{corollary}
@@
 \begin{proof}
-Do we need this?
+Sketch?? Let $S_k$ be some elements of the sequence which aren't the first $k$ elements.  Then these elements are less than or equal to the first $k$ elements.
 \end{proof}
@@
         \end{tikzpicture}
-        \caption{Graph that Craig wanted}
+        \caption{Example of neighbourhood degree filtering cases}
         \label{fig:nds}
@@
 
-We're not going to thank anyone, no, no.
+We're not going to thank anyone, no, no.  Thanks to Frances for making us less smelly throughout the writing of the paper (by thieving toiletries from a fancy hotel).
 

### 2016-09-01 paper/paper.tex
An algorithm
Don't showframe

@@
 \usepackage{graphicx}
+\usepackage{multicol}
+\usepackage[ruled,vlined]{algorithm2e}
 
-\usepackage{showframe}
+% \usepackage{showframe}
 
@@
 \section{A New Algorithm}
+
+\begin{algorithm*}[tb]
+\DontPrintSemicolon
+\begin{multicols}{2}
+\nl $\FuncSty{klessSubgraphIsomorphism}$ (\\\hspace*{2em}Graph $\mathcal{P}$, Graph $\mathcal{T}$, Int $k$) $\rightarrow$ Bool \;
+\nl \Begin{
+    \nl \lIf{$\left|\V(\mathcal{P})\right| + k > \left|\V(\mathcal{T})\right|$}{$\KwSty{return}~\KwSty{false}$\label{line:enough}}
+    \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\shortoverline{\mathcal{P}},
+        \shortoverline{\mathcal{T}}),$
+        \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
+    \mathcal{T}^{2,2}), (\mathcal{P}^{3 + k,2},\ \mathcal{T}^{3,2}) \big]$ \;
+    \nl \ForEach{$v \in \V(\mathcal{P})$}{
+        \nl $D_v \gets \V(\mathcal{T})$\;
+        \nl \ForEach{$(P,\,T) \in L$}{
+            \nl $D_v \gets D_v \cap \{ w \in D_v : $ \\
+            \hspace*{7em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
+            \hspace*{7em}$\nds_P(v) \lesspreceq{k} \nds_T(w)\}$ \;
+        }
+        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values}$
+    }
+    \nl \lIf{\FuncSty{propagate}(D)}{$\KwSty{return}~\FuncSty{search}(L, D, k)$}
+    \nl \lElse{$\KwSty{return}~\KwSty{false}$}
+}
+\bigskip
+\nl $\FuncSty{search}$ (GraphPairs $L$, Domains $D$, Int $k$) $\rightarrow$ Bool \;
+\nl \Begin{
+    \nl \lIf{$D = \emptyset$}{$\KwSty{return}~\KwSty{true}$}
+    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \;
+    \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
+        \nl \If{$v'$ \textnormal{is not the first wildcard we have tried}}{
+            \nl \KwSty{continue} \;
+        }
+        \nl $D' \gets \FuncSty{clone}(D)$ \;
+        \nl $D'_v \gets \{ v' \} $ \;
+        \nl \If{\FuncSty{propagate}(D')}{
+            \nl \If{$\FuncSty{search}(L, \{ D \in D' : \left|D\right| > 1 \}, k)$}{
+                \nl $\KwSty{return}~\KwSty{true}$ \;
+            }
+        }
+    }
+}
+\bigskip
+\nl $\FuncSty{propagate}$ (GraphPairs $L$, Domains $D$) $\rightarrow$ Bool \;
+\nl \Begin{
+    \nl \While{\KwSty{true}}{
+        \nl \If{\textnormal{no unit domains remain}}{
+            \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
+                \nl $\KwSty{return}~\KwSty{false}$ \;
+            }
+        }
+        \nl \lIf{$\textnormal{no unit domains remain}$}{$\KwSty{return}~\KwSty{true}$}
+        \nl $D_v = \{ v' \} \gets \textnormal{a unit domain from}~D$ \;
+        \nl \ForEach{$D_w \in D \setminus \{ D_v \}$}{
+            \nl $D_w \gets D_w \setminus \{ v' \}$ \label{line:removev} \;
+            \nl \ForEach{$(P,\,T) \in L$}{
+                \nl \If{$v \sim_P w$}{
+                    \nl $D_w \gets D_w \cap \left(\N_T(v') \cup \textnormal{wildcards}\right)$
+                }
+            }
+            \nl \lIf{$D_w = \emptyset$}{$\KwSty{return}~\KwSty{false}$}
+        }
+    }
+}
+\bigskip
+\nl $\FuncSty{allDifferent}$ (Domains $D$) $\rightarrow$ Bool \;
+\nl \Begin{
+\nl $(F,\,H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,\emptyset,\,0)$ \;
+\nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
+    \nl $F \gets F + v$ \;
+    \nl $D_v \gets D_v \setminus H$ \label{line:elimhall} \;
+    \nl $(A,\,n) \gets (A \cup D_v,\,n + 1)$ \label{line:acc} \;
+    \nl \lIf{$D_v = \emptyset~\KwSty{or}~|A| < n$}{$\KwSty{return}~\KwSty{false}$\label{line:failhall}}
+    \nl \lIf{$|A| = n$}{$(H,\,A,\,n) \gets (H \cup A,\,\emptyset,\,0)$\label{line:hall}}
+}
+\nl $\KwSty{return}~\KwSty{true}$ \;
+}
+\end{multicols}
+\vspace*{0.4cm}% bug in algorithm2e + multicol: incorrect space left above the vertical line
+\caption{An algorithm for the $k$-less subgraph isomorphism problem.}
+\label{algorithm:sip}
+\end{algorithm*}
 

### 2016-09-01 paper/paper.tex
Make things look a bit prettier

--- 2016-09-01 paper/paper.tex
@@
 
+\begin{algorithm*}[tb]
+\DontPrintSemicolon
+\begin{multicols}{2}
+\nl $\FuncSty{klessSubgraphIsomorphism}$ (\\\hspace*{2em}Graph $\mathcal{P}$, Graph $\mathcal{T}$, Int $k$) $\rightarrow$ Bool \;
+\nl \Begin{
+    \nl \lIf{$\left|\V(\mathcal{P})\right| + k > \left|\V(\mathcal{T})\right|$}{$\KwSty{return}~\KwSty{false}$\label{line:enough}}
+    \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\shortoverline{\mathcal{P}},
+        \shortoverline{\mathcal{T}}),$
+        \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
+    \mathcal{T}^{2,2}), (\mathcal{P}^{3 + k,2},\ \mathcal{T}^{3,2}) \big]$ \;
+    \nl \ForEach{$v \in \V(\mathcal{P})$}{
+        \nl $D_v \gets \V(\mathcal{T})$\;
+        \nl \ForEach{$(P,\,T) \in L$}{
+            \nl $D_v \gets D_v \cap \{ w \in D_v : $ \\
+            \hspace*{7em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
+            \hspace*{7em}$\nds_P(v) \lesspreceq{k} \nds_T(w)\}$ \;
+        }
+        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values}$
+    }
+    \nl \lIf{\FuncSty{propagate}(D)}{$\KwSty{return}~\FuncSty{search}(L, D, k)$}
+    \nl \lElse{$\KwSty{return}~\KwSty{false}$}
+}
+\bigskip
+\nl $\FuncSty{search}$ (GraphPairs $L$, Domains $D$, Int $k$) $\rightarrow$ Bool \;
+\nl \Begin{
+    \nl \lIf{$D = \emptyset$}{$\KwSty{return}~\KwSty{true}$}
+    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \;
+    \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
+        \nl \If{$v'$ \textnormal{is not the first wildcard we have tried}}{
+            \nl \KwSty{continue} \;
+        }
+        \nl $D' \gets \FuncSty{clone}(D)$ \;
+        \nl $D'_v \gets \{ v' \} $ \;
+        \nl \If{\FuncSty{propagate}(D')}{
+            \nl \If{$\FuncSty{search}(L, \{ D \in D' : \left|D\right| > 1 \}, k)$}{
+                \nl $\KwSty{return}~\KwSty{true}$ \;
+            }
+        }
+    }
+}
+\bigskip
+\nl $\FuncSty{propagate}$ (GraphPairs $L$, Domains $D$) $\rightarrow$ Bool \;
+\nl \Begin{
+    \nl \While{\KwSty{true}}{
+        \nl \If{\textnormal{no unit domains remain}}{
+            \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
+                \nl $\KwSty{return}~\KwSty{false}$ \;
+            }
+        }
+        \nl \lIf{$\textnormal{no unit domains remain}$}{$\KwSty{return}~\KwSty{true}$}
+        \nl $D_v = \{ v' \} \gets \textnormal{a unit domain from}~D$ \;
+        \nl \ForEach{$D_w \in D \setminus \{ D_v \}$}{
+            \nl $D_w \gets D_w \setminus \{ v' \}$ \label{line:removev} \;
+            \nl \ForEach{$(P,\,T) \in L$}{
+                \nl \If{$v \sim_P w$}{
+                    \nl $D_w \gets D_w \cap \left(\N_T(v') \cup \textnormal{wildcards}\right)$
+                }
+            }
+            \nl \lIf{$D_w = \emptyset$}{$\KwSty{return}~\KwSty{false}$}
+        }
+    }
+}
+\bigskip
+\nl $\FuncSty{allDifferent}$ (Domains $D$) $\rightarrow$ Bool \;
+\nl \Begin{
+\nl $(F,\,H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,\emptyset,\,0)$ \;
+\nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
+    \nl $F \gets F + v$ \;
+    \nl $D_v \gets D_v \setminus H$ \label{line:elimhall} \;
+    \nl $(A,\,n) \gets (A \cup D_v,\,n + 1)$ \label{line:acc} \;
+    \nl \lIf{$D_v = \emptyset~\KwSty{or}~|A| < n$}{$\KwSty{return}~\KwSty{false}$\label{line:failhall}}
+    \nl \lIf{$|A| = n$}{$(H,\,A,\,n) \gets (H \cup A,\,\emptyset,\,0)$\label{line:hall}}
+}
+\nl $\KwSty{return}~\KwSty{true}$ \;
+}
+\end{multicols}
+\vspace*{0.4cm}% bug in algorithm2e + multicol: incorrect space left above the vertical line
+\caption{An algorithm for the $k$-less subgraph isomorphism problem.}
+\label{algorithm:sip}
+\end{algorithm*}
+
 \section{Empirical Evaluation}

### 2016-09-01 paper/paper.tex
\left| \right| and Craigs EPSRC grant number

--- 2016-09-01 paper/paper.tex
@@
 \author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
-Research Council [grant number EP/K503058/1]} \and Craig Reilly \\
+Research Council [grant number EP/K503058/1]} \and Craig Reilly\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M506539/1]} \\
 University of Glasgow, Glasgow, Scotland \\
@@
 Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
-implies that $|\nds(p)| -k \leq |\nds(t)|$.
+implies that $|\nds(p)| -k \leq \left| \nds(t) \right| $.
 
-Also, $p \lessmap{k} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
-is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
+Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$
+is some subset of $P$ with $\left| P_k \right| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
 each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
@@
 \end{align*}
-So $\paths(p,q,2) = | \N(p)\cap \N(q)| \leq deg(p)$.
+So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq deg(p)$.
 
@@
 \[
-|\N(p)\cap \N(q)| - k \leq deg(p) - k \leq deg(t).
+\left| \N(p)\cap \N(q)\right| - k \leq deg(p) - k \leq deg(t).
 \]
-As $|\N(p)\cap \N(q)|\leq deg(p) \leq |\N(t)\cap \N(u)|\leq deg(t)$, we have
+As $\left|\N(p)\cap \N(q)\right|\leq deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq deg(t)$, we have
 \[
-|\N(p)\cap \N(q)| - k \leq deg(p) - k\leq |\N(t)\cap \N(u)|\leq deg(t)
+\left|\N(p)\cap \N(q)\right| - k \leq deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq deg(t)
 \]

### 2016-09-02 paper/paper.tex
A bit of writing and moving

@@
 
+The \emph{complement} of a graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are
+non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$. The
+following proposition follows directly from the definitions.
+
+\begin{proposition}\label{prop:comp}
+Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P
+\hookrightarrow T$ if and only if $i$ satisfies both the definition of $P \rightarrowtail T$ and
+of $\bar{P} \rightarrowtail \bar{T}$.
+Similarly, $i$ satisfies the definition of $P
+\lessind{k} T$ if and only if $i$ satisfies both the definition of $P \lessnonind{k} T$ and of
+$\bar{P}
+\lessnonind{k} \bar{T}$.
+\end{proposition}
+
 A common induced subgraph of graphs $G$ and $H$ is a graph $P$, together with two induced subgraph
@@
 
+For both subgraph isomorphism and maximum common subgraph, constraint-based models are the best
+approach (although constraint programming toolkits are not used, to facilitate better memory layouts
+and propagation queues). For both problems, we create a variable for each vertex in the pattern
+graph (the smaller graph, in the case of maximum common subgraph), with domains ranging over the
+vertices in the target graph (the larger graph). For maximum common subgraph, each domain is given
+an additional $\bot$ value, meaning ``unmapped''.
+
+We also have constraints for adjacency and non-adjacency. For the maximum common subgraph case,
+$\bot$ is ignored.
+
+In our algorithm we make use of \cref{prop:comp} by seeking an $i$ which simultaneously satisfies $P
+\rightarrowtail T$ and $\bar{P} \rightarrowtail \bar{T}$ when searching for an induced subgraph
+isomorphism.  Further, \cref{prop:comp} tells us that every induced subgraph isomorphism is
+equivalent to simultaneous non-induced subgraph isomorphisms both $P$ and $T$ as well as their
+complements.
+
+All different.
+
+For subgraph isomorphism, we can also do domain filtering at the top of search. We discuss this in
+??. Additional constraints, discuss this in ??.
+
 \subsection{Experimental Setup}
-
-\section{Relationship between non-induced and induced subgraph isomorphism}
-
-The \emph{complement} of a graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.
-
-\begin{proposition}\label{prop:comp}
-Let $i$ be an assignment of $T$ vertices to $P$ vertices.
-Then $i$ satisfies the definition of $P \hookrightarrow T$ if and only if both $i$ satisfies the definition of $P \rightarrowtail T$ and $\bar{P} \rightarrowtail \bar{T}$.
-\end{proposition}
-
-\begin{proof}
-Follows directly from the definition of an induced subgraph isomorphism and the definition of the complement of a graph.  Could flesh this out if we need to fill up space and look cleverer??
-\end{proof}
-
-\begin{corollary}
-Let $i$ be an assignment of $T$ vertices to $P$ vertices.
-Then $i$ satisfies the definition of $P \lessind{k} T$ if and only if both $i$ satisfies the definition of $P \lessnonind{k} T$ and $\bar{P} \lessnonind{k} \bar{T}$.
-\end{corollary}
-
-Should we just give the corollary as the proof??
-
-In our algorithm we make use of \cref{prop:comp} by seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\bar{P} \rightarrowtail \bar{T}$ when searching for an induced subgraph isomorphism.
-Further, \cref{prop:comp} tells us that every induced subgraph isomorphism is equivalent to simultaneous non-induced subgraph isomorphisms both $P$ and $T$ as well as their complements.
 

### 2016-09-02 paper/paper.tex
Finish Craig's job

@@
 many vertices as possible. An induced $k$-less subgraph isomorphism $P \lessind{k} T$ is equivalent
-to a common induced subgraph of $P$ and $T$ with $|\V(P)| - k$ vertices.
+to a common induced subgraph of $P$ and $T$ with $\left|\V(P)\right| - k$ vertices.
 
@@
 Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
-implies that $|\nds(p)| -k \leq \left| \nds(t) \right| $.
+implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.
 
@@
     \nl $(A,\,n) \gets (A \cup D_v,\,n + 1)$ \label{line:acc} \;
-    \nl \lIf{$D_v = \emptyset~\KwSty{or}~|A| < n$}{$\KwSty{return}~\KwSty{false}$\label{line:failhall}}
-    \nl \lIf{$|A| = n$}{$(H,\,A,\,n) \gets (H \cup A,\,\emptyset,\,0)$\label{line:hall}}
+    \nl \lIf{$D_v = \emptyset~\KwSty{or}~\left|A\right| < n$}{$\KwSty{return}~\KwSty{false}$\label{line:failhall}}
+    \nl \lIf{$\left|A\right| = n$}{$(H,\,A,\,n) \gets (H \cup A,\,\emptyset,\,0)$\label{line:hall}}
 }

### 2016-09-02 paper/paper.tex
Advanced box moving skills
More writing

@@
 vertices, the state of the art for the maximum common subgraph problem becomes computationally
-infeasible at only 35 vertices when working with unlabelled graphs \citep{CP2016MCSPaper}. This is
+infeasible at only 35 vertices when working with unlabelled graphs \citep{DBLP:conf/cp/McCreeshNPS16}. This is
 largely because strong inference, based upon the degrees of vertices
@@
 For subgraph isomorphism, we can also do domain filtering at the top of search. We discuss this in
-??. Additional constraints, discuss this in ??.
+\cref{section:degreefiltering}. Additional constraints, discuss this in \cref{section:pathfiltering}.
 
@@
 
-\section{Domain Filtering using Degrees}
+We perform our experiments on systems with dual Intel Xeon CPU E5-2640 processors with 64GBytes of
+RAM, running Ubuntu 14.04. Our algorithm was implemented in C++\footnote{URL removed for anonymous
+review}, and source code was compiled using
+GCC 5.3.0. We used a timeout of 1,000 seconds for each instance.
+
+For datasets, we use the same 5,725 instances used in a recent work on portfolios of algorithms for
+subgraph isomorphism \cite{thelionpaper}. This collection includes randomly generated scale-free
+graphs \cite{constraints10}, an assortment of real-world graphs of varying sizes \cite{LV02},
+randomly generated graph pairs (using bounded degree, regular mesh, and uniform models; all are
+satisfiable), segmented images~\cite{pr15,cviu11}, meshes from modelling 3D objects \cite{cviu11},
+and graphs close to the satisfiable-unsatisfiable phase transition
+\cite{DBLP:conf/ijcai/McCreeshPT16}; all these instances are available in a simple text
+format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.
+
+?? Note about the size of these instances, and how they're much larger than MCS instances.
+
+\section{Domain Filtering using Degrees}\label{section:degreefiltering}
 
@@
 \[
-\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t).
+\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
 \]
@@
 
-\section{Filtering During Search Using Paths}
+\section{Filtering During Search Using Paths}\label{section:pathfiltering}
 
@@
 \[
-\paths(p, q, 2) - k \leq \paths(t, u, 2).
+\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
 \]

### 2016-09-02 code/sequential.cc
It's a unit domain if it just contains wildcards

@@ -573,8 +573,9 @@ namespace
 
         auto select_unit_domain(Domains & domains) -> typename Domains::iterator
         {
-            return find_if(domains.begin(), domains.end(), [] (const auto & a) {
-                    return (! a.fixed) && 1 == a.values.count();
+            return find_if(domains.begin(), domains.end(), [&] (const auto & a) {
+                    auto c = a.values.count();
+                    return (! a.fixed) && (1 == c || (c > 1 && a.values.find_first() >= wildcard_start));
                     });
         }
 

### 2016-09-02 code/sequential.cc
Slightly fasterer

@@ -574,8 +574,12 @@ namespace
         auto select_unit_domain(Domains & domains) -> typename Domains::iterator
         {
             return find_if(domains.begin(), domains.end(), [&] (const auto & a) {
-                    auto c = a.values.count();
-                    return (! a.fixed) && (1 == c || (c > 1 && a.values.find_first() >= wildcard_start));
+                    if (! a.fixed) {
+                        auto c = a.values.count();
+                        return 1 == c || (c > 1 && a.values.find_first() >= wildcard_start);
+                    }
+                    else
+                        return false;
                     });
         }
 

### 2016-09-02 code/sequential.cc
Some stats which might tell us something fun

@@ -417,6 +417,13 @@ namespace
             }
 
             if (params.expensive_stats) {
+                Bitset_ initial_domains_union = Bitset_(domain_size);
+                for (unsigned p = 0 ; p < pattern.size() ; ++p)
+                    initial_domains_union |= initial_domains[p].values;
+
+                result.stats.emplace("UA", to_string(initial_domains_union.count()));
+                result.stats.emplace("UP", to_string(domain_size));
+
                 vector<pair<Domain *, unsigned> > assignments;
 
                 for (auto & d : initial_domains)

### 2016-09-02 clique/clique.cc
Add clique code

@@ -1,0 +1,238 @@
+/* vim: set sw=4 sts=4 et foldmethod=syntax : */
+
+#include "clique.hh"
+#include "bit_graph.hh"
+#include "template_voodoo.hh"
+
+#include <algorithm>
+#include <limits>
+#include <iostream>
+#include <atomic>
+#include <mutex>
+
+namespace
+{
+    using Association = std::map<std::pair<unsigned, unsigned>, unsigned>;
+    using AssociatedEdges = std::vector<std::pair<unsigned, unsigned> >;
+
+    auto modular_product(const VFGraph & g1, const VFGraph & g2) -> std::pair<Association, AssociatedEdges>
+    {
+        unsigned next_vertex = 0;
+        Association association;
+        AssociatedEdges edges;
+
+        for (unsigned l = 0 ; l < std::min(g1.vertices_by_label.size(), g2.vertices_by_label.size()) ; ++l)
+            for (unsigned v1 : g1.vertices_by_label[l])
+                for (unsigned v2 : g2.vertices_by_label[l])
+                    for (unsigned m = 0 ; m < std::min(g1.vertices_by_label.size(), g2.vertices_by_label.size()) ; ++m)
+                        for (unsigned w1 : g1.vertices_by_label[m])
+                            for (unsigned w2 : g2.vertices_by_label[m])
+                                if (v1 != w1 && v2 != w2
+                                        && (g1.edges[v1][v1] == g2.edges[v2][v2])
+                                        && (g1.edges[w1][w1] == g2.edges[w2][w2])
+                                        && (g1.edges[v1][w1] == g2.edges[v2][w2])
+                                        && (g1.edges[w1][v1] == g2.edges[w2][v2])) {
+
+                                    if (! association.count({v1, v2}))
+                                        association.insert({{v1, v2}, next_vertex++});
+                                    if (! association.count({w1, w2}))
+                                        association.insert({{w1, w2}, next_vertex++});
+
+                                    edges.push_back({association.find({v1, v2})->second, association.find({w1, w2})->second});
+                                }
+
+        return { association, edges };
+    }
+
+    auto unproduct(const Association & association, unsigned v) -> std::pair<unsigned, unsigned>
+    {
+        for (auto & a : association)
+            if (a.second == v)
+                return a.first;
+
+        throw "oops";
+    }
+
+    struct Incumbent
+    {
+        std::atomic<unsigned> value{ 0 };
+
+        std::mutex mutex;
[…]

### 2016-09-02 clique/solve_max_common_subgraph.cc

@@ -1,0 +1,291 @@
+/* vim: set sw=4 sts=4 et foldmethod=syntax : */
+
+#include "clique.hh"
+
+#include <boost/program_options.hpp>
+#include <boost/regex.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <exception>
+#include <cstdlib>
+#include <chrono>
+#include <thread>
+#include <mutex>
+#include <condition_variable>
+#include <algorithm>
+
+namespace po = boost::program_options;
+
+using std::chrono::steady_clock;
+using std::chrono::duration_cast;
+using std::chrono::milliseconds;
+
+namespace
+{
+    class GraphFileError :
+        public std::exception
+    {
+        private:
+            std::string _what;
+
+        public:
+            GraphFileError(const std::string & filename, const std::string & message) throw ();
+
+            auto what() const throw () -> const char *;
+    };
+
+    GraphFileError::GraphFileError(const std::string & filename, const std::string & message) throw () :
+        _what("Error reading graph file '" + filename + "': " + message)
+    {
+    }
+
+    auto GraphFileError::what() const throw () -> const char *
+    {
+        return _what.c_str();
+    }
+
+    auto read_word(std::ifstream & infile) -> unsigned
+    {
+        unsigned x;
+        infile >> x;
+        return x;
+    }
+
+    auto read_lad(const std::string & filename) -> VFGraph
+    {
+        VFGraph result;
+
+        std::ifstream infile{ filename };
+        if (! infile)
+            throw GraphFileError{ filename, "unable to open file" };
+
+        result.size = read_word(infile);
+        if (! infile)
+            throw GraphFileError{ filename, "error reading size" };
+
+        result.vertices_by_label.resize(1);
+        result.vertex_labels.resize(result.size);
+
+        result.edges.resize(result.size);
+        for (auto & e : result.edges)
+            e.resize(result.size);
+
+        for (unsigned r = 0 ; r < result.size ; ++r) {
+            result.vertex_labels.at(r) = 0;
+            result.vertices_by_label.at(0).push_back(r);
+        }
+
+        for (unsigned r = 0 ; r < result.size ; ++r) {
+            unsigned c_end = read_word(infile);
+            if (! infile)
+                throw GraphFileError{ filename, "error reading edges count" };
+
+            for (unsigned c = 0 ; c < c_end ; ++c) {
+                unsigned e = read_word(infile);
+
+                if (e >= result.size)
[…]

### 2016-09-02 paper/paper.tex
Wildcards as unit domains

@@
 
+?? Also the clique encoding.
+
 \subsection{Experimental Setup}
@@
 
-?? Note about the size of these instances, and how they're much larger than MCS instances.
+?? Using the French code, and the Glasgow clique code.
+
+Note that many of these instances are \emph{much} larger than were used in the recent comparison of
+maximum common subgraph algorithms by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs,
+they used pairs of graphs with up to 35 vertices in each, whilst our dataset contains patterns with
+up to ?? vertices and targets with up to ?? vertices. This causes problems: both the maximum common
+subgraph algorithm and the clique encoding require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$
+memory. For maximum common subgraph, 1,560 of the instances cannot fit in the amount of RAM we have
+available---we treat these instances as having timed out. The situation for the clique encoding is
+even worse, and 3,653 of these instances do not fit in RAM. In contrast, the approach we discuss
+here requires only $O(\left|\V(P)\right|^2\left|\V(T)\right|)$ space (which would still be a problem
+on some desktop machines, but not on our server hardware).
 
@@
     \nl \While{\KwSty{true}}{
-        \nl \If{\textnormal{no unit domains remain}}{
+        \nl \If{\textnormal{no effectively-unit (treating all wildcard values as a single value)
+        domains remain}}{
             \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
@@
         }
-        \nl \lIf{$\textnormal{no unit domains remain}$}{$\KwSty{return}~\KwSty{true}$}
-        \nl $D_v = \{ v' \} \gets \textnormal{a unit domain from}~D$ \;
+        \nl \If{\textnormal{no effectively-unit domains remain}}{
+            \nl $\KwSty{return}~\KwSty{true}$ \;
+        }
+        \nl $D_v \gets \textnormal{an effectively-unit domain from}~D$ \;
+        \nl $v' \gets $ the single value in $D_v$, or an arbitrary wildcard value if there is more
+        than one \;
         \nl \ForEach{$D_w \in D \setminus \{ D_v \}$}{

### 2016-09-02 code/sequential.cc
Optional ILF support

@@ -353,67 +353,92 @@ namespace
                         ++cn;
                     }
                 }
-
-                for (unsigned t = 0 ; t < target.size() ; ++t) {
-                    unsigned cn = 0;
-                    for (auto & c : adjacency_constraints) {
-                        t_nds[cn].resize(target.size());
-                        for (unsigned q = 0 ; q < target.size() ; ++q)
-                            if (c.second[t][q])
-                                t_nds[cn][t].push_back(c.second[q].count());
-                        sort(t_nds[cn][t].begin(), t_nds[cn][t].end(), greater<unsigned>());
-                        ++cn;
-                    }
-                }
             }
 
             // build up initial domains
-            for (unsigned p = 0 ; p < pattern.size() ; ++p) {
-                initial_domains[p].v = p;
-                initial_domains[p].values = Bitset_(domain_size);
-                initial_domains[p].fixed = false;
+            Bitset_ initial_domains_union = Bitset_(domain_size);
+            for (unsigned q = 0 ; q < domain_size ; ++q)
+                initial_domains_union.set(q);
 
-                // decide initial domain values
-                for (unsigned t = 0 ; t < target.size() ; ++t) {
-                    bool ok = true;
+            while (true) {
+                if (params.nds) {
+                    t_nds = vector<vector<vector<unsigned> > >(adjacency_constraints.size());
 
-                    for (auto & c : adjacency_constraints) {
-                        // check loops
-                        if (c.first[p][p] && ! c.second[t][t])
-                            ok = false;
-
-                        // check degree
-                        if (ok && params.degree && 0 == params.except && ! (c.first[p].count() <= c.second[t].count()))
-                            ok = false;
-
-                        // check except-degree
-                        if (ok && params.degree && params.except >= 1 && ! (c.first[p].count() <= c.second[t].count() + params.except))
-                            ok = false;
-
-                        if (! ok)
-                            break;
+                    for (unsigned t = 0 ; t < target.size() ; ++t) {
+                        unsigned cn = 0;
+                        for (auto & c : adjacency_constraints) {
+                            t_nds[cn].resize(target.size());
+                            for (unsigned q = 0 ; q < target.size() ; ++q)
+                                if (c.second[t][q])
+                                    t_nds[cn][t].push_back((c.second[q] & initial_domains_union).count());
+                            sort(t_nds[cn][t].begin(), t_nds[cn][t].end(), greater<unsigned>());
+                            ++cn;
+                        }
                     }
[…]

### 2016-09-02 code/solve_subgraph_isomorphism.cc

@@ -114,6 +114,7 @@ auto main(int argc, char * argv[]) -> int
             ("degree",                                "Use degree filtering")
             ("nds",                                   "Use NDS filtering")
             ("cnds",                                  "Use Combined NDS filtering")
+            ("ilf",                                   "Use ILF filtering")
             ("except",             po::value<int>(),  "Allow this many pattern vertices to be excluded")
             ("high-wildcards",                        "Treat wildcard vertices as having high degree")
             ("induced",                               "Induced")
@@ -183,6 +184,7 @@ auto main(int argc, char * argv[]) -> int
         params.cnds = options_vars.count("cnds");
         params.expensive_stats = options_vars.count("expensive-stats");
         params.high_wildcards = options_vars.count("high-wildcards");
+        params.ilf = options_vars.count("ilf");
         if (options_vars.count("except"))
             params.except = options_vars["except"].as<int>();
 

### 2016-09-02 paper/paper.tex
Tweaking
I tried ILF, it's not very helpful and is hard to explain

@@
 
+?? Explain effectively-unit domain, multiple $\bot$ values.
+
 \subsection{Experimental Setup}
@@
 \end{figure}
+
+?? Talk about iterating, what to do when a vertex disappears from all target graphs.
 
@@
     \nl \While{\KwSty{true}}{
-        \nl \If{\textnormal{no effectively-unit (treating all wildcard values as a single value)
-        domains remain}}{
+        \nl \If{\textnormal{no effectively-unit domains (treating all wildcard values as a single
+        value) remain}}{
             \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
@@
 \nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
-    \nl $F \gets F + v$ \;
+    \nl $F \gets F \cup \{ v \}$ \;
     \nl $D_v \gets D_v \setminus H$ \label{line:elimhall} \;

### 2016-09-07 paper/paper.tex
More compact notation
minute notation fixes.

@@
 \usepackage{color}
-\newcommand{\todo}[1]{{\color{red} {[}{#1}{]}}}
+\newcommand{\todo}[1]{{\color{red} {?? [}{#1}{]}}}
 
@@
 \begin{corollary}
-Since both $\nds(p)$ and $\nds(t)$ are non-ascending, wlog we can replace $S \setminus S_k$ from the definition of $S \lesspreceq{k}
-T$ with $S[k, n]$.
+Since both $\nds(p)$ and $\nds(t)$ are non-ascending, without loss of generality we can replace
+$S \setminus S_k$ from the definition of $S \lesspreceq{k} T$ with $S[k, n]$.
 \end{corollary}
@@
 \begin{proof}
-Sketch?? Let $S_k$ be some elements of the sequence which aren't the first $k$ elements.  Then these elements are less than or equal to the first $k$ elements.
+\todo{Sketch?? Let $S_k$ be some elements of the sequence which aren't the first $k$ elements.  Then these elements are less than or equal to the first $k$ elements.}
 \end{proof}
@@
 \end{align*}
-So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq deg(p)$.
+So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
 
@@
 \[
-\left| \N(p)\cap \N(q)\right| - k \leq deg(p) - k \leq deg(t).
+\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
 \]
-As $\left|\N(p)\cap \N(q)\right|\leq deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq deg(t)$, we have
+As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
 \[
-\left|\N(p)\cap \N(q)\right| - k \leq deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq deg(t)
+\left|\N(p)\cap \N(q)\right| - k \leq \deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
 \]
@@
         \nl \ForEach{$(P,\,T) \in L$}{
-            \nl $D_v \gets D_v \cap \{ w \in D_v : $ \\
-            \hspace*{7em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
-            \hspace*{7em}$\nds_P(v) \lesspreceq{k} \nds_T(w)\}$ \;
+            \nl $D_v \gets \{ w \in D_v : $ \\
+            \hspace*{4em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
+            \hspace*{4em}$\nds_P(v) \lesspreceq{k} \nds_T(w)\}$ \;
         }

### 2016-09-08 paper/paper.tex
Muck around with abstract and intro

@@
     common subgraph problem, which is much more computationally challenging in practice than
-    subgraph isomorphism. We present and evaluate a new constraint-style algorithm which lies
-    between these two approaches, for cases when nearly all of the pattern is present.
+    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
+    vertices from the pattern can be found in the target. This allows us to develop slightly
+    weakened forms of certain invariants from subgraph isomorphism, retaining most of their
+    effectiveness. For small values of $k$, we can solve this problem on most of the standard problem
+    instances used to benchmark subgraph isomorphism algorithms, despite these instances being much
+    too large for current maximum common subgraph algorithms to handle.
 \end{abstract}
@@
 vertices, the state of the art for the maximum common subgraph problem becomes computationally
-infeasible at only 35 vertices when working with unlabelled graphs \citep{DBLP:conf/cp/McCreeshNPS16}. This is
-largely because strong inference, based upon the degrees of vertices
-\citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
+infeasible at only 35 vertices when working with unlabelled graphs
+\citep{DBLP:conf/cp/McCreeshNPS16}. This is largely because strong inference, based upon the degrees
+of vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
 \citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
-but not maximum common subgraph, and so the state space in the former is much more restricted. In
-this work we discuss an intermediate problem, where we must map all but $k$ vertices of the pattern
-graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then weakened
-forms of degree and path based filterings are still effective in pruning the search space and
-providing additional constraints respectively. We then show that combining these techniques does
-lead to a practical algorithm which can scale to work with the families of graphs commonly used to
-benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in a substantial
-portion of ; in many more cases, we can at least obtain an upper bound.
+but not maximum common subgraph, and so the state space in the former is much more restricted,
+whilst filtering during search is vastly stronger.
+
+In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
+pattern graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then
+weakened forms of degree and path based filterings are still effective in pruning the initial search
+space and in providing additional constraints respectively. We then show that combining these
+techniques leads to a practical algorithm which can scale to work with the families of graphs
+commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in
+a substantial portion of ??; in ?? more cases, we can at least obtain an upper bound.
 

### 2016-09-08 paper/paper.tex
minor word changes to abstract.

@@
     When a small pattern graph does not occur inside a larger target graph, we can ask how to find
-    ``as much of the pattern as possible'' inside the target graph. In general, this is maximum
-    common subgraph problem, which is much more computationally challenging in practice than
-    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
-    vertices from the pattern can be found in the target. This allows us to develop slightly
-    weakened forms of certain invariants from subgraph isomorphism, retaining most of their
-    effectiveness. For small values of $k$, we can solve this problem on most of the standard problem
-    instances used to benchmark subgraph isomorphism algorithms, despite these instances being much
-    too large for current maximum common subgraph algorithms to handle.
+    ``as much of the pattern as possible'' inside the target graph. In general, this is known as
+    the maximum common subgraph problem, which is much more computationally challenging in practice
+    than subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
+    vertices from the pattern can be found in the target. This allows for the development of
+    slightly weakened forms of certain invariants from subgraph isomorphism, while retaining most
+    of their effectiveness. For small values of $k$, we solve this problem on most of the standard
+    problem instances used to benchmark subgraph isomorphism algorithms, despite these instances
+    being too large for current maximum common subgraph algorithms to handle.
 \end{abstract}

### 2016-09-08 paper/paper.tex
more changes.

@@
     than subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
-    vertices from the pattern can be found in the target. This allows for the development of
-    slightly weakened forms of certain invariants from subgraph isomorphism, while retaining most
-    of their effectiveness. For small values of $k$, we solve this problem on most of the standard
+    vertices from the pattern can be found in the target graph. This allows for the development of
+    slightly weakened forms of certain invariants from subgraph isomorphism, while retaining their
+    effectiveness. For small values of $k$, we solve this problem on most of the standard
     problem instances used to benchmark subgraph isomorphism algorithms, despite these instances

### 2016-09-08 paper/paper.tex
Better abstract

@@
     When a small pattern graph does not occur inside a larger target graph, we can ask how to find
-    ``as much of the pattern as possible'' inside the target graph. In general, this is known as
-    the maximum common subgraph problem, which is much more computationally challenging in practice
-    than subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
+    ``as much of the pattern as possible'' inside the target graph. In general, this is known as the maximum
+    common subgraph problem, which is much more computationally challenging in practice than
+    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
     vertices from the pattern can be found in the target graph. This allows for the development of
-    slightly weakened forms of certain invariants from subgraph isomorphism, while retaining their
-    effectiveness. For small values of $k$, we solve this problem on most of the standard
-    problem instances used to benchmark subgraph isomorphism algorithms, despite these instances
-    being too large for current maximum common subgraph algorithms to handle.
+    slightly weakened forms of certain invariants from subgraph isomorphism which are based upon degree and
+    number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
+    their effectiveness. We are then able to solve this problem on most of the standard problem
+    instances used to benchmark subgraph isomorphism algorithms, despite these instances being much
+    too large for current maximum common subgraph algorithms to handle.
 \end{abstract}

### 2016-09-08 paper/paper.tex
added reminders
added reformulation comment

@@
 \end{abstract}
-
+\todo{try code on MCS instances}
 \section{Introduction}
-
+\todo{talk about subgraph isomorphism applications, particularly vision}
+\todo{talk about reformulating}
 The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger

### 2016-09-08 paper/paper.tex
more comment reminders.

@@
 \begin{abstract}
+    \todo{anonymise abstract}
     When a small pattern graph does not occur inside a larger target graph, we can ask how to find

### 2016-09-08 paper/paper.tex
fixes to abstract.

@@
     number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
-    their effectiveness. We are then able to solve this problem on most of the standard problem
-    instances used to benchmark subgraph isomorphism algorithms, despite these instances being much
+    their effectiveness. We are then able to solve this problem on the standard problem
+    instances used to benchmark subgraph isomorphism algorithms, despite these instances being
     too large for current maximum common subgraph algorithms to handle.

### 2016-09-08 paper/paper.tex
added sip to abstract.

@@
     number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
-    their effectiveness. We are then able to solve this problem on the standard problem
+    their effectiveness. We are then able to solve this problem on the standard SIP problem
     instances used to benchmark subgraph isomorphism algorithms, despite these instances being

### 2016-09-09 paper/paper.tex
loop complement \lcomp operator.
loopcomp name update.
fixed loop complement spacing.
loop complements

@@
 \newcommand{\nds}{\operatorname{S}}
+\newcommand{\loopcomp}[1]{\overset{\multimap}{#1}}
 % to do comments
@@
 
-The \emph{complement} of a graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are
-non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$. The
-following proposition follows directly from the definitions.
+The \emph{complement} of a (simple) graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are
+non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.
+The \emph{loop complement} of a graph $P$ is the graph $\loopcomp{P}$.
+The constructcion of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.
+When solving an induced subgraph isomorphism problem we make use of the loop complement; we care about mapping vertices with loops to vertices with loops, and edges without loops to vertices without loops.
+(Although when we filter by paths we make use of the complement rather than the loop complement.)  The following proposition follows directly from the definitions.
 
@@
 \hookrightarrow T$ if and only if $i$ satisfies both the definition of $P \rightarrowtail T$ and
-of $\bar{P} \rightarrowtail \bar{T}$.
+of $\loopcomp{P} \rightarrowtail \loopcomp{T}$.
 Similarly, $i$ satisfies the definition of $P
 \lessind{k} T$ if and only if $i$ satisfies both the definition of $P \lessnonind{k} T$ and of
-$\bar{P}
-\lessnonind{k} \bar{T}$.
+$\loopcomp{P}
+\lessnonind{k} \loopcomp{T}$.
 \end{proposition}

### 2016-09-09 code/sequential.cc
Support VF format graphs

@@ -848,8 +848,10 @@ auto sequential_ix_subgraph_isomorphism(const pair<Graph, Graph> & graphs, const
             modified_result.stats.emplace("SIZE", to_string(graphs.first.size() - modified_params.except));
             return modified_result;
         }
-        else
+        else {
+            cerr << "-- " << pass_time.count() << " <" << graphs.first.size() - modified_params.except << endl;
             modified_result.stats.emplace("FAIL" + to_string(modified_params.except), to_string(pass_time.count()));
+        }
 
         if (++modified_params.except >= graphs.first.size())
             break;

### 2016-09-09 code/solve_subgraph_isomorphism.cc

@@ -1,6 +1,7 @@
 /* vim: set sw=4 sts=4 et foldmethod=syntax : */
 
 #include "lad.hh"
+#include "vf.hh"
 #include "dimacs.hh"
 #include "sequential.hh"
 
@@ -108,7 +109,7 @@ auto main(int argc, char * argv[]) -> int
         display_options.add_options()
             ("help",                                  "Display help information")
             ("timeout",            po::value<int>(),  "Abort after this many seconds")
-            ("format",             po::value<std::string>(), "Specify graph file format (lad or dimacs)")
+            ("format",             po::value<std::string>(), "Specify graph file format (lad, dimacs or vf)")
             ("d2graphs",                              "Use d2 graphs")
             ("d2cgraphs",                             "Use d2 complement graphs")
             ("degree",                                "Use degree filtering")
@@ -195,6 +196,8 @@ auto main(int argc, char * argv[]) -> int
                 read_function = read_lad;
             else if (options_vars["format"].as<std::string>() == "dimacs")
                 read_function = read_dimacs;
+            else if (options_vars["format"].as<std::string>() == "vf")
+                read_function = read_vf;
             else {
                 std::cerr << "Unknown format " << options_vars["format"].as<std::string>() << std::endl;
                 return EXIT_FAILURE;

### 2016-09-10 paper/paper.tex
added distinct to the definition of the complement
Anonymouse

@@
 \newcommand{\nds}{\operatorname{S}}
-\newcommand{\loopcomp}[1]{\overset{\multimap}{#1}}
+\newcommand{\loopcomp}[1]{\oset[.1ex]{\multimap}{#1}}
 % to do comments
@@
 
+\makeatletter
+\newcommand{\oset}[3][0ex]{%
+  \mathrel{\mathop{#3}\limits^{
+    \vbox to#1{\kern-2\ex@
+    \hbox{$\scriptstyle#2$}\vss}}}}
+\makeatother
+
 \title{Between Subgraph Isomorphism and Maximum Common Subgraph}
 
-\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
-Research Council [grant number EP/K503058/1]} \and Craig Reilly\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M506539/1]} \\
-University of Glasgow, Glasgow, Scotland \\
-ruth.hoffmann@glasgow.ac.uk \and \{c.mccreesh.1,c.reilly.2\}@research.gla.ac.uk}
+\author{Anonymous \and Anonymous\thanks{This work was supported by an anonymous funding agency [grant number 12345]} \and Anonymous\thanks{This work was supported by an anonymous funding agency [grant number 67890]} \\
+Top Secret Research Lab, Atlantis \\
+anonymous@anonymous}
 
@@
     /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
-    /Author (Ruth Hoffmann and Ciaran McCreesh and Craig Reilly)
+    /Author (Anonymous and Anonymous and Anonymous)
 }
@@
 \begin{abstract}
-    \todo{anonymise abstract}
     When a small pattern graph does not occur inside a larger target graph, we can ask how to find
@@
 
-The \emph{complement} of a (simple) graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are
-non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.
+The \emph{complement} of a (simple) graph $P$ is the graph $\bar{P}~$.
+Adjacent distinct vertices in $P$ are non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.
 The \emph{loop complement} of a graph $P$ is the graph $\loopcomp{P}$.
@@
 \begin{figure}
-    \includegraphics*{gen-graph-ids.pdf}
+    % \includegraphics*{gen-graph-ids.pdf}
     \caption{We get domain filtering. Woohoo.}\label{figure:ids}
@@
 \begin{figure*}
-    \includegraphics*{gen-graph-constraints.pdf}\\[0.1cm]
-    \includegraphics*{gen-graph-constraints-induced.pdf}
+    % \includegraphics*{gen-graph-constraints.pdf}\\[0.1cm]
+    % \includegraphics*{gen-graph-constraints-induced.pdf}
     \caption{We get new constraints. More woohoo.}\label{figure:constraints}
@@
 \begin{figure}
-    \includegraphics*{gen-graph-runtimes.pdf}
+    % \includegraphics*{gen-graph-runtimes.pdf}
     \caption{Look how amazing our stuff is.}\label{figure:runtimes}
@@
 \begin{figure}
-    \includegraphics*{gen-graph-which-k-by-family.pdf}
+    % \includegraphics*{gen-graph-which-k-by-family.pdf}
     \caption{There are satisfiable instances for small values of $k$. Yay.}\label{figure:which-k}
@@
 \begin{figure}
-    \includegraphics*{gen-graph-versus-cp.pdf}
+    % \includegraphics*{gen-graph-versus-cp.pdf}
     \caption{A righteous spanking.}\label{figure:versus-cp}
@@
 
-\section*{Acknowledgements}
-
-We're not going to thank anyone, no, no.  Thanks to Frances for making us less smelly throughout the writing of the paper (by thieving toiletries from a fancy hotel).
+% \section*{Acknowledgements}
+% 
+% Thanks to Christine, Samba, Patrick.
 

### 2016-09-10 paper/paper.tex
Improverate the figures

@@
 \begin{figure}
-    % \includegraphics*{gen-graph-ids.pdf}
-    \caption{We get domain filtering. Woohoo.}\label{figure:ids}
+    \includegraphics*{gen-graph-ids.pdf}
+    \caption{The amount of domain reduction achieved for the induced problem, with increasing values
+    of $k$. The $y$ value shows for how many instances we may reduce the domain size to be at most
+    the $x$ proportion of the size the domains would be for the maximum common subgraph
+    problem.}\label{figure:ids}
 \end{figure}
@@
 \section{Filtering During Search Using Paths}\label{section:pathfiltering}
+
+\begin{figure*}[tb]
+    \centering
+    \includegraphics*{gen-graph-constraints-induced-0.pdf}
+    \includegraphics*{gen-graph-constraints-induced-1.pdf}
+    \includegraphics*{gen-graph-constraints-induced-2.pdf}
+    \includegraphics*{gen-graph-constraints-induced-3.pdf}
+    \includegraphics*{gen-graph-constraints-induced-4.pdf}
+    \includegraphics*{gen-graph-constraints-induced-5.pdf}
+
+    \caption{For the induced problem, the proportion of pairs of assignments from the filtered
+    domains which are not permitted simultaneously, without path constraints on the $x$-axis and
+    with path constraints on the $y$-axis, for increasing values of $k$.}\label{figure:constraints}
+\end{figure*}
 
@@
 graphs\footnote{Because of the large sizes of the domains, we randomly sample one million pairs
-rather than considering every pair. In some cases, we have nearly a thousand domains, each with nearly
-ten thousand values---a complete quadratic calculation involving even a trivial arithmetic operation
-on this would take many hours.}. For $k = 0$, we see many points above the $x-y$ diagonal, which
-shows that for many instances, we are able to create a substantial number of new constraints at the
-top of search; on the other hand, there are also points on the diagonal, which shows that sometimes
-this technique provides no benefit. (Occasionally, points fall below the $x-y$ diagonal. This is
-because the use of neighbourhood degree sequence reasoning on supplemental graphs can also lead to
-increased domain filtering, which could in turn eliminate a higher proportion of forbidden than
-permitted assignment pairs.) For $k = 1$ and $k = 2$, the proportion of points above the diagonal
-diminishes, but we are still able to create new constraints for many instances. By the time $k = 3$,
-most of the benefit is disappearing---although sometimes we are still able to make a difference, and
-bear in mind that sometimes adding just one new constrained pair can vastly reduce the search space.
-
-A closer inspection of the raw data shows that for $k = 3$, nearly all of the instances showing a
-strong improvement are from the ``LV'' family of graphs.
-
-\begin{figure*}
-    % \includegraphics*{gen-graph-constraints.pdf}\\[0.1cm]
-    % \includegraphics*{gen-graph-constraints-induced.pdf}
-    \caption{We get new constraints. More woohoo.}\label{figure:constraints}
-\end{figure*}
+rather than considering every pair. In some cases, we have nearly a thousand domains, each with
+nearly ten thousand values---a complete quadratic calculation involving even a trivial arithmetic
+operation on this would take many hours.}. For $k = 0$, we see many points above the $x-y$ diagonal,
+which shows that for many instances, we are able to create a substantial number of new constraints
+at the top of search; on the other hand, there are also points on the diagonal, which shows that
+sometimes this technique provides no benefit. (Occasionally, points fall below the $x-y$ diagonal.
+This is because the use of neighbourhood degree sequence reasoning on supplemental graphs can also
+lead to increased domain filtering, which could in turn eliminate a higher proportion of forbidden
+than permitted assignment pairs.) For $k = 1$ and $k = 2$, the proportion of points above the
+diagonal diminishes, but we are still able to create new constraints for many instances. By the time
+$k = 3$, most of the benefit is disappearing---although sometimes we are still able to make a
+difference, and bear in mind that sometimes adding just one new constrained pair can vastly reduce
+the search space.  A closer inspection of the raw data shows that for $k \ge 3$, nearly all of the
+instances showing a strong improvement are from the ``LV'' family of graphs.
 
@@
 \begin{figure}
-    % \includegraphics*{gen-graph-runtimes.pdf}
-    \caption{Look how amazing our stuff is.}\label{figure:runtimes}
+    \includegraphics*{gen-graph-runtimes.pdf}
+    \caption{The cumulative number of instances solved over time, for the induced and non-induced
+    problems, with different values of $k$. We also show the results of iteratively decreasing $k$
+    until a solution is found, and in the induced case, the performance of a leading maximum common
+    subgraph algorithm.}\label{figure:runtimes}
 \end{figure}
@@
 \begin{figure}
-    % \includegraphics*{gen-graph-which-k-by-family.pdf}
-    \caption{There are satisfiable instances for small values of $k$. Yay.}\label{figure:which-k}
+    \includegraphics*{gen-graph-which-k-by-family.pdf}
+    \caption{The proportion of instances, in different families, which become satisfiable for
+    increasing values of $k$. The larger instances are those where we can prove unsatisfiability for
+    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
+    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
 \end{figure}
@@
 \subsection{Solving from the Top Down}
-
-\begin{figure}
-    % \includegraphics*{gen-graph-versus-cp.pdf}
-    \caption{A righteous spanking.}\label{figure:versus-cp}
-\end{figure}
 

### 2016-09-11 paper/paper.tex
We don't need F without CBJ
Complements to the algorithm
Committing from 36,000ft

@@
 \Crefname{figure}{Figure}{Figures}
+
+\crefname{algocf}{Algorithm}{Algorithms}
+\Crefname{algocf}{Algorithm}{Algorithms}
 
@@
 commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in
-a substantial portion of ??; in ?? more cases, we can at least obtain an upper bound.
+a substantial portion of ??; in ?? more cases, we can at least obtain an upper bound. This is a
+significant improvement over state of the art maximum common subgraph solvers, which cannot even fit
+many of these instances in RAM.
 
@@
 
-The \emph{complement} of a (simple) graph $P$ is the graph $\bar{P}~$.
-Adjacent distinct vertices in $P$ are non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.
-The \emph{loop complement} of a graph $P$ is the graph $\loopcomp{P}$.
-The constructcion of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.
-When solving an induced subgraph isomorphism problem we make use of the loop complement; we care about mapping vertices with loops to vertices with loops, and edges without loops to vertices without loops.
-(Although when we filter by paths we make use of the complement rather than the loop complement.)  The following proposition follows directly from the definitions.
+The \emph{complement} of a (simple) graph $P$ is the graph $\shortoverline{P}~$.  Adjacent distinct
+vertices in $P$ are non-adjacent in $\shortoverline{P}$ while non-adjacent vertices in $P$ are
+adjacent in $\shortoverline{P}$.  The \emph{loop complement} of a graph $P$ is the graph
+$\loopcomp{P}$.  The construction of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however
+whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an
+induced subgraph isomorphism problem we make use of the loop complement; we care about mapping
+vertices with loops to vertices with loops, and vertices without loops to vertices without loops.
+(Although when we filter by paths we make use of the complement rather than the loop complement.)
+The following proposition follows directly from the definitions.
 
@@
 
-For both subgraph isomorphism and maximum common subgraph, constraint-based models are the best
-approach (although constraint programming toolkits are not used, to facilitate better memory layouts
-and propagation queues). For both problems, we create a variable for each vertex in the pattern
-graph (the smaller graph, in the case of maximum common subgraph), with domains ranging over the
-vertices in the target graph (the larger graph). For maximum common subgraph, each domain is given
-an additional $\bot$ value, meaning ``unmapped''.
+For both subgraph isomorphism and maximum common subgraph, constraint programming is the best known
+approach\footnote{Note that toolkits are not used, to facilitate better memory layouts and
+propagation queues, although the algorithms are heavily inspired by the constraint programming
+literature}. For both problems, we create a variable for each vertex in the pattern graph (the
+smaller graph, in the case of maximum common subgraph), with domains ranging over the vertices in
+the target graph (the larger graph). For maximum common subgraph, each domain is given an additional
+$\bot$ value, meaning ``unmapped''.
 
@@
 In our algorithm we make use of \cref{prop:comp} by seeking an $i$ which simultaneously satisfies $P
-\rightarrowtail T$ and $\bar{P} \rightarrowtail \bar{T}$ when searching for an induced subgraph
+\rightarrowtail T$ and $\loopcomp{P} \rightarrowtail \loopcomp{T}$ when searching for an induced subgraph
 isomorphism.  Further, \cref{prop:comp} tells us that every induced subgraph isomorphism is
@@
 
-All different.
+?? All different.
 
-For subgraph isomorphism, we can also do domain filtering at the top of search. We discuss this in
-\cref{section:degreefiltering}. Additional constraints, discuss this in \cref{section:pathfiltering}.
+For subgraph isomorphism, we can do domain filtering at the top of search, to reduce the initial
+sizes of domains---we discuss this in \cref{section:degreefiltering}. Subgraph isomorphism also
+allows us to generate additional implied constraints, which we discuss in
+\cref{section:pathfiltering}. Neither of these techniques are valid for the maximum common subgraph
+problem.
 
@@
 
+Some other forms do not translate. For example, another invariant which can be effective on regular
+graphs is to count the number of neighbours of a vertex which are present in a triangle. Removing a
+single vertex can alter this count arbitrarily, so we cannot make use of this fact.
+
 \begin{figure}
@@
     \caption{The amount of domain reduction achieved for the induced problem, with increasing values
-    of $k$. The $y$ value shows for how many instances we may reduce the domain size to be at most
-    the $x$ proportion of the size the domains would be for the maximum common subgraph
+    of $k$. The $y$ value shows for how many instances we may reduce the initial search space to be
+    at most the $x$ proportion of the size the search space would be for the maximum common subgraph
     problem.}\label{figure:ids}
@@
 
-To allow for fast propagation, we create supplemental graphs for paths of length 2, looking at
-counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).
-We then investigate whether this leads to new constraints being generated. By an assignment, we mean
-considering mapping a pattern vertex $p$ to a target vertex $t$ (and not $\bot$) which does not
-violate any loop constraints. An assignment pair is two assignments with distinct $p$ and distinct
-$t$, which we say is permitted if it does not violate any adjacency constraint. We define the
-permitted assignment pair ratio to be the proportion of assignment pairs which are permitted.
-Finally, we scatter plot the permitted assignment pair ratio with and without supplemental
-graphs\footnote{Because of the large sizes of the domains, we randomly sample one million pairs
-rather than considering every pair. In some cases, we have nearly a thousand domains, each with
-nearly ten thousand values---a complete quadratic calculation involving even a trivial arithmetic
-operation on this would take many hours.}. For $k = 0$, we see many points above the $x-y$ diagonal,
-which shows that for many instances, we are able to create a substantial number of new constraints
-at the top of search; on the other hand, there are also points on the diagonal, which shows that
-sometimes this technique provides no benefit. (Occasionally, points fall below the $x-y$ diagonal.
-This is because the use of neighbourhood degree sequence reasoning on supplemental graphs can also
-lead to increased domain filtering, which could in turn eliminate a higher proportion of forbidden
-than permitted assignment pairs.) For $k = 1$ and $k = 2$, the proportion of points above the
-diagonal diminishes, but we are still able to create new constraints for many instances. By the time
-$k = 3$, most of the benefit is disappearing---although sometimes we are still able to make a
-difference, and bear in mind that sometimes adding just one new constrained pair can vastly reduce
-the search space.  A closer inspection of the raw data shows that for $k \ge 3$, nearly all of the
-instances showing a strong improvement are from the ``LV'' family of graphs.
+Unlike in conventional subgraph isomorphism, we cannot extend this filtering to look at paths of
+length three: removing a single vertex can delete arbitrarily many such paths. We could count paths
+of any length which are vertex disjoint, although calculating this is too expensive to be useful in
+practice.
+
+To allow for fast propagation, rather than calculating paths dynamically, we follow the approach of
+\citet{DBLP:conf/cp/McCreeshP15} and construct supplemental graphs. We use paths of length 2,
+looking at counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the
+pattern).  We then investigate whether this leads to new constraints being generated.
+
+By an assignment, we mean considering mapping a pattern vertex $p$ to a target vertex $t$ (and not
+$\bot$) which does not violate any loop constraints. An assignment pair is two assignments with
+distinct $p$ and distinct $t$, which we say is permitted if it does not violate any adjacency
+constraint. We define the permitted assignment pair ratio to be the proportion of assignment pairs
+which are permitted.  Finally, we scatter plot the permitted assignment pair ratio with and without
+supplemental graphs\footnote{Because of the large sizes of the domains, we randomly sample one
+million pairs rather than considering every pair. In some cases, we have nearly a thousand domains,
+each with nearly ten thousand values---a complete quadratic calculation involving even a trivial
+arithmetic operation on this would take many hours.}.
+
+For $k = 0$, we see many points above the $x-y$ diagonal, which shows that for many instances, we
+are able to create a substantial number of new constraints at the top of search; on the other hand,
+there are also points on the diagonal, which shows that sometimes this technique provides no
+benefit. (Occasionally, points fall below the $x-y$ diagonal.  This is because the use of
+neighbourhood degree sequence reasoning on supplemental graphs can also lead to increased domain
+filtering, which could in turn eliminate a higher proportion of forbidden than permitted assignment
+pairs.) For $k = 1$ and $k = 2$, the proportion of points above the diagonal diminishes, but we are
+still able to create new constraints for many instances. By the time $k = 3$, most of the benefit is
+disappearing---although sometimes we are still able to make a difference, and bear in mind that
+sometimes adding just one new constrained pair can vastly reduce the search space.  A closer
+inspection of the raw data shows that for $k \ge 3$, nearly all of the instances showing a strong
+improvement are from the ``LV'' family of graphs.
 
@@
     \nl \lIf{$\left|\V(\mathcal{P})\right| + k > \left|\V(\mathcal{T})\right|$}{$\KwSty{return}~\KwSty{false}$\label{line:enough}}
-    \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\shortoverline{\mathcal{P}},
-        \shortoverline{\mathcal{T}}),$
+    \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\loopcomp{\mathcal{P}},
+        \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced},$
         \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
@@
     \nl \While{\KwSty{true}}{
-        \nl \If{\textnormal{no effectively-unit domains (treating all wildcard values as a single
+        \nl \If{\textnormal{no effectively-unit domains (treating all wildcard~values as a single
         value) remain}}{
@@
         \nl $D_v \gets \textnormal{an effectively-unit domain from}~D$ \;
-        \nl $v' \gets $ the single value in $D_v$, or an arbitrary wildcard value if there is more
+        \nl $v' \gets $ the single value in $D_v$, or an arbitrary wildcard~value if there is more
         than one \;
@@
 \nl \Begin{
-\nl $(F,\,H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,\emptyset,\,0)$ \;
+\nl $(H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,\emptyset,\,0)$ \;
 \nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
-    \nl $F \gets F \cup \{ v \}$ \;
     \nl $D_v \gets D_v \setminus H$ \label{line:elimhall} \;
@@
 
+\cref{algorithm:sip}. This is derived from a subgraph isomorphism due to
+\citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of algorithm portfolios
+\citep{thelionpaper} was the single strongest solver. As well as the modifications to solve $k$-less
+and induced problems, we have made two simplifications: we do not use conflict-directed backjumping,
+and we do not use iterated label filtering to recalculate neighbourhood degree sequences if vertices
+are not present in any target domain after construction---in preliminary experiments, these
+techniques were not beneficial for $k > 0$.
+
+?? Discuss how we did wildcards, effectively unit domains. The all diff propagator.
+
+?? Discuss how we do induced. We do not look at paths in the loop complements, since this is
+expensive to calculate and provides little benefit in practice on the instances we considered.
+
 \section{Empirical Evaluation}
 
-\begin{figure}
+\begin{figure}[tb]
     \includegraphics*{gen-graph-runtimes.pdf}
@@
 
-\begin{figure}
+\begin{figure}[tb]
     \includegraphics*{gen-graph-which-k-by-family.pdf}
@@
 
-% \section*{Acknowledgements}
-% 
-% Thanks to Christine, Samba, Patrick.
+We looked at . We saw that we could modify invariants, and that doing so still provided additional
+domain reduction and filtering power.
+
+Relaxed form of the problem which is easier to solve. Far from making maximum common subgraph scale
+as well as subgraph isomorphism, but we can at least get somewhere.
+
+Future work.
+
+\section*{Acknowledgements}
+
+We'd like to thank some people whose names we've removed for anonymous review for providing us with
+source code and problem instances, and someone at one of our institutions for inspiration.
 

### 2016-09-11 paper/paper.tex
Committing from 25,000ft

@@
 
+\subsection{Algorithms for the $k$-Less Problem}
+
+A non-induced $k$-less-subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph isomorphism
+between $P$ and $T$ with $k$ extra universally-adjacent vertices added to $T$. However, using such
+an approach is not ideal, because it would introduce symmetries; for induced $k$-less-subgraph
+isomorphisms, an approach based around adding vertices to $T$ cannot work at all.
+
+Another algorithmic approach could be to try each way of removing $k$ vertices from the pattern
+graph, and solving the subgraph isomorphism problem in turn. This approach might be feasible for $k
+= 1$, although it would involve a lot of duplication of search effort, but for larger values of $k$
+the number of searches which would have to be made would grow very quickly.
+
+Finally, for the induced case we could try adapting maximum common subgraph algorithms to solve the
+decision problem. However, both the maximum common subgraph algorithm and the clique encoding
+require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$ memory, which is extremely problematic on the
+instances we wish to work with.
+
+Instead, we introduce a new algorithm, inspired by a state of the art subgraph isomorphism
+algorithm. The approach we discuss requires only $O(\left|\V(P)\right|^2\left|\V(T)\right|)$ space
+(this can be thousands of times less than maximum common subgraph approaches, once the constant
+factors and orders of $T$ in our instances are considered). We list the algorithm in
+\cref{algorithm:sip}, explain it fully in \cref{section:algorithm}, and evaluate it in
+\cref{section:evaluation}, but first we will discuss our experimental setup, and then detail some
+experiments to verify that we can gain effective domain filtering (\cref{section:degreefiltering})
+and implied constraints (\cref{section:pathfiltering}) by using subgraph isomorphism style reasoning
+about degrees and paths in the $k$-less setting.
+
 ?? Explain effectively-unit domain, multiple $\bot$ values.
 
-\subsection{Experimental Setup}
+\section{Experimental Setup}
 
@@
 they used pairs of graphs with up to 35 vertices in each, whilst our dataset contains patterns with
-up to ?? vertices and targets with up to ?? vertices. This causes problems: both the maximum common
-subgraph algorithm and the clique encoding require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$
-memory. For maximum common subgraph, 1,560 of the instances cannot fit in the amount of RAM we have
-available---we treat these instances as having timed out. The situation for the clique encoding is
-even worse, and 3,653 of these instances do not fit in RAM. In contrast, the approach we discuss
-here requires only $O(\left|\V(P)\right|^2\left|\V(T)\right|)$ space (which would still be a problem
-on some desktop machines, but not on our server hardware).
+up to ?? vertices and targets with up to ?? vertices. For maximum common subgraph, 1,560 of the
+instances cannot fit in the amount of RAM we have available---we treat these instances as having
+timed out. The situation for the clique encoding is even worse, and 3,653 of these instances do not
+fit in RAM. In contrast, for our algorithm, every instance fits comfortably (at least on modern
+server-class hardware).
 
 \section{Domain Filtering using Degrees}\label{section:degreefiltering}
-
-A non-induced $k$-less-subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph
-isomorphism between $P$ and $T$ with $k$ extra universally-adjacent vertices. (However, we can do a
-bit better algorithmically.) For induced $k$-less-subgraph isomorphisms, such an approach cannot
-work.
 
@@
 Unlike in conventional subgraph isomorphism, we cannot extend this filtering to look at paths of
-length three: removing a single vertex can delete arbitrarily many such paths. We could count paths
-of any length which are vertex disjoint, although calculating this is too expensive to be useful in
-practice.
+length three: removing a single vertex can delete arbitrarily many such paths. We \emph{could}
+instead count paths of any length which are vertex disjoint, although calculating this appears to be
+too expensive to be beneficial in practice.
 
 To allow for fast propagation, rather than calculating paths dynamically, we follow the approach of
-\citet{DBLP:conf/cp/McCreeshP15} and construct supplemental graphs. We use paths of length 2,
-looking at counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the
-pattern).  We then investigate whether this leads to new constraints being generated.
+\citet{DBLP:conf/cp/McCreeshP15} and construct supplemental graphs, and find a mapping which is
+simultaneously a non-induced subgraph isomorphism between every supplemental graph pair. We use
+paths of length 2, looking at counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up
+to $3 + k$ in the pattern).  We then investigate whether this leads to new constraints being
+generated.
 
@@
 
-\section{A New Algorithm}
+\section{A New Algorithm}\label{section:algorithm}
 
@@
 
-\section{Empirical Evaluation}
+\section{Empirical Evaluation}\label{section:evaluation}
 

### 2016-09-11 paper/paper.tex
Committing from -2ft

@@
 
-Let $p$ be a vertex in a graph $P$, the \emph{degree} of $p$, $\deg(p)$, is the number of vertices
-to which it is adjacent
+Let $p$ be a vertex in a graph $P$. The \emph{degree} of $p$, $\deg(p)$, is the number of vertices
+to which it is adjacent. The degree of vertices gives us an invariant, which may be used to
+eliminate some infeasible values from domains.
 

### 2016-09-11 paper/paper.tex
Committing from 38,000ft

@@
 For both subgraph isomorphism and maximum common subgraph, constraint programming is the best known
-approach\footnote{Note that toolkits are not used, to facilitate better memory layouts and
-propagation queues, although the algorithms are heavily inspired by the constraint programming
-literature}. For both problems, we create a variable for each vertex in the pattern graph (the
-smaller graph, in the case of maximum common subgraph), with domains ranging over the vertices in
-the target graph (the larger graph). For maximum common subgraph, each domain is given an additional
-$\bot$ value, meaning ``unmapped''.
+approach\footnote{Note that toolkits are not used in state of the art implementations, to facilitate
+better memory layouts and propagation queues, although the algorithms are heavily inspired by
+constraint programming.}. For both problems, we create a variable for each vertex in the
+pattern graph (the smaller graph, in the case of maximum common subgraph), with domains ranging over
+the vertices in the target graph (the larger graph). For maximum common subgraph, each domain is
+given an additional $\bot$ value, meaning ``unmapped''.
 
-We also have constraints for adjacency and non-adjacency. For the maximum common subgraph case,
-$\bot$ is ignored.
-
-In our algorithm we make use of \cref{prop:comp} by seeking an $i$ which simultaneously satisfies $P
-\rightarrowtail T$ and $\loopcomp{P} \rightarrowtail \loopcomp{T}$ when searching for an induced subgraph
-isomorphism.  Further, \cref{prop:comp} tells us that every induced subgraph isomorphism is
-equivalent to simultaneous non-induced subgraph isomorphisms both $P$ and $T$ as well as their
-complements.
+Constraints are used to ensure that adjacency pairs of vertices are mapped to adjacenct pairs of
+vertices. For the maximum common subgraph case, any pair of assignments with $\bot$ as either value
+is also permitted.  To handle the induced case, rather than the more usual approach of directly
+having constraints for non-adjacent pairs of vertices, we will make use of \cref{prop:comp} by
+seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
+\rightarrowtail \loopcomp{T}$.
 
@@
 A non-induced $k$-less-subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph isomorphism
-between $P$ and $T$ with $k$ extra universally-adjacent vertices added to $T$. However, using such
+between $P$ and $T$, with $k$ extra universally-adjacent vertices added to $T$. However, using such
 an approach is not ideal, because it would introduce symmetries; for induced $k$-less-subgraph
 isomorphisms, an approach based around adding vertices to $T$ cannot work at all.
-
 Another algorithmic approach could be to try each way of removing $k$ vertices from the pattern
@@
 the number of searches which would have to be made would grow very quickly.
-
 Finally, for the induced case we could try adapting maximum common subgraph algorithms to solve the
@@
 
-\section{Experimental Setup}
+\subsection{Experimental Setup}
 
@@
 \subsection{Solving from the Top Down}
-
 \section{Conclusion}

### 2016-09-12 paper/paper.tex
added nauty reference

@@
 Some other forms do not translate. For example, another invariant which can be effective on regular
-graphs is to count the number of neighbours of a vertex which are present in a triangle. Removing a
-single vertex can alter this count arbitrarily, so we cannot make use of this fact.
+graphs is to count the number of neighbours of a vertex which are present in a triangle \cite{mckay2014practical}.
+Removing a single vertex can alter this count arbitrarily, so we cannot make use of this fact.
 

### 2016-09-13 paper/paper.tex
Added graphs.

@@
 
-\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds}
+\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds,shapes.misc}
+%cross
+\tikzset{cross/.style={cross out, draw=uofgcobalt, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt},cross/.default={1.5mm}}
 
@@
 many of these instances in RAM.
+\begin{figure}
+    \begin{center}
+        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm,node distance=10mm,fill=black}]
+            \node[fill=uofgcobalt] (a) {};
+            \node (a1) [below left of = a] {};
+            \node (b1) [below right of = a] {};
+            \node (aa) [below right of = a1] {};
 
+            \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
+            \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
+            \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
+            \node (ac2) [fill=gray!70,above left of = ab2,node distance=13mm,xshift=-2mm] {};
+            \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
+            \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
+            \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
+            \node (bc2) [fill=gray!70,above right of = bb2,node distance=13mm,xshift=2mm] {};
+
+            \node (aaa) [below of =aa, node distance=20mm] {};
+
+            \path[dotted] (a) edge (a1) edge (b1);
+            \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
+                (a1) edge (b1)
+                (aaa) edge (a2) edge (b2)
+                (a2) edge (aa2) edge (ab2)
+                (b2) edge (ba2) edge (bb2);
+            \path[color=gray!70] (ac2) edge (ab2) edge (aa2)
+                (bc2) edge (bb2) edge (ba2);
+
+            \node [cross] {};
+        \end{tikzpicture}
+        \caption{Example of  ``as much of the pattern'' as possible.}
+        \label{fig:subgraphexample}
+    \end{center}
+\end{figure}
 \subsection{Definitions and Notations}
@@
 
-\todo{is this example graph still needed?? yes, Patrick likes pictures}
+\begin{figure}
+    \begin{center}
+        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+            \node[fill=black] (p) {};
+            \node[fill=black] (b) [above of = p,node distance=10mm] {};
+            \node[fill=black] (a) [left of = b] {};
+            \node[fill=black] (c) [right of = b] {};
+            \node[fill=black] (d) [above of = b,node distance=10mm] {};
+
+            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
+            \node[draw=none,left of = a,node distance=3mm,yshift=-1mm] {$a$};
+            \node[draw=none,left of = b,node distance=3mm,yshift=-1mm] {$b$};
+            \node[draw=none,right of = c,node distance=3mm,yshift= 1mm] {$c$};
+            \node[draw=none,above of = d,node distance=3mm,yshift=1mm] {$d$};
+
+            \node[draw=none, below of = p, node distance=6mm] {$P$};
+
+            \path (p) edge (a) edge (b) edge (c)
+                (a) edge (d)
+                (b) edge (c) edge (d)
+                (c) edge (d);
+        \end{tikzpicture}
+
+        \vspace{5mm}
+
+        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+            \node[fill=black] (a1) {};
+            \node[fill=black] (b1) [right of = a1] {};
+            \node[fill=black] (c1) [right of = b1] {};
+            \node[fill=black] (a2) [below of = a1] {};
+            \node[fill=black] (b2) [right of = a2] {};
+            \node[fill=black] (c2) [right of = b2] {};
+            \node[fill=black] (a3) [below of = a2] {};
+            \node[fill=black] (b3) [right of = a3] {};
+            \node[fill=black] (c3) [right of = b3] {};
+
+            \node[draw=none, below of = b3, node distance=6mm] {$T_{1}$};
+
+            \path[color=gray!70] (a1) edge (b1) edge (a2)
+                (b1) edge (c1)
+                (c1) edge (c2)
+                (a2) edge (b2) edge (a3)
+                (c2) edge (c3)
+                (a3) edge (b3)
+                (b3) edge (c3);
+            \path[line width=0.4mm] (b1) edge (a2) edge (b2) edge (c2)
+                (a2) edge (b3)
+                (b2) edge (c2) edge (b3)
+                (c2) edge (b3);
+        \end{tikzpicture}
+        \hspace{1cm}
+        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+            \node[fill=black] (p) {};
+            \node[draw=none] (b) [above of = p,node distance=10mm] {};
+            \node[fill=black] (a) [left of = b] {};
+            \node[fill=black] (c) [right of = b] {};
+            \node[fill=black] (d) [above of = b,node distance=10mm] {};
+
+            \node[draw=none, below of = p, node distance=6mm] {$T_{2}$};
+
+            \path (p) edge (a) edge (c)
+                (a) edge (d)
+                (c) edge (d);
+        \end{tikzpicture}
+        \caption{$P\rightarrowtail T_{1}$, $P\lessnonind{1} T_{2}$}
+        \label{fig:klessexample}
+    \end{center}
+\end{figure}
 

### 2016-09-13 paper/paper.tex
Esthetic update to fig2, commented out fig3, ref'd fig2 instead in proof.

@@
             \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
-            \node (ac2) [fill=gray!70,above left of = ab2,node distance=13mm,xshift=-2mm] {};
+            \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
             \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
@@
             \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
-            \node (bc2) [fill=gray!70,above right of = bb2,node distance=13mm,xshift=2mm] {};
+            \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};
 
@@
                 (b2) edge (ba2) edge (bb2);
-            \path[color=gray!70] (ac2) edge (ab2) edge (aa2)
+            \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
                 (bc2) edge (bb2) edge (ba2);
@@
         \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
-            \node[fill=black] (a1) {};
+            \node[fill=gray!50] (a1) {};
             \node[fill=black] (b1) [right of = a1] {};
-            \node[fill=black] (c1) [right of = b1] {};
+            \node[fill=gray!50] (c1) [right of = b1] {};
             \node[fill=black] (a2) [below of = a1] {};
@@
             \node[fill=black] (c2) [right of = b2] {};
-            \node[fill=black] (a3) [below of = a2] {};
+            \node[fill=gray!50] (a3) [below of = a2] {};
             \node[fill=black] (b3) [right of = a3] {};
-            \node[fill=black] (c3) [right of = b3] {};
+            \node[fill=gray!50] (c3) [right of = b3] {};
 
@@
 
-            \path[color=gray!70] (a1) edge (b1) edge (a2)
+            \path[color=gray!50] (a1) edge (b1) edge (a2)
                 (b1) edge (c1)
@@
 
-Figure\ref{fig:nds} illustrates the three cases possible when filtering by neighbourhood degree
+Figure\ref{fig:klessexample} illustrates the three cases possible when filtering by neighbourhood degree
 sequence.  Removing the top node causes each entry in $\nds(p)$ to be reduced; removing the
@@
 
-\begin{figure}
-    \begin{center}
-        \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
-            \node[fill=black] (p) {};
-            \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
-            \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
-            \node[fill=uofgpumpkin] (n1) [left of = n2] {};
-            \node[fill=uofglawn] (n3) [right of = n2] {};
-            \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
-            \path (p) edge (n1) edge (n2) edge (n3)
-                (n1) edge (q)
-                (n2) edge (n3) edge (q)
-                (n3) edge (q);
-        \end{tikzpicture}
-        \caption{Example of neighbourhood degree filtering cases}
-        \label{fig:nds}
-    \end{center}
-\end{figure}
+% \begin{figure}
+%     \begin{center}
+%         \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
+%             \node[fill=black] (p) {};
+%             \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
+%             \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
+%             \node[fill=uofgpumpkin] (n1) [left of = n2] {};
+%             \node[fill=uofglawn] (n3) [right of = n2] {};
+%             \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
+%             \path (p) edge (n1) edge (n2) edge (n3)
+%                 (n1) edge (q)
+%                 (n2) edge (n3) edge (q)
+%                 (n3) edge (q);
+%         \end{tikzpicture}
+%         \caption{Example of neighbourhood degree filtering cases}
+%         \label{fig:nds}
+%     \end{center}
+% \end{figure}
 

### 2016-09-13 paper/paper.tex
More text

@@
 
-\subsection{Experimental Setup}
+\subsection{Experimental Setup} \label{section:setup}
 
@@
 
-\subsection{Induced}
-
-What proportion of instances are actually satisfiable as $k$ increases?
-
 \begin{figure}[tb]
@@
 
-\subsection{Non-Induced}
+We now evaluate our algorithm and show that it is effective in practice, even on the larger subgraph
+isomorphism instances. In \cref{figure:runtimes} we give cumulative distribution plots for the
+induced and non-induced problems, with $k$ ranging from $0$ to $5$ (we discuss the dotted lines in
+this plot below). The results are strong: with $k = 0$ we may solve nearly every instance, whilst
+even at $k = 5$ we can solve over $4,000$ instances in both variants.
 
-What proportion of instances are actually satisfiable as $k$ increases?
+But are we learning anything about the results---that is, are there instances for which $k = 0$ is
+unsatisfiable, but that are satisfiable for small $k$? For the problem families which do not consist
+entirely of satisfiable instances, we plot this in \cref{figure:which-k}. In the ``phase'' family,
+which consists of instances crafted to be extremely difficult to solve, we are not able to answer
+this question, and in the ``scalefree'' family we see no satisfiable instances with low but not zero
+$k$ (this is simply due to there being many vertices with loops in some pattern graphs, but no loops
+at all in the targets). However, in several of the remaining families we can over double the number
+of instances for which exact solutions are known, and gain upper bounds on many more. This is
+particularly interesting for the ``images-CVIU11'' family, where the size of the solution has a
+direct real-world interpretation in terms of closeness of image matching.
 
 \subsection{Solving from the Top Down}
+
+What would happen if we used our approach to solve the maximum common induced problem? We could
+simply start at $k = 0$, and increase $k$ until a solution is found. This would be tackling the
+problem in the opposite direction from existing approaches, which work by attempting to construct
+larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
+\downarrrow$ is our algorithm, whilst ``MCS'' and ``clique'' are the two algorithms discussed in ??.
+Bearing in mind the disclaimer in \cref{section:setup} regarding instances not fitting in RAM, we
+see that our approach is able to close over twice as many of these instances as the previous state
+of the art. (The same conclusion holds even if every instance which is satisfiable with $k = 0$ is
+removed from the dataset.)
+
 \section{Conclusion}

### 2016-09-13 paper/paper.tex
MCS instances

@@
 larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
-\downarrrow$ is our algorithm, whilst ``MCS'' and ``clique'' are the two algorithms discussed in ??.
+\downarrow$ is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed in ??.
 Bearing in mind the disclaimer in \cref{section:setup} regarding instances not fitting in RAM, we
@@
 removed from the dataset.)
+
+\begin{figure}[tb]
+    \includegraphics*{gen-graph-mcsruntimes.pdf}
+    \caption{The cumulative number of maximum common induced subgraph instances solved over time,
+    comparing our decreasing $k$ approach with two state of the art
+    solvers.}\label{figure:mcsruntimes}
+\end{figure}
+
+What about if we use instances designed for the maximum common subgraph problem? In
+\cref{figure:mcsruntimes} we again compare these approaches, but using the first ten instances from
+each family of a standard benchmark set
+\citep{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}, selecting undirected, unlabelled
+graphs with up to 50 vertices---this gives us a total of 4,110 instances. In these instances the
+number of vertices in the pattern and target graphs is the same, which is not ideal for our
+algorithm (although our invariants are still effective in many cases). Nonetheless, we are by a
+small margin the single strongest solver. Interestingly, our algorithm tends to have complementary
+performance to the other two approaches (which are much more correlated), which suggests that there
+is scope for an algorithm which runs both an upper bound and a constructive, lower bound approach
+simultaneously or in parallel, stopping when the two bounds meet in the middle.
 

### 2016-09-13 paper/paper.tex
Muck around with graphs

@@
 
-\begin{figure}[tb]
+\begin{figure*}[tb]
     \includegraphics*{gen-graph-runtimes.pdf}
-    \caption{The cumulative number of instances solved over time, for the induced and non-induced
-    problems, with different values of $k$. We also show the results of iteratively decreasing $k$
-    until a solution is found, and in the induced case, the performance of a leading maximum common
-    subgraph algorithm.}\label{figure:runtimes}
-\end{figure}
+    \caption{In the first two plots, the cumulative number of instances solved over time, for the
+        induced and non-induced problems, with different values of $k$. We also show the results of
+        iteratively decreasing $k$ until a solution is found, and in the induced case, the
+        performance of two leading maximum common subgraph algorithms. In the third plot, results
+        comparing our algorithm with iteratively decreasing $k$ to other approaches on maximum
+        common induced subgraph instances.}\label{figure:runtimes}
+\end{figure*}
 
-\begin{figure}[tb]
+\begin{figure*}[tb]
     \includegraphics*{gen-graph-which-k-by-family.pdf}
@@
     instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[tb]
-    \includegraphics*{gen-graph-mcsruntimes.pdf}
-    \caption{The cumulative number of maximum common induced subgraph instances solved over time,
-    comparing our decreasing $k$ approach with two state of the art
-    solvers.}\label{figure:mcsruntimes}
-\end{figure}
-
-What about if we use instances designed for the maximum common subgraph problem? In
-\cref{figure:mcsruntimes} we again compare these approaches, but using the first ten instances from
+What about if we use instances designed for the maximum common subgraph problem? In the third plot
+in \cref{figure:runtimes} we again compare these approaches, but using the first ten instances from
 each family of a standard benchmark set

### 2016-09-13 paper/paper.tex
Muck around to see how much space we have
Cref is your friend
Move proofs to appendix

@@
 
-% \usepackage{showframe}
+\usepackage{placeins}
+
+\usepackage{showframe}
 
@@
 \end{proposition}
-\begin{proof}
-Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$.
-Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$.
-Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$.
-Then
-\[
-\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
-\]
-\end{proof}
 
@@
 
-\begin{proof}
-Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
-implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.
-
-Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$
-is some subset of $P$ with $\left| P_k \right| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
-each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
-\lesspreceq{k} \nds(t)$.
-\end{proof}
-
-Figure\ref{fig:klessexample} illustrates the three cases possible when filtering by neighbourhood degree
+\Cref{fig:klessexample} illustrates the three cases possible when filtering by neighbourhood degree
 sequence.  Removing the top node causes each entry in $\nds(p)$ to be reduced; removing the
@@
 \end{corollary}
-
-\begin{proof}
-\todo{Sketch?? Let $S_k$ be some elements of the sequence which aren't the first $k$ elements.  Then these elements are less than or equal to the first $k$ elements.}
-\end{proof}
 
@@
 \begin{figure}
+    \centering
     \includegraphics*{gen-graph-ids.pdf}
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:paths}
     Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
@@
 \end{proposition}
-\begin{proof}
-Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
-\begin{align*}
-P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
- = & \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \} \\
- = & \{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} .
-\end{align*}
-So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
 
-If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
-\[
-\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
-\]
-As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
-\[
-\left|\N(p)\cap \N(q)\right| - k \leq \deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
-\]
-which is
-\[
-\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
-\]
-\end{proof}
-
-This leads to the following:
-
-\begin{proposition}
+\begin{corollary}
     For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$. The
@@
     $P^{n+k, 2}\lessnonind{k} T^{n, 2}$.
-\end{proposition}
+\end{corollary}
 
@@
 \begin{figure*}[tb]
+    \centering
     \includegraphics*{gen-graph-runtimes.pdf}
@@
 \begin{figure*}[tb]
+    \centering
     \includegraphics*{gen-graph-which-k-by-family.pdf}
@@
 
+\FloatBarrier
+
 \bibliographystyle{named}
@@
 
+\clearpage
+\appendix
+
+\section{Proofs Omitted From Main Text}
+
+\begin{proof}[Proof of \cref{prop:deg}]
+Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$.
+Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$.
+Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$.
+Then
+\[
+\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
+\]
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:nds}]
+Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
+implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.
+
+Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$
+is some subset of $P$ with $\left| P_k \right| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
+each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
+\lesspreceq{k} \nds(t)$.
+\end{proof}
+
+\begin{proof}[Proof of \cref{prop:paths}]
+Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
+\begin{align*}
+P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
+ = & \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \} \\
+ = & \{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} .
+\end{align*}
+So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
+
+If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
+\[
+\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
+\]
+As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
+\[
+\left|\N(p)\cap \N(q)\right| - k \leq \deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
+\]
+which is
+\[
+\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
+\]
+\end{proof}
+
 \end{document}

### 2016-09-13 paper/paper.tex
Remove some hackery
Make figure smaller
Be a bit more abstract
More introductioning

@@
 
-\usepackage{placeins}
-
-\usepackage{showframe}
+% \usepackage{showframe}
 
@@
     instances used to benchmark subgraph isomorphism algorithms, despite these instances being
-    too large for current maximum common subgraph algorithms to handle.
+    too large for current maximum common subgraph algorithms to handle. Finally, by iteratively
+    increasing $k$, we obtain an algorithm which is also competitive for the maximum common subgraph
+    problem.
 \end{abstract}
-\todo{try code on MCS instances}
+
 \section{Introduction}
@@
 techniques leads to a practical algorithm which can scale to work with the families of graphs
-commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in
-a substantial portion of ??; in ?? more cases, we can at least obtain an upper bound. This is a
-significant improvement over state of the art maximum common subgraph solvers, which cannot even fit
-many of these instances in RAM.
+commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, we
+can close a substantial portion of the instances, and in many more cases, we can at least obtain an
+upper bound. This is a significant improvement over state of the art maximum common subgraph
+solvers, which cannot even fit many of these instances in RAM. Finally, we show that iteratively
+increasing $k$ gives a competitive algorithm for the maximum common induced subgraph problem.
+
 \begin{figure}
@@
 \begin{figure}
-    \begin{center}
+    \centering
     \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
@@
             (c) edge (d);
-        \end{tikzpicture}
-
-        \vspace{5mm}
-
-        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+        \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
         \node[fill=gray!50] (a1) {};
@@
             (c2) edge (b3);
-        \end{tikzpicture}
-        \hspace{1cm}
-        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+    \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
         \node[fill=black] (p) {};
@@
     \label{fig:klessexample}
-    \end{center}
 \end{figure}
@@
 
-\FloatBarrier
-
 \bibliographystyle{named}

### 2016-09-13 paper/paper.tex
Remove text we don't use
All different
Are we still doing phrasing?

@@
 vertices with loops to vertices with loops, and vertices without loops to vertices without loops.
-(Although when we filter by paths we make use of the complement rather than the loop complement.)
 The following proposition follows directly from the definitions.
@@
 seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
-\rightarrowtail \loopcomp{T}$.
+\rightarrowtail \loopcomp{T}$. Finally, an all different except $\bot$ constraint ensures
+injectivity.
 
-?? All different.
-
-For subgraph isomorphism, we can do domain filtering at the top of search, to reduce the initial
-sizes of domains---we discuss this in \cref{section:degreefiltering}. Subgraph isomorphism also
-allows us to generate additional implied constraints, which we discuss in
+For subgraph isomorphism, this model can be enhanced with domain filtering at the top of search, to
+reduce the initial sizes of domains---we discuss this in \cref{section:degreefiltering}. Subgraph
+isomorphism also allows us to generate additional implied constraints, which we discuss in
 \cref{section:pathfiltering}. Neither of these techniques are valid for the maximum common subgraph

### 2016-09-13 paper/paper.tex
Not here
Reformulation is in the conclusion
We used the CP codes

@@
 \todo{talk about subgraph isomorphism applications, particularly vision}
-\todo{talk about reformulating}
+
 The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
@@
 
-?? Explain effectively-unit domain, multiple $\bot$ values.
-
 \subsection{Experimental Setup} \label{section:setup}
@@
 review}, and source code was compiled using
-GCC 5.3.0. We used a timeout of 1,000 seconds for each instance.
+GCC 5.3.0. We used a timeout of 1,000 seconds for each instance. For comparison, we used the
+implementations of \citet{DBLP:conf/cp/McCreeshNPS16}.
 
@@
 format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.
-
-?? Using the French code, and the Glasgow clique code.
-
 Note that many of these instances are \emph{much} larger than were used in the recent comparison of

### 2016-09-13 paper/paper.tex
How big are your graphs

@@
 \cite{DBLP:conf/ijcai/McCreeshPT16}; all these instances are available in a simple text
-format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.
-Note that many of these instances are \emph{much} larger than were used in the recent comparison of
-maximum common subgraph algorithms by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs,
-they used pairs of graphs with up to 35 vertices in each, whilst our dataset contains patterns with
-up to ?? vertices and targets with up to ?? vertices. For maximum common subgraph, 1,560 of the
-instances cannot fit in the amount of RAM we have available---we treat these instances as having
-timed out. The situation for the clique encoding is even worse, and 3,653 of these instances do not
-fit in RAM. In contrast, for our algorithm, every instance fits comfortably (at least on modern
-server-class hardware).
+format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.  Note that many of these instances
+are \emph{much} larger than were used in the recent comparison of maximum common subgraph algorithms
+by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs, they used pairs of graphs with up to
+35 vertices in each, whilst our dataset contains graphs with up to 6,671 vertices. For the CP
+algorithm, 1,560 of the instances cannot fit in the amount of RAM we have available---we treat these
+instances as having timed out. The situation for the clique encoding is even worse, and 3,653 of
+these instances do not fit in RAM. In contrast, for our algorithm, every instance fits comfortably
+(at least on modern server-class hardware).
 

### 2016-09-13 paper/paper.tex
Explain figure 3

@@
 
-In \cref{figure:ids} we show that this is useful in practice.
+In \cref{figure:ids} we show that this is effective in practice: we show the amount of domain reduction
+we can achieve at the top of search by using invariants and a fixed $k$, compared to the search
+space size for the maximum common induced subgraph problem. (The results on the non-induced version
+show a similar but slightly weaker trend.)
 
-Some other forms do not translate. For example, another invariant which can be effective on regular
-graphs is to count the number of neighbours of a vertex which are present in a triangle \cite{mckay2014practical}.
-Removing a single vertex can alter this count arbitrarily, so we cannot make use of this fact.
+Some other invariants do not translate. For example, another rule which can be effective on regular
+graphs involves count the number of neighbours of a vertex which are present in a triangle
+\cite{mckay2014practical}. Removing a single vertex can alter this count arbitrarily, so we cannot
+make use of this fact.
 

### 2016-09-13 paper/paper.tex
Merge paragraphs
Make it look like we're citing more stuff

@@
 
-As well as reasoning about degrees, we can also reason about paths.
-
-A \emph{path} between two vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$.
-We define $\paths(p,q,n)$ to be the number of paths of length $n$ between the vertices $p$ and $q$.
-%\todo{Define paths}
+As well as reasoning about degrees, we can also reason about paths.  A \emph{path} between two
+vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$. We define
+$\paths(p,q,n)$ to be the number of paths of length $n$ between the vertices $p$ and $q$.
 
@@
 
-To allow for fast propagation, rather than calculating paths dynamically, we follow the approach of
-\citet{DBLP:conf/cp/McCreeshP15} and construct supplemental graphs, and find a mapping which is
-simultaneously a non-induced subgraph isomorphism between every supplemental graph pair. We use
-paths of length 2, looking at counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up
-to $3 + k$ in the pattern).  We then investigate whether this leads to new constraints being
-generated.
+To allow for fast propagation, rather than calculating paths dynamically like
+\citet{DBLP:conf/cp/AudemardLMGP14}, we follow the approach of \citet{DBLP:conf/cp/McCreeshP15} and
+construct supplemental graphs, and find a mapping which is simultaneously a non-induced subgraph
+isomorphism between every supplemental graph pair. We use paths of length 2, looking at counts of 1,
+2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).  We then
+investigate whether this leads to new constraints being generated.
 

### 2016-09-13 paper/paper.tex
Gratuitous italics

@@
 \citet{DBLP:conf/cp/AudemardLMGP14}, we follow the approach of \citet{DBLP:conf/cp/McCreeshP15} and
-construct supplemental graphs, and find a mapping which is simultaneously a non-induced subgraph
+construct \emph{supplemental graphs}, and find a mapping which is simultaneously a non-induced subgraph
 isomorphism between every supplemental graph pair. We use paths of length 2, looking at counts of 1,

### 2016-09-13 paper/paper.tex
Let's not say this

@@
 \newtheorem{corollary}{Corollary}
+\newtheorem{example}{Example}
 
@@
 
+\begin{example}
+Take a pattern graph $P$ with vertices $V=\{p, a, b, c, d\}$ and edges $E=\{(a,d), (a,p), (b,c),
+(b,d), (b,p), (c,d), (c,p)\}$, which is shown in \cref{fig:klessexample} along with two target
+graphs $T_{1}$ and $T_{2}$. The degree of the vertex $p$ in $P$ is $\deg(p)=3$, the neighbours of
+$p$ are $\N(p)=\{a,b,c\}$, the neighbourhood degree sequence of $p$ is $\nds(p)=(3,3,2)$, as the
+degrees of the neighbours of $p$ are $\deg(a)=2,\ \deg(b)=3$ and $deg(c)=3$.
+
+We can find a subgraph in $T_{1}$ which is non-induced isomorphic to $P$ (indicated through the bold edges and black vertices in $T_{1}$).
+The vertex $p$ can be  mapped to $t_{1}$ in the target graph $T_{1}$, where $\deg(t_{1})=5$ and $\nds(t_{1})=(5,5,4,2,2)$.
+
+There is a non-induced mapping of the pattern graph $P$ into $T_{2}$ by removing one vertex of $P$.
+This removal changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$, to $\nds(p)=(2,2)$.
+
 \begin{figure}
@@
 
+        \node[draw=none,right of = b3,node distance=1mm, yshift=-2mm] {$t_{1}$};
+
         \node[draw=none, below of = b3, node distance=6mm] {$T_{1}$};
@@
 \end{figure}
+\end{example}
 
@@
 disappearing---although sometimes we are still able to make a difference, and bear in mind that
-sometimes adding just one new constrained pair can vastly reduce the search space.  A closer
-inspection of the raw data shows that for $k \ge 3$, nearly all of the instances showing a strong
-improvement are from the ``LV'' family of graphs.
+sometimes adding just one new constrained pair can vastly reduce the search space.
 

### 2016-09-13 paper/paper.tex
example text added.

@@
 
+\theoremstyle{plain}
+\newtheorem{example}{Example}
+
 \theoremstyle{definition}
@@
 \newtheorem{corollary}{Corollary}
-\newtheorem{example}{Example}
 
@@
     instances used to benchmark subgraph isomorphism algorithms, despite these instances being
-    too large for current maximum common subgraph algorithms to handle. Finally, by iteratively
-    increasing $k$, we obtain an algorithm which is also competitive for the maximum common subgraph
-    problem.
+    too large for current maximum common subgraph algorithms to handle.
 \end{abstract}
@@
 \todo{talk about subgraph isomorphism applications, particularly vision}
-
+\todo{talk about reformulating}
 The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
@@
 techniques leads to a practical algorithm which can scale to work with the families of graphs
-commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, we
-can close a substantial portion of the instances, and in many more cases, we can at least obtain an
-upper bound. This is a significant improvement over state of the art maximum common subgraph
-solvers, which cannot even fit many of these instances in RAM. Finally, we show that iteratively
-increasing $k$ gives a competitive algorithm for the maximum common induced subgraph problem.
-
+commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, in
+a substantial portion of ??; in ?? more cases, we can at least obtain an upper bound. This is a
+significant improvement over state of the art maximum common subgraph solvers, which cannot even fit
+many of these instances in RAM.
 \begin{figure}
@@
 vertices with loops to vertices with loops, and vertices without loops to vertices without loops.
+(Although when we filter by paths we make use of the complement rather than the loop complement.)
 The following proposition follows directly from the definitions.
@@
 seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
-\rightarrowtail \loopcomp{T}$. Finally, an all different except $\bot$ constraint ensures
-injectivity.
+\rightarrowtail \loopcomp{T}$.
 
-For subgraph isomorphism, this model can be enhanced with domain filtering at the top of search, to
-reduce the initial sizes of domains---we discuss this in \cref{section:degreefiltering}. Subgraph
-isomorphism also allows us to generate additional implied constraints, which we discuss in
+?? All different.
+
+For subgraph isomorphism, we can do domain filtering at the top of search, to reduce the initial
+sizes of domains---we discuss this in \cref{section:degreefiltering}. Subgraph isomorphism also
+allows us to generate additional implied constraints, which we discuss in
 \cref{section:pathfiltering}. Neither of these techniques are valid for the maximum common subgraph
@@
 
+?? Explain effectively-unit domain, multiple $\bot$ values.
+
 \subsection{Experimental Setup} \label{section:setup}
@@
 review}, and source code was compiled using
-GCC 5.3.0. We used a timeout of 1,000 seconds for each instance. For comparison, we used the
-implementations of \citet{DBLP:conf/cp/McCreeshNPS16}.
+GCC 5.3.0. We used a timeout of 1,000 seconds for each instance.
 
@@
 \cite{DBLP:conf/ijcai/McCreeshPT16}; all these instances are available in a simple text
-format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.  Note that many of these instances
-are \emph{much} larger than were used in the recent comparison of maximum common subgraph algorithms
-by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs, they used pairs of graphs with up to
-35 vertices in each, whilst our dataset contains graphs with up to 6,671 vertices. For the CP
-algorithm, 1,560 of the instances cannot fit in the amount of RAM we have available---we treat these
-instances as having timed out. The situation for the clique encoding is even worse, and 3,653 of
-these instances do not fit in RAM. In contrast, for our algorithm, every instance fits comfortably
-(at least on modern server-class hardware).
+format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.
+
+?? Using the French code, and the Glasgow clique code.
+
+Note that many of these instances are \emph{much} larger than were used in the recent comparison of
+maximum common subgraph algorithms by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs,
+they used pairs of graphs with up to 35 vertices in each, whilst our dataset contains patterns with
+up to ?? vertices and targets with up to ?? vertices. For maximum common subgraph, 1,560 of the
+instances cannot fit in the amount of RAM we have available---we treat these instances as having
+timed out. The situation for the clique encoding is even worse, and 3,653 of these instances do not
+fit in RAM. In contrast, for our algorithm, every instance fits comfortably (at least on modern
+server-class hardware).
 
@@
 
-In \cref{figure:ids} we show that this is effective in practice: we show the amount of domain reduction
-we can achieve at the top of search by using invariants and a fixed $k$, compared to the search
-space size for the maximum common induced subgraph problem. (The results on the non-induced version
-show a similar but slightly weaker trend.)
+In \cref{figure:ids} we show that this is useful in practice.
 
-Some other invariants do not translate. For example, another rule which can be effective on regular
-graphs involves count the number of neighbours of a vertex which are present in a triangle
-\cite{mckay2014practical}. Removing a single vertex can alter this count arbitrarily, so we cannot
-make use of this fact.
+Some other forms do not translate. For example, another invariant which can be effective on regular
+graphs is to count the number of neighbours of a vertex which are present in a triangle \cite{mckay2014practical}.
+Removing a single vertex can alter this count arbitrarily, so we cannot make use of this fact.
 
@@
 
-As well as reasoning about degrees, we can also reason about paths.  A \emph{path} between two
-vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$. We define
-$\paths(p,q,n)$ to be the number of paths of length $n$ between the vertices $p$ and $q$.
+As well as reasoning about degrees, we can also reason about paths.
+
+A \emph{path} between two vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$.
+We define $\paths(p,q,n)$ to be the number of paths of length $n$ between the vertices $p$ and $q$.
+%\todo{Define paths}
 
@@
 
-To allow for fast propagation, rather than calculating paths dynamically like
-\citet{DBLP:conf/cp/AudemardLMGP14}, we follow the approach of \citet{DBLP:conf/cp/McCreeshP15} and
-construct \emph{supplemental graphs}, and find a mapping which is simultaneously a non-induced subgraph
-isomorphism between every supplemental graph pair. We use paths of length 2, looking at counts of 1,
-2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).  We then
-investigate whether this leads to new constraints being generated.
+To allow for fast propagation, rather than calculating paths dynamically, we follow the approach of
+\citet{DBLP:conf/cp/McCreeshP15} and construct supplemental graphs, and find a mapping which is
+simultaneously a non-induced subgraph isomorphism between every supplemental graph pair. We use
+paths of length 2, looking at counts of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up
+to $3 + k$ in the pattern).  We then investigate whether this leads to new constraints being
+generated.
 
@@
 disappearing---although sometimes we are still able to make a difference, and bear in mind that
-sometimes adding just one new constrained pair can vastly reduce the search space.
+sometimes adding just one new constrained pair can vastly reduce the search space.  A closer
+inspection of the raw data shows that for $k \ge 3$, nearly all of the instances showing a strong
+improvement are from the ``LV'' family of graphs.
 

### 2016-09-13 paper/paper.tex
More algorithm text

--- 2016-09-13 paper/paper.tex
@@
     \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\loopcomp{\mathcal{P}},
-        \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced},$
+        \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced\label{line:comp}},$
         \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
@@
     \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
-        \nl \If{$v'$ \textnormal{is not the first wildcard we have tried}}{
+        \nl \If{$v'$ \textnormal{is not the first wildcard we have tried\label{line:sym}}}{
             \nl \KwSty{continue} \;
@@
         \nl \If{\textnormal{no effectively-unit domains (treating all wildcard~values as a single
-        value) remain}}{
+            value) remain\label{line:effect}}}{
             \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
@@
 
-\cref{algorithm:sip}. This is derived from a subgraph isomorphism due to
-\citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of algorithm portfolios
-\citep{thelionpaper} was the single strongest solver. As well as the modifications to solve $k$-less
-and induced problems, we have made two simplifications: we do not use conflict-directed backjumping,
-and we do not use iterated label filtering to recalculate neighbourhood degree sequences if vertices
-are not present in any target domain after construction---in preliminary experiments, these
-techniques were not beneficial for $k > 0$.
+We bring these techniques into a full algorithm, listed as \cref{algorithm:sip}. This is derived
+from a subgraph isomorphism due to \citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of
+algorithm portfolios \citep{thelionpaper} was the single strongest solver. As well as the
+modifications to solve $k$-less and induced problems, we have made two simplifications: we do not
+use conflict-directed backjumping, and we do not use iterated label filtering to recalculate
+neighbourhood degree sequences if vertices are not present in any target domain after
+construction---in preliminary experiments, these techniques were not beneficial for $k > 0$. We also
+do not strip isolated vertices, as this is not a valid simplification in the induced case.
 
-?? Discuss how we did wildcards, effectively unit domains. The all diff propagator.
+To handle wildcards, we include $k$ additional $\bot$ values in domains, rather than a single value
+which may be used $k$ times. These are treated as having degree zero, in an attempt to maximising
+the expected number of solutions remaining during search \cite{DBLP:conf/ijcai/McCreeshPT16}. This
+technique allows us to retain the bit-parallel all different propagator used in the original
+algorithm. However, we must be careful to treat domains containing multiple wildcard values (which
+we call ``effectively unit'') specially during unit propagation (line~\ref{line:effect}), and we
+introduce a symmetry break (line~\ref{line:sym}) to try only a single wildcard value for each
+variable.
 
-?? Discuss how we do induced. We do not look at paths in the loop complements, since this is
-expensive to calculate and provides little benefit in practice on the instances we considered.
+To handle the induced case, we make use of \cref{prop:comp} (line~\ref{line:comp}). We also tested
+using path reasoning on complement graphs, but this is expensive to calculate and provides little
+benefit in practice on the instances we considered.
 

### 2016-09-13 paper/paper.tex
Made the example non-italic.
Ruthless editing

@@
 \begin{example}
-Take a pattern graph $P$ with vertices $V=\{p, a, b, c, d\}$ and edges $E=\{(a,d), (a,p), (b,c),
-(b,d), (b,p), (c,d), (c,p)\}$, which is shown in \cref{fig:klessexample} along with two target
-graphs $T_{1}$ and $T_{2}$. The degree of the vertex $p$ in $P$ is $\deg(p)=3$, the neighbours of
-$p$ are $\N(p)=\{a,b,c\}$, the neighbourhood degree sequence of $p$ is $\nds(p)=(3,3,2)$, as the
-degrees of the neighbours of $p$ are $\deg(a)=2,\ \deg(b)=3$ and $deg(c)=3$.
+Consider the pattern graph $P$ and the two target graphs $T_1$ and $T_2$ shown in
+\cref{fig:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
+$\nds(p)=(3,3,2)$.
 
-We can find a subgraph in $T_{1}$ which is non-induced isomorphic to $P$ (indicated through the bold edges and black vertices in $T_{1}$).
-The vertex $p$ can be  mapped to $t_{1}$ in the target graph $T_{1}$, where $\deg(t_{1})=5$ and $\nds(t_{1})=(5,5,4,2,2)$.
-
-There is a non-induced mapping of the pattern graph $P$ into $T_{2}$ by removing one vertex of $P$.
-This removal changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$, to $\nds(p)=(2,2)$.
+We highlight a subgraph in $T_{1}$ which is non-induced isomorphic to $P$. The vertex $p$ can be
+mapped to $t_{1}$ in the target graph $T_{1}$, as $\nds(t_{1})=(5,5,4,2,2)$.  There is a non-induced
+mapping of the pattern graph $P$ into $T_{2}$ by removing the central vertex of $P$.  This removal
+changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$ to $\nds(p)=(2,2)$.
 

### 2016-09-13 paper/paper.tex
Caption
Sliiiightly more space

@@
 
-        \node[draw=none,right of = b3,node distance=1mm, yshift=-2mm] {$t_{1}$};
+        \node[draw=none,right of = b3,node distance=1mm, yshift=-2.5mm] {$t_{1}$};
 
@@
     \end{tikzpicture}
-    \caption{$P\rightarrowtail T_{1}$, $P\lessnonind{1} T_{2}$}
-    \label{fig:klessexample}
+    \caption{There is a non-induced isomorphism $P\rightarrowtail T_{1}$ from the first graph to the
+    second, using the highlighted vertices. No such isomorphism exists to the third graph, but there
+    is a $1$-less isomorphism $P\lessnonind{1} T_{2}$ omitting vertex $b$.}\label{fig:klessexample}
 \end{figure}

### 2016-09-13 paper/paper.tex
Talk about the clique encoding

@@
 better memory layouts and propagation queues, although the algorithms are heavily inspired by
-constraint programming.}. For both problems, we create a variable for each vertex in the
-pattern graph (the smaller graph, in the case of maximum common subgraph), with domains ranging over
-the vertices in the target graph (the larger graph). For maximum common subgraph, each domain is
-given an additional $\bot$ value, meaning ``unmapped''.
+constraint programming.}, although a reduction to maximum clique is better when edge labels are
+present \citep{DBLP:conf/cp/NdiayeS11,DBLP:conf/cp/McCreeshNPS16}. For both problems, we create a variable for each vertex
+in the pattern graph (the smaller graph, in the case of maximum common subgraph), with domains
+ranging over the vertices in the target graph (the larger graph). For maximum common subgraph, each
+domain is given an additional $\bot$ value, meaning ``unmapped''.
 
@@
 problem.
-
-?? Also the clique encoding.
 

### 2016-09-13 paper/paper.tex
fixed graphs and example.

--- 2016-09-13 paper/paper.tex
@@
 \begin{example}
-Consider the pattern graph $P$ and the two target graphs $T_1$ and $T_2$ shown in
+Consider the pattern graph $P$ and the two target graphs $T$ and $U$ shown in
 \cref{fig:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
@@
 
-We highlight a subgraph in $T_{1}$ which is non-induced isomorphic to $P$. The vertex $p$ can be
-mapped to $t_{1}$ in the target graph $T_{1}$, as $\nds(t_{1})=(5,5,4,2,2)$.  There is a non-induced
-mapping of the pattern graph $P$ into $T_{2}$ by removing the central vertex of $P$.  This removal
+We highlight a subgraph in $T$ which is non-induced isomorphic to $P$. The vertex $p$ can be
+mapped to $q$ in the target graph $T$, as $\nds(q)=(5,5,4,2,2)$.  There is a non-induced
+mapping of the pattern graph $P$ into $U$ by removing $b$ of $P$.  This removal
 changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$ to $\nds(p)=(2,2)$.
@@
         \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
-        \node[fill=gray!50] (a1) {};
+        \node[fill=gray!50] (a1) [right of = d, node distance = 2cm] {};
         \node[fill=black] (b1) [right of = a1] {};
@@
 
-        \node[draw=none,right of = b3,node distance=1mm, yshift=-2mm] {$t_{1}$};
+        \node[draw=none,right of = b3,node distance=1mm, yshift=-2mm] {$q$};
 
-        \node[draw=none, below of = b3, node distance=6mm] {$T_{1}$};
+        \node[draw=none, below of = b3, node distance=6mm] {$T$};
 
@@
 
-        \node[draw=none, below of = p, node distance=6mm] {$T_{2}$};
+        \node[draw=none, below of = p, node distance=6mm] {$U$};
 
@@
     \end{tikzpicture}
-    \caption{$P\rightarrowtail T_{1}$, $P\lessnonind{1} T_{2}$}
+    \caption{$P\rightarrowtail T$, $P\lessnonind{1} U$}
     \label{fig:klessexample}
@@
 \begin{proof}[Proof of \cref{prop:paths}]
-Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
+Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, $P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the end vertex on the
 \begin{align*}
-P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
+ \\
  = & \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \} \\

### 2016-09-13 paper/paper.tex
Related work

--- 2016-09-13 paper/paper.tex
@@
 In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
-pattern graph into the target. We show that if $k$ is reasonably small (say, between 1 and 5), then
-weakened forms of degree and path based filterings are still effective in pruning the initial search
-space and in providing additional constraints respectively. We then show that combining these
-techniques leads to a practical algorithm which can scale to work with the families of graphs
-commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark family, we
-can close a substantial portion of the instances, and in many more cases, we can at least obtain an
-upper bound. This is a significant improvement over state of the art maximum common subgraph
-solvers, which cannot even fit many of these instances in RAM. Finally, we show that iteratively
-increasing $k$ gives a competitive algorithm for the maximum common induced subgraph problem.
+pattern graph into the target. (This in some ways resembles the approximate subgraph matching model
+of \citet{DBLP:conf/cp/ZampelliDD05}, although we allow any vertex to be removed.) We show that if
+$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
+filterings are still effective in pruning the initial search space and in providing additional
+constraints respectively. We then show that combining these techniques leads to a practical
+algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
+isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
+the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
+improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
+these instances in RAM. Finally, we show that iteratively increasing $k$ gives a competitive
+algorithm for the maximum common induced subgraph problem.
 

### 2016-09-13 paper/paper.tex
We say iterating later
Cite

--- 2016-09-13 paper/paper.tex
@@
     \end{tikzpicture}
-    \caption{$P\rightarrowtail T$, $P\lessnonind{1} U$}
-    \label{fig:klessexample}
+    \caption{There is a non-induced isomorphism $P\rightarrowtail T_{1}$ from the first graph to the
+    second, using the highlighted vertices. No such isomorphism exists to the third graph, but there
+    is a $1$-less isomorphism $P\lessnonind{1} T_{2}$ omitting vertex $b$.}\label{fig:klessexample}
 \end{figure}

### 2016-09-13 paper/paper.tex

@@
 
-Instead, we introduce a new algorithm, inspired by a state of the art subgraph isomorphism
-algorithm. The approach we discuss requires only $O(\left|\V(P)\right|^2\left|\V(T)\right|)$ space
-(this can be thousands of times less than maximum common subgraph approaches, once the constant
-factors and orders of $T$ in our instances are considered). We list the algorithm in
-\cref{algorithm:sip}, explain it fully in \cref{section:algorithm}, and evaluate it in
-\cref{section:evaluation}, but first we will discuss our experimental setup, and then detail some
-experiments to verify that we can gain effective domain filtering (\cref{section:degreefiltering})
-and implied constraints (\cref{section:pathfiltering}) by using subgraph isomorphism style reasoning
-about degrees and paths in the $k$-less setting.
+Instead, we introduce a new algorithm, inspired by a state of the art subgraph isomorphism algorithm
+\citep{DBLP:conf/cp/McCreeshP15}. The approach we discuss requires only
+$O(\left|\V(P)\right|^2\left|\V(T)\right|)$ space (this can be thousands of times less than maximum
+    common subgraph approaches, once the constant factors and orders of $T$ in our instances are
+considered). We list the algorithm in \cref{algorithm:sip}, explain it fully in
+\cref{section:algorithm}, and evaluate it in \cref{section:evaluation}, but first we will discuss
+our experimental setup, and then detail some experiments to verify that we can gain effective domain
+filtering (\cref{section:degreefiltering}) and implied constraints (\cref{section:pathfiltering}) by
+using subgraph isomorphism style reasoning about degrees and paths in the $k$-less setting.
 
@@
 % \end{figure}
-
-?? Talk about iterating, what to do when a vertex disappears from all target graphs.
 
@@
 larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
-\downarrow$ is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed in ??.
-Bearing in mind the disclaimer in \cref{section:setup} regarding instances not fitting in RAM, we
-see that our approach is able to close over twice as many of these instances as the previous state
-of the art. (The same conclusion holds even if every instance which is satisfiable with $k = 0$ is
-removed from the dataset.)
+\downarrow$ is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed by
+\citet{DBLP:conf/cp/McCreeshNPS16}.  Bearing in mind the disclaimer in \cref{section:setup}
+regarding instances not fitting in RAM, we see that our approach is able to close over twice as many
+of these instances as the previous state of the art. (The same conclusion holds even if every
+instance which is satisfiable with $k = 0$ is removed from the dataset.)
 

### 2016-09-13 paper/paper.tex
Unbackwards the text

--- 2016-09-13 paper/paper.tex
@@
         induced and non-induced problems, with different values of $k$. We also show the results of
-        iteratively decreasing $k$ until a solution is found, and in the induced case, the
+        iteratively increasing $k$ until a solution is found, and in the induced case, the
         performance of two leading maximum common subgraph algorithms. In the third plot, results
-        comparing our algorithm with iteratively decreasing $k$ to other approaches on maximum
+        comparing our algorithm with iteratively increasing $k$ to other approaches on maximum
         common induced subgraph instances.}\label{figure:runtimes}
@@
 \begin{proof}[Proof of \cref{prop:paths}]
-Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, $P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the end vertex on the
-\begin{align*}
- \\
- = & \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \} \\
- = & \{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} .
-\end{align*}
-So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
+Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
+$P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the
+intermediate vertices lie in both neigbour vertex sets of $p$ and $q$. We can rewrite $P_{2}$ as
+$P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}$, in other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and $q$,
+$P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \}$. So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
 

### 2016-09-13 paper/paper.tex
proof of prop4 is word-y now.

@@
         induced and non-induced problems, with different values of $k$. We also show the results of
-        iteratively increasing $k$ until a solution is found, and in the induced case, the
+        iteratively decreasing $k$ until a solution is found, and in the induced case, the
         performance of two leading maximum common subgraph algorithms. In the third plot, results
-        comparing our algorithm with iteratively increasing $k$ to other approaches on maximum
+        comparing our algorithm with iteratively decreasing $k$ to other approaches on maximum
         common induced subgraph instances.}\label{figure:runtimes}

### 2016-09-13 paper/paper.tex
fixed proof for prop4.
Applications take up space, never mind
No todos left
more fixes to proof4.
restatable props.

--- 2016-09-13 paper/paper.tex
@@
 \usepackage[ruled,vlined]{algorithm2e}
+
+% to restate the propostions
+\usepackage{thmtools,thm-restate}
+
+\declaretheorem[name=Proposition,style=definition]{proposition}
 
@@
 \theoremstyle{definition}
-\newtheorem{proposition}{Proposition}
 \newtheorem{corollary}{Corollary}
@@
 \newcommand{\loopcomp}[1]{\oset[.1ex]{\multimap}{#1}}
-% to do comments
-\usepackage{color}
-\newcommand{\todo}[1]{{\color{red} {?? [}{#1}{]}}}
 
@@
 \section{Introduction}
-\todo{talk about subgraph isomorphism applications, particularly vision}
 
@@
     \begin{center}
-        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm,node distance=10mm,fill=black}]
+        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm,node
+            distance=10mm,fill=black}, scale=0.2]
             \node[fill=uofgcobalt] (a) {};
@@
 
-\begin{proposition}\label{prop:comp}
+\begin{proposition}
+    \label{prop:comp}
 Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P
@@
 
-\begin{proposition}
-    \label{prop:deg}
+\begin{restatable}{proposition}{propdeg}\label{prop:deg}
     Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
@@
     $\deg(p) - k \le \deg(t)$.
-\end{proposition}
+\end{restatable}
 
@@
 
-\begin{proposition}\label{prop:nds}
+\begin{restatable}{proposition}{propnds}\label{prop:nds}
 If $p \lessmap{k} t$, then $\nds(p) \lesspreceq{k} \nds(t)$.
-\end{proposition}
+\end{restatable}
 
@@
 
-\begin{proposition}\label{prop:paths}
+\begin{restatable}{proposition}{proppaths}\label{prop:paths}
     Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
      $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
-\end{proposition}
+\end{restatable}
 
@@
 \section{Proofs Omitted From Main Text}
-
-\begin{proof}[Proof of \cref{prop:deg}]
+\propdeg*
+\begin{proof}
 Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$.
@@
 
-\begin{proof}[Proof of \cref{prop:nds}]
+\propnds*
+\begin{proof}
 Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
@@
 
-\begin{proof}[Proof of \cref{prop:paths}]
+\proppaths*
+\begin{proof}
 Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
@@
 As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
-\[
-\left|\N(p)\cap \N(q)\right| - k \leq \deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
-\]
+\begin{align*}
+\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k \\
+ & \leq \left|\N(t)\cap \N(u)\right|\\
+ & \leq \deg(t)
+\end{align*}
 which is

### 2016-09-13 paper/paper.tex
Conclude

@@
 
-We looked at . We saw that we could modify invariants, and that doing so still provided additional
-domain reduction and filtering power.
+By considering a restricted variation of the problem, we have been able to go some of the way
+towards tackling the maximum common subgraph problem on much larger graphs than have previously been
+possible. We saw that some invariants from the subgraph isomorphism problem can still be used,
+albeit in a weakened form, with considerable effect when a small number of vertices can be removed.
+We have by no means cracked the problem completely---our results are still far from where we
+would like them to be for use in real-world applications, and many instances remain open. However,
+for many of the open instances cases we are at least able to get upper bounds on the result for the
+first time.
 
-Relaxed form of the problem which is easier to solve. Far from making maximum common subgraph scale
-as well as subgraph isomorphism, but we can at least get somewhere.
-
-Future work.
+In future work, we will combine this approach with existing lower bounding construction methods, to
+deliver a hybrid algorithm. We also intend to allow restrictions on which vertices may or may not be
+removed, similar to the approach of \citet{DBLP:conf/cp/ZampelliDD05}, but with much stronger
+filtering now being possible.
 

### 2016-09-13 paper/paper.tex
More text in proofs section
changed figure 1

--- 2016-09-13 paper/paper.tex
@@
     \begin{center}
-        \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm,node distance=10mm,fill=black}]
-            \node[fill=uofgcobalt] (a) {};
-            \node (a1) [below left of = a] {};
-            \node (b1) [below right of = a] {};
-            \node (aa) [below right of = a1] {};
+        \begin{tikzpicture}[scale=0.6]%[every node/.style={circle, inner sep=0.5mm,node
+            %distance=10mm,fill=black}, scale=0.2]
 
-            \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
-            \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
-            \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
-            \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
-            \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
-            \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
-            \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
-            \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};
+            \begin{scope}[xshift=-1cm, yshift=-3cm, color=black]
+            \node at (0, -0.5) {$P$};
+            \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
+            \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
+            \node [fill, circle, inner sep=1.5pt] (c) at (0,1) {};
+            \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
+            \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};
 
-            \node (aaa) [below of =aa, node distance=20mm] {};
+            \path[solid] (a) edge (b) edge (c) edge (d)
+                (e) edge (b) edge (c) edge (d);
+            % \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
+            % \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
+            % \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
+            % \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
+            % \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
+            % \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
+            % \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
+            % \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};
 
-            \path[dotted] (a) edge (a1) edge (b1);
-            \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
-                (a1) edge (b1)
-                (aaa) edge (a2) edge (b2)
-                (a2) edge (aa2) edge (ab2)
-                (b2) edge (ba2) edge (bb2);
-            \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
-                (bc2) edge (bb2) edge (ba2);
+            % \node (aaa) [below of =aa, node distance=20mm] {};
+            %
+            % \path[dotted] (a) edge (a1) edge (b1);
+            % \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
+            %     (a1) edge (b1)
+            %     (aaa) edge (a2) edge (b2)
+            %     (a2) edge (aa2) edge (ab2)
+            %     (b2) edge (ba2) edge (bb2);
+            % \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
+            %     (bc2) edge (bb2) edge (ba2);
+            %
+            % \node [cross] {};
+            \end{scope}
 
-            \node [cross] {};
+            \begin{scope}[xshift=2cm, yshift=-3cm, color=black]
+            \node at (0, -0.5) {$T$};
+            \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
+            \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
+            \node [fill, circle, inner sep=1.5pt] (c) at (1,2) {};
+            \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
+            \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};
+            \node [fill, circle, inner sep=1.5pt] (f) at (1,0) {};
+            \node [fill, circle, inner sep=1.5pt] (g) at (2,0) {};
+            \node [fill, circle, inner sep=1.5pt] (h) at (2,2) {};
+
+            \path[solid] (a) edge (b) edge (d)
+                (e) edge (b) edge (d)
+                (d) edge (c) edge (f)
+                (c) edge (h)
+                (f) edge (g);
+
+            % \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
+            % \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
+            % \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
+            % \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
+            % \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
+            % \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
+            % \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
+            % \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};
+
+            % \node (aaa) [below of =aa, node distance=20mm] {};
+            %
+            % \path[dotted] (a) edge (a1) edge (b1);
+            % \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
+            %     (a1) edge (b1)
+            %     (aaa) edge (a2) edge (b2)
+            %     (a2) edge (aa2) edge (ab2)
+            %     (b2) edge (ba2) edge (bb2);
+            % \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
+            %     (bc2) edge (bb2) edge (ba2);
+            %
+            % \node [cross] {};
+            \end{scope}
+
         \end{tikzpicture}
-        \caption{Example of  ``as much of the pattern'' as possible.}
+        \caption{Notice that $P$ would be isormorphic to a subgraph of $T$ if the middle vertex in the diamond is removed.}
         \label{fig:subgraphexample}
@@
 As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
-\[
-\left|\N(p)\cap \N(q)\right| - k \leq \deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
-\]
+\begin{align*}
+\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k\leq \\
+ &\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
+\end{align*}
 which is

### 2016-09-13 paper/paper.tex

@@
 
-\begin{proof}[Proof of \cref{prop:deg}]
+The following proofs have been omitted from the main text. If the reviewers feel they are helpful
+and not obvious, we will pay for an extra page to include them.
+
+\bigskip
+
+\propdeg*
+\begin{proof}
 Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$.
@@
 
-\begin{proof}[Proof of \cref{prop:nds}]
+\bigskip
+
+\propnds*
+\begin{proof}
 Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
@@
 
-\begin{proof}[Proof of \cref{prop:paths}]
+\bigskip
+
+\proppaths*
+\begin{proof}
 Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
@@
 \begin{align*}
-\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k\leq \\
- &\leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)
+\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k \\
+ & \leq \left|\N(t)\cap \N(u)\right|\\
+ & \leq \deg(t)
 \end{align*}

### 2016-09-13 paper/paper.tex
Muck around with the example

@@
 
-            \begin{scope}[xshift=2cm, yshift=-3cm, color=black]
+            \begin{scope}[xshift=3cm, yshift=-3cm, color=black]
             \node at (0, -0.5) {$T$};
@@
         \end{tikzpicture}
-        \caption{Notice that $P$ would be isormorphic to a subgraph of $T$ if the middle vertex in the diamond is removed.}
+        \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
+        the central vertex in the diamond is removed, then a subgraph isomorphism exists.}
         \label{fig:subgraphexample}

### 2016-09-13 paper/paper.tex
Centering, not center
Gratuitous mucking around

@@
 recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
-vertices, the state of the art for the maximum common subgraph problem becomes computationally
-infeasible at only 35 vertices when working with unlabelled graphs
-\citep{DBLP:conf/cp/McCreeshNPS16}. This is largely because strong inference, based upon the degrees
-of vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
+vertices, the state of the art for the maximum common subgraph problem
+\citep{DBLP:conf/cp/McCreeshNPS16} becomes computationally infeasible at only 35 vertices when
+working with unlabelled graphs. This is largely because strong inference, based upon the degrees of
+vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
 \citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
@@
 In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
-pattern graph into the target. (This in some ways resembles the approximate subgraph matching model
-of \citet{DBLP:conf/cp/ZampelliDD05}, although we allow any vertex to be removed.) We show that if
-$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
-filterings are still effective in pruning the initial search space and in providing additional
-constraints respectively. We then show that combining these techniques leads to a practical
-algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
-isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
-the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
-improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
-these instances in RAM. Finally, we show that iteratively increasing $k$ gives a competitive
-algorithm for the maximum common induced subgraph problem.
+pattern graph into the target---we show an example in \cref{fig:subgraphexample}. (This in some
+ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
+although we allow any vertex to be removed.) We show that if $k$ is reasonably small (say, between 1
+and 5), then weakened forms of degree and path based filterings are still effective in pruning the
+initial search space and in providing additional constraints respectively. We then show that
+combining these techniques leads to a practical algorithm which can scale to work with the families
+of graphs commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark
+family, we can close a substantial portion of the instances, and in many more cases, we can at least
+obtain an upper bound. This is a significant improvement over state of the art maximum common
+subgraph solvers, which cannot even fit many of these instances in RAM. Finally, we show that
+iteratively increasing $k$ gives a competitive algorithm for the maximum common induced subgraph
+problem.
 
 \begin{figure}
-    \begin{center}
+    \centering
     \begin{tikzpicture}[scale=0.6]%[every node/.style={circle, inner sep=0.5mm,node
@@
     \label{fig:subgraphexample}
-    \end{center}
 \end{figure}

### 2016-09-13 paper/paper.tex
Easy changes first

@@
 \Crefname{figure}{Figure}{Figures}
+\crefname{section}{Section}{Sections}
+\Crefname{section}{Section}{Sections}
+\crefname{proposition}{Proposition}{Propositions}
+\Crefname{proposition}{Proposition}{Propositions}
 
@@
     number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
-    their effectiveness. We are then able to solve this problem on the standard SIP problem
+    their effectiveness. We are then able to solve this problem on the standard problem
     instances used to benchmark subgraph isomorphism algorithms, despite these instances being
@@
 many vertices of the pattern into the target as possible. In the induced case, this is known as the
-maximum common induced subgraph problem (we discuss the non-induced case below). However, although
+maximum common induced subgraph problem (we discuss the non-induced case in
+\cref{section:definitions}). However, although
 recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
@@
 \end{figure}
-\subsection{Definitions and Notations}
+\subsection{Definitions and Notations} \label{section:definitions}
 
@@
 isomorphism $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
-We define a $k$-less-subgraph isomorphism from $P$ to $T$ to be a subgraph isomorphism from all but
+We define a $k$-less subgraph isomorphism from $P$ to $T$ to be a subgraph isomorphism from all but
 $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
@@
 Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P
-\hookrightarrow T$ if and only if $i$ satisfies both the definition of $P \rightarrowtail T$ and
-of $\loopcomp{P} \rightarrowtail \loopcomp{T}$.
+\hookrightarrow T$ if and only if $i$ satisfies $P \rightarrowtail T$ and
+$\loopcomp{P} \rightarrowtail \loopcomp{T}$.
 Similarly, $i$ satisfies the definition of $P
-\lessind{k} T$ if and only if $i$ satisfies both the definition of $P \lessnonind{k} T$ and of
+\lessind{k} T$ if and only if $i$ satisfies both $P \lessnonind{k} T$ and
 $\loopcomp{P}
@@
 
-A common induced subgraph of graphs $G$ and $H$ is a graph $P$, together with two induced subgraph
-isomorphisms to $G$ and $H$; a maximum common induced subgraph is a common induced subgraph with as
+A \emph{common induced subgraph} of graphs $G$ and $H$ is a graph $P$, together with two induced subgraph
+isomorphisms to $G$ and $H$; a \emph{maximum common induced subgraph} is a common induced subgraph with as
 many vertices as possible. An induced $k$-less subgraph isomorphism $P \lessind{k} T$ is equivalent
@@
     \end{tikzpicture}
-    \caption{There is a non-induced isomorphism $P\rightarrowtail T_{1}$ from the first graph to the
+    \caption{There is a non-induced isomorphism $P\rightarrowtail T$ from the first graph to the
     second, using the highlighted vertices. No such isomorphism exists to the third graph, but there
-    is a $1$-less isomorphism $P\lessnonind{1} T_{2}$ omitting vertex $b$.}\label{fig:klessexample}
+    is a $1$-less isomorphism $P\lessnonind{1} U$ omitting vertex $b$.}\label{fig:klessexample}
 \end{figure}
@@
 
-Constraints are used to ensure that adjacency pairs of vertices are mapped to adjacenct pairs of
+Constraints are used to ensure that adjacent pairs of vertices are mapped to adjacenct pairs of
 vertices. For the maximum common subgraph case, any pair of assignments with $\bot$ as either value
-is also permitted.  To handle the induced case, rather than the more usual approach of directly
+is also permitted.  To handle the induced case, rather than the usual approach of directly
 having constraints for non-adjacent pairs of vertices, we will make use of \cref{prop:comp} by
-seeking an $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
-\rightarrowtail \loopcomp{T}$. Finally, an all different except $\bot$ constraint ensures
+seeking a mapping $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
+\rightarrowtail \loopcomp{T}$. Finally, an ``all different except $\bot$ constraint'' ensures
 injectivity.
@@
 
-A non-induced $k$-less-subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph isomorphism
-between $P$ and $T$, with $k$ extra universally-adjacent vertices added to $T$. However, using such
-an approach is not ideal, because it would introduce symmetries; for induced $k$-less-subgraph
+There are three easy ways we might try to approach this problem.
+A non-induced $k$-less subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph isomorphism
+between $P$ and $T$, with $k$ extra universally-adjacent vertices added to $T$, and so we could try
+solving subgraph isomorphism with a modified target graph. However, using such
+an approach is not ideal, because it would introduce symmetries; for induced $k$-less subgraph
 isomorphisms, an approach based around adding vertices to $T$ cannot work at all.
 Another algorithmic approach could be to try each way of removing $k$ vertices from the pattern
-graph, and solving the subgraph isomorphism problem in turn. This approach might be feasible for $k
+graph, and solving each subgraph isomorphism problem in turn. This approach might be feasible for $k
 = 1$, although it would involve a lot of duplication of search effort, but for larger values of $k$
@@
 decision problem. However, both the maximum common subgraph algorithm and the clique encoding
-require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$ memory, which is extremely problematic on the
-instances we wish to work with.
+require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$ memory \citep{DBLP:conf/cp/McCreeshNPS16},
+which is extremely problematic on the instances we wish to work with.
 
@@
 and graphs close to the satisfiable-unsatisfiable phase transition
-\cite{DBLP:conf/ijcai/McCreeshPT16}; all these instances are available in a simple text
+\cite{DBLP:conf/ijcai/McCreeshPT16}. All of these instances are available in a simple text
 format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.  Note that many of these instances
@@
 instances as having timed out. The situation for the clique encoding is even worse, and 3,653 of
-these instances do not fit in RAM. In contrast, for our algorithm, every instance fits comfortably
-(at least on modern server-class hardware).
-
-\section{Domain Filtering using Degrees}\label{section:degreefiltering}
+these instances do not fit in 64GBytes of RAM. In contrast, for our algorithm, every instance fits
+comfortably.  \section{Domain Filtering using Degrees}\label{section:degreefiltering}
 
@@
     Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
-    $k$-less-subgraph isomorphisms, if $p \lessmap{k} t$ then
+    $k$-less subgraph isomorphisms, if $p \lessmap{k} t$ then
     $\deg(p) - k \le \deg(t)$.
@@
 A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $\N(p) = \{ q \in \V(P) :
- p \text{ and } q \text{ are adjacent }\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
+ p~\textnormal{and}~q~\textnormal{are adjacent}\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
 degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
@@
 \preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
-t_j$.  When considering a $k$-less-subgraph isomorphism we say that $S \lesspreceq{k}
-T$ if $n - k \leq m$ and $\forall s_i \in S \setminus S_k$, where $S_k$ is a subsequence of $S$
-containing up to $k$ members of $S$, there exists a distinct $t_j \in T$ with $s_i - k \leq t_j$.
+t_j$.  When considering a $k$-less subgraph isomorphism we say that $S \lesspreceq{k} T$ if $n - k
+\leq m$, and if there exists some subsequence $S_k$ of $S$ containing up to $k$ members such that
+$\forall s_i \in S \setminus S_k$, there exists a distinct $t_j \in T$ with $s_i - k \leq t_j$.
 
@@
 Since both $\nds(p)$ and $\nds(t)$ are non-ascending, without loss of generality we can replace
-$S \setminus S_k$ from the definition of $S \lesspreceq{k} T$ with $S[k, n]$.
+$S \setminus S_k$ from the definition of $S \lesspreceq{k} T$ with the subsequence consisting of all
+    but the first $k$ members of $S$.
 \end{corollary}
@@
 
-In \cref{figure:ids} we show that this is effective in practice: we show the amount of domain reduction
-we can achieve at the top of search by using invariants and a fixed $k$, compared to the search
-space size for the maximum common induced subgraph problem. (The results on the non-induced version
-show a similar but slightly weaker trend.)
+\Cref{figure:ids} demonstrates that this is effective in practice: we show the amount of domain
+reduction we can achieve at the top of search by using invariants and a fixed $k$, compared to the
+search space size for the maximum common induced subgraph problem. (The results on the non-induced
+version show a similar but slightly weaker trend.)
 
 Some other invariants do not translate. For example, another rule which can be effective on regular
-graphs involves count the number of neighbours of a vertex which are present in a triangle
+graphs involves counting the number of neighbours of a vertex which are present in a triangle
 \cite{mckay2014practical}. Removing a single vertex can alter this count arbitrarily, so we cannot
@@
     For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$. The
-    vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent, if there are at least $n$ simple paths of
-    length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less-subgraph isomorphism
-    $P \lessnonind{k} T$ induces a new $k$-less-subgraph isomorphism
+    vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent if there are at least $n$ simple paths of
+    length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less subgraph isomorphism
+    $P \lessnonind{k} T$ induces a new $k$-less subgraph isomorphism
     $P^{n+k, 2}\lessnonind{k} T^{n, 2}$.
@@
 construct \emph{supplemental graphs}, and find a mapping which is simultaneously a non-induced subgraph
-isomorphism between every supplemental graph pair. We use paths of length 2, looking at counts of 1,
-2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).  We then
+isomorphism between every supplemental graph pair. We use paths of length 2, looking at path counts
+of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).  We then
 investigate whether this leads to new constraints being generated.
@@
 constraint. We define the permitted assignment pair ratio to be the proportion of assignment pairs
-which are permitted.  Finally, we scatter plot the permitted assignment pair ratio with and without
-supplemental graphs\footnote{Because of the large sizes of the domains, we randomly sample one
-million pairs rather than considering every pair. In some cases, we have nearly a thousand domains,
-each with nearly ten thousand values---a complete quadratic calculation involving even a trivial
-arithmetic operation on this would take many hours.}.
+which are permitted.  Finally, in \cref{figure:constraints} we scatter plot the permitted assignment
+pair ratio with and without supplemental graphs\footnote{Because of the large sizes of the domains,
+we randomly sample one million pairs rather than considering every pair. In some cases, we have
+nearly a thousand domains, each with nearly ten thousand values---a complete quadratic calculation
+involving even a trivial arithmetic operation on this would take many hours.}.
 
@@
     \nl \While{\KwSty{true}}{
-        \nl \If{\textnormal{no effectively-unit domains (treating all wildcard~values as a single
-            value) remain\label{line:effect}}}{
+        \nl \If{\textnormal{no effectively-unit domains remain (treating all wildcard~values as a single
+            value)\label{line:effect}}}{
             \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
@@
 \nl \Begin{
-\nl $(H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,\emptyset,\,0)$ \;
+\nl $(H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,0)$ \;
 \nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
@@
 
-We bring these techniques into a full algorithm, listed as \cref{algorithm:sip}. This is derived
-from a subgraph isomorphism due to \citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of
-algorithm portfolios \citep{thelionpaper} was the single strongest solver. As well as the
-modifications to solve $k$-less and induced problems, we have made two simplifications: we do not
-use conflict-directed backjumping, and we do not use iterated label filtering to recalculate
-neighbourhood degree sequences if vertices are not present in any target domain after
-construction---in preliminary experiments, these techniques were not beneficial for $k > 0$. We also
-do not strip isolated vertices, as this is not a valid simplification in the induced case.
+\Cref{algorithm:sip} integrates these techniques into a full algorithm. This is derived from an
+algorithm due to \citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of using portfolios
+of subgraph isomorphism algorithms was the single strongest solver portfolios \citep{thelionpaper}.
+As well as the modifications to solve $k$-less and induced problems, we have made two
+simplifications: we do not use conflict-directed backjumping, and we do not use iterated label
+filtering to recalculate neighbourhood degree sequences if vertices are not present in any target
+domain after construction---in preliminary experiments, these techniques were not beneficial for $k
+> 0$. We also do not strip isolated vertices, as this is not a valid simplification in the induced
+case.
 
@@
     \includegraphics*{gen-graph-runtimes.pdf}
-    \caption{In the first two plots, the cumulative number of instances solved over time, for the
+    \caption{In the first two plots we show the cumulative number of instances solved over time, for the
         induced and non-induced problems, with different values of $k$. We also show the results of
         iteratively increasing $k$ until a solution is found, and in the induced case, the
-        performance of two leading maximum common subgraph algorithms. In the third plot, results
-        comparing our algorithm with iteratively increasing $k$ to other approaches on maximum
+        performance of two leading maximum common subgraph algorithms. In the third plot we show results
+        comparing iteratively increasing $k$ with our algorithm to other approaches on maximum
         common induced subgraph instances.}\label{figure:runtimes}
@@
     \caption{The proportion of instances, in different families, which become satisfiable for
-    increasing values of $k$. The larger instances are those where we can prove unsatisfiability for
+    increasing values of $k$. The ``larger'' instances are those where we can prove unsatisfiability for
     $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
@@
 We now evaluate our algorithm and show that it is effective in practice, even on the larger subgraph
-isomorphism instances. In \cref{figure:runtimes} we give cumulative distribution plots for the
-induced and non-induced problems, with $k$ ranging from $0$ to $5$ (we discuss the dotted lines in
-this plot below). The results are strong: with $k = 0$ we may solve nearly every instance, whilst
-even at $k = 5$ we can solve over $4,000$ instances in both variants.
+isomorphism instances. In the first two plots of \cref{figure:runtimes} we give cumulative
+distributions for the induced and non-induced problems, with $k$ ranging from $0$ to $5$ (we
+discuss the dotted lines in this plot below). The results are strong: with $k = 0$ we may solve
+nearly every instance, whilst even at $k = 5$ we can solve over $4,000$ instances in both variants.
 
@@
 $k$ (this is simply due to there being many vertices with loops in some pattern graphs, but no loops
-at all in the targets). However, in several of the remaining families we can over double the number
-of instances for which exact solutions are known, and gain upper bounds on many more. This is
-particularly interesting for the ``images-CVIU11'' family, where the size of the solution has a
-direct real-world interpretation in terms of closeness of image matching.
+at all in the targets). However, in several of the remaining families we can more than double the
+number of instances for which exact solutions are known, and gain upper bounds on many more. This is
+particularly interesting for the ``images-CVIU11'' family due to \citet{cviu11}, where the size of
+the solution has a direct real-world interpretation in terms of closeness of image matching.
 
@@
 \downarrow$ is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed by
-\citet{DBLP:conf/cp/McCreeshNPS16}.  Bearing in mind the disclaimer in \cref{section:setup}
-regarding instances not fitting in RAM, we see that our approach is able to close over twice as many
-of these instances as the previous state of the art. (The same conclusion holds even if every
-instance which is satisfiable with $k = 0$ is removed from the dataset.)
+\citet{DBLP:conf/cp/McCreeshNPS16}.  Recalling the disclaimer in \cref{section:setup}
+regarding instances not fitting in the 64GBytes of RAM we have available, we see that our approach is
+able to close over twice as many of these instances as the previous state of the art. (The same
+conclusion holds even if every instance which is satisfiable with $k = 0$ is removed from the
+dataset.)
 
@@
 would like them to be for use in real-world applications, and many instances remain open. However,
-for many of the open instances cases we are at least able to get upper bounds on the result for the
+for many of the open instances we are at least able to get upper bounds on the result for the
 first time.
@@
 Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$
-is some subset of $P$ with $\left| P_k \right| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
+is some subset of $P$ with $\left| P_k \right| \leq k$, we have $q \lessmap{k} u$, where $u \in N(t)$ and
 each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
@@
 \begin{proof}
-Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
-$P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the
-intermediate vertices lie in both neigbour vertex sets of $p$ and $q$. We can rewrite $P_{2}$ as
-$P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}$, in other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and $q$,
-$P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \}$. So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
+Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, \[P_{2} = \{((p,x),(x,q)) :
+(p,x),(x,q)\in \operatorname{E}(P) \}\textnormal{.}\] As we are looking at paths of length 2,
+the intermediate vertices lie in both neighbour vertex sets of $p$ and $q$. We can rewrite
+$P_{2}$ as \[P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}\textnormal{,}\] in
+other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and
+$q$, \[ P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} \textnormal{.}\] Therefore
+$\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
 
-If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
+If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of
+    the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$,
 \[
@@
 \end{align*}
-which is
+which tells us
 \[

### 2016-09-13 paper/paper.tex
Patrick's fixes
Move the example
More tweaking

@@
 subgraph is sought---this problem is usually called the maximum common \emph{partial} subgraph
-problem instead. However, this is not what we will be discussing in this paper: maximum common
-subgraph problems are symmetric in their inputs, but when discussing the non-induced case we are
-allowing extra edges only in the target graph, not in the pattern.
-
-\begin{example}
-Consider the pattern graph $P$ and the two target graphs $T$ and $U$ shown in
-\cref{fig:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
-$\nds(p)=(3,3,2)$.
-
-We highlight a subgraph in $T$ which is non-induced isomorphic to $P$. The vertex $p$ can be
-mapped to $q$ in the target graph $T$, as $\nds(q)=(5,5,4,2,2)$.  There is a non-induced
-mapping of the pattern graph $P$ into $U$ by removing $b$ of $P$.  This removal
-changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$ to $\nds(p)=(2,2)$.
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
-        \node[fill=black] (p) {};
-        \node[fill=black] (b) [above of = p,node distance=10mm] {};
-        \node[fill=black] (a) [left of = b] {};
-        \node[fill=black] (c) [right of = b] {};
-        \node[fill=black] (d) [above of = b,node distance=10mm] {};
-
-        \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
-        \node[draw=none,left of = a,node distance=3mm,yshift=-1mm] {$a$};
-        \node[draw=none,left of = b,node distance=3mm,yshift=-1mm] {$b$};
-        \node[draw=none,right of = c,node distance=3mm,yshift= 1mm] {$c$};
-        \node[draw=none,above of = d,node distance=3mm,yshift=1mm] {$d$};
-
-        \node[draw=none, below of = p, node distance=6mm] {$P$};
-
-        \path (p) edge (a) edge (b) edge (c)
-            (a) edge (d)
-            (b) edge (c) edge (d)
-            (c) edge (d);
-        \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
-        \node[fill=gray!50] (a1) [right of = d, node distance = 2cm] {};
-        \node[fill=black] (b1) [right of = a1] {};
-        \node[fill=gray!50] (c1) [right of = b1] {};
-        \node[fill=black] (a2) [below of = a1] {};
-        \node[fill=black] (b2) [right of = a2] {};
-        \node[fill=black] (c2) [right of = b2] {};
-        \node[fill=gray!50] (a3) [below of = a2] {};
-        \node[fill=black] (b3) [right of = a3] {};
-        \node[fill=gray!50] (c3) [right of = b3] {};
-
-        \node[draw=none,right of = b3,node distance=1mm, yshift=-2mm] {$q$};
-
-        \node[draw=none, below of = b3, node distance=6mm] {$T$};
-
-        \path[color=gray!50] (a1) edge (b1) edge (a2)
-            (b1) edge (c1)
-            (c1) edge (c2)
-            (a2) edge (b2) edge (a3)
-            (c2) edge (c3)
-            (a3) edge (b3)
-            (b3) edge (c3);
-        \path[line width=0.4mm] (b1) edge (a2) edge (b2) edge (c2)
-            (a2) edge (b3)
-            (b2) edge (c2) edge (b3)
-            (c2) edge (b3);
-    \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
-        \node[fill=black] (p) {};
-        \node[draw=none] (b) [above of = p,node distance=10mm] {};
-        \node[fill=black] (a) [left of = b] {};
-        \node[fill=black] (c) [right of = b] {};
-        \node[fill=black] (d) [above of = b,node distance=10mm] {};
-
-        \node[draw=none, below of = p, node distance=6mm] {$U$};
-
-        \path (p) edge (a) edge (c)
-            (a) edge (d)
-            (c) edge (d);
-    \end{tikzpicture}
-    \caption{There is a non-induced isomorphism $P\rightarrowtail T$ from the first graph to the
-    second, using the highlighted vertices. No such isomorphism exists to the third graph, but there
-    is a $1$-less isomorphism $P\lessnonind{1} U$ omitting vertex $b$.}\label{fig:klessexample}
-\end{figure}
-\end{example}
+problem instead \citep{DBLP:conf/cp/NdiayeS11}. However, this is not what we will be discussing in
+this paper: maximum common subgraph problems are symmetric in their inputs, but when discussing the
+non-induced case we are allowing extra edges only in the target graph, not in the pattern.
 
@@
 isomorphism also allows us to generate additional implied constraints, which we discuss in
-\cref{section:pathfiltering}. Neither of these techniques are valid for the maximum common subgraph
-problem.
+\cref{section:pathfiltering}. However, neither of these techniques are valid for the maximum common
+subgraph problem.
 
@@
 
+\begin{figure}[t]
+    \centering
+    \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+        \node[fill=black] (p) {};
+        \node[fill=black] (b) [above of = p,node distance=10mm] {};
+        \node[fill=black] (a) [left of = b] {};
+        \node[fill=black] (c) [right of = b] {};
+        \node[fill=black] (d) [above of = b,node distance=10mm] {};
+
+        \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
+        \node[draw=none,left of = a,node distance=3mm,yshift=-1mm] {$a$};
+        \node[draw=none,left of = b,node distance=3mm,yshift=-1mm] {$b$};
+        \node[draw=none,right of = c,node distance=3mm,yshift= 1mm] {$c$};
+        \node[draw=none,above of = d,node distance=3mm,yshift=1mm] {$d$};
+
+        \node[draw=none, below of = p, node distance=6mm] {$P$};
+
+        \path (p) edge (a) edge (b) edge (c)
+            (a) edge (d)
+            (b) edge (c) edge (d)
+            (c) edge (d);
+        \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+        \node[fill=gray!50] (a1) [right of = d, node distance = 2cm] {};
+        \node[fill=black] (b1) [right of = a1] {};
+        \node[fill=gray!50] (c1) [right of = b1] {};
+        \node[fill=black] (a2) [below of = a1] {};
+        \node[fill=black] (b2) [right of = a2] {};
+        \node[fill=black] (c2) [right of = b2] {};
+        \node[fill=gray!50] (a3) [below of = a2] {};
+        \node[fill=black] (b3) [right of = a3] {};
+        \node[fill=gray!50] (c3) [right of = b3] {};
+
+        \node[draw=none,right of = b3,node distance=1mm, yshift=-2mm] {$q$};
+
+        \node[draw=none, below of = b3, node distance=6mm] {$T$};
+
+        \path[color=gray!50] (a1) edge (b1) edge (a2)
+            (b1) edge (c1)
+            (c1) edge (c2)
+            (a2) edge (b2) edge (a3)
+            (c2) edge (c3)
+            (a3) edge (b3)
+            (b3) edge (c3);
+        \path[line width=0.4mm] (b1) edge (a2) edge (b2) edge (c2)
+            (a2) edge (b3)
+            (b2) edge (c2) edge (b3)
+            (c2) edge (b3);
+    \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+        \node[fill=black] (p) {};
+        \node[draw=none] (b) [above of = p,node distance=10mm] {};
+        \node[fill=black] (a) [left of = b] {};
+        \node[fill=black] (c) [right of = b] {};
+        \node[fill=black] (d) [above of = b,node distance=10mm] {};
+
+        \node[draw=none, below of = p, node distance=6mm] {$U$};
+
+        \path (p) edge (a) edge (c)
+            (a) edge (d)
+            (c) edge (d);
+    \end{tikzpicture}
+    \caption{There is a non-induced isomorphism $P\rightarrowtail T$ from the first graph to the
+    second, using the highlighted vertices. No such isomorphism exists to the third graph, but there
+    is a $1$-less isomorphism $P\lessnonind{1} U$ omitting vertex $b$.}\label{fig:klessexample}
+\end{figure}
+
 \begin{restatable}{proposition}{propnds}\label{prop:nds}
@@
 
-\Cref{fig:klessexample} illustrates the three cases possible when filtering by neighbourhood degree
+\begin{example}
+Consider the pattern graph $P$ and the two target graphs $T$ and $U$ shown in
+\cref{fig:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
+$\nds(p)=(3,3,2)$.
+We highlight a subgraph in $T$ which is non-induced isomorphic to $P$. The vertex $p$ can be
+mapped to $q$ in the target graph $T$, as $\nds(q)=(5,5,4,2,2)$.  There is a non-induced
+mapping of the pattern graph $P$ into $U$ by removing $b$ of $P$.  This removal
+changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$ to $\nds(p)=(2,2)$.
+\end{example}
+
+\Cref{fig:klessexample} also illustrates the three cases possible when filtering by neighbourhood degree
 sequence.  Removing the top node causes each entry in $\nds(p)$ to be reduced; removing the
@@
     }
-    \nl \lIf{\FuncSty{propagate}(D)}{$\KwSty{return}~\FuncSty{search}(L, D, k)$}
+    \nl \lIf{\FuncSty{propagate}(L, D)}{$\KwSty{return}~\FuncSty{search}(L, D, k)$}
     \nl \lElse{$\KwSty{return}~\KwSty{false}$}
@@
         \nl $D'_v \gets \{ v' \} $ \;
-        \nl \If{\FuncSty{propagate}(D')}{
+        \nl \If{\FuncSty{propagate}(L, D')}{
             \nl \If{$\FuncSty{search}(L, \{ D \in D' : \left|D\right| > 1 \}, k)$}{

### 2016-09-13 paper/paper.tex
More citations

@@
 The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
-\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
-edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
-mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
-many vertices of the pattern into the target as possible. In the induced case, this is known as the
-maximum common induced subgraph problem (we discuss the non-induced case in
-\cref{section:definitions}). However, although
-recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
-vertices, the state of the art for the maximum common subgraph problem
+\emph{target} graph. This is used in many areas, including bioinformatics \citep{Bonnici:2013},
+computer vision \citep{cviu11,pr15}, malware detection \citep{DBLP:conf/dimva/BruschiMM06},
+compilers \citep{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, and pattern recognition
+\citep{Conte:2004}.  The problem comes in two forms: in the non-induced variant, edges must be
+mapped to edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges
+may only be mapped to non-edges.
+
+When a pattern cannot be found, we may wish to be given a result which maps as many vertices of the
+pattern into the target as possible. In the induced case, this is known as the maximum common
+induced subgraph problem (we discuss the non-induced case in \cref{section:definitions}). However,
+although recent subgraph isomorphism algorithms are comfortable working with graphs with thousands
+of vertices, the state of the art for the maximum common subgraph problem
 \citep{DBLP:conf/cp/McCreeshNPS16} becomes computationally infeasible at only 35 vertices when

### 2016-09-13 paper/paper.tex
Use citep

@@
 For datasets, we use the same 5,725 instances used in a recent work on portfolios of algorithms for
-subgraph isomorphism \cite{thelionpaper}. This collection includes randomly generated scale-free
-graphs \cite{constraints10}, an assortment of real-world graphs of varying sizes \cite{LV02},
+subgraph isomorphism \citep{thelionpaper}. This collection includes randomly generated scale-free
+graphs \citep{constraints10}, an assortment of real-world graphs of varying sizes \citep{LV02},
 randomly generated graph pairs (using bounded degree, regular mesh, and uniform models; all are
-satisfiable), segmented images~\cite{pr15,cviu11}, meshes from modelling 3D objects \cite{cviu11},
+satisfiable), segmented images~\citep{pr15,cviu11}, meshes from modelling 3D objects \citep{cviu11},
 and graphs close to the satisfiable-unsatisfiable phase transition
-\cite{DBLP:conf/ijcai/McCreeshPT16}. All of these instances are available in a simple text
+\citep{DBLP:conf/ijcai/McCreeshPT16}. All of these instances are available in a simple text
 format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.  Note that many of these instances
@@
 graphs involves counting the number of neighbours of a vertex which are present in a triangle
-\cite{mckay2014practical}. Removing a single vertex can alter this count arbitrarily, so we cannot
+\citep{mckay2014practical}. Removing a single vertex can alter this count arbitrarily, so we cannot
 make use of this fact.
@@
 which may be used $k$ times. These are treated as having degree zero, in an attempt to maximising
-the expected number of solutions remaining during search \cite{DBLP:conf/ijcai/McCreeshPT16}. This
+the expected number of solutions remaining during search \citep{DBLP:conf/ijcai/McCreeshPT16}. This
 technique allows us to retain the bit-parallel all different propagator used in the original

### 2016-09-13 paper/paper.tex
Move around and reduce

@@
 
-\subsection{Algorithms for the $k$-Less Problem}
-
-There are three easy ways we might try to approach this problem.
+There are three easy ways we might try to extend existing algorithms for this problem.
 A non-induced $k$-less subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph isomorphism
@@
 
-Instead, we introduce a new algorithm, inspired by a state of the art subgraph isomorphism algorithm
-\citep{DBLP:conf/cp/McCreeshP15}. The approach we discuss requires only
+Instead, this paper introduces a new algorithm, inspired by a state of the art subgraph isomorphism
+algorithm \citep{DBLP:conf/cp/McCreeshP15}. The approach we discuss requires only
 $O(\left|\V(P)\right|^2\left|\V(T)\right|)$ space (this can be thousands of times less than maximum
 common subgraph approaches, once the constant factors and orders of $T$ in our instances are
-considered). We list the algorithm in \cref{algorithm:sip}, explain it fully in
-\cref{section:algorithm}, and evaluate it in \cref{section:evaluation}, but first we will discuss
-our experimental setup, and then detail some experiments to verify that we can gain effective domain
-filtering (\cref{section:degreefiltering}) and implied constraints (\cref{section:pathfiltering}) by
-using subgraph isomorphism style reasoning about degrees and paths in the $k$-less setting.
+considered).
 
@@
 eliminate some infeasible values from domains.
-
-\begin{restatable}{proposition}{propdeg}\label{prop:deg}
-    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
-    $k$-less subgraph isomorphisms, if $p \lessmap{k} t$ then
-    $\deg(p) - k \le \deg(t)$.
-\end{restatable}
-
-A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $\N(p) = \{ q \in \V(P) :
- p~\textnormal{and}~q~\textnormal{are adjacent}\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
-degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
-neighbours.
-
-Let $S = ( s_1 , \ldots , s_n )$ and $T = ( t_1 , \ldots , t_m)$ be two sequences.  We say that $S
-\preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
-t_j$.  When considering a $k$-less subgraph isomorphism we say that $S \lesspreceq{k} T$ if $n - k
-\leq m$, and if there exists some subsequence $S_k$ of $S$ containing up to $k$ members such that
-$\forall s_i \in S \setminus S_k$, there exists a distinct $t_j \in T$ with $s_i - k \leq t_j$.
 
@@
 \end{figure}
+
+\begin{restatable}{proposition}{propdeg}\label{prop:deg}
+    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
+    $k$-less subgraph isomorphisms, if $p \lessmap{k} t$ then
+    $\deg(p) - k \le \deg(t)$.
+\end{restatable}
+
+A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $\N(p) = \{ q \in \V(P) :
+ p~\textnormal{and}~q~\textnormal{are adjacent}\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
+degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
+neighbours.
+
+Let $S = ( s_1 , \ldots , s_n )$ and $T = ( t_1 , \ldots , t_m)$ be two sequences.  We say that $S
+\preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
+t_j$.  When considering a $k$-less subgraph isomorphism we say that $S \lesspreceq{k} T$ if $n - k
+\leq m$, and if there exists some subsequence $S_k$ of $S$ containing up to $k$ members such that
+$\forall s_i \in S \setminus S_k$, there exists a distinct $t_j \in T$ with $s_i - k \leq t_j$.
 

### 2016-09-13 paper/paper.tex
Just nuke the acks for now, for space
Switch to AAAI style
Page layout rejiggery

@@
 
-\usepackage[pass]{geometry}
+\setlength{\pdfpagewidth}{8.5in}
+\setlength{\pdfpageheight}{11in}
 
-\usepackage{ijcai16}
+\usepackage{aaai17}
+
 \usepackage{times}
+\usepackage{helvet}
+\usepackage{courier}
 \usepackage{complexity}
@@
 \declaretheorem[name=Proposition,style=definition]{proposition}
+
+\setcounter{secnumdepth}{2}
 
@@
         \node[fill=black] (p) {};
-        \node[fill=black] (b) [above of = p,node distance=10mm] {};
+        \node[fill=black] (b) [above of = p,node distance=5mm] {};
         \node[fill=black] (a) [left of = b] {};
         \node[fill=black] (c) [right of = b] {};
-        \node[fill=black] (d) [above of = b,node distance=10mm] {};
+        \node[fill=black] (d) [above of = b,node distance=5mm] {};
 
@@
         \node[fill=gray!50] (c1) [right of = b1] {};
-        \node[fill=black] (a2) [below of = a1] {};
+        \node[fill=black] (a2) [below of = a1, node distance=6mm] {};
         \node[fill=black] (b2) [right of = a2] {};
         \node[fill=black] (c2) [right of = b2] {};
-        \node[fill=gray!50] (a3) [below of = a2] {};
+        \node[fill=gray!50] (a3) [below of = a2, node distance=6mm] {};
         \node[fill=black] (b3) [right of = a3] {};
@@
         \node[fill=black] (p) {};
-        \node[draw=none] (b) [above of = p,node distance=10mm] {};
+        \node[draw=none] (b) [above of = p,node distance=5mm] {};
         \node[fill=black] (a) [left of = b] {};
         \node[fill=black] (c) [right of = b] {};
-        \node[fill=black] (d) [above of = b,node distance=10mm] {};
+        \node[fill=black] (d) [above of = b,node distance=5mm] {};
 
@@
 
-% \begin{figure}
-%     \begin{center}
-%         \begin{tikzpicture}[every node/.style={circle, inner sep=1mm}]
-%             \node[fill=black] (p) {};
-%             \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
-%             \node[fill=uofglawn] (n2) [above of = p,node distance=12mm] {};
-%             \node[fill=uofgpumpkin] (n1) [left of = n2] {};
-%             \node[fill=uofglawn] (n3) [right of = n2] {};
-%             \node[fill=uofgcobalt] (q) [above of = n2,node distance=12mm] {};
-%             \path (p) edge (n1) edge (n2) edge (n3)
-%                 (n1) edge (q)
-%                 (n2) edge (n3) edge (q)
-%                 (n3) edge (q);
-%         \end{tikzpicture}
-%         \caption{Example of neighbourhood degree filtering cases}
-%         \label{fig:nds}
-%     \end{center}
-% \end{figure}
+\begin{figure}
+    \centering
+    \includegraphics*{gen-graph-ids.pdf}
+    \caption{The amount of domain reduction achieved for the induced problem, with increasing
+    $k$. The $y$ value shows for how many instances we may reduce the initial search space to be
+    at most the $x$ proportion of the size the search space would be for the maximum common subgraph
+    problem.}\label{figure:ids}
+\end{figure}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics*{gen-graph-ids.pdf}
-    \caption{The amount of domain reduction achieved for the induced problem, with increasing values
-    of $k$. The $y$ value shows for how many instances we may reduce the initial search space to be
-    at most the $x$ proportion of the size the search space would be for the maximum common subgraph
-    problem.}\label{figure:ids}
-\end{figure}
-
-\section{Filtering During Search Using Paths}\label{section:pathfiltering}
-
-\begin{figure*}[tb]
+\begin{figure*}[t]
     \centering
@@
 \end{figure*}
+
+\section{Filtering During Search Using Paths}\label{section:pathfiltering}
 
@@
 
-\begin{figure*}[tb]
+\begin{figure}[h!]
     \centering
@@
     instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
-\end{figure*}
+\end{figure}
 
@@
 
-\section*{Acknowledgements}
+% \section*{Acknowledgements}
 
-We'd like to thank some people whose names we've removed for anonymous review for providing us with
-source code and problem instances, and someone at one of our institutions for inspiration.
-
-\bibliographystyle{named}
+\bibliographystyle{aaai}
 \bibliography{paper}

### 2016-09-13 paper/paper.tex
Remove vspace hackery
More mucking around

@@
 
+\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
+
 \title{Between Subgraph Isomorphism and Maximum Common Subgraph}
 
-\author{Anonymous \and Anonymous\thanks{This work was supported by an anonymous funding agency [grant number 12345]} \and Anonymous\thanks{This work was supported by an anonymous funding agency [grant number 67890]} \\
+\author{Anonymous \and Anonymous\thanks{This work was supported by an anonymous funding agency
+[grant numbers 12345 and 67890]} \and Anonymous\samethanks \\
 Top Secret Research Lab, Atlantis \\
@@
 The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
-\emph{target} graph. This is used in many areas, including bioinformatics \citep{Bonnici:2013},
-computer vision \citep{cviu11,pr15}, malware detection \citep{DBLP:conf/dimva/BruschiMM06},
-compilers \citep{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, and pattern recognition
-\citep{Conte:2004}.  The problem comes in two forms: in the non-induced variant, edges must be
-mapped to edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges
-may only be mapped to non-edges.
+\emph{target} graph. The problem arises in many areas, including bioinformatics
+\citep{Bonnici:2013}, computer vision \citep{cviu11,pr15}, malware detection
+\citep{DBLP:conf/dimva/BruschiMM06}, compilers
+\citep{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, and pattern recognition
+\citep{Conte:2004}, which has lead to substantial research into how best to solve the problem in
+practice \cite[and
+more]{mcgregor79,Ullman,Cordella:2004,DBLP:journals/ai/Solnon10,DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}.
+The problem comes in two forms: in the non-induced variant, edges must be mapped to edges, but the
+target may have ``extra edges'', whilst in the induced variant, non-edges must be mapped to
+non-edges.
+
+\begin{figure}[b]
+    \centering
+    \begin{tikzpicture}[scale=0.5]%[every node/.style={circle, inner sep=0.5mm,node
+        %distance=10mm,fill=black}, scale=0.2]
+
+        \begin{scope}[xshift=-1cm, yshift=-3cm, color=black]
+        \node at (-2, 1) {$P$:};
+        \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
+        \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
+        \node [fill, circle, inner sep=1.5pt] (c) at (0,1) {};
+        \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
+        \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};
+
+        \path[solid] (a) edge (b) edge (c) edge (d)
+            (e) edge (b) edge (c) edge (d);
+        \end{scope}
+
+        \begin{scope}[xshift=4cm, yshift=-3cm, color=black]
+        \node at (-2, 1) {$T$:};
+        \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
+        \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
+        \node [fill, circle, inner sep=1.5pt] (c) at (1,2) {};
+        \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
+        \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};
+        \node [fill, circle, inner sep=1.5pt] (f) at (1,0) {};
+        \node [fill, circle, inner sep=1.5pt] (g) at (2,0) {};
+        \node [fill, circle, inner sep=1.5pt] (h) at (2,2) {};
+
+        \path[solid] (a) edge (b) edge (d)
+            (e) edge (b) edge (d)
+            (d) edge (c) edge (f)
+            (c) edge (h)
+            (f) edge (g);
+        \end{scope}
+
+    \end{tikzpicture}
+    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
+    the central vertex in the diamond is removed, then a subgraph isomorphism exists.}
+    \label{figure:subgraphexample}
+\end{figure}
 
@@
 In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
-pattern graph into the target---we show an example in \cref{fig:subgraphexample}. (This in some
+pattern graph into the target---we show an example in \cref{figure:subgraphexample}. (This in some
 ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
-although we allow any vertex to be removed.) We show that if $k$ is reasonably small (say, between 1
-and 5), then weakened forms of degree and path based filterings are still effective in pruning the
-initial search space and in providing additional constraints respectively. We then show that
-combining these techniques leads to a practical algorithm which can scale to work with the families
-of graphs commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark
-family, we can close a substantial portion of the instances, and in many more cases, we can at least
-obtain an upper bound. This is a significant improvement over state of the art maximum common
-subgraph solvers, which cannot even fit many of these instances in RAM. Finally, we show that
-iteratively increasing $k$ gives a competitive algorithm for the maximum common induced subgraph
-problem.
+although we allow any vertex to be removed.) We show that if
+$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
+filterings are still effective in pruning the initial search space and in providing additional
+constraints respectively. We then show that combining these techniques leads to a practical
+algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
+isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
+the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
+improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
+these instances in RAM. Finally, we show that iteratively increasing $k$ gives a competitive
+algorithm for the maximum common induced subgraph problem.
 
-\begin{figure}
-    \centering
-    \begin{tikzpicture}[scale=0.6]%[every node/.style={circle, inner sep=0.5mm,node
-        %distance=10mm,fill=black}, scale=0.2]
-
-        \begin{scope}[xshift=-1cm, yshift=-3cm, color=black]
-        \node at (0, -0.5) {$P$};
-        \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
-        \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
-        \node [fill, circle, inner sep=1.5pt] (c) at (0,1) {};
-        \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
-        \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};
-
-        \path[solid] (a) edge (b) edge (c) edge (d)
-            (e) edge (b) edge (c) edge (d);
-        % \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
-        % \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
-        % \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
-        % \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
-        % \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
-        % \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
-        % \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
-        % \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};
-
-        % \node (aaa) [below of =aa, node distance=20mm] {};
-        %
-        % \path[dotted] (a) edge (a1) edge (b1);
-        % \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
-        %     (a1) edge (b1)
-        %     (aaa) edge (a2) edge (b2)
-        %     (a2) edge (aa2) edge (ab2)
-        %     (b2) edge (ba2) edge (bb2);
-        % \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
-        %     (bc2) edge (bb2) edge (ba2);
-        %
-        % \node [cross] {};
-        \end{scope}
-
-        \begin{scope}[xshift=3cm, yshift=-3cm, color=black]
-        \node at (0, -0.5) {$T$};
-        \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
-        \node [fill, circle, inner sep=1.5pt] (b) at (-1,1) {};
-        \node [fill, circle, inner sep=1.5pt] (c) at (1,2) {};
-        \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
-        \node [fill, circle, inner sep=1.5pt] (e) at (0,2) {};
-        \node [fill, circle, inner sep=1.5pt] (f) at (1,0) {};
-        \node [fill, circle, inner sep=1.5pt] (g) at (2,0) {};
-        \node [fill, circle, inner sep=1.5pt] (h) at (2,2) {};
-
-        \path[solid] (a) edge (b) edge (d)
-            (e) edge (b) edge (d)
-            (d) edge (c) edge (f)
-            (c) edge (h)
-            (f) edge (g);
-
-        % \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
-        % \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
-        % \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
-        % \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
-        % \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
-        % \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
-        % \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
-        % \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};
-
-        % \node (aaa) [below of =aa, node distance=20mm] {};
-        %
-        % \path[dotted] (a) edge (a1) edge (b1);
-        % \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
-        %     (a1) edge (b1)
-        %     (aaa) edge (a2) edge (b2)
-        %     (a2) edge (aa2) edge (ab2)
-        %     (b2) edge (ba2) edge (bb2);
-        % \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
-        %     (bc2) edge (bb2) edge (ba2);
-        %
-        % \node [cross] {};
-        \end{scope}
-
-    \end{tikzpicture}
-    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
-    the central vertex in the diamond is removed, then a subgraph isomorphism exists.}
-    \label{fig:subgraphexample}
-\end{figure}
 \subsection{Definitions and Notations} \label{section:definitions}
@@
     \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+        \begin{scope}
         \node[fill=black] (p) {};
         \node[fill=black] (b) [above of = p,node distance=5mm] {};
-        \node[fill=black] (a) [left of = b] {};
-        \node[fill=black] (c) [right of = b] {};
+        \node[fill=black] (a) [left of = b, node distance=7mm] {};
+        \node[fill=black] (c) [right of = b, node distance=7mm] {};
         \node[fill=black] (d) [above of = b,node distance=5mm] {};
 
-        \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
-        \node[draw=none,left of = a,node distance=3mm,yshift=-1mm] {$a$};
-        \node[draw=none,left of = b,node distance=3mm,yshift=-1mm] {$b$};
-        \node[draw=none,right of = c,node distance=3mm,yshift= 1mm] {$c$};
-        \node[draw=none,above of = d,node distance=3mm,yshift=1mm] {$d$};
+        \node[draw=none,right of = p,node distance=3mm,yshift=-0.5mm] {$p$};
+        \node[draw=none,left of = a,node distance=3mm,anchor=base] {$a$};
+        \node[draw=none,left of = b,node distance=1.8mm,anchor=base] {$b$};
+        \node[draw=none,right of = c,node distance=2mm,anchor=base] {$c$};
+        \node[draw=none,right of = d,node distance=3mm,anchor=base] {$d$};
 
-        \node[draw=none, below of = p, node distance=6mm] {$P$};
+        \node[draw=none, left of = a, node distance=8mm] {$P$:};
 
@@
             (c) edge (d);
-        \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
-        \node[fill=gray!50] (a1) [right of = d, node distance = 2cm] {};
-        \node[fill=black] (b1) [right of = a1] {};
-        \node[fill=gray!50] (c1) [right of = b1] {};
-        \node[fill=black] (a2) [below of = a1, node distance=6mm] {};
-        \node[fill=black] (b2) [right of = a2] {};
-        \node[fill=black] (c2) [right of = b2] {};
-        \node[fill=gray!50] (a3) [below of = a2, node distance=6mm] {};
-        \node[fill=black] (b3) [right of = a3] {};
-        \node[fill=gray!50] (c3) [right of = b3] {};
+
+        \node[fill=gray!50] (a1) [right of = d, node distance = 2.2cm] {};
+        \node[fill=black] (b1) [right of = a1, node distance=7mm] {};
+        \node[fill=gray!50] (c1) [right of = b1, node distance=7mm] {};
+        \node[fill=black] (a2) [below of = a1, node distance=5mm] {};
+        \node[fill=black] (b2) [right of = a2, node distance=7mm] {};
+        \node[fill=black] (c2) [right of = b2, node distance=7mm] {};
+        \node[fill=gray!50] (a3) [below of = a2, node distance=5mm] {};
+        \node[fill=black] (b3) [right of = a3, node distance=7mm] {};
+        \node[fill=gray!50] (c3) [right of = b3, node distance=7mm] {};
 
@@
 
-        \node[draw=none, below of = b3, node distance=6mm] {$T$};
+        \node[draw=none, left of = a2, node distance=6mm] {$T$:};
 
@@
             (c2) edge (b3);
-    \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
-        \node[fill=black] (p) {};
-        \node[draw=none] (b) [above of = p,node distance=5mm] {};
-        \node[fill=black] (a) [left of = b] {};
-        \node[fill=black] (c) [right of = b] {};
+
+        \node[draw=none] (b) [right of = c2, node distance=2cm] {};
+        \node[fill=black] (p) [below of = b, node distance=5mm] {};
+        \node[fill=black] (a) [left of = b, node distance=7mm] {};
+        \node[fill=black] (c) [right of = b, node distance=7mm] {};
         \node[fill=black] (d) [above of = b,node distance=5mm] {};
 
-        \node[draw=none, below of = p, node distance=6mm] {$U$};
+        \node[draw=none, left of = a, node distance=5mm] {$U$:};
 
@@
             (c) edge (d);
+        \end{scope}
     \end{tikzpicture}
@@
     second, using the highlighted vertices. No such isomorphism exists to the third graph, but there
-    is a $1$-less isomorphism $P\lessnonind{1} U$ omitting vertex $b$.}\label{fig:klessexample}
+    is a $1$-less isomorphism $P\lessnonind{1} U$ omitting vertex $b$.}\label{figure:klessexample}
 \end{figure}
@@
 Consider the pattern graph $P$ and the two target graphs $T$ and $U$ shown in
-\cref{fig:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
+\cref{figure:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
 $\nds(p)=(3,3,2)$.
@@
 
-\Cref{fig:klessexample} also illustrates the three cases possible when filtering by neighbourhood degree
-sequence.  Removing the top node causes each entry in $\nds(p)$ to be reduced; removing the
-left-middle node removes an entry from $\nds(p)$; and removing either of the connected nodes in the
-middle layer causes both the size of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.
+\Cref{figure:klessexample} also illustrates the three cases possible when filtering by neighbourhood
+degree sequence.  Removing vertex $d$ causes each entry in $\nds(p)$ to be reduced; removing vertex
+$a$ removes an entry from $\nds(p)$; and removing either of vertex $b$ or $c$ in the middle layer
+causes both the size of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.
 
@@
 \end{multicols}
-\vspace*{0.4cm}% bug in algorithm2e + multicol: incorrect space left above the vertical line
 \caption{An algorithm for the $k$-less subgraph isomorphism problem.}

### 2016-09-13 paper/paper.tex
We've room for another reference
Up with which we shall not put

@@
 \citep{DBLP:conf/dimva/BruschiMM06}, compilers
-\citep{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, and pattern recognition
+\citep{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, model checking \cite{Sevegnani:2015}, and pattern recognition
 \citep{Conte:2004}, which has lead to substantial research into how best to solve the problem in
@@
 require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$ memory \citep{DBLP:conf/cp/McCreeshNPS16},
-which is extremely problematic on the instances we wish to work with.
+which is extremely problematic on the instances with which we wish to work.
 

### 2016-09-13 paper/paper.tex
Unnecessary word which starts a new line

@@
 approach\footnote{Note that toolkits are not used in state of the art implementations, to facilitate
-better memory layouts and propagation queues, although the algorithms are heavily inspired by
+better memory layouts and propagation queues, although the algorithms are inspired by
 constraint programming.}, although a reduction to maximum clique is better when edge labels are

### 2016-09-13 paper/paper.tex
Need quotes

@@
 problem in the opposite direction from existing approaches, which work by attempting to construct
-larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
-\downarrow$ is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed by
+larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: ``$k
+\downarrow$'' is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed by
 \citet{DBLP:conf/cp/McCreeshNPS16}.  Recalling the disclaimer in \cref{section:setup}

### 2016-09-13 paper/paper.tex
No vlined
minor changes.

--- 2016-09-13 paper/paper.tex
@@
 
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
 \title{Between Subgraph Isomorphism and Maximum Common Subgraph}
 
-\author{Anonymous \and Anonymous\thanks{This work was supported by an anonymous funding agency
-[grant numbers 12345 and 67890]} \and Anonymous\samethanks \\
+\author{Anonymous \and Anonymous\thanks{This work was supported by an anonymous funding agency [grant number 12345]} \and Anonymous\thanks{This work was supported by an anonymous funding agency [grant number 67890]} \\
 Top Secret Research Lab, Atlantis \\
@@
 The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
-\emph{target} graph. The problem arises in many areas, including bioinformatics
-\citep{Bonnici:2013}, computer vision \citep{cviu11,pr15}, malware detection
-\citep{DBLP:conf/dimva/BruschiMM06}, compilers
-\citep{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, model checking \cite{Sevegnani:2015}, and pattern recognition
-\citep{Conte:2004}, which has lead to substantial research into how best to solve the problem in
-practice \cite[and
-more]{mcgregor79,Ullman,Cordella:2004,DBLP:journals/ai/Solnon10,DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}.
-The problem comes in two forms: in the non-induced variant, edges must be mapped to edges, but the
-target may have ``extra edges'', whilst in the induced variant, non-edges must be mapped to
-non-edges.
+\emph{target} graph. This is used in many areas, including bioinformatics \citep{Bonnici:2013},
+computer vision \citep{cviu11,pr15}, malware detection \citep{DBLP:conf/dimva/BruschiMM06},
+compilers \citep{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, and pattern recognition
+\citep{Conte:2004}.  The problem comes in two forms: in the non-induced variant, edges must be
+mapped to edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges
+may only be mapped to non-edges.
 
-\begin{figure}[b]
+When a pattern cannot be found, we may wish to be given a result which maps as many vertices of the
+pattern into the target as possible. In the induced case, this is known as the maximum common
+induced subgraph problem (we discuss the non-induced case in \cref{section:definitions}). However,
+although recent subgraph isomorphism algorithms are comfortable working with graphs with thousands
+of vertices, the state of the art for the maximum common subgraph problem
+\citep{DBLP:conf/cp/McCreeshNPS16} becomes computationally infeasible at only 35 vertices when
+working with unlabelled graphs. This is largely because strong inference, based upon the degrees of
+vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
+\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
+but not maximum common subgraph, and so the state space in the former is much more restricted,
+whilst filtering during search is vastly stronger.
+
+In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
+pattern graph into the target---we show an example in \cref{fig:subgraphexample}. This in some
+ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
+although we allow any vertex to be removed. We show that if $k$ is reasonably small (say, between 1
+and 5), then weakened forms of degree and path based filterings are still effective in pruning the
+initial search space and in providing additional constraints respectively. We then show that
+combining these techniques leads to a practical algorithm which can scale to work with the families
+of graphs commonly used to benchmark subgraph isomorphism algorithms: depending upon the benchmark
+family, we can close a substantial portion of the instances, and in many more cases, we can at least
+obtain an upper bound. This is a significant improvement over state of the art maximum common
+subgraph solvers, which cannot even fit many of these instances in RAM. Finally, we show that
+iteratively increasing $k$ gives a competitive algorithm for the maximum common induced subgraph
+problem.
+
+\begin{figure}
     \centering
-    \begin{tikzpicture}[scale=0.5]%[every node/.style={circle, inner sep=0.5mm,node
+    \begin{tikzpicture}[scale=0.6]%[every node/.style={circle, inner sep=0.5mm,node
         %distance=10mm,fill=black}, scale=0.2]
@@
         \begin{scope}[xshift=-1cm, yshift=-3cm, color=black]
-        \node at (-2, 1) {$P$:};
+        \node at (0, -0.5) {$P$};
         \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
@@
             (e) edge (b) edge (c) edge (d);
+        % \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
+        % \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
+        % \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
+        % \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
+        % \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
+        % \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
+        % \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
+        % \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};
+
+        % \node (aaa) [below of =aa, node distance=20mm] {};
+        %
+        % \path[dotted] (a) edge (a1) edge (b1);
+        % \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
+        %     (a1) edge (b1)
+        %     (aaa) edge (a2) edge (b2)
+        %     (a2) edge (aa2) edge (ab2)
+        %     (b2) edge (ba2) edge (bb2);
+        % \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
+        %     (bc2) edge (bb2) edge (ba2);
+        %
+        % \node [cross] {};
         \end{scope}
 
-        \begin{scope}[xshift=4cm, yshift=-3cm, color=black]
-        \node at (-2, 1) {$T$:};
+        \begin{scope}[xshift=3cm, yshift=-3cm, color=black]
+        \node at (0, -0.5) {$T$};
         \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
@@
             (f) edge (g);
+
+        % \node (a2) [below left of = aa,node distance=13mm,xshift=2mm] {};
+        % \node (aa2) [above left of = a2,node distance=13mm,xshift=-2mm] {};
+        % \node (ab2) [below left of = a2,node distance=13mm,xshift=-2mm] {};
+        % \node (ac2) [fill=gray!50,above left of = ab2,node distance=13mm,xshift=-2mm] {};
+        % \node (b2) [below right of = aa,node distance=13mm,xshift=-2mm] {};
+        % \node (ba2) [above right of = b2,node distance=13mm,xshift=2mm] {};
+        % \node (bb2) [below right of = b2,node distance=13mm,xshift=2mm] {};
+        % \node (bc2) [fill=gray!50,above right of = bb2,node distance=13mm,xshift=2mm] {};
+
+        % \node (aaa) [below of =aa, node distance=20mm] {};
+        %
+        % \path[dotted] (a) edge (a1) edge (b1);
+        % \path (aa) edge (a1) edge (b1) edge (a2) edge (b2)
+        %     (a1) edge (b1)
+        %     (aaa) edge (a2) edge (b2)
+        %     (a2) edge (aa2) edge (ab2)
+        %     (b2) edge (ba2) edge (bb2);
+        % \path[color=gray!50] (ac2) edge (ab2) edge (aa2)
+        %     (bc2) edge (bb2) edge (ba2);
+        %
+        % \node [cross] {};
         \end{scope}
@@
     \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
-    the central vertex in the diamond is removed, then a subgraph isomorphism exists.}
-    \label{figure:subgraphexample}
+    the central vertex in $P$ is removed, then a subgraph isomorphism exists.}
+    \label{fig:subgraphexample}
 \end{figure}
-
-When a pattern cannot be found, we may wish to be given a result which maps as many vertices of the
-pattern into the target as possible. In the induced case, this is known as the maximum common
-induced subgraph problem (we discuss the non-induced case in \cref{section:definitions}). However,
-although recent subgraph isomorphism algorithms are comfortable working with graphs with thousands
-of vertices, the state of the art for the maximum common subgraph problem
-\citep{DBLP:conf/cp/McCreeshNPS16} becomes computationally infeasible at only 35 vertices when
-working with unlabelled graphs. This is largely because strong inference, based upon the degrees of
-vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
-\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
-but not maximum common subgraph, and so the state space in the former is much more restricted,
-whilst filtering during search is vastly stronger.
-
-In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
-pattern graph into the target---we show an example in \cref{figure:subgraphexample}. (This in some
-ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
-although we allow any vertex to be removed.) We show that if
-$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
-filterings are still effective in pruning the initial search space and in providing additional
-constraints respectively. We then show that combining these techniques leads to a practical
-algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
-isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
-the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
-improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
-these instances in RAM. Finally, we show that iteratively increasing $k$ gives a competitive
-algorithm for the maximum common induced subgraph problem.
-
 \subsection{Definitions and Notations} \label{section:definitions}
 
-A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping $P
-\rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
-isomorphism $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
-We define a $k$-less subgraph isomorphism from $P$ to $T$ to be a subgraph isomorphism from all but
+A \emph{non-induced subgraph isomorphism} from a graph $P$ to a graph $T$ is an injective mapping $P
+\rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An \emph{induced subgraph
+isomorphism} $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
+We define a \emph{$k$-less subgraph isomorphism} from $P$ to $T$ to be a subgraph isomorphism from all but
 $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
@@
 adjacent in $\shortoverline{P}$.  The \emph{loop complement} of a graph $P$ is the graph
-$\loopcomp{P}$.  The construction of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however
+$\loopcomp{P}$.  The construction of $\loopcomp{P}$ is similar to that of $\shortoverline{P}~$, however
 whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an
@@
 require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$ memory \citep{DBLP:conf/cp/McCreeshNPS16},
-which is extremely problematic on the instances with which we wish to work.
+which is extremely problematic on the instances we wish to work with.
 
@@
     \begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
-        \begin{scope}
         \node[fill=black] (p) {};
         \node[fill=black] (b) [above of = p,node distance=5mm] {};
-        \node[fill=black] (a) [left of = b, node distance=7mm] {};
-        \node[fill=black] (c) [right of = b, node distance=7mm] {};
+        \node[fill=black] (a) [left of = b] {};
+        \node[fill=black] (c) [right of = b] {};
         \node[fill=black] (d) [above of = b,node distance=5mm] {};
 
-        \node[draw=none,right of = p,node distance=3mm,yshift=-0.5mm] {$p$};
-        \node[draw=none,left of = a,node distance=3mm,anchor=base] {$a$};
-        \node[draw=none,left of = b,node distance=1.8mm,anchor=base] {$b$};
-        \node[draw=none,right of = c,node distance=2mm,anchor=base] {$c$};
-        \node[draw=none,right of = d,node distance=3mm,anchor=base] {$d$};
+        \node[draw=none,right of = p,node distance=3mm,yshift=-1mm] {$p$};
+        \node[draw=none,left of = a,node distance=3mm,yshift=-1mm] {$a$};
+        \node[draw=none,left of = b,node distance=3mm,yshift=-1mm] {$b$};
+        \node[draw=none,right of = c,node distance=3mm,yshift= 1mm] {$c$};
+        \node[draw=none,above of = d,node distance=3mm,yshift=1mm] {$d$};
 
-        \node[draw=none, left of = a, node distance=8mm] {$P$:};
+        \node[draw=none, below of = p, node distance=6mm] {$P$};
 
@@
             (c) edge (d);
-
-        \node[fill=gray!50] (a1) [right of = d, node distance = 2.2cm] {};
-        \node[fill=black] (b1) [right of = a1, node distance=7mm] {};
-        \node[fill=gray!50] (c1) [right of = b1, node distance=7mm] {};
-        \node[fill=black] (a2) [below of = a1, node distance=5mm] {};
-        \node[fill=black] (b2) [right of = a2, node distance=7mm] {};
-        \node[fill=black] (c2) [right of = b2, node distance=7mm] {};
-        \node[fill=gray!50] (a3) [below of = a2, node distance=5mm] {};
-        \node[fill=black] (b3) [right of = a3, node distance=7mm] {};
-        \node[fill=gray!50] (c3) [right of = b3, node distance=7mm] {};
+        \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+        \node[fill=gray!50] (a1) [right of = d, node distance = 2cm] {};
+        \node[fill=black] (b1) [right of = a1] {};
+        \node[fill=gray!50] (c1) [right of = b1] {};
+        \node[fill=black] (a2) [below of = a1, node distance=6mm] {};
+        \node[fill=black] (b2) [right of = a2] {};
+        \node[fill=black] (c2) [right of = b2] {};
+        \node[fill=gray!50] (a3) [below of = a2, node distance=6mm] {};
+        \node[fill=black] (b3) [right of = a3] {};
+        \node[fill=gray!50] (c3) [right of = b3] {};
 
@@
 
-        \node[draw=none, left of = a2, node distance=6mm] {$T$:};
+        \node[draw=none, below of = b3, node distance=6mm] {$T$};
 
@@
             (c2) edge (b3);
-
-        \node[draw=none] (b) [right of = c2, node distance=2cm] {};
-        \node[fill=black] (p) [below of = b, node distance=5mm] {};
-        \node[fill=black] (a) [left of = b, node distance=7mm] {};
-        \node[fill=black] (c) [right of = b, node distance=7mm] {};
+    \end{tikzpicture}\hspace{0.5cm}\begin{tikzpicture}[every node/.style={circle, inner sep=0.5mm}]
+        \node[fill=black] (p) {};
+        \node[draw=none] (b) [above of = p,node distance=5mm] {};
+        \node[fill=black] (a) [left of = b] {};
+        \node[fill=black] (c) [right of = b] {};
         \node[fill=black] (d) [above of = b,node distance=5mm] {};
 
-        \node[draw=none, left of = a, node distance=5mm] {$U$:};
+        \node[draw=none, below of = p, node distance=6mm] {$U$};
 
@@
             (c) edge (d);
-        \end{scope}
     \end{tikzpicture}
@@
     second, using the highlighted vertices. No such isomorphism exists to the third graph, but there
-    is a $1$-less isomorphism $P\lessnonind{1} U$ omitting vertex $b$.}\label{figure:klessexample}
+    is a $1$-less isomorphism $P\lessnonind{1} U$ omitting vertex $b$.}\label{fig:klessexample}
 \end{figure}
@@
 A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $\N(p) = \{ q \in \V(P) :
- p~\textnormal{and}~q~\textnormal{are adjacent}\}$ be the set of neighbours of $p$.  The \emph{neighbourhood
+ p~\textnormal{and}~q~\textnormal{are adjacent}\}$ be the \emph{set of neighbours} of $p$.  The \emph{neighbourhood
 degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
@@
 Consider the pattern graph $P$ and the two target graphs $T$ and $U$ shown in
-\cref{figure:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
+\cref{fig:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
 $\nds(p)=(3,3,2)$.
@@
 
-\Cref{figure:klessexample} also illustrates the three cases possible when filtering by neighbourhood
-degree sequence.  Removing vertex $d$ causes each entry in $\nds(p)$ to be reduced; removing vertex
-$a$ removes an entry from $\nds(p)$; and removing either of vertex $b$ or $c$ in the middle layer
-causes both the size of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.
+\Cref{fig:klessexample} also illustrates the three cases possible when filtering by neighbourhood degree
+sequence.  Removing the top node causes each entry in $\nds(p)$ to be reduced; removing the
+left-middle node removes an entry from $\nds(p)$; and removing either of the connected nodes in the
+middle layer causes both the size of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.
 
@@
 vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$. We define
-$\paths(p,q,n)$ to be the number of paths of length $n$ between the vertices $p$ and $q$.
+$\paths(p,q,n)$ to be the \emph{number of paths of length $n$} between the vertices $p$ and $q$.
 

### 2016-09-13 paper/paper.tex
Duplicated word

--- 2016-09-13 paper/paper.tex
@@
 \usepackage{multicol}
-\usepackage[ruled,vlined]{algorithm2e}
+\usepackage[vlined]{algorithm2e}
 
@@
 algorithm due to \citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of using portfolios
-of subgraph isomorphism algorithms was the single strongest solver portfolios \citep{thelionpaper}.
+of subgraph isomorphism algorithms was the single strongest solver \citep{thelionpaper}.
 As well as the modifications to solve $k$-less and induced problems, we have made two

### 2016-09-13 paper/paper.tex

--- 2016-09-13 paper/paper.tex
@@
     \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
-    the central vertex in the diamond is removed, then a subgraph isomorphism exists.}
-    \label{figure:subgraphexample}
+    the central vertex in $P$ is removed, then a subgraph isomorphism exists.}
+    \label{fig:subgraphexample}
 \end{figure}
@@
 
-A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping $P
-\rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
-isomorphism $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
-We define a $k$-less subgraph isomorphism from $P$ to $T$ to be a subgraph isomorphism from all but
+A \emph{non-induced subgraph isomorphism} from a graph $P$ to a graph $T$ is an injective mapping $P
+\rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An \emph{induced subgraph
+isomorphism} $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
+We define a \emph{$k$-less subgraph isomorphism} from $P$ to $T$ to be a subgraph isomorphism from all but
 $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P

### 2016-09-13 paper/paper.tex
found and fixed ref bug.

@@
 In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
-pattern graph into the target---we show an example in \cref{figure:subgraphexample}. (This in some
+pattern graph into the target---we show an example in \cref{fig:subgraphexample}. (This in some
 ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},

### 2016-09-13 paper/paper.tex
Be consistent
What goes back in later
fixed loopcomp, and removed bracket.

@@
 \newcommand{\nds}{\operatorname{S}}
-\newcommand{\loopcomp}[1]{\oset[.1ex]{\multimap}{#1}}
+\newcommand{\loopcomp}[1]{\tset{\multimap}{#1}}
 
-\makeatletter
-\newcommand{\oset}[3][0ex]{%
-  \mathrel{\mathop{#3}\limits^{
-    \vbox to#1{\kern-2\ex@
-    \hbox{$\scriptstyle#2$}\vss}}}}
-\makeatother
+\newcommand{\tset}[2]{%
+    \tikz[baseline=(X.base),inner sep=0pt,outer sep=0pt]{%
+        \node[inner sep=0pt,outer sep=0pt] (X) {$#2$};
+        \node[yshift=1.5pt,xshift=1pt] at (X.north) {$\scriptstyle#1$};
+}}
 
@@
 In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
-pattern graph into the target---we show an example in \cref{fig:subgraphexample}. (This in some
+pattern graph into the target---we show an example in \cref{fig:subgraphexample}. This in some
 ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
-although we allow any vertex to be removed.) We show that if
+although we allow any vertex to be removed. We show that if
 $k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based

### 2016-09-13 paper/paper.tex
fixing reference mistake.

@@
     the central vertex in $P$ is removed, then a subgraph isomorphism exists.}
-    \label{fig:subgraphexample}
+    \label{figure:subgraphexample}
 \end{figure}
@@
 In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
-pattern graph into the target---we show an example in \cref{fig:subgraphexample}. This in some
+pattern graph into the target---we show an example in \cref{figure:subgraphexample}. This in some
 ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
@@
 
+% Other stuff to stick back in: proofs, example of paths of length 3, correlation heatmap
+
 \bibliographystyle{aaai}

### 2016-09-13 paper/paper.tex
emphasising.

@@
 
-By an assignment, we mean considering mapping a pattern vertex $p$ to a target vertex $t$ (and not
-$\bot$) which does not violate any loop constraints. An assignment pair is two assignments with
+By an \emph{assignment}, we mean considering mapping a pattern vertex $p$ to a target vertex $t$ (and not
+$\bot$) which does not violate any loop constraints. An \emph{assignment pair} is two assignments with
 distinct $p$ and distinct $t$, which we say is permitted if it does not violate any adjacency
-constraint. We define the permitted assignment pair ratio to be the proportion of assignment pairs
-which are permitted.  Finally, in \cref{figure:constraints} we scatter plot the permitted assignment
+constraint. We define the \emph{permitted assignment pair ratio} to be the proportion of assignment pairs
+which are permitted.  Given this, in \cref{figure:constraints} we scatter plot the permitted assignment
 pair ratio with and without supplemental graphs\footnote{Because of the large sizes of the domains,

### 2016-09-13 paper/paper.tex
Below

@@
 isomorphism instances. In the first two plots of \cref{figure:runtimes} we give cumulative
-distributions for the induced and non-induced problems, with $k$ ranging from $0$ to $5$ (we
-discuss the dotted lines in this plot below). The results are strong: with $k = 0$ we may solve
-nearly every instance, whilst even at $k = 5$ we can solve over $4,000$ instances in both variants.
+distributions for the induced and non-induced problems, with $k$ ranging from $0$ to $5$ (we discuss
+the dotted lines in this plot in \cref{section:topdown}). The results are strong: with $k = 0$ we
+may solve nearly every instance, whilst even at $k = 5$ we can solve over $4,000$ instances in both
+variants.
 
@@
 
-\subsection{Solving from the Top Down}
+\subsection{Solving from the Top Down}\label{section:topdown}
 

### 2016-11-12 paper/paper.tex
Our Crushing And Humiliating Vanquishing Of Reviewer #3

@@
 
-\author{Anonymous \and Anonymous\thanks{This work was supported by an anonymous funding agency
-[grant numbers 12345 and 67890]} \and Anonymous\samethanks \\
-Top Secret Research Lab, Atlantis \\
-anonymous@anonymous}
+\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and
+Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M506539/1]} \and Craig
+Reilly\samethanks \\ University of Glasgow, Glasgow, Scotland \\ ruth.hoffmann@glasgow.ac.uk \and
+\{c.mccreesh.1,c.reilly.2\}@research.gla.ac.uk}
 
@@
     /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
-    /Author (Anonymous and Anonymous and Anonymous)
+    /Author (Ruth Hoffmann and Ciaran McCreesh and Craig Reilly)
 }
@@
 We perform our experiments on systems with dual Intel Xeon CPU E5-2640 processors with 64GBytes of
-RAM, running Ubuntu 14.04. Our algorithm was implemented in C++\footnote{URL removed for anonymous
-review}, and source code was compiled using
-GCC 5.3.0. We used a timeout of 1,000 seconds for each instance. For comparison, we used the
-implementations of \citet{DBLP:conf/cp/McCreeshNPS16}.
+RAM, running Ubuntu 14.04. Our algorithm was implemented in
+C++\footnote{https://github.com/ciaranm/aaai17-between-subgraph-isomorphism-and-maximum-common-subgraph-paper},
+and source code was compiled using GCC 5.3.0. We used a timeout of 1,000 seconds for each instance.
+For comparison, we used the implementations of \citet{DBLP:conf/cp/McCreeshNPS16}.
 

### 2016-11-13 paper/paper.tex
proofs moved in and changed cor2.

@@
 % to restate the propostions
-\usepackage{thmtools,thm-restate}
+%\usepackage{thmtools,thm-restate}
 
-\declaretheorem[name=Proposition,style=definition]{proposition}
+%\declaretheorem[name=Proposition,style=definition]{proposition}
 
@@
 \newtheorem{example}{Example}
+\newtheorem{proposition}{Proposition}
 
@@
 
-\begin{restatable}{proposition}{propdeg}\label{prop:deg}
+\begin{proposition}\label{prop:deg}
     Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
@@
     $\deg(p) - k \le \deg(t)$.
-\end{restatable}
+\end{proposition}
+\begin{proof}
+Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$.
+Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$.
+Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$.
+Then
+\[
+\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
+\]
+\end{proof}
 
@@
 
-\begin{restatable}{proposition}{propnds}\label{prop:nds}
+\begin{proposition}\label{prop:nds}
 If $p \lessmap{k} t$, then $\nds(p) \lesspreceq{k} \nds(t)$.
-\end{restatable}
+\end{proposition}
+\begin{proof}
+Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
+implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.
+
+Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$
+is some subset of $P$ with $\left| P_k \right| \leq k$, we have $q \lessmap{k} u$, where $u \in N(t)$ and
+each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
+\lesspreceq{k} \nds(t)$.
+\end{proof}
 
@@
 
-\begin{restatable}{proposition}{proppaths}\label{prop:paths}
+\begin{proposition}\label{prop:paths}
     Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
      $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
-\end{restatable}
+\end{proposition}
+\begin{proof}
+Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, \[P_{2} = \{((p,x),(x,q)) :
+(p,x),(x,q)\in \operatorname{E}(P) \}\textnormal{.}\] As we are looking at paths of length 2,
+the intermediate vertices lie in both neighbour vertex sets of $p$ and $q$. We can rewrite
+$P_{2}$ as \[P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}\textnormal{,}\] in
+other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and
+$q$, \[ P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} \textnormal{.}\] Therefore
+$\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
+
+If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of
+    the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$,
+\[
+\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
+\]
+As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
+\begin{align*}
+\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k \\
+ & \leq \left|\N(t)\cap \N(u)\right|\\
+ & \leq \deg(t)
+\end{align*}
+which tells us
+\[
+\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
+\]
+\end{proof}
 
 \begin{corollary}
-    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$. The
-    vertices $p$ and $q$ in $G^{n, \ell}$ are adjacent if there are at least $n$ simple paths of
+    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$, and edges between vertices $p$ and $q$ if there are at least $n$ simple paths of
     length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less subgraph isomorphism
@@
 
-\clearpage
-\appendix
-
-\section{Proofs Omitted From Main Text}
-
-The following proofs have been omitted from the main text. If the reviewers feel they are helpful
-and not obvious, we will pay for an extra page to include them.
-
-\bigskip
-
-\propdeg*
-\begin{proof}
-Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$.
-Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$.
-Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$.
-Then
-\[
-\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
-\]
-\end{proof}
-
-\bigskip
-
-\propnds*
-\begin{proof}
-Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
-implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.
-
-Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$
-is some subset of $P$ with $\left| P_k \right| \leq k$, we have $q \lessmap{k} u$, where $u \in N(t)$ and
-each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
-\lesspreceq{k} \nds(t)$.
-\end{proof}
-
-\bigskip
-
-\proppaths*
-\begin{proof}
-Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, \[P_{2} = \{((p,x),(x,q)) :
-(p,x),(x,q)\in \operatorname{E}(P) \}\textnormal{.}\] As we are looking at paths of length 2,
-the intermediate vertices lie in both neighbour vertex sets of $p$ and $q$. We can rewrite
-$P_{2}$ as \[P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}\textnormal{,}\] in
-other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and
-$q$, \[ P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} \textnormal{.}\] Therefore
-$\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
-
-If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of
-    the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$,
-\[
-\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
-\]
-As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
-\begin{align*}
-\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k \\
- & \leq \left|\N(t)\cap \N(u)\right|\\
- & \leq \deg(t)
-\end{align*}
-which tells us
-\[
-\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
-\]
-\end{proof}
-
 \end{document}

### 2016-11-13 paper/paper.tex
Temporarily force refs onto new page, so we can see how much room we have
Thanks Frances
We have the proofs

@@
 \usepackage[vlined]{algorithm2e}
+
+\usepackage{placeins}
 
@@
 
+\begin{figure}[b]
+    \centering
+    \begin{tikzpicture}[scale=0.5]%[every node/.style={circle, inner sep=0.5mm,node
+        %distance=10mm,fill=black}, scale=0.2]
+
+        \begin{scope}[xshift=-1cm, yshift=-3cm, color=black]
+        \node at (-1,0) {$P$:};
+        \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
+        \node [fill, circle, inner sep=1.5pt] (b) at (1,-1) {};
+        \node [fill, circle, inner sep=1.5pt] (c) at (1,0) {};
+        \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
+        \node [fill, circle, inner sep=1.5pt] (e) at (2,0) {};
+        \node [fill, circle, inner sep=1.5pt] (f) at (3,0) {};
+        \node[draw=none,below of = e,node distance=3mm,anchor=base] {$p$};
+
+        \path[solid] (a) edge (b) edge (c) edge (d)
+            (b) edge (e)
+            (c) edge (e)
+            (d) edge (e)
+            (e) edge (f);
+        \end{scope}
+
+        \begin{scope}[xshift=6cm, yshift=-3cm, color=black]
+        \node at (-1,0) {$T$:};
+        \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
+        \node [fill, circle, inner sep=1.5pt] (b) at (1,-1) {};
+        \node [fill, circle, inner sep=1.5pt] (c) at (1,0) {};
+        \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
+        %\node [fill, circle, inner sep=1.5pt] (e) at (2,0) {};
+        \node [fill, circle, inner sep=1.5pt] (f) at (3,0) {};
+
+        \path[solid] (a) edge (b) edge (c) edge (d);
+        %    (b) edge (e)
+        %    (c) edge (e)
+        %    (d) edge (e)
+        %    (e) edge (f);
+        \end{scope}
+
+    \end{tikzpicture}
+    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
+    the vertex $p$ in $P$ is removed, then a subgraph isomorphism exists.}
+    \label{figure:pathlength3example}
+\end{figure}
+
 To allow for fast propagation, rather than calculating paths dynamically like
@@
 
-% \section*{Acknowledgements}
+\section*{Acknowledgements}
 
-% Other stuff to stick back in: proofs, example of paths of length 3, correlation heatmap
+We would like to thank Frances Cooper for her comments.
+
+% Other stuff to stick back in: example of paths of length 3, correlation heatmap
+
+\FloatBarrier
+\clearpage
 

### 2016-11-16 paper/paper.tex
sketch of path length 3 example added.
Ref figure, and reorder hackery for now

@@
 
-\begin{figure*}[t]
-    \centering
-    \includegraphics*{gen-graph-constraints-induced-0.pdf}
-    \includegraphics*{gen-graph-constraints-induced-1.pdf}
-    \includegraphics*{gen-graph-constraints-induced-2.pdf}
-    \includegraphics*{gen-graph-constraints-induced-3.pdf}
-    \includegraphics*{gen-graph-constraints-induced-4.pdf}
-    \includegraphics*{gen-graph-constraints-induced-5.pdf}
-
-    \caption{For the induced problem, the proportion of pairs of assignments from the filtered
-    domains which are not permitted simultaneously, without path constraints on the $x$-axis and
-    with path constraints on the $y$-axis, for increasing values of $k$.}\label{figure:constraints}
-\end{figure*}
-
 \section{Filtering During Search Using Paths}\label{section:pathfiltering}
@@
 Unlike in conventional subgraph isomorphism, we cannot extend this filtering to look at paths of
-length three: removing a single vertex can delete arbitrarily many such paths. We \emph{could}
-instead count paths of any length which are vertex disjoint, although calculating this appears to be
-too expensive to be beneficial in practice.
+length three: as the example in \cref{figure:pathlength3example} shows, removing a single vertex can
+delete arbitrarily many such paths. We \emph{could} instead count paths of any length which are
+vertex disjoint, although calculating this appears to be too expensive to be beneficial in practice.
 
-\begin{figure}[b]
+\begin{figure}[tb]
     \centering
@@
 \end{figure}
+
+\begin{figure*}[tb]
+    \centering
+    \includegraphics*{gen-graph-constraints-induced-0.pdf}
+    \includegraphics*{gen-graph-constraints-induced-1.pdf}
+    \includegraphics*{gen-graph-constraints-induced-2.pdf}
+    \includegraphics*{gen-graph-constraints-induced-3.pdf}
+    \includegraphics*{gen-graph-constraints-induced-4.pdf}
+    \includegraphics*{gen-graph-constraints-induced-5.pdf}
+
+    \caption{For the induced problem, the proportion of pairs of assignments from the filtered
+    domains which are not permitted simultaneously, without path constraints on the $x$-axis and
+    with path constraints on the $y$-axis, for increasing values of $k$.}\label{figure:constraints}
+\end{figure*}
 

### 2016-11-25 paper/paper.tex
What we need to write for the algorithm

@@
 of subgraph isomorphism algorithms was the single strongest solver \citep{thelionpaper}.
-As well as the modifications to solve $k$-less and induced problems, we have made two
-simplifications: we do not use conflict-directed backjumping, and we do not use iterated label
-filtering to recalculate neighbourhood degree sequences if vertices are not present in any target
-domain after construction---in preliminary experiments, these techniques were not beneficial for $k
-> 0$. We also do not strip isolated vertices, as this is not a valid simplification in the induced
-case.
 
-To handle wildcards, we include $k$ additional $\bot$ values in domains, rather than a single value
-which may be used $k$ times. These are treated as having degree zero, in an attempt to maximising
-the expected number of solutions remaining during search \citep{DBLP:conf/ijcai/McCreeshPT16}. This
-technique allows us to retain the bit-parallel all different propagator used in the original
-algorithm. However, we must be careful to treat domains containing multiple wildcard values (which
-we call ``effectively unit'') specially during unit propagation (line~\ref{line:effect}), and we
-introduce a symmetry break (line~\ref{line:sym}) to try only a single wildcard value for each
-variable.
+The algorithm performs a constraint-based search. We have a variable $D_v$ for each vertex $v$ in
+the pattern graph, each of which has a domain containing one value for every vertex in the target
+graph.
+
+In lines ?? we use the reasoning from section ?? to eliminate infeasible initial values from the
+domains. We do not use iterated label filtering ?? cite to recalculate neighbourhood degree
+sequences if any vertices are not present in any target domain after construction: preliminary
+experiments indicated that this happened very rarely.
+
+To handle unmapped vertices, on line ?? we include $k$ additional wildcard $\bot$ values in each
+domain (rather than a single value which may be used $k$ times).
+
+?? Constraints and unit propagation
+
+?? Supplemental graphs. These are also used for eliminating infeasible values.
+
+?? All different
+
+We must be careful to treat domains containing multiple wildcard values (which we call ``effectively
+unit'') specially during unit propagation (line~\ref{line:effect}), and we introduce a symmetry
+break (line~\ref{line:sym}) to try only a single wildcard value for each variable.
+
+?? Search. No backjumping.
+
+?? Heuristics
+
+Wildcards are treated as having degree zero, in an attempt to maximising the expected number of
+solutions remaining during search \citep{DBLP:conf/ijcai/McCreeshPT16}. This technique allows us to
+retain the bit-parallel all different propagator used in the original algorithm.
+
+?? As well as the modifications to solve $k$-less and induced problems, we have made two
+simplifications: we do not use conflict-directed backjumping, and in preliminary experiments, these
+techniques were not beneficial for $k > 0$.
 
@@
 using path reasoning on complement graphs, but this is expensive to calculate and provides little
-benefit in practice on the instances we considered.
+benefit in practice on the instances we considered.  We also do not strip isolated vertices as
+cite?? did, as this is not a valid simplification in the induced case.
 

### 2016-11-28 paper/paper.tex
Some more things to write
More

@@
     }
-    \nl \lIf{\FuncSty{propagate}(L, D)}{$\KwSty{return}~\FuncSty{search}(L, D, k)$}
+    \nl \If{\FuncSty{propagate}(L, D)}{
+        \nl $\KwSty{return}~\FuncSty{search}(L, \{ E \in D : \left|E\right| > 1 \}, k)$\;
+    }
     \nl \lElse{$\KwSty{return}~\KwSty{false}$}
@@
         \nl \If{\FuncSty{propagate}(L, D')}{
-            \nl \If{$\FuncSty{search}(L, \{ D \in D' : \left|D\right| > 1 \}, k)$}{
+            \nl \If{$\FuncSty{search}(L, \{ E \in D' : \left|E\right| > 1 \}, k)$}{
                 \nl $\KwSty{return}~\KwSty{true}$ \;
@@
 \end{multicols}
-\caption{An algorithm for the $k$-less subgraph isomorphism problem.}
+\vspace{0.5cm}% Do not remove! Otherwise, the caption overlaps the algorithm due to algorithm2e and
+% multicol[vlined] not being entirely happy with each other.
+\caption{A bit-parallel algorithm for the $k$-less subgraph isomorphism problem.}
 \label{algorithm:sip}
@@
 of subgraph isomorphism algorithms was the single strongest solver \citep{thelionpaper}.
+
+?? Bit parallel.
 
@@
 
-?? Constraints and unit propagation
+We begin by trying to infer domain deletions. The ?? function looks for domains which contains
+either only a single value, or only wildcards---we call such a domain ``effectively-unit''. If such
+a domain $D_v$ exists, we eliminate its value from every other domain, and then propagate adjacency:
+for each domain corresponding to a vertex adjacent to $v$, we eliminate any value from its domain
+which is not adjacent to $v$ (treating wildcards as being adjacent to all vertices). If a domain
+wipeout occurs, we return failure.
 
@@
 
-?? All different
+If no effectively-unit domains remain, we attempt stronger propagation for the all-different
+constraint. Our ?? function is the bit-parallel propagator taken from
+\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator ?? which
+guarantees generalised arc consistency. ?? a bit more on how it works. It can easily be seen that
+this propagator will always find Hall sets or failed Hall sets of size zero or one, but it may miss
+larger sets. This propagation could create new effectively-unit domains; if so, we loop.
 
-We must be careful to treat domains containing multiple wildcard values (which we call ``effectively
-unit'') specially during unit propagation (line~\ref{line:effect}), and we introduce a symmetry
+?? Search
+
+we introduce a symmetry
 break (line~\ref{line:sym}) to try only a single wildcard value for each variable.
-
-?? Search. No backjumping.
 

### 2016-11-28 paper/paper.tex
Consistent URL style
No need for page layout hacks
Correlation is tricky

@@
 \usepackage[vlined]{algorithm2e}
-
-\usepackage{placeins}
 
@@
 \citep{DBLP:conf/ijcai/McCreeshPT16}. All of these instances are available in a simple text
-format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.  Note that many of these instances
+format\footnote{http://liris.cnrs.fr/csolnon/SIP.html}.  Note that many of these instances
 are \emph{much} larger than were used in the recent comparison of maximum common subgraph algorithms
@@
 small margin the single strongest solver. Interestingly, our algorithm tends to have complementary
-performance to the other two approaches (which are much more correlated), which suggests that there
-is scope for an algorithm which runs both an upper bound and a constructive, lower bound approach
-simultaneously or in parallel, stopping when the two bounds meet in the middle.
+performance to the clique approach, which suggests that there is scope for an algorithm which runs
+both an upper bound and a constructive, lower bound approach simultaneously or in parallel, stopping
+when the two bounds meet in the middle.
 
@@
 
-\FloatBarrier
-\clearpage
-
 \bibliographystyle{aaai}

### 2016-11-28 paper/paper.tex
More words

@@
 
-?? Search
+?? This technique allows us to retain the bit-parallel all different propagator used in the original
+algorithm.
 
-we introduce a symmetry
-break (line~\ref{line:sym}) to try only a single wildcard value for each variable.
-
-?? Heuristics
-
-Wildcards are treated as having degree zero, in an attempt to maximising the expected number of
-solutions remaining during search \citep{DBLP:conf/ijcai/McCreeshPT16}. This technique allows us to
-retain the bit-parallel all different propagator used in the original algorithm.
+If propagation is unable to prove unsatisfiability, we search. We pick the smallest domain (line
+??), and try giving it each of its remaining values in turn. We use the value the ordering heuristic
+from the original algorithm; wildcards are treated as having degree zero, in an attempt to
+maximising the expected number of solutions remaining during search
+\citep{DBLP:conf/ijcai/McCreeshPT16}.  We introduce a symmetry break (line~\ref{line:sym}) to try
+only a single wildcard value for each variable.
 

### 2016-11-29 paper/paper.tex
No CP

@@
 by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs, they used pairs of graphs with up to
-35 vertices in each, whilst our dataset contains graphs with up to 6,671 vertices. For the CP
-algorithm, 1,560 of the instances cannot fit in the amount of RAM we have available---we treat these
-instances as having timed out. The situation for the clique encoding is even worse, and 3,653 of
-these instances do not fit in 64GBytes of RAM. In contrast, for our algorithm, every instance fits
-comfortably.  \section{Domain Filtering using Degrees}\label{section:degreefiltering}
+35 vertices in each, whilst our dataset contains graphs with up to 6,671 vertices. For the
+forward checking algorithm described by \citet{DBLP:conf/cp/NdiayeS11}, 1,560 of the instances
+cannot fit in the amount of RAM we have available---we treat these instances as having timed out.
+The situation for the clique encoding is even worse, and 3,653 of these instances do not fit in
+64GBytes of RAM. In contrast, for our algorithm, every instance fits comfortably.
+
+\section{Domain Filtering using Degrees}\label{section:degreefiltering}
 

### 2016-11-29 paper/paper.tex
Define lessmap
Explain a bit more

@@
 $k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
-\lessind{k} T$ respectively.
+\lessind{k} T$ respectively. We write $p \lessmap{k} t$ to mean that the pattern vertex p is mapped
+to the target vertex v.
 
@@
     $P \lessnonind{k} T$ induces a new $k$-less subgraph isomorphism
-    $P^{n+k, 2}\lessnonind{k} T^{n, 2}$.
+    $P^{n+k, 2}\lessnonind{k} T^{n, 2}$ using the same vertex assignments.
 \end{corollary}

### 2016-11-30 paper/paper.tex
An explicit RAM
Bit-parallel

@@
 improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
-these instances in RAM. Finally, we show that iteratively increasing $k$ gives a competitive
-algorithm for the maximum common induced subgraph problem.
+these instances in 64 GBytes of RAM. Finally, we show that iteratively increasing $k$ gives a
+competitive algorithm for the maximum common induced subgraph problem.
 
@@
 
-?? Bit parallel.
-
 The algorithm performs a constraint-based search. We have a variable $D_v$ for each vertex $v$ in
 the pattern graph, each of which has a domain containing one value for every vertex in the target
-graph.
+graph. The algorithm is bit-parallel: each $D_v$ is a bitset, and all graphs are stored as adjacency
+matrices.
 

### 2016-11-30 paper/paper.tex
More algorithm

@@
 
-In lines ?? we use the reasoning from section ?? to eliminate infeasible initial values from the
-domains. We do not use iterated label filtering ?? cite to recalculate neighbourhood degree
-sequences if any vertices are not present in any target domain after construction: preliminary
-experiments indicated that this happened very rarely.
+In lines ?? we use the reasoning from \cref{section:degreefiltering} to eliminate infeasible initial
+values from the domains. We do not use iterated label filtering \citep{constraints10} to recalculate
+neighbourhood degree sequences if any vertices are not present in any target domain after
+construction: preliminary experiments indicated that this happened very rarely on our instances.
 
@@
 
-We begin by trying to infer domain deletions. The ?? function looks for domains which contains
-either only a single value, or only wildcards---we call such a domain ``effectively-unit''. If such
-a domain $D_v$ exists, we eliminate its value from every other domain, and then propagate adjacency:
-for each domain corresponding to a vertex adjacent to $v$, we eliminate any value from its domain
-which is not adjacent to $v$ (treating wildcards as being adjacent to all vertices). If a domain
-wipeout occurs, we return failure.
+We begin by trying to infer domain deletions. The $\FuncSty{propagate}$ function looks for domains
+which contains either only a single value, or only wildcards---we call such a domain
+``effectively-unit''. If such a domain $D_v$ exists, we eliminate its value from every other domain,
+and then propagate adjacency: for each domain corresponding to a vertex adjacent to $v$, we
+eliminate any value from its domain which is not adjacent to $v$ (treating wildcards as being
+adjacent to all vertices). If a domain wipeout occurs, we return failure.
 
-?? Supplemental graphs. These are also used for eliminating infeasible values.
+?? Describe supplemental graphs. These are also used for eliminating infeasible values.
 
 If no effectively-unit domains remain, we attempt stronger propagation for the all-different
-constraint. Our ?? function is the bit-parallel propagator taken from
-\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator ?? which
-guarantees generalised arc consistency. ?? a bit more on how it works. It can easily be seen that
-this propagator will always find Hall sets or failed Hall sets of size zero or one, but it may miss
-larger sets. This propagation could create new effectively-unit domains; if so, we loop.
-
-?? This technique allows us to retain the bit-parallel all different propagator used in the original
-algorithm.
+constraint. Our $\FuncSty{allDifferent}$ function is the bit-parallel propagator taken from
+\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator ?? cite
+which guarantees generalised arc consistency. Because we use multiple wildcard values, we do not
+need to modify the algorithm to allow a single wildcard value to be used more than once. ?? a bit
+more on how it works?. It can easily be seen that this propagator will always find Hall sets or
+failed Hall sets of size zero or one, but it may miss larger sets. This propagation could create new
+effectively-unit domains; if so, we loop.
 
@@
 
-?? As well as the modifications to solve $k$-less and induced problems, we have made two
-simplifications: we do not use conflict-directed backjumping, and in preliminary experiments, these
-techniques were not beneficial for $k > 0$.
-
 To handle the induced case, we make use of \cref{prop:comp} (line~\ref{line:comp}). We also tested
 using path reasoning on complement graphs, but this is expensive to calculate and provides little
-benefit in practice on the instances we considered.  We also do not strip isolated vertices as
-cite?? did, as this is not a valid simplification in the induced case.
+benefit in practice on the instances we considered.  We also do not strip isolated vertices as the
+original algorithm did, as this is not a valid simplification in the induced case, and we do not use
+conflict-directed backjumping as in our experiments it had very little effect for $k > 0$.
 

### 2016-11-30 paper/paper.tex
More algorithm

@@
 
-\begin{corollary}
+\begin{corollary}\label{corollary:supplemental}
     For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$, and edges between vertices $p$ and $q$ if there are at least $n$ simple paths of
@@
     \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\loopcomp{\mathcal{P}},
-        \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced\label{line:comp}},$
+            \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced\label{line:comp}}, \label{line:supplemental}$
         \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
@@
         \nl \ForEach{$(P,\,T) \in L$}{
-            \nl $D_v \gets \{ w \in D_v : $ \\
+            \nl $D_v \gets \{ w \in D_v : $ \label{line:degreefiltering} \\
             \hspace*{4em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
@@
         }
-        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values}$
+        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values} \label{line:wildcards}$
     }
@@
     \nl \lIf{$D = \emptyset$}{$\KwSty{return}~\KwSty{true}$}
-    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \;
+    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \label{line:pickd} \;
     \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
@@
 
-In lines ?? we use the reasoning from \cref{section:degreefiltering} to eliminate infeasible initial
-values from the domains. We do not use iterated label filtering \citep{constraints10} to recalculate
-neighbourhood degree sequences if any vertices are not present in any target domain after
-construction: preliminary experiments indicated that this happened very rarely on our instances.
+In line~\ref{line:degreefiltering} we use the reasoning from \cref{section:degreefiltering} to
+eliminate infeasible initial values from the domains. We do not use iterated label filtering
+\citep{constraints10} to recalculate neighbourhood degree sequences if any vertices are not present
+in any target domain after construction: preliminary experiments indicated that this happened very
+rarely on our instances.
 
-To handle unmapped vertices, on line ?? we include $k$ additional wildcard $\bot$ values in each
-domain (rather than a single value which may be used $k$ times).
+To handle unmapped vertices, on line~\ref{line:wildcards} we include $k$ additional wildcard $\bot$
+values in each domain (rather than a single value which may be used $k$ times).
 
@@
 
-?? Describe supplemental graphs. These are also used for eliminating infeasible values.
+We deal with the additional constraints discussed in \cref{section:pathfiltering} by constructing
+supplemental graphs, as in the \citet{DBLP:conf/cp/McCreeshP15} algorithm. This is done on
+line~\ref{line:supplemental}: the variable $L$ contains a list of pattern / target pairs, and
+following \cref{corollary:supplemental}, we will search for a mapping which is simultaneously a
+subgraph isomorphism between every pair in this list. We also do degree-based reasoning using each
+of these graph pairs.
 
@@
 constraint. Our $\FuncSty{allDifferent}$ function is the bit-parallel propagator taken from
-\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator ?? cite
-which guarantees generalised arc consistency. Because we use multiple wildcard values, we do not
-need to modify the algorithm to allow a single wildcard value to be used more than once. ?? a bit
-more on how it works?. It can easily be seen that this propagator will always find Hall sets or
-failed Hall sets of size zero or one, but it may miss larger sets. This propagation could create new
-effectively-unit domains; if so, we loop.
+\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator
+\citep{DBLP:conf/aaai/Regin94} which guarantees generalised arc consistency. Because we use multiple
+wildcard values, we do not need to modify the algorithm to allow a single wildcard value to be used
+more than once. ?? A few sentences on how this works. It can easily be seen that this propagator
+will always find Hall sets or failed Hall sets of size zero or one, but it may miss larger sets.
+This propagation could create new effectively-unit domains; if so, we loop.
 
-If propagation is unable to prove unsatisfiability, we search. We pick the smallest domain (line
-??), and try giving it each of its remaining values in turn. We use the value the ordering heuristic
-from the original algorithm; wildcards are treated as having degree zero, in an attempt to
-maximising the expected number of solutions remaining during search
+If propagation is unable to prove unsatisfiability, we search. We pick the smallest domain
+(line~\ref{line:pickd}) and try giving it each of its remaining values in turn. We use the value the
+ordering heuristic from the original algorithm; wildcards are treated as having degree zero, in an
+attempt to maximising the expected number of solutions remaining during search
 \citep{DBLP:conf/ijcai/McCreeshPT16}.  We introduce a symmetry break (line~\ref{line:sym}) to try

### 2016-11-30 paper/paper.tex
Notation

@@
 \newcommand{\V}{\operatorname{V}}
+\newcommand{\EdgeSet}{\operatorname{E}}
 \newcommand{\N}{\operatorname{N}}
@@
 
-A \emph{non-induced subgraph isomorphism} from a graph $P$ to a graph $T$ is an injective mapping $P
-\rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An \emph{induced subgraph
+Throughout, our graphs are undirected, but may have loops.  We write $\V(G)$ for the vertex set of a
+graph $G$, and $\EdgeSet(G)$ for its set of edges. We write $\N_G(v)$ for the \emph{neighbourhood}
+of a vertex $v$ in $G$, and $v \sim_G w$ to mean $v$ is adjacent to $w$; where the graph is clear
+from the context, the subscript is omitted.
+
+A \emph{non-induced subgraph isomorphism} from a graph $P$ to a graph $T$ is an injective mapping
+$\V(P) \rightarrowtail \V(T) $ which maps adjacent vertices to adjacent vertices. An \emph{induced subgraph
 isomorphism} $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
@@
 \lessind{k} T$ respectively. We write $p \lessmap{k} t$ to mean that the pattern vertex p is mapped
-to the target vertex v.
+to the target vertex v under either kind of mapping.
 
@@
 
-A vertex $q$ which is adjacent to $p$ is called its \emph{neighbour}.  Let $\N(p) = \{ q \in \V(P) :
- p~\textnormal{and}~q~\textnormal{are adjacent}\}$ be the \emph{set of neighbours} of $p$.  The \emph{neighbourhood
-degree sequence} (NDS) of $p$, $\nds(p)$, is the (non-ascending) sequence of degrees of its
-neighbours.
+The \emph{neighbourhood degree sequence} (NDS) of a vertex $p$, $\nds(p)$, is the (non-ascending)
+sequence of degrees of its neighbours.
 
@@
 Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, \[P_{2} = \{((p,x),(x,q)) :
-(p,x),(x,q)\in \operatorname{E}(P) \}\textnormal{.}\] As we are looking at paths of length 2,
+(p,x),(x,q)\in \EdgeSet(P) \}\textnormal{.}\] As we are looking at paths of length 2,
 the intermediate vertices lie in both neighbour vertex sets of $p$ and $q$. We can rewrite

### 2016-11-30 paper/paper.tex
Let's not talk about Hall sets
Search space size

@@
 search space size for the maximum common induced subgraph problem. (The results on the non-induced
-version show a similar but slightly weaker trend.)
+version show a similar but slightly weaker trend.) We look at the product of the domain sizes,
+rather than the number of eliminations, as this better reflects the number of combinations remaining
+to be considered.
 
@@
 wildcard values, we do not need to modify the algorithm to allow a single wildcard value to be used
-more than once. ?? A few sentences on how this works. It can easily be seen that this propagator
-will always find Hall sets or failed Hall sets of size zero or one, but it may miss larger sets.
-This propagation could create new effectively-unit domains; if so, we loop.
+more than once. This propagation could create new effectively-unit domains; if so, we loop.
 

### 2016-11-30 paper/paper.tex
Some of Ruth's things

@@
 \Crefname{proposition}{Proposition}{Propositions}
+\crefname{corollary}{Corollary}{Corollaries}
+\Crefname{corollary}{Corollary}{Corollaries}
 
@@
     \label{prop:comp}
-Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P
+Let $i$ be an assignment of vertices of $T$ to vertices of $P$.  Then $i$ satisfies the definition of $P
 \hookrightarrow T$ if and only if $i$ satisfies $P \rightarrowtail T$ and
@@
 approach\footnote{Note that toolkits are not used in state of the art implementations, to facilitate
-better memory layouts and propagation queues, although the algorithms are inspired by
-constraint programming.}, although a reduction to maximum clique is better when edge labels are
-present \citep{DBLP:conf/cp/NdiayeS11,DBLP:conf/cp/McCreeshNPS16}. For both problems, we create a variable for each vertex
-in the pattern graph (the smaller graph, in the case of maximum common subgraph), with domains
-ranging over the vertices in the target graph (the larger graph). For maximum common subgraph, each
-domain is given an additional $\bot$ value, meaning ``unmapped''.
+better memory layouts and propagation queues, although the algorithms are inspired by constraint
+programming.}, although a reduction to the maximum clique problem is better when edge labels are
+present \citep{DBLP:conf/cp/NdiayeS11,DBLP:conf/cp/McCreeshNPS16}. For both problems, we create a
+variable for each vertex in the pattern graph (the smaller graph, in the case of maximum common
+subgraph), with domains ranging over the vertices in the target graph (the larger graph). For
+maximum common subgraph, each domain is given an additional $\bot$ value, meaning ``unmapped''.
 
@@
 
-There are three easy ways we might try to extend existing algorithms for this problem.
+There are three easy ways we might try to extend existing algorithms to handle the $k$-less problem.
 A non-induced $k$-less subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph isomorphism
@@
     \caption{There is a non-induced isomorphism $P\rightarrowtail T$ from the first graph to the
-    second, using the highlighted vertices. No such isomorphism exists to the third graph, but there
-    is a $1$-less isomorphism $P\lessnonind{1} U$ omitting vertex $b$.}\label{figure:klessexample}
+    second, using the highlighted vertices. No such isomorphism exists between $P$ and $U$, but there
+    is a $1$-less isomorphism $P\lessnonind{1} U$ which omits vertex $b$.}\label{figure:klessexample}
 \end{figure}
@@
 degree sequence.  Removing vertex $d$ causes each entry in $\nds(p)$ to be reduced; removing vertex
-$a$ removes an entry from $\nds(p)$; and removing either of vertex $b$ or $c$ in the middle layer
-causes both the size of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.
+$a$ removes an entry from $\nds(p)$; and removing either of vertex $b$ or $c$ causes both the size
+of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.
 
@@
 
-\Cref{figure:ids} demonstrates that this is effective in practice: we show the amount of domain
-reduction we can achieve at the top of search by using invariants and a fixed $k$, compared to the
-search space size for the maximum common induced subgraph problem. (The results on the non-induced
-version show a similar but slightly weaker trend.) We look at the product of the domain sizes,
-rather than the number of eliminations, as this better reflects the number of combinations remaining
-to be considered.
+\Cref{figure:ids} demonstrates that \cref{prop:nds} is effective in practice: we show the amount of
+domain reduction we can achieve at the top of search by using invariants and a fixed $k$, compared
+to the search space size for the maximum common induced subgraph problem. (The results on the
+non-induced version show a similar but slightly weaker trend.) We look at the product of the domain
+sizes, rather than the number of eliminations, as this better reflects the number of combinations
+remaining to be considered.
 
@@
 which contains either only a single value, or only wildcards---we call such a domain
-``effectively-unit''. If such a domain $D_v$ exists, we eliminate its value from every other domain,
+\emph{effectively-unit}. If such a domain $D_v$ exists, we eliminate its value from every other domain,
 and then propagate adjacency: for each domain corresponding to a vertex adjacent to $v$, we
@@
 wildcard values, we do not need to modify the algorithm to allow a single wildcard value to be used
-more than once. This propagation could create new effectively-unit domains; if so, we loop.
+more than once. This propagation could create new effectively-unit domains; if so, we repeat the
+process.
 

### 2016-11-30 paper/paper.tex
Count, mwa ha ha

@@
 construct \emph{supplemental graphs}, and find a mapping which is simultaneously a non-induced subgraph
-isomorphism between every supplemental graph pair. We use paths of length 2, looking at path counts
-of 1, 2, and 3 in the target graph (and so counts of $1 + k$ up to $3 + k$ in the pattern).  We then
-investigate whether this leads to new constraints being generated.
+isomorphism between every supplemental graph pair. We use paths of length 2, looking at whether
+there are at least 1, 2, and 3 in the target graph (and so whether there are at least $1 + k$ up to
+$3 + k$ in the pattern).  We then investigate whether this leads to new constraints being generated.
 

### 2016-11-30 paper/paper.tex
the vertices of

@@
 
-Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$
-is some subset of $P$ with $\left| P_k \right| \leq k$, we have $q \lessmap{k} u$, where $u \in N(t)$ and
-each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
-\lesspreceq{k} \nds(t)$.
+Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$ is some subset
+of the vertices of $P$ with $\left| P_k \right| \leq k$, we have $q \lessmap{k} u$, where $u \in
+N(t)$ and each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence
+$\nds(p) \lesspreceq{k} \nds(t)$.
 \end{proof}

### 2016-11-30 paper/paper.tex
Clarify

@@
 
-The algorithm performs a constraint-based search. We have a variable $D_v$ for each vertex $v$ in
-the pattern graph, each of which has a domain containing one value for every vertex in the target
-graph. The algorithm is bit-parallel: each $D_v$ is a bitset, and all graphs are stored as adjacency
-matrices.
+The algorithm performs a constraint-based search. We have a set $D$ containing a variable $D_v$ for
+each vertex $v$ in the pattern graph. Each variable has a domain containing one value for every
+vertex in the target graph. The algorithm is bit-parallel: each $D_v$ is stored using bitset, and
+all graphs are stored as adjacency matrices.
 

### 2016-11-30 paper/paper.tex
Clean up for submission

@@
 
-% to restate the propostions
-%\usepackage{thmtools,thm-restate}
-
-%\declaretheorem[name=Proposition,style=definition]{proposition}
-
 \setcounter{secnumdepth}{2}
 
-% \usepackage{showframe}
-
-\makeatletter\@ifpackageloaded{showframe}{
-    % show lines down the middle columns too
-    % http://tex.stackexchange.com/questions/16199/test-if-a-package-or-package-option-is-loaded
-\newlength\Fcolumnseprule\setlength\Fcolumnseprule{0.4pt}\def\@outputdblcol{%
-  \if@firstcolumn\global \@firstcolumnfalse \global \setbox\@leftcolumn \box\@outputbox
-  \else
-    \global \@firstcolumntrue
-    \setbox\@outputbox \vbox{\hb@xt@\textwidth{\hb@xt@\columnwidth{\box\@leftcolumn \hss}%
-    \vrule \@width\Fcolumnseprule\hfil{\normalcolor\vrule \@width\columnseprule}
-    \hfil\vrule \@width\Fcolumnseprule\hb@xt@\columnwidth {\box\@outputbox \hss}}}\@combinedblfloats\@outputpage
-    \begingroup\@dblfloatplacement\@startdblcolumn\@whilesw\if@fcolmade \fi{\@outputpage\@startdblcolumn}\endgroup
-  \fi
-}}{}
-\makeatother
-
-\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds,shapes.misc}
-%cross
-\tikzset{cross/.style={cross out, draw=uofgcobalt, minimum size=2*(#1-\pgflinewidth), inner sep=0pt, outer sep=0pt},cross/.default={1.5mm}}
-
-\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
-\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
-\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
-\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
-\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
+\usetikzlibrary{decorations, decorations.pathreplacing, calc}
 
@@
 
-\section{Domain Filtering using Degrees}\label{section:degreefiltering}
+\section{Domain Filtering Using Degrees}\label{section:degreefiltering}
 
@@
 \end{multicols}
-\vspace{0.5cm}% Do not remove! Otherwise, the caption overlaps the algorithm due to algorithm2e and
-% multicol[vlined] not being entirely happy with each other.
+\vspace{0.5cm}% Be careful if you remove this! Something weird happens where the caption overlaps
+% the algorithm due to algorithm2e and multicol[vlined] not being entirely happy with each other.
+% If you take this out, please check the space between the algorithm and the caption very very
+% carefully.
 \caption{A bit-parallel algorithm for the $k$-less subgraph isomorphism problem.}
@@
 
-\begin{figure}[h!]
+\begin{figure}[h!]% The ! is needed to avoid this being bumped forward a page
     \centering
@@
 
-% Other stuff to stick back in: example of paths of length 3, correlation heatmap
-
 \bibliographystyle{aaai}

### 2016-11-30 paper/paper.tex
Don't use multicols, it upsets AAAI
Murican

@@
 \usepackage{graphicx}
-\usepackage{multicol}
 \usepackage[vlined]{algorithm2e}
@@
 \DontPrintSemicolon
-\begin{multicols}{2}
+    \begin{minipage}[t]{\dimexpr.5\textwidth-.5\columnsep}
 \nl $\FuncSty{klessSubgraphIsomorphism}$ (\\\hspace*{2em}Graph $\mathcal{P}$, Graph $\mathcal{T}$, Int $k$) $\rightarrow$ Bool \;
@@
 }
-\bigskip
+\end{minipage}\hfill%
+    \begin{minipage}[t]{\dimexpr.5\textwidth-.5\columnsep}
 \nl $\FuncSty{propagate}$ (GraphPairs $L$, Domains $D$) $\rightarrow$ Bool \;
@@
 }
-\end{multicols}
-\vspace{0.5cm}% Be careful if you remove this! Something weird happens where the caption overlaps
-% the algorithm due to algorithm2e and multicol[vlined] not being entirely happy with each other.
-% If you take this out, please check the space between the algorithm and the caption very very
-% carefully.
+\end{minipage}
 \caption{A bit-parallel algorithm for the $k$-less subgraph isomorphism problem.}
@@
 
-\begin{figure}[h!]% The ! is needed to avoid this being bumped forward a page
+\begin{figure}[ht!] % This is necessary to avoid really awful figure placement midway through the
+    % references...
     \centering
@@
 
-\subsection{Solving from the Top Down}\label{section:topdown}
+\subsection{Solving From the Top Down}\label{section:topdown}
 

### 2016-12-01 paper/paper.tex
Don't use microtype to avoid inevitable whining
New improved page layout
Little tweaks

@@
 \usepackage{complexity}
-\usepackage{microtype}
 \usepackage{amsmath}
@@
     \centering
-    \begin{tikzpicture}[scale=0.5]%[every node/.style={circle, inner sep=0.5mm,node
+    \begin{tikzpicture}[scale=0.58]%[every node/.style={circle, inner sep=0.5mm,node
         %distance=10mm,fill=black}, scale=0.2]
@@
 improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
-these instances in 64 GBytes of RAM. Finally, we show that iteratively increasing $k$ gives a
-competitive algorithm for the maximum common induced subgraph problem.
+these instances in 64 GBytes of RAM. Finally, we show that starting with $k = 0$ and iteratively
+increasing $k$ gives a competitive algorithm for the maximum common induced subgraph problem.
 
@@
 graph $G$, and $\EdgeSet(G)$ for its set of edges. We write $\N_G(v)$ for the \emph{neighbourhood}
-of a vertex $v$ in $G$, and $v \sim_G w$ to mean $v$ is adjacent to $w$; where the graph is clear
-from the context, the subscript is omitted.
+of a vertex $v$ in $G$, and $v \sim_G w$ to mean $v$ is adjacent to $w$. The \emph{degree} of $p$,
+$\deg_G(p)$, is the number of vertices to which it is adjacent. Where the graph is clear from the
+context, the subscripts are omitted.
 
-A \emph{non-induced subgraph isomorphism} from a graph $P$ to a graph $T$ is an injective mapping
-$\V(P) \rightarrowtail \V(T) $ which maps adjacent vertices to adjacent vertices. An \emph{induced subgraph
-isomorphism} $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
-We define a \emph{$k$-less subgraph isomorphism} from $P$ to $T$ to be a subgraph isomorphism from all but
-$k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
-\lessind{k} T$ respectively. We write $p \lessmap{k} t$ to mean that the pattern vertex p is mapped
-to the target vertex v under either kind of mapping.
+A \emph{non-induced subgraph isomorphism} from a graph $P$ (called the \emph{pattern}) to a graph
+$T$ (the \emph{target}) is an injective mapping $\V(P) \rightarrowtail \V(T) $ which maps adjacent
+vertices to adjacent vertices. An \emph{induced subgraph isomorphism} $P \hookrightarrow T$
+additionally maps non-adjacent vertices to non-adjacent vertices.  We define a \emph{$k$-less
+subgraph isomorphism} from $P$ to $T$ to be a subgraph isomorphism from all but $k$ vertices of $P$
+to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P \lessind{k} T$
+respectively. We write $p \lessmap{k} t$ to mean that the pattern vertex p is mapped to the target
+vertex v under either kind of mapping.
 
@@
 \hookrightarrow T$ if and only if $i$ satisfies $P \rightarrowtail T$ and
-$\loopcomp{P} \rightarrowtail \loopcomp{T}$.
+$\loopcomp{P} \rightarrowtail \loopcomp{T}$ simultaneously.
 Similarly, $i$ satisfies the definition of $P
@@
 is also permitted.  To handle the induced case, rather than the usual approach of directly
-having constraints for non-adjacent pairs of vertices, we will make use of \cref{prop:comp} by
+having constraints for non-adjacent pairs of vertices, we will be making use of \cref{prop:comp} by
 seeking a mapping $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
@@
 and source code was compiled using GCC 5.3.0. We used a timeout of 1,000 seconds for each instance.
-For comparison, we used the implementations of \citet{DBLP:conf/cp/McCreeshNPS16}.
+For comparison, we used the implementations of \citet{DBLP:conf/cp/NdiayeS11} and \citet{DBLP:conf/cp/McCreeshNPS16}.
 
@@
 35 vertices in each, whilst our dataset contains graphs with up to 6,671 vertices. For the
-forward checking algorithm described by \citet{DBLP:conf/cp/NdiayeS11}, 1,560 of the instances
+forward-checking algorithm described by \citet{DBLP:conf/cp/NdiayeS11}, 1,560 of the instances
 cannot fit in the amount of RAM we have available---we treat these instances as having timed out.
@@
 
-Let $p$ be a vertex in a graph $P$. The \emph{degree} of $p$, $\deg(p)$, is the number of vertices
-to which it is adjacent. The degree of vertices gives us an invariant, which may be used to
-eliminate some infeasible values from domains.
+Let $p$ be a vertex in a graph $P$. The degree of vertices gives us an invariant, which may be used to
+eliminate some infeasible values from domains as follows.
 
@@
 The \emph{neighbourhood degree sequence} (NDS) of a vertex $p$, $\nds(p)$, is the (non-ascending)
-sequence of degrees of its neighbours.
+sequence of degrees of its neighbours. \citet{constraints10} showed how this may be used for
+filtering in subgraph isomorphism. We extend this for the $k$-less setting as follows.
 
@@
 
-\begin{algorithm*}[tb]
+\begin{algorithm*}[p]
 \DontPrintSemicolon
@@
 
+\begin{figure*}[p]
+    \centering
+    \includegraphics*{gen-graph-runtimes.pdf}
+    \caption{In the first two plots we show the cumulative number of instances solved over time, for the
+        induced and non-induced problems, with different values of $k$. We also show the results of
+        iteratively increasing $k$ until a solution is found, and in the induced case, the
+        performance of two leading maximum common subgraph algorithms. In the third plot we show results
+        comparing iteratively increasing $k$ with our algorithm to other approaches on maximum
+        common induced subgraph instances.}\label{figure:runtimes}
+\end{figure*}
+
 \Cref{algorithm:sip} integrates these techniques into a full algorithm. This is derived from an
@@
 We begin by trying to infer domain deletions. The $\FuncSty{propagate}$ function looks for domains
-which contains either only a single value, or only wildcards---we call such a domain
+which contain either only a single value, or only wildcards---we call such a domain
 \emph{effectively-unit}. If such a domain $D_v$ exists, we eliminate its value from every other domain,
@@
 
-To handle the induced case, we make use of \cref{prop:comp} (line~\ref{line:comp}). We also tested
+To handle the induced case, we make use of \cref{prop:comp} (line~\ref{line:comp}). We considered
 using path reasoning on complement graphs, but this is expensive to calculate and provides little
-benefit in practice on the instances we considered.  We also do not strip isolated vertices as the
+benefit in practice on these instances.  We also do not strip isolated vertices as the
 original algorithm did, as this is not a valid simplification in the induced case, and we do not use
@@
 
-\begin{figure*}[tb]
-    \centering
-    \includegraphics*{gen-graph-runtimes.pdf}
-    \caption{In the first two plots we show the cumulative number of instances solved over time, for the
-        induced and non-induced problems, with different values of $k$. We also show the results of
-        iteratively increasing $k$ until a solution is found, and in the induced case, the
-        performance of two leading maximum common subgraph algorithms. In the third plot we show results
-        comparing iteratively increasing $k$ with our algorithm to other approaches on maximum
-        common induced subgraph instances.}\label{figure:runtimes}
-\end{figure*}
-
-\begin{figure}[ht!] % This is necessary to avoid really awful figure placement midway through the
-    % references...
+\begin{figure}[t]
     \centering

### 2017-01-05 poster/poster.tex
Write the poster

% vim: set spell spelllang=en tw=100 et sw=4 sts=4 :

\documentclass[a0paper]{tikzposter}

\usepackage{complexity}
\usepackage{wrapfig}
\usepackage{microtype}
\usepackage{gnuplot-lua-tikz}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{sfmath}

\usepackage{lmodern}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\title{Between Subgraph Isomorphism and Maximum Common Subgraph}
\author{Ruth Hoffmann, Ciaran McCreesh and Craig Reilly}
\institute{University of Glasgow, Glasgow, Scotland}
\titlegraphic{\includegraphics[keepaspectratio=true,scale=3.5]{UoG_keyline.pdf}}

\settitle{
    \begin{tikzpicture}
        \node (T) [inner sep=0pt] {\begin{minipage}{\linewidth}
                \color{titlefgcolor}
                {\bfseries \Huge \hspace*{10mm}Between Subgraph Isomorphism and \\
                \hspace*{10mm}Maximum Common Subgraph \par}
                \vspace*{1em}
                {\Large {\bfseries \hspace{10mm}\@author}, \@institute}
        \end{minipage}};

        \node at (T.east) [anchor=center, inner sep=0pt, xshift=-12cm] {\@titlegraphic};
    \end{tikzpicture}
}

% University of Glasgow standard colours
\definecolor{uofguniversityblue}{rgb}{0, 0.219608, 0.396078}

\definecolor{uofgheather}{rgb}{0.356863, 0.32549, 0.490196}
\definecolor{uofgaquamarine}{rgb}{0.603922, 0.72549, 0.678431}
\definecolor{uofgslate}{rgb}{0.309804, 0.34902, 0.380392}
\definecolor{uofgrose}{rgb}{0.823529, 0.470588, 0.709804}
\definecolor{uofgmocha}{rgb}{0.709804, 0.564706, 0.47451}

\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgturquoise}{rgb}{0, 0.709804, 0.819608}
\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
\definecolor{uofgpillarbox}{rgb}{0.701961, 0.047059, 0}
\definecolor{uofglavendar}{rgb}{0.356863, 0.301961, 0.580392}

\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{uofgforest}{rgb}{0, 0.317647, 0.2}
\definecolor{uofgburgundy}{rgb}{0.490196, 0.133333, 0.223529}
\definecolor{uofgrust}{rgb}{0.603922, 0.227451, 0.023529}

\definecolorstyle{UofG}{
}{
    % Background Colors
    \colorlet{backgroundcolor}{uofgsandstone!80!white}
    \colorlet{framecolor}{black}
    % Title Colors
    \colorlet{titlefgcolor}{white}
    \colorlet{titlebgcolor}{uofguniversityblue}
    % Block Colors
    \colorlet{blocktitlebgcolor}{white}
    \colorlet{blocktitlefgcolor}{uofguniversityblue}
    \colorlet{blockbodybgcolor}{white}
    \colorlet{blockbodyfgcolor}{black}
    % Innerblock Colors
    \colorlet{innerblocktitlebgcolor}{uofguniversityblue}
    \colorlet{innerblocktitlefgcolor}{black}
    \colorlet{innerblockbodybgcolor}{uofgsandstone}
    \colorlet{innerblockbodyfgcolor}{black}
    % Note colors
    \colorlet{notefgcolor}{black}
    \colorlet{notebgcolor}{uofgrust}
    \colorlet{noteframecolor}{red}
}

\usetheme{Autumn}
\usecolorstyle{UofG}

\tikzposterlatexaffectionproofoff

\useblockstyle[bodyverticalshift=-1cm, roundedcorners=1]{Default}

\renewcommand{\Huge}{\fontsize{77.2}{96}\selectfont}

% Styles for drawings

\tikzset{edge/.style={line width=3pt, color=uofgsandstone}}
\tikzset{ledge/.style={line width=3pt, color=uofgsandstone!40!white}}
\tikzset{hedge/.style={line width=3pt, color=uofgsandstone, dashed}}

\setlength\intextsep{0pt}

\begin{document}
\maketitle

{
    \colorlet{blockbodybgcolor}{uofgcobalt}
    \colorlet{blocktitlebgcolor}{uofgcobalt}
    \block[bodyverticalshift=0cm, bodyinnersep=3mm]{}{
        \centering\begin{minipage}{0.94\textwidth}
    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
    ``as much of the pattern as possible'' inside the target graph. In general, this is known as the maximum
    common subgraph problem, which is much more computationally challenging in practice than
    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
    vertices from the pattern can be found in the target graph. This allows for the development of
    slightly weakened forms of certain invariants from subgraph isomorphism which are based upon degree and
    number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
    their effectiveness. We are then able to solve this problem on the standard problem
    instances used to benchmark subgraph isomorphism algorithms, despite these instances being
    too large for current maximum common subgraph algorithms to handle. Finally, by iteratively
    increasing $k$, we obtain an algorithm which is also competitive for the maximum common subgraph
    problem.
        \end{minipage}
    }
}

\begin{columns}
\column{0.5}

\block{Subgraph Isomorphism (Finding Patterns in Graphs)}{
\begin{wrapfigure}[11]{r}{0.46\linewidth}
    \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (Na) at (1,  0)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (Nb) at (1, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (Nc) at (0, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (Nd) at (2, -4)
        {\vphantom{0}};

        \draw [edge] (Na) -- (Nb);
        \draw [edge] (Nb) -- (Nc);
        \draw [edge] (Nc) -- (Nd);
        \draw [edge] (Nb) -- (Nd);

        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (N1) at (7.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N2) at (9.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (N3) at (7.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N4) at (9.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (N5) at (7.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (N6) at (9.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N7) at (5.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N8) at (5.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N9) at (5.5, -4) {\vphantom{0}};

        \draw [ledge] (N1) -- (N2);
        \draw [edge] (N1) -- (N3);
        \draw [ledge] (N1) -- (N4);
        \draw [ledge] (N2) -- (N4);
        \draw [edge] (N3) -- (N5);
        \draw [edge] (N3) -- (N6);
        \draw [ledge] (N4) -- (N6);
        \draw [edge] (N5) -- (N6);
        \draw [ledge] (N2) to [in=45, out=315] (N6);
        \draw [ledge] (N1) -- (N7);
        \draw [ledge] (N5) -- (N9);
        \draw [ledge] (N7) -- (N8);
        \draw [ledge] (N8) -- (N9);
    \end{tikzpicture}\end{center}

    \vspace*{1.5cm}

    \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Na) at (1,  0)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nb) at (1, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nc) at (0, -4)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nd) at (2, -4)
        {\vphantom{0}};

        \draw [edge] (Na) -- (Nb);
        \draw [edge] (Nb) -- (Nc);
        \draw [edge] (Nc) -- (Nd);
        \draw [edge] (Nb) -- (Nd);

        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N1) at (7.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N2) at (9.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N3) at (7.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N4) at (9.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N5) at (7.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N6) at (9.5, -4) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N7) at (5.5,  0) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N8) at (5.5, -2) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N9) at (5.5, -4) {\vphantom{0}};

        \draw [edge] (N1) -- (N2);
        \draw [ledge] (N1) -- (N3);
        \draw [edge] (N1) -- (N4);
        \draw [edge] (N2) -- (N4);
        \draw [ledge] (N3) -- (N5);
        \draw [ledge] (N3) -- (N6);
        \draw [edge] (N4) -- (N6);
        \draw [ledge] (N5) -- (N6);
        \draw [hedge] (N2) to [in=45, out=315] (N6);
        \draw [ledge] (N1) -- (N7);
        \draw [ledge] (N5) -- (N9);
        \draw [ledge] (N7) -- (N8);
        \draw [ledge] (N8) -- (N9);
    \end{tikzpicture}\end{center}
\end{wrapfigure}

The \textbf{non-induced subgraph isomorphism problem} is to find an injective mapping from a given
pattern graph to a given target graph which preserves adjacency---in essence, we are ``finding a
copy of'' the pattern inside the target.

\bigskip

The \textbf{induced} variant of the problem additionally requires that the mapping preserve
non-adjacency, so there are no ``extra edges'' in the copy of the pattern that we find. The top
example is induced, whereas the bottom example is not, due to the dashed edge.

\bigskip

Despite these problems being \NP-complete, modern practical subgraph isomorphism algorithms can
handle problem instances with many hundreds of vertices in the pattern graph, and up to \textbf{ten thousand
vertices} in the target graph, leading to successful application in areas such as \textbf{computer
vision}, \textbf{biochemistry}, and \textbf{pattern recognition}. However, these algorithms cannot
handle arbitrary instances of this size---here we generate instances with thirty and one hundred and
fifty vertices respectively which cannot be solved within one hour.
}

\column{0.5}

\end{columns}

\begin{columns}
\column{0.5}

\block{See the Paper For\ldots}{
    \begin{itemize}
        \item ~ Delicious cake
    \end{itemize}
}

\column{0.5}

\block{Future Work}{
    \begin{itemize}
        \item ~ Replace Craig with James because James is better
    \end{itemize}
}

\end{columns}

{
    \colorlet{blockbodybgcolor}{uofgsandstone!80!white}
    \colorlet{blocktitlebgcolor}{uofgsandstone!80!white}
    \block[bodyverticalshift=-0.5cm]{}{
        This work was supported by the Engineering and Physical Sciences Research Council [grant
        numbers EP/K503058/1 and EP/M506539/1]. \hfill \texttt{\textcolor{white}{c.mccreesh.1@research.gla.ac.uk}}
    }
}

\end{document}

### 2017-01-30 slide/talkpreamble.tex
Advert slide added.

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{amsmath}                   % \operatorname
\usepackage{amssymb}                   % \nexists
\usepackage{amsthm}

\usepackage{float}      % Allows for [H] positioning option in
\usepackage{subfigure}

\usepackage{media9}

\usepackage{listings}
\lstset{basicstyle=\footnotesize}

\usepackage{tikz}
\usetikzlibrary{automata,shapes,arrows,positioning}

\definecolor{uofguniversityblue}{rgb}{0, 0.219608, 0.396078}

\definecolor{uofgheather}{rgb}{0.356863, 0.32549, 0.490196}
\definecolor{uofgaquamarine}{rgb}{0.603922, 0.72549, 0.678431}
\definecolor{uofgslate}{rgb}{0.309804, 0.34902, 0.380392}
\definecolor{uofgrose}{rgb}{0.823529, 0.470588, 0.709804}
\definecolor{uofgmocha}{rgb}{0.709804, 0.564706, 0.47451}
\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{uofgforest}{rgb}{0, 0.2, 0.129412}
\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgturquoise}{rgb}{0, 0.709804, 0.819608}
\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
\definecolor{uofgrust}{rgb}{0.603922, 0.227451, 0.023529}
\definecolor{uofgburgundy}{rgb}{0.490196, 0.133333, 0.223529}
\definecolor{uofgpillarbox}{rgb}{0.701961, 0.047059, 0}
\definecolor{uofglavendar}{rgb}{0.356863, 0.301961, 0.580392}

\tikzset{vertex/.style={draw, circle, inner sep=0pt, minimum size=0.5cm, font=\small\bfseries}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{vertexc1/.style={vertex, fill=uofgcobalt}}
\tikzset{vertexc2/.style={vertex, fill=uofglawn}}
\tikzset{vertexc3/.style={vertex, fill=uofgpumpkin}}
\tikzset{vertexc4/.style={vertex, fill=uofgheather}}
\tikzset{edge/.style={color=black!50!white}}
\tikzset{bedge/.style={ultra thick}}
\tikzset{edged/.style={color=screengrey, dashed}}
\tikzset{edgel3/.style={color=uofgthistle, ultra thick}}

\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=0pt] (char) {#1};}}

% {{{ theme things
\useoutertheme[footline=authortitle]{miniframes}
\useinnertheme{rectangles}

\setbeamerfont{block title}{size={}}
\setbeamerfont{title}{size=\large,series=\bfseries}
\setbeamerfont{section title}{size=\large,series=\mdseries}
\setbeamerfont{author}{size=\normalsize,series=\mdseries}
\setbeamercolor*{structure}{fg=uofguniversityblue}
\setbeamercolor*{palette primary}{use=structure,fg=black,bg=white}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=uofgcobalt}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=uofguniversityblue}
\setbeamercolor*{palette quaternary}{fg=white,bg=black}

\setbeamercolor*{titlelike}{parent=palette primary}

\beamertemplatenavigationsymbolsempty

\setbeamertemplate{title page}
{
    \begin{tikzpicture}[remember picture, overlay]
        \node at (current page.north west) {
            \begin{tikzpicture}[remember picture, overlay]
                \fill [fill=uofguniversityblue, anchor=north west] (0, 0) rectangle (\paperwidth, -2.4cm);
            \end{tikzpicture}
        };

        \node (logo) [anchor=north east, shift={(-0.6cm,-0.6cm)}] at (current page.north east) {
            \includegraphics*[keepaspectratio=true,scale=0.5]{UoG_keyline.pdf}
        };

        \node [anchor=west, xshift=0.2cm] at (current page.west |- logo.west) {
            \begin{minipage}{0.65\paperwidth}\raggedright
                {\usebeamerfont{title}\usebeamercolor[white]{}\inserttitle}\\[0.1cm]
                {\usebeamerfont{author}\usebeamercolor[white]{}\insertauthor}
            \end{minipage}
        };
    \end{tikzpicture}
}

\setbeamertemplate{section page}
{
    \begin{centering}
        \begin{beamercolorbox}[sep=12pt,center]{part title}
            \usebeamerfont{section title}\insertsection\par
        \end{beamercolorbox}
    \end{centering}
}

\newcommand{\frameofframes}{/}
\newcommand{\setframeofframes}[1]{\renewcommand{\frameofframes}{#1}}

\makeatletter
\setbeamertemplate{footline}
{%
    \begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
    \end{beamercolorbox}
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
        leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
        \leavevmode{\usebeamerfont{author in head/foot}\insertshortauthor}%
        \hfill%
        {\usebeamerfont{institute in head/foot}\usebeamercolor[fg]{institute in head/foot}\insertshortinstitute}%
    \end{beamercolorbox}%
    \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
        leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
        {\usebeamerfont{title in head/foot}\insertshorttitle}%
        \hfill%
%        {\usebeamerfont{frame number}\usebeamercolor[fg]{frame number}\insertframenumber~\frameofframes~\inserttotalframenumber}
    \end{beamercolorbox}%
    \begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
    \end{beamercolorbox}
}

% }}}

### 2017-01-31 poster/poster.tex
first draft

@@
 \usepackage{microtype}
+\usepackage{tikz}
 \usepackage{gnuplot-lua-tikz}
@@
     When a small pattern graph does not occur inside a larger target graph, we can ask how to find
-    ``as much of the pattern as possible'' inside the target graph. In general, this is known as the maximum
-    common subgraph problem, which is much more computationally challenging in practice than
-    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
+    \textbf{``as much of the pattern as possible''} inside the target graph. In general, this is known as the \textbf{maximum
+    common subgraph problem}, which is much more computationally challenging in practice than
+    \textbf{subgraph isomorphism}. We introduce a restricted alternative, where we ask if all but $k$
     vertices from the pattern can be found in the target graph. This allows for the development of
@@
 \begin{wrapfigure}[11]{r}{0.46\linewidth}
+
 \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
@@
 vertices} in the target graph, leading to successful application in areas such as \textbf{computer
-vision}, \textbf{biochemistry}, and \textbf{pattern recognition}. However, these algorithms cannot
-handle arbitrary instances of this size---here we generate instances with thirty and one hundred and
-fifty vertices respectively which cannot be solved within one hour.
+vision}, \textbf{biochemistry}, and \textbf{pattern recognition}.
 }
+
+\vspace*{3cm}
+
+\block{Maximum Common Subgraph (Comparing Graphs)}{
+\begin{wrapfigure}[11]{r}{0.46\linewidth}
+    \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Na) at (0,  0)
+        {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nb) at (0, -2)
+        {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nc) at (2, 0)
+        {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nd) at (2, -2)
+        {\vphantom{0}};
+        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (Ne) at (1, -4) 
+        {\vphantom{0}};
+
+        \draw [edge] (Na) -- (Nb);
+        \draw [edge] (Na) -- (Nc);
+        \draw [edge] (Nb) -- (Nd);
+        \draw [edge] (Nc) -- (Nd);
+        \draw [ledge] (Nb) -- (Ne);
+        \draw [ledge] (Nd) -- (Ne);
+
+   \end{tikzpicture}\end{center}
+
+    \vspace*{1.5cm}
+
+    \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
+         \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N1) at (0,  0) {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N2) at (0,  -4) {\vphantom{0}};
+        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N3) at (2, -2) {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N4) at (4, 0) {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N5) at (4, -4) {\vphantom{0}};
+
+        \draw [edge] (N1) -- (N2);
+        \draw [ledge] (N1) -- (N3);
+        \draw [edge] (N1) -- (N4);
+        \draw [ledge] (N2) -- (N3);
+        \draw [edge] (N2) -- (N5);
+        \draw [edge] (N3) -- (N4);
+        \draw [edge] (N3) -- (N5);
+        \draw [edge] (N4) -- (N5);
+
+   \end{tikzpicture}\end{center}
+\end{wrapfigure}
+
+Given two graphs $G$ and $H$, the \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to
+a subgraph of both $G$ and $H$ --- the size of the maximum common subgraph gives us a measure of how similar two graphs are.
+
+\bigskip
+
+In the induced variant of subgraph isormorphism when a pattern cannot be found in a target graph, we may seek a result which maps as many vertices of the pattern into the target as possible.
+This is precisely the maximum common subgraph problem.
+
+\bigskip
+
+The maximum common subgraph problem is much more difficult in practice than subgraph isomorphism.
+The state of the art for the maximum common subgraph
+problem becomes \textbf{computationally
+infeasible at only 35 vertices} when working with
+unlabelled graphs. This is largely because strong inference,
+based upon the degrees of vertices and the
+distances or paths between them, is possible with subgraph isomorphism,
+but not maximum common subgraph, and so the
+state space in the former is much more restricted, whilst filtering
+during search is vastly stronger.}
 
@@
 
+\block{$k$-less Subgraph Isomorphism (Finding Most of a Pattern)}{
+
+A \textbf{$k$-less subgraph isomorphism} between a pattern and target graph, is a subgraph isomorphism
+where we seek a mapping from all but $k$ verticies of the pattern to the target.
+
+\bigskip
+
+If $k$ is reasonably small, weakened forms of invariants from subgraph isomorphism (based on vertex degrees and paths) are still effective at reducing the search space.
+In the example it is clear that the pattern graph is not isomorphism to a subgraph of the target, but upon removal of the central vertex we have a $1$-less isomorphism from the pattern to the target.
+
+\bigskip
+
+\begin{center}
+    \begin{tikzpicture}[scale=1.1]%[every node/.style={circle, inner sep=0.5mm,node
+        %distance=10mm,fill=black}, scale=0.2]
+
+        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (d) at (0,0) {\vphantom{0}}; 
+        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries]  (a) at (-2,2){\vphantom{0}}; 
+        \node[draw, circle, fill=uofgpillarbox, inner sep=5pt, font=\bfseries]  (c) at (0,2) {\vphantom{0}}; 
+        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries]  (e) at (2,2) {\vphantom{0}}; 
+        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries]  (b) at (0,4) {\vphantom{0}};
+
+        \draw[edge] (a) -- (b);
+        \draw[edge] (a) -- (d);
+        \draw[edge] (b) -- (e);
+        \draw[ledge] (b) -- (c);
+        \draw[ledge] (c) -- (d);
+        \draw[edge] (d) -- (e);
+
+        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (f) at (8,0) {\vphantom{0}};
+        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (g) at (6,2) {\vphantom{0}};
+        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (h) at (10,4) {\vphantom{0}};
+        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (i) at (10,2) {\vphantom{0}};
+        \node[draw, circle, fill=uofgrose, inner sep=5pt, font=\bfseries] (j) at (8,4) {\vphantom{0}};
+        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (k) at (10,0) {\vphantom{0}};
+        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (l) at (12,0){\vphantom{0}};
+        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (m) at (12,4) {\vphantom{0}};
+
+        \draw[edge] (f) -- (i);
+        \draw[edge] (g) -- (f);
+        \draw[edge] (i) -- (j);
+        \draw[edge] (g) -- (j);
+        \draw[ledge] (h) -- (m);
+        \draw[ledge] (h) -- (i);
+        \draw[ledge] (i) -- (k);
+        \draw[ledge] (k) -- (l);   
+        %\path[solid] (a) edge (b) edge (d)
+        %    (e) edge (b) edge (d)
+        %    (d) edge (c) edge (f)
+        %    (c) edge (h)
+        %    (f) edge (g);
+    \end{tikzpicture}
+\end{center}
+\bigskip
+
+Are there instances for which k = 0 is unsatisfiable, but that
+are satisfiable for small k? For the problem families which
+do not consist entirely of satisfiable instances, we plot this for both the induced and non-induced variants.
+
+\bigskip
+
+\begin{center}
+\input{gen-graph-which-k-by-family}
+\end{center}
+
+\bigskip
+
+In the ``phase'' family, which consists of instances
+crafted to be extremely difficult to solve, we are not able
+to answer this question, and in the ``scalefree'' family we
+see no satisfiable instances with low but not zero k. 
+However, in several of the remaining families our algorithm manages to more than double
+the number of instances for which exact solutions are
+known, and we gain upper bounds on many more. This is particularly
+interesting for the ``images-CVIU11'', where the size of the solution has a
+direct \textbf{real-world interpretation} in terms of \textbf{closeness of image
+matching}.
+
+}
+
 \end{columns}
 
+\block{Maximum Common Subgraph: Solving from the Top Down}{
+
+\begin{wrapfigure}[11]{r}{0.66\linewidth}
+\begin{center}
+\input{gen-graph-runtimes}
+\end{center}
+\end{wrapfigure}
+What would happen if we used the $k$-less approach to solve the
+maximum common induced problem? We could simply start
+at k = 0, and increase k until a solution is found. This \textbf{tackles the problem in the opposite direction from existing
+approaches}, which work by attempting to construct
+larger and larger solutions. In the figure, ``$k\downarrow$'' is our algorithm, whilst ``FC'' and
+``clique'' are state of the art maximum common subgraph algorithms.
+
+\bigskip
+
+We see that \textbf{our approach is able to close over twice
+as many of these instances as the previous state of the art} --- which struggles due to it's RAM requirements.
+(The same conclusion holds even if every instance which is
+satisfiable with k = 0 is removed from the dataset.)
+On instances designed for the maximum subgraph problem we are still the single strongest solver, and our performace is complementary to that of the clique encoding. 
+}
 \begin{columns}
@@
     \begin{itemize}
-        \item ~ Delicious cake
+        \item ~ Description of our new invariants, and proofs that they hold. 
+        \item ~ Description of the algorithm the algorithm.
     \end{itemize}
@@
     \begin{itemize}
-        \item ~ Replace Craig with James because James is better
+        \item ~ Develop an algorithm for maximum common subgraph which makes use of an upper bound from our approach and a lower bound from the clique approach, stopping when the bounds converge.
     \end{itemize}

### 2017-01-31 slide/slide.tex

--- 2016-11-30 paper/paper.tex
@@
-% vim: set spell spelllang=en tw=100 :
+\documentclass{beamer}
+\usepackage[export]{adjustbox}
 
-\documentclass[letterpaper]{article}
+\usepackage{tikz}
+\usetikzlibrary{automata,shapes,arrows,positioning,fit}
 
-\setlength{\pdfpagewidth}{8.5in}
-\setlength{\pdfpageheight}{11in}
+\input{talkpreamble}
 
-\usepackage{aaai17}
-
-\usepackage{times}
-\usepackage{helvet}
-\usepackage{courier}
-\usepackage{complexity}
-\usepackage{microtype}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{cleveref}
-\usepackage{tikz}
-\usepackage{mathtools}
-\usepackage{graphicx}
-\usepackage[vlined]{algorithm2e}
-
-\setcounter{secnumdepth}{2}
-
-\usetikzlibrary{decorations, decorations.pathreplacing, calc}
-
-\newcommand{\citet}[1]{\citeauthor{#1} \shortcite{#1}}
-\newcommand{\citep}[1]{\cite{#1}}
-
-\theoremstyle{definition}
-\newtheorem{corollary}{Corollary}
-\newtheorem{example}{Example}
-\newtheorem{proposition}{Proposition}
-
-% cref style
-\crefname{figure}{Figure}{Figures}
-\Crefname{figure}{Figure}{Figures}
-\crefname{section}{Section}{Sections}
-\Crefname{section}{Section}{Sections}
-\crefname{proposition}{Proposition}{Propositions}
-\Crefname{proposition}{Proposition}{Propositions}
-\crefname{corollary}{Corollary}{Corollaries}
-\Crefname{corollary}{Corollary}{Corollaries}
-
-\crefname{algocf}{Algorithm}{Algorithms}
-\Crefname{algocf}{Algorithm}{Algorithms}
-
-% http://tex.stackexchange.com/questions/22100/the-bar-and-overline-commands
-\newcommand{\shortoverline}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
-
-% Maths operators
-\newcommand{\paths}{\operatorname{paths}}
-\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
-\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
-\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
-\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
-\newcommand{\V}{\operatorname{V}}
-\newcommand{\EdgeSet}{\operatorname{E}}
-\newcommand{\N}{\operatorname{N}}
-\newcommand{\nds}{\operatorname{S}}
-\newcommand{\loopcomp}[1]{\tset{\multimap}{#1}}
-
-\newcommand{\tset}[2]{%
-    \tikz[baseline=(X.base),inner sep=0pt,outer sep=0pt]{%
-        \node[inner sep=0pt,outer sep=0pt] (X) {$#2$};
-        \node[yshift=1.5pt,xshift=1pt] at (X.north) {$\scriptstyle#1$};
-}}
-
-\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
-
-\title{Between Subgraph Isomorphism and Maximum Common Subgraph}
-
-\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and
-Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M506539/1]} \and Craig
-Reilly\samethanks \\ University of Glasgow, Glasgow, Scotland \\ ruth.hoffmann@glasgow.ac.uk \and
-\{c.mccreesh.1,c.reilly.2\}@research.gla.ac.uk}
-
-\pdfinfo{
-    /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
-    /Author (Ruth Hoffmann and Ciaran McCreesh and Craig Reilly)
-}
+\title[Between Subgraph Isomorphism and Maximum Common Subgraph]{Between Subgraph Isomorphism and \\ Maximum Common Subgraph}
+\author[Ruth Hoffmann, Ciaran McCreesh and Craig Reilly]{Ruth Hoffmann, Ciaran McCreesh and  \textbf{Craig Reilly}}
 
@@
 
-\maketitle
-
-\begin{abstract}
-    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
-    ``as much of the pattern as possible'' inside the target graph. In general, this is known as the maximum
-    common subgraph problem, which is much more computationally challenging in practice than
-    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
-    vertices from the pattern can be found in the target graph. This allows for the development of
-    slightly weakened forms of certain invariants from subgraph isomorphism which are based upon degree and
-    number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
-    their effectiveness. We are then able to solve this problem on the standard problem
-    instances used to benchmark subgraph isomorphism algorithms, despite these instances being
-    too large for current maximum common subgraph algorithms to handle. Finally, by iteratively
-    increasing $k$, we obtain an algorithm which is also competitive for the maximum common subgraph
-    problem.
-\end{abstract}
-
-\section{Introduction}
-
-The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
-\emph{target} graph. The problem arises in many areas, including bioinformatics
-\citep{Bonnici:2013}, computer vision \citep{cviu11,pr15}, malware detection
-\citep{DBLP:conf/dimva/BruschiMM06}, compilers
-\citep{DBLP:conf/cgo/MurrayF12,DBLP:conf/cp/BlindellLCS15}, model checking \cite{Sevegnani:2015}, and pattern recognition
-\citep{Conte:2004}, which has lead to substantial research into how best to solve the problem in
-practice \cite[and
-more]{mcgregor79,Ullman,Cordella:2004,DBLP:journals/ai/Solnon10,DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}.
-The problem comes in two forms: in the non-induced variant, edges must be mapped to edges, but the
-target may have ``extra edges'', whilst in the induced variant, non-edges must be mapped to
-non-edges.
-
+    \begin{frame}[plain,noframenumbering]
+        \titlepage
+        \vspace{2.2cm}
         \begin{figure}[b]
             \centering
-    \begin{tikzpicture}[scale=0.5]%[every node/.style={circle, inner sep=0.5mm,node
+            \begin{tikzpicture}[scale=0.58]%[every node/.style={circle, inner sep=0.5mm,node
                 %distance=10mm,fill=black}, scale=0.2]
@@
             \end{tikzpicture}
-    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
-    the central vertex in $P$ is removed, then a subgraph isomorphism exists.}
-    \label{figure:subgraphexample}
         \end{figure}
-
-When a pattern cannot be found, we may wish to be given a result which maps as many vertices of the
-pattern into the target as possible. In the induced case, this is known as the maximum common
-induced subgraph problem (we discuss the non-induced case in \cref{section:definitions}). However,
-although recent subgraph isomorphism algorithms are comfortable working with graphs with thousands
-of vertices, the state of the art for the maximum common subgraph problem
-\citep{DBLP:conf/cp/McCreeshNPS16} becomes computationally infeasible at only 35 vertices when
-working with unlabelled graphs. This is largely because strong inference, based upon the degrees of
-vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
-\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
-but not maximum common subgraph, and so the state space in the former is much more restricted,
-whilst filtering during search is vastly stronger.
-
-In this work we discuss an intermediate problem, where we must map all but $k$ vertices of the
-pattern graph into the target---we show an example in \cref{figure:subgraphexample}. This in some
-ways resembles the approximate subgraph matching model of \citet{DBLP:conf/cp/ZampelliDD05},
-although we allow any vertex to be removed. We show that if
-$k$ is reasonably small (say, between 1 and 5), then weakened forms of degree and path based
-filterings are still effective in pruning the initial search space and in providing additional
-constraints respectively. We then show that combining these techniques leads to a practical
-algorithm which can scale to work with the families of graphs commonly used to benchmark subgraph
-isomorphism algorithms: depending upon the benchmark family, we can close a substantial portion of
-the instances, and in many more cases, we can at least obtain an upper bound. This is a significant
-improvement over state of the art maximum common subgraph solvers, which cannot even fit many of
-these instances in 64 GBytes of RAM. Finally, we show that iteratively increasing $k$ gives a
-competitive algorithm for the maximum common induced subgraph problem.
-
-\subsection{Definitions and Notations} \label{section:definitions}
-
-Throughout, our graphs are undirected, but may have loops.  We write $\V(G)$ for the vertex set of a
-graph $G$, and $\EdgeSet(G)$ for its set of edges. We write $\N_G(v)$ for the \emph{neighbourhood}
-of a vertex $v$ in $G$, and $v \sim_G w$ to mean $v$ is adjacent to $w$; where the graph is clear
-from the context, the subscript is omitted.
-
-A \emph{non-induced subgraph isomorphism} from a graph $P$ to a graph $T$ is an injective mapping
-$\V(P) \rightarrowtail \V(T) $ which maps adjacent vertices to adjacent vertices. An \emph{induced subgraph
-isomorphism} $P \hookrightarrow T$ additionally maps non-adjacent vertices to non-adjacent vertices.
-We define a \emph{$k$-less subgraph isomorphism} from $P$ to $T$ to be a subgraph isomorphism from all but
-$k$ vertices of $P$ to $T$; this may be non-induced or induced, written $P \lessnonind{k} T$ and $P
-\lessind{k} T$ respectively. We write $p \lessmap{k} t$ to mean that the pattern vertex p is mapped
-to the target vertex v under either kind of mapping.
-
-The \emph{complement} of a (simple) graph $P$ is the graph $\shortoverline{P}~$.  Adjacent distinct
-vertices in $P$ are non-adjacent in $\shortoverline{P}$ while non-adjacent vertices in $P$ are
-adjacent in $\shortoverline{P}$.  The \emph{loop complement} of a graph $P$ is the graph
-$\loopcomp{P}$.  The construction of $\loopcomp{P}$ is similar to that of $\shortoverline{P}~$, however
-whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an
-induced subgraph isomorphism problem we make use of the loop complement; we care about mapping
-vertices with loops to vertices with loops, and vertices without loops to vertices without loops.
-The following proposition follows directly from the definitions.
-
-\begin{proposition}
-    \label{prop:comp}
-Let $i$ be an assignment of vertices of $T$ to vertices of $P$.  Then $i$ satisfies the definition of $P
-\hookrightarrow T$ if and only if $i$ satisfies $P \rightarrowtail T$ and
-$\loopcomp{P} \rightarrowtail \loopcomp{T}$.
-Similarly, $i$ satisfies the definition of $P
-\lessind{k} T$ if and only if $i$ satisfies both $P \lessnonind{k} T$ and
-$\loopcomp{P}
-\lessnonind{k} \loopcomp{T}$.
-\end{proposition}
-
-A \emph{common induced subgraph} of graphs $G$ and $H$ is a graph $P$, together with two induced subgraph
-isomorphisms to $G$ and $H$; a \emph{maximum common induced subgraph} is a common induced subgraph with as
-many vertices as possible. An induced $k$-less subgraph isomorphism $P \lessind{k} T$ is equivalent
-to a common induced subgraph of $P$ and $T$ with $\left|\V(P)\right| - k$ vertices.
-
-If defined similarly, a maximum common non-induced subgraph would allow us to select every vertex in
-the smaller of the two graphs, and none of the edges. It is therefore traditional to change the
-objective to maximise the number of edges selected, rather than vertices, when a non-induced common
-subgraph is sought---this problem is usually called the maximum common \emph{partial} subgraph
-problem instead \citep{DBLP:conf/cp/NdiayeS11}. However, this is not what we will be discussing in
-this paper: maximum common subgraph problems are symmetric in their inputs, but when discussing the
-non-induced case we are allowing extra edges only in the target graph, not in the pattern.
-
-\subsection{Constraint Models and Algorithms}
-
-For both subgraph isomorphism and maximum common subgraph, constraint programming is the best known
-approach\footnote{Note that toolkits are not used in state of the art implementations, to facilitate
-better memory layouts and propagation queues, although the algorithms are inspired by constraint
-programming.}, although a reduction to the maximum clique problem is better when edge labels are
-present \citep{DBLP:conf/cp/NdiayeS11,DBLP:conf/cp/McCreeshNPS16}. For both problems, we create a
-variable for each vertex in the pattern graph (the smaller graph, in the case of maximum common
-subgraph), with domains ranging over the vertices in the target graph (the larger graph). For
-maximum common subgraph, each domain is given an additional $\bot$ value, meaning ``unmapped''.
-
-Constraints are used to ensure that adjacent pairs of vertices are mapped to adjacenct pairs of
-vertices. For the maximum common subgraph case, any pair of assignments with $\bot$ as either value
-is also permitted.  To handle the induced case, rather than the usual approach of directly
-having constraints for non-adjacent pairs of vertices, we will make use of \cref{prop:comp} by
-seeking a mapping $i$ which simultaneously satisfies $P \rightarrowtail T$ and $\loopcomp{P}
-\rightarrowtail \loopcomp{T}$. Finally, an ``all different except $\bot$ constraint'' ensures
-injectivity.
-
-For subgraph isomorphism, this model can be enhanced with domain filtering at the top of search, to
-reduce the initial sizes of domains---we discuss this in \cref{section:degreefiltering}. Subgraph
-isomorphism also allows us to generate additional implied constraints, which we discuss in
-\cref{section:pathfiltering}. However, neither of these techniques are valid for the maximum common
-subgraph problem.
-
-There are three easy ways we might try to extend existing algorithms to handle the $k$-less problem.
-A non-induced $k$-less subgraph isomorphism from $P$ to $T$ is equivalent to a subgraph isomorphism
-between $P$ and $T$, with $k$ extra universally-adjacent vertices added to $T$, and so we could try
-solving subgraph isomorphism with a modified target graph. However, using such
-an approach is not ideal, because it would introduce symmetries; for induced $k$-less subgraph
-isomorphisms, an approach based around adding vertices to $T$ cannot work at all.
-Another algorithmic approach could be to try each way of removing $k$ vertices from the pattern
-graph, and solving each subgraph isomorphism problem in turn. This approach might be feasible for $k
-= 1$, although it would involve a lot of duplication of search effort, but for larger values of $k$
-the number of searches which would have to be made would grow very quickly.
-Finally, for the induced case we could try adapting maximum common subgraph algorithms to solve the
-decision problem. However, both the maximum common subgraph algorithm and the clique encoding
-require $O(\left|\V(P)\right|^2\left|\V(T)\right|^2)$ memory \citep{DBLP:conf/cp/McCreeshNPS16},
-which is extremely problematic on the instances with which we wish to work.
-
-Instead, this paper introduces a new algorithm, inspired by a state of the art subgraph isomorphism
-algorithm \citep{DBLP:conf/cp/McCreeshP15}. The approach we discuss requires only
-$O(\left|\V(P)\right|^2\left|\V(T)\right|)$ space (this can be thousands of times less than maximum
-common subgraph approaches, once the constant factors and orders of $T$ in our instances are
-considered).
-
-\subsection{Experimental Setup} \label{section:setup}
-
-We perform our experiments on systems with dual Intel Xeon CPU E5-2640 processors with 64GBytes of
-RAM, running Ubuntu 14.04. Our algorithm was implemented in
-C++\footnote{https://github.com/ciaranm/aaai17-between-subgraph-isomorphism-and-maximum-common-subgraph-paper},
-and source code was compiled using GCC 5.3.0. We used a timeout of 1,000 seconds for each instance.
-For comparison, we used the implementations of \citet{DBLP:conf/cp/McCreeshNPS16}.
-
-For datasets, we use the same 5,725 instances used in a recent work on portfolios of algorithms for
-subgraph isomorphism \citep{thelionpaper}. This collection includes randomly generated scale-free
-graphs \citep{constraints10}, an assortment of real-world graphs of varying sizes \citep{LV02},
-randomly generated graph pairs (using bounded degree, regular mesh, and uniform models; all are
-satisfiable), segmented images~\citep{pr15,cviu11}, meshes from modelling 3D objects \citep{cviu11},
-and graphs close to the satisfiable-unsatisfiable phase transition
-\citep{DBLP:conf/ijcai/McCreeshPT16}. All of these instances are available in a simple text
-format\footnote{http://liris.cnrs.fr/csolnon/SIP.html}.  Note that many of these instances
-are \emph{much} larger than were used in the recent comparison of maximum common subgraph algorithms
-by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs, they used pairs of graphs with up to
-35 vertices in each, whilst our dataset contains graphs with up to 6,671 vertices. For the
-forward checking algorithm described by \citet{DBLP:conf/cp/NdiayeS11}, 1,560 of the instances
-cannot fit in the amount of RAM we have available---we treat these instances as having timed out.
-The situation for the clique encoding is even worse, and 3,653 of these instances do not fit in
-64GBytes of RAM. In contrast, for our algorithm, every instance fits comfortably.
-
-\section{Domain Filtering Using Degrees}\label{section:degreefiltering}
-
-Let $p$ be a vertex in a graph $P$. The \emph{degree} of $p$, $\deg(p)$, is the number of vertices
-to which it is adjacent. The degree of vertices gives us an invariant, which may be used to
-eliminate some infeasible values from domains.
 
@@
             \end{tikzpicture}
-    \caption{There is a non-induced isomorphism $P\rightarrowtail T$ from the first graph to the
-    second, using the highlighted vertices. No such isomorphism exists between $P$ and $U$, but there
-    is a $1$-less isomorphism $P\lessnonind{1} U$ which omits vertex $b$.}\label{figure:klessexample}
         \end{figure}
-
-\begin{proposition}\label{prop:deg}
-    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
-    $k$-less subgraph isomorphisms, if $p \lessmap{k} t$ then
-    $\deg(p) - k \le \deg(t)$.
-\end{proposition}
-\begin{proof}
-Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$.
-Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$.
-Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$.
-Then
-\[
-\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t). \qedhere
-\]
-\end{proof}
-
-The \emph{neighbourhood degree sequence} (NDS) of a vertex $p$, $\nds(p)$, is the (non-ascending)
-sequence of degrees of its neighbours.
-
-Let $S = ( s_1 , \ldots , s_n )$ and $T = ( t_1 , \ldots , t_m)$ be two sequences.  We say that $S
-\preceq T$ if $n \leq m$ and $\forall s_i \in S$ there exists a distinct $t_j \in T$ with $s_i \leq
-t_j$.  When considering a $k$-less subgraph isomorphism we say that $S \lesspreceq{k} T$ if $n - k
-\leq m$, and if there exists some subsequence $S_k$ of $S$ containing up to $k$ members such that
-$\forall s_i \in S \setminus S_k$, there exists a distinct $t_j \in T$ with $s_i - k \leq t_j$.
-
-\begin{proposition}\label{prop:nds}
-If $p \lessmap{k} t$, then $\nds(p) \lesspreceq{k} \nds(t)$.
-\end{proposition}
-\begin{proof}
-Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
-implies that $\left|\nds(p)\right| -k \leq \left| \nds(t) \right| $.
-
-Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$ is some subset
-of the vertices of $P$ with $\left| P_k \right| \leq k$, we have $q \lessmap{k} u$, where $u \in
-N(t)$ and each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence
-$\nds(p) \lesspreceq{k} \nds(t)$.
-\end{proof}
-
-\begin{example}
-Consider the pattern graph $P$ and the two target graphs $T$ and $U$ shown in
-\cref{figure:klessexample}. The neighbourhood degree sequence of pattern vertex $p$ is
-$\nds(p)=(3,3,2)$.
-We highlight a subgraph in $T$ which is non-induced isomorphic to $P$. The vertex $p$ can be
-mapped to $q$ in the target graph $T$, as $\nds(q)=(5,5,4,2,2)$.  There is a non-induced
-mapping of the pattern graph $P$ into $U$ by removing $b$ of $P$.  This removal
-changes the neighbourhood degree sequence of $p$ in the $k$-less version of $P$ to $\nds(p)=(2,2)$.
-\end{example}
-
-\Cref{figure:klessexample} also illustrates the three cases possible when filtering by neighbourhood
-degree sequence.  Removing vertex $d$ causes each entry in $\nds(p)$ to be reduced; removing vertex
-$a$ removes an entry from $\nds(p)$; and removing either of vertex $b$ or $c$ causes both the size
-of $\nds(p)$ to be reduced and an entry in $\nds(p)$ to be reduced.
-
-\begin{corollary}
-Since both $\nds(p)$ and $\nds(t)$ are non-ascending, without loss of generality we can replace
-$S \setminus S_k$ from the definition of $S \lesspreceq{k} T$ with the subsequence consisting of all
-    but the first $k$ members of $S$.
-\end{corollary}
-
-\begin{figure}
-    \centering
-    \includegraphics*{gen-graph-ids.pdf}
-    \caption{The amount of domain reduction achieved for the induced problem, with increasing
-    $k$. The $y$ value shows for how many instances we may reduce the initial search space to be
-    at most the $x$ proportion of the size the search space would be for the maximum common subgraph
-    problem.}\label{figure:ids}
-\end{figure}
-
-\Cref{figure:ids} demonstrates that \cref{prop:nds} is effective in practice: we show the amount of
-domain reduction we can achieve at the top of search by using invariants and a fixed $k$, compared
-to the search space size for the maximum common induced subgraph problem. (The results on the
-non-induced version show a similar but slightly weaker trend.) We look at the product of the domain
-sizes, rather than the number of eliminations, as this better reflects the number of combinations
-remaining to be considered.
-
-Some other invariants do not translate. For example, another rule which can be effective on regular
-graphs involves counting the number of neighbours of a vertex which are present in a triangle
-\citep{mckay2014practical}. Removing a single vertex can alter this count arbitrarily, so we cannot
-make use of this fact.
-
-\section{Filtering During Search Using Paths}\label{section:pathfiltering}
-
-As well as reasoning about degrees, we can also reason about paths.  A \emph{path} between two
-vertices $p$ and $q$ is a sequence of edges which can be traversed from $p$ to reach $q$. We define
-$\paths(p,q,n)$ to be the \emph{number of paths of length $n$} between the vertices $p$ and $q$.
-
-\begin{proposition}\label{prop:paths}
-    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
-     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
-\end{proposition}
-\begin{proof}
-Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, \[P_{2} = \{((p,x),(x,q)) :
-(p,x),(x,q)\in \EdgeSet(P) \}\textnormal{.}\] As we are looking at paths of length 2,
-the intermediate vertices lie in both neighbour vertex sets of $p$ and $q$. We can rewrite
-$P_{2}$ as \[P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}\textnormal{,}\] in
-other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and
-$q$, \[ P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} \textnormal{.}\] Therefore
-$\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
-
-If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of
-    the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$,
-\[
-\left| \N(p)\cap \N(q)\right| - k \leq \deg(p) - k \leq \deg(t).
-\]
-As $\left|\N(p)\cap \N(q)\right|\leq \deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq \deg(t)$, we have
-\begin{align*}
-\left|\N(p)\cap \N(q)\right| - k & \leq \deg(p) - k \\
- & \leq \left|\N(t)\cap \N(u)\right|\\
- & \leq \deg(t)
-\end{align*}
-which tells us
-\[
-\paths(p, q, 2) - k \leq \paths(t, u, 2). \qedhere
-\]
-\end{proof}
-
-\begin{corollary}\label{corollary:supplemental}
-    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\V(G)$, and edges between vertices $p$ and $q$ if there are at least $n$ simple paths of
-    length exactly $\ell$ between $p$ and $q$ in $G$. Then any $k$-less subgraph isomorphism
-    $P \lessnonind{k} T$ induces a new $k$-less subgraph isomorphism
-    $P^{n+k, 2}\lessnonind{k} T^{n, 2}$ using the same vertex assignments.
-\end{corollary}
-
-Unlike in conventional subgraph isomorphism, we cannot extend this filtering to look at paths of
-length three: as the example in \cref{figure:pathlength3example} shows, removing a single vertex can
-delete arbitrarily many such paths. We \emph{could} instead count paths of any length which are
-vertex disjoint, although calculating this appears to be too expensive to be beneficial in practice.
-
         \begin{figure}[tb]
@@
             \end{tikzpicture}
-    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
-    the vertex $p$ in $P$ is removed, then a subgraph isomorphism exists.}
-    \label{figure:pathlength3example}
         \end{figure}
-
-\begin{figure*}[tb]
-    \centering
-    \includegraphics*{gen-graph-constraints-induced-0.pdf}
-    \includegraphics*{gen-graph-constraints-induced-1.pdf}
-    \includegraphics*{gen-graph-constraints-induced-2.pdf}
-    \includegraphics*{gen-graph-constraints-induced-3.pdf}
-    \includegraphics*{gen-graph-constraints-induced-4.pdf}
-    \includegraphics*{gen-graph-constraints-induced-5.pdf}
-
-    \caption{For the induced problem, the proportion of pairs of assignments from the filtered
-    domains which are not permitted simultaneously, without path constraints on the $x$-axis and
-    with path constraints on the $y$-axis, for increasing values of $k$.}\label{figure:constraints}
-\end{figure*}
-
-To allow for fast propagation, rather than calculating paths dynamically like
-\citet{DBLP:conf/cp/AudemardLMGP14}, we follow the approach of \citet{DBLP:conf/cp/McCreeshP15} and
-construct \emph{supplemental graphs}, and find a mapping which is simultaneously a non-induced subgraph
-isomorphism between every supplemental graph pair. We use paths of length 2, looking at whether
-there are at least 1, 2, and 3 in the target graph (and so whether there are at least $1 + k$ up to
-$3 + k$ in the pattern).  We then investigate whether this leads to new constraints being generated.
-
-By an \emph{assignment}, we mean considering mapping a pattern vertex $p$ to a target vertex $t$ (and not
-$\bot$) which does not violate any loop constraints. An \emph{assignment pair} is two assignments with
-distinct $p$ and distinct $t$, which we say is permitted if it does not violate any adjacency
-constraint. We define the \emph{permitted assignment pair ratio} to be the proportion of assignment pairs
-which are permitted.  Given this, in \cref{figure:constraints} we scatter plot the permitted assignment
-pair ratio with and without supplemental graphs\footnote{Because of the large sizes of the domains,
-we randomly sample one million pairs rather than considering every pair. In some cases, we have
-nearly a thousand domains, each with nearly ten thousand values---a complete quadratic calculation
-involving even a trivial arithmetic operation on this would take many hours.}.
-
-For $k = 0$, we see many points above the $x-y$ diagonal, which shows that for many instances, we
-are able to create a substantial number of new constraints at the top of search; on the other hand,
-there are also points on the diagonal, which shows that sometimes this technique provides no
-benefit. (Occasionally, points fall below the $x-y$ diagonal.  This is because the use of
-neighbourhood degree sequence reasoning on supplemental graphs can also lead to increased domain
-filtering, which could in turn eliminate a higher proportion of forbidden than permitted assignment
-pairs.) For $k = 1$ and $k = 2$, the proportion of points above the diagonal diminishes, but we are
-still able to create new constraints for many instances. By the time $k = 3$, most of the benefit is
-disappearing---although sometimes we are still able to make a difference, and bear in mind that
-sometimes adding just one new constrained pair can vastly reduce the search space.
-
-\section{A New Algorithm}\label{section:algorithm}
-
-\begin{algorithm*}[tb]
-\DontPrintSemicolon
-    \begin{minipage}[t]{\dimexpr.5\textwidth-.5\columnsep}
-\nl $\FuncSty{klessSubgraphIsomorphism}$ (\\\hspace*{2em}Graph $\mathcal{P}$, Graph $\mathcal{T}$, Int $k$) $\rightarrow$ Bool \;
-\nl \Begin{
-    \nl \lIf{$\left|\V(\mathcal{P})\right| + k > \left|\V(\mathcal{T})\right|$}{$\KwSty{return}~\KwSty{false}$\label{line:enough}}
-    \nl $L \gets \big[ (\mathcal{P},\ \mathcal{T}), (\loopcomp{\mathcal{P}},
-            \loopcomp{\mathcal{T}}) \textnormal{~only if we want induced\label{line:comp}}, \label{line:supplemental}$
-        \\\hspace*{1.0em}$(\mathcal{P}^{1 + k,2},\ \mathcal{T}^{1,2}), (\mathcal{P}^{2 + k,2},\
-    \mathcal{T}^{2,2}), (\mathcal{P}^{3 + k,2},\ \mathcal{T}^{3,2}) \big]$ \;
-    \nl \ForEach{$v \in \V(\mathcal{P})$}{
-        \nl $D_v \gets \V(\mathcal{T})$\;
-        \nl \ForEach{$(P,\,T) \in L$}{
-            \nl $D_v \gets \{ w \in D_v : $ \label{line:degreefiltering} \\
-            \hspace*{4em}$v \sim_P v \Rightarrow w \sim_T w~\wedge$ \\
-            \hspace*{4em}$\nds_P(v) \lesspreceq{k} \nds_T(w)\}$ \;
-        }
-        \nl $D_v \gets D_v \cup k~\textnormal{distinct wildcard values} \label{line:wildcards}$
-    }
-    \nl \If{\FuncSty{propagate}(L, D)}{
-        \nl $\KwSty{return}~\FuncSty{search}(L, \{ E \in D : \left|E\right| > 1 \}, k)$\;
-    }
-    \nl \lElse{$\KwSty{return}~\KwSty{false}$}
-}
-\bigskip
-\nl $\FuncSty{search}$ (GraphPairs $L$, Domains $D$, Int $k$) $\rightarrow$ Bool \;
-\nl \Begin{
-    \nl \lIf{$D = \emptyset$}{$\KwSty{return}~\KwSty{true}$}
-    \nl $D_v \gets \textnormal{the smallest domain in}~D$ \label{line:pickd} \;
-    \nl \ForEach {$v' \in D_v~\textnormal{ordered by static degree in}~\mathcal{T}$\label{line:parforeach}}{
-        \nl \If{$v'$ \textnormal{is not the first wildcard we have tried\label{line:sym}}}{
-            \nl \KwSty{continue} \;
-        }
-        \nl $D' \gets \FuncSty{clone}(D)$ \;
-        \nl $D'_v \gets \{ v' \} $ \;
-        \nl \If{\FuncSty{propagate}(L, D')}{
-            \nl \If{$\FuncSty{search}(L, \{ E \in D' : \left|E\right| > 1 \}, k)$}{
-                \nl $\KwSty{return}~\KwSty{true}$ \;
-            }
-        }
-    }
-}
-\end{minipage}\hfill%
-    \begin{minipage}[t]{\dimexpr.5\textwidth-.5\columnsep}
-\nl $\FuncSty{propagate}$ (GraphPairs $L$, Domains $D$) $\rightarrow$ Bool \;
-\nl \Begin{
-    \nl \While{\KwSty{true}}{
-        \nl \If{\textnormal{no effectively-unit domains remain (treating all wildcard~values as a single
-            value)\label{line:effect}}}{
-            \nl \If{$\KwSty{not}~\FuncSty{allDifferent}(D)$}{
-                \nl $\KwSty{return}~\KwSty{false}$ \;
-            }
-        }
-        \nl \If{\textnormal{no effectively-unit domains remain}}{
-            \nl $\KwSty{return}~\KwSty{true}$ \;
-        }
-        \nl $D_v \gets \textnormal{an effectively-unit domain from}~D$ \;
-        \nl $v' \gets $ the single value in $D_v$, or an arbitrary wildcard~value if there is more
-        than one \;
-        \nl \ForEach{$D_w \in D \setminus \{ D_v \}$}{
-            \nl $D_w \gets D_w \setminus \{ v' \}$ \label{line:removev} \;
-            \nl \ForEach{$(P,\,T) \in L$}{
-                \nl \If{$v \sim_P w$}{
-                    \nl $D_w \gets D_w \cap \left(\N_T(v') \cup \textnormal{wildcards}\right)$
-                }
-            }
-            \nl \lIf{$D_w = \emptyset$}{$\KwSty{return}~\KwSty{false}$}
-        }
-    }
-}
-\bigskip
-\nl $\FuncSty{allDifferent}$ (Domains $D$) $\rightarrow$ Bool \;
-\nl \Begin{
-\nl $(H,\,A,\,n) \gets (\emptyset,\,\emptyset,\,0)$ \;
-\nl \ForEach{$D_v \in D$ \textnormal{from smallest to largest\label{line:eachdomain}}}{
-    \nl $D_v \gets D_v \setminus H$ \label{line:elimhall} \;
-    \nl $(A,\,n) \gets (A \cup D_v,\,n + 1)$ \label{line:acc} \;
-    \nl \lIf{$D_v = \emptyset~\KwSty{or}~\left|A\right| < n$}{$\KwSty{return}~\KwSty{false}$\label{line:failhall}}
-    \nl \lIf{$\left|A\right| = n$}{$(H,\,A,\,n) \gets (H \cup A,\,\emptyset,\,0)$\label{line:hall}}
-}
-\nl $\KwSty{return}~\KwSty{true}$ \;
-}
-\end{minipage}
-\caption{A bit-parallel algorithm for the $k$-less subgraph isomorphism problem.}
-\label{algorithm:sip}
-\end{algorithm*}
-
-\Cref{algorithm:sip} integrates these techniques into a full algorithm. This is derived from an
-algorithm due to \citet{DBLP:conf/cp/McCreeshP15}, which in a recent evaluation of using portfolios
-of subgraph isomorphism algorithms was the single strongest solver \citep{thelionpaper}.
-
-The algorithm performs a constraint-based search. We have a set $D$ containing a variable $D_v$ for
-each vertex $v$ in the pattern graph. Each variable has a domain containing one value for every
-vertex in the target graph. The algorithm is bit-parallel: each $D_v$ is stored using bitset, and
-all graphs are stored as adjacency matrices.
-
-In line~\ref{line:degreefiltering} we use the reasoning from \cref{section:degreefiltering} to
-eliminate infeasible initial values from the domains. We do not use iterated label filtering
-\citep{constraints10} to recalculate neighbourhood degree sequences if any vertices are not present
-in any target domain after construction: preliminary experiments indicated that this happened very
-rarely on our instances.
-
-To handle unmapped vertices, on line~\ref{line:wildcards} we include $k$ additional wildcard $\bot$
-values in each domain (rather than a single value which may be used $k$ times).
-
-We begin by trying to infer domain deletions. The $\FuncSty{propagate}$ function looks for domains
-which contains either only a single value, or only wildcards---we call such a domain
-\emph{effectively-unit}. If such a domain $D_v$ exists, we eliminate its value from every other domain,
-and then propagate adjacency: for each domain corresponding to a vertex adjacent to $v$, we
-eliminate any value from its domain which is not adjacent to $v$ (treating wildcards as being
-adjacent to all vertices). If a domain wipeout occurs, we return failure.
-
-We deal with the additional constraints discussed in \cref{section:pathfiltering} by constructing
-supplemental graphs, as in the \citet{DBLP:conf/cp/McCreeshP15} algorithm. This is done on
-line~\ref{line:supplemental}: the variable $L$ contains a list of pattern / target pairs, and
-following \cref{corollary:supplemental}, we will search for a mapping which is simultaneously a
-subgraph isomorphism between every pair in this list. We also do degree-based reasoning using each
-of these graph pairs.
-
-If no effectively-unit domains remain, we attempt stronger propagation for the all-different
-constraint. Our $\FuncSty{allDifferent}$ function is the bit-parallel propagator taken from
-\citet{DBLP:conf/cp/McCreeshP15}, and is \emph{not} the usual matching-based propagator
-\citep{DBLP:conf/aaai/Regin94} which guarantees generalised arc consistency. Because we use multiple
-wildcard values, we do not need to modify the algorithm to allow a single wildcard value to be used
-more than once. This propagation could create new effectively-unit domains; if so, we repeat the
-process.
-
-If propagation is unable to prove unsatisfiability, we search. We pick the smallest domain
-(line~\ref{line:pickd}) and try giving it each of its remaining values in turn. We use the value the
-ordering heuristic from the original algorithm; wildcards are treated as having degree zero, in an
-attempt to maximising the expected number of solutions remaining during search
-\citep{DBLP:conf/ijcai/McCreeshPT16}.  We introduce a symmetry break (line~\ref{line:sym}) to try
-only a single wildcard value for each variable.
-
-To handle the induced case, we make use of \cref{prop:comp} (line~\ref{line:comp}). We also tested
-using path reasoning on complement graphs, but this is expensive to calculate and provides little
-benefit in practice on the instances we considered.  We also do not strip isolated vertices as the
-original algorithm did, as this is not a valid simplification in the induced case, and we do not use
-conflict-directed backjumping as in our experiments it had very little effect for $k > 0$.
-
-\section{Empirical Evaluation}\label{section:evaluation}
-
-\begin{figure*}[tb]
-    \centering
-    \includegraphics*{gen-graph-runtimes.pdf}
-    \caption{In the first two plots we show the cumulative number of instances solved over time, for the
-        induced and non-induced problems, with different values of $k$. We also show the results of
-        iteratively increasing $k$ until a solution is found, and in the induced case, the
-        performance of two leading maximum common subgraph algorithms. In the third plot we show results
-        comparing iteratively increasing $k$ with our algorithm to other approaches on maximum
-        common induced subgraph instances.}\label{figure:runtimes}
-\end{figure*}
-
-\begin{figure}[ht!] % This is necessary to avoid really awful figure placement midway through the
-    % references...
-    \centering
-    \includegraphics*{gen-graph-which-k-by-family.pdf}
-    \caption{The proportion of instances, in different families, which become satisfiable for
-    increasing values of $k$. The ``larger'' instances are those where we can prove unsatisfiability for
-    $k = 5$, whilst the gap between the top of the bar and the top of the graph is the fraction of
-    instances where a timeout was reached for at least one value of $k$.}\label{figure:which-k}
-\end{figure}
-
-We now evaluate our algorithm and show that it is effective in practice, even on the larger subgraph
-isomorphism instances. In the first two plots of \cref{figure:runtimes} we give cumulative
-distributions for the induced and non-induced problems, with $k$ ranging from $0$ to $5$ (we discuss
-the dotted lines in this plot in \cref{section:topdown}). The results are strong: with $k = 0$ we
-may solve nearly every instance, whilst even at $k = 5$ we can solve over $4,000$ instances in both
-variants.
-
-But are we learning anything about the results---that is, are there instances for which $k = 0$ is
-unsatisfiable, but that are satisfiable for small $k$? For the problem families which do not consist
-entirely of satisfiable instances, we plot this in \cref{figure:which-k}. In the ``phase'' family,
-which consists of instances crafted to be extremely difficult to solve, we are not able to answer
-this question, and in the ``scalefree'' family we see no satisfiable instances with low but not zero
-$k$ (this is simply due to there being many vertices with loops in some pattern graphs, but no loops
-at all in the targets). However, in several of the remaining families we can more than double the
-number of instances for which exact solutions are known, and gain upper bounds on many more. This is
-particularly interesting for the ``images-CVIU11'' family due to \citet{cviu11}, where the size of
-the solution has a direct real-world interpretation in terms of closeness of image matching.
-
-\subsection{Solving From the Top Down}\label{section:topdown}
-
-What would happen if we used our approach to solve the maximum common induced problem? We could
-simply start at $k = 0$, and increase $k$ until a solution is found. This would be tackling the
-problem in the opposite direction from existing approaches, which work by attempting to construct
-larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: ``$k
-\downarrow$'' is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed by
-\citet{DBLP:conf/cp/McCreeshNPS16}.  Recalling the disclaimer in \cref{section:setup}
-regarding instances not fitting in the 64GBytes of RAM we have available, we see that our approach is
-able to close over twice as many of these instances as the previous state of the art. (The same
-conclusion holds even if every instance which is satisfiable with $k = 0$ is removed from the
-dataset.)
-
-What about if we use instances designed for the maximum common subgraph problem? In the third plot
-in \cref{figure:runtimes} we again compare these approaches, but using the first ten instances from
-each family of a standard benchmark set
-\citep{DBLP:journals/prl/SantoFSV03,DBLP:journals/jgaa/ConteFV07}, selecting undirected, unlabelled
-graphs with up to 50 vertices---this gives us a total of 4,110 instances. In these instances the
-number of vertices in the pattern and target graphs is the same, which is not ideal for our
-algorithm (although our invariants are still effective in many cases). Nonetheless, we are by a
-small margin the single strongest solver. Interestingly, our algorithm tends to have complementary
-performance to the clique approach, which suggests that there is scope for an algorithm which runs
-both an upper bound and a constructive, lower bound approach simultaneously or in parallel, stopping
-when the two bounds meet in the middle.
-
-\section{Conclusion}
-
-By considering a restricted variation of the problem, we have been able to go some of the way
-towards tackling the maximum common subgraph problem on much larger graphs than have previously been
-possible. We saw that some invariants from the subgraph isomorphism problem can still be used,
-albeit in a weakened form, with considerable effect when a small number of vertices can be removed.
-We have by no means cracked the problem completely---our results are still far from where we
-would like them to be for use in real-world applications, and many instances remain open. However,
-for many of the open instances we are at least able to get upper bounds on the result for the
-first time.
-
-In future work, we will combine this approach with existing lower bounding construction methods, to
-deliver a hybrid algorithm. We also intend to allow restrictions on which vertices may or may not be
-removed, similar to the approach of \citet{DBLP:conf/cp/ZampelliDD05}, but with much stronger
-filtering now being possible.
-
-\section*{Acknowledgements}
-
-We would like to thank Frances Cooper for her comments.
-
-\bibliographystyle{aaai}
-\bibliography{paper}
+    \end{frame}
 

### 2017-01-31 poster/poster.tex
initial redraft - text cut, figures improved

@@
 The \textbf{non-induced subgraph isomorphism problem} is to find an injective mapping from a given
-pattern graph to a given target graph which preserves adjacency---in essence, we are ``finding a
-copy of'' the pattern inside the target.
+pattern graph to a given target graph which preserves adjacency.
 
@@
 vertices} in the target graph, leading to successful application in areas such as \textbf{computer
-vision}, \textbf{biochemistry}, and \textbf{pattern recognition}.
+vision}, \textbf{malware detection}, \textbf{compilers}, \textbf{model checking}, \textbf{biochemistry}, and \textbf{pattern recognition}.
 }
@@
 distances or paths between them, is possible with subgraph isomorphism,
-but not maximum common subgraph, and so the
-state space in the former is much more restricted, whilst filtering
-during search is vastly stronger.}
+but not maximum common subgraph.}
 
@@
 If $k$ is reasonably small, weakened forms of invariants from subgraph isomorphism (based on vertex degrees and paths) are still effective at reducing the search space.
-In the example it is clear that the pattern graph is not isomorphism to a subgraph of the target, but upon removal of the central vertex we have a $1$-less isomorphism from the pattern to the target.
+In the example, upon removal of the central vertex from the pattern, we have a $1$-less isomorphism from the pattern to the target.
 
@@
 
-Are there instances for which k = 0 is unsatisfiable, but that
-are satisfiable for small k? For the problem families which
+Are there instances for which $k = 0$ is unsatisfiable, but that
+are satisfiable for small $k$? For the problem families which
 do not consist entirely of satisfiable instances, we plot this for both the induced and non-induced variants.
@@
 to answer this question, and in the ``scalefree'' family we
-see no satisfiable instances with low but not zero k. 
-However, in several of the remaining families our algorithm manages to more than double
-the number of instances for which exact solutions are
-known, and we gain upper bounds on many more. This is particularly
+see no satisfiable instances with low but not zero $k$.
+
+\bigskip
+
+However, in several of the remaining families our algorithm manages to provide exact solutions for many instances. This is particularly
 interesting for the ``images-CVIU11'', where the size of the solution has a
@@
 maximum common induced problem? We could simply start
-at k = 0, and increase k until a solution is found. This \textbf{tackles the problem in the opposite direction from existing
+at $k = 0$, and increase $k$ until a solution is found. This \textbf{tackles the problem in the opposite direction to existing
 approaches}, which work by attempting to construct
@@
 We see that \textbf{our approach is able to close over twice
-as many of these instances as the previous state of the art} --- which struggles due to it's RAM requirements.
-(The same conclusion holds even if every instance which is
-satisfiable with k = 0 is removed from the dataset.)
-On instances designed for the maximum subgraph problem we are still the single strongest solver, and our performace is complementary to that of the clique encoding. 
+as many of these instances as the previous state of the art}---which struggles due to its RAM requirements.
+On instances designed for the maximum subgraph problem we are still the \newline single strongest solver.
 }
@@
 
-\block{See the Paper For\ldots}{
+\block{See the Paper for\ldots}{
     \begin{itemize}
         \item ~ Description of our new invariants, and proofs that they hold. 
-        \item ~ Description of the algorithm the algorithm.
+        \item ~ Description of the algorithm.
     \end{itemize}
@@
         This work was supported by the Engineering and Physical Sciences Research Council [grant
-        numbers EP/K503058/1 and EP/M506539/1]. \hfill \texttt{\textcolor{white}{c.mccreesh.1@research.gla.ac.uk}}
+        numbers EP/K503058/1 and EP/M506539/1]. \hfill \texttt{\textcolor{white}{c.reilly.2@research.gla.ac.uk}}
     }

### 2017-01-31 poster/poster.tex
applications block, better key, graph font and space fixes

@@
 
+}
+
+\block{Applications}{
 Despite these problems being \NP-complete, modern practical subgraph isomorphism algorithms can
@@
 }
-
-\vspace*{3cm}
+%\vspace*{3cm}
 
 \block{Maximum Common Subgraph (Comparing Graphs)}{
-\begin{wrapfigure}[11]{r}{0.46\linewidth}
+\begin{wrapfigure}[6]{r}{0.46\linewidth}
     \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
@@
 
-   \end{tikzpicture}\end{center}
-
-    \vspace*{1.5cm}
-
-    \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
-         \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N1) at (0,  0) {\vphantom{0}};
-        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N2) at (0,  -4) {\vphantom{0}};
-        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N3) at (2, -2) {\vphantom{0}};
-        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N4) at (4, 0) {\vphantom{0}};
-        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N5) at (4, -4) {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N1) at (4,  0) {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N2) at (4,  -4) {\vphantom{0}};
+        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N3) at (6, -2) {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N4) at (8, 0) {\vphantom{0}};
+        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N5) at (8, -4) {\vphantom{0}};
 
@@
 
-\block{$k$-less Subgraph Isomorphism (Finding Most of a Pattern)}{
+\block{$k$-less Subgraph Isomorphism (Most of a Pattern)}{
 

### 2017-01-31 poster/poster.tex
Better hyphening

@@
 
-Given two graphs $G$ and $H$, the \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to
-a subgraph of both $G$ and $H$ --- the size of the maximum common subgraph gives us a measure of how similar two graphs are.
+The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to
+a subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.
 

### 2017-02-01 poster/poster.tex
heading size, vspace round figure

@@
 
-\renewcommand{\Huge}{\fontsize{77.2}{96}\selectfont}
+\renewcommand{\Huge}{\fontsize{96}{124}\selectfont}
 
@@
 }
+
+\bigskip
 
@@
 
-The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to
-a subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.
+The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to  subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.
 
@@
 do not consist entirely of satisfiable instances, we plot this for both the induced and non-induced variants.
-
+\vspace*{1.48cm}
 \bigskip
-
 \begin{center}
@@
 \end{center}
-
 \bigskip
-
+\vspace*{1.46cm}
 In the ``phase'' family, which consists of instances
@@
 
-\begin{wrapfigure}[11]{r}{0.66\linewidth}
+\begin{wrapfigure}[13]{r}{0.66\linewidth}
 \begin{center}
@@
 as many of these instances as the previous state of the art}---which struggles due to its RAM requirements.
-On instances designed for the maximum subgraph problem we are still the \newline single strongest solver.
+On instances designed for the maximum subgraph problem we are still the single strongest solvers, and our performance tends to be complementary to that of the clique encoding.
 }
@@
 \block{Future Work}{
-    \begin{itemize}
-        \item ~ Develop an algorithm for maximum common subgraph which makes use of an upper bound from our approach and a lower bound from the clique approach, stopping when the bounds converge.
-    \end{itemize}
+Develop an algorithm for maximum common subgraph which makes use of an upper bound from our approach and a lower bound from the clique approach, stopping when the bounds converge.
 }
@@
     \colorlet{blocktitlebgcolor}{uofgsandstone!80!white}
-    \block[bodyverticalshift=-0.5cm]{}{
+    \block[bodyverticalshift=1.2cm]{}{
         This work was supported by the Engineering and Physical Sciences Research Council [grant

### 2017-02-01 poster/poster.tex

@@
 
-The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to  subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.
+The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to
+a subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.
 
